### 2019-04-19 Manuscript Tex file/Texfile/Table1.tex
Init Commit

\begin{center}
\begin{table}[]
\begin{tabular}{lllll}
Pair & Weight & Community & Title                                                                                         &                                                             \\
1    & 6.03                      & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       &                                                             \\
     &                           & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                         &                                                             \\
2    & 3.08                      & MulT      & Innovated higher criticism for detecting sparse signals in correlated noise                   &                                                             \\
     &                           & VarSel    & Regularized estimation of large covariance matrices                                           &                                                             \\
3    & 2.47                      & DimRed    & Contour projected DimRed                                                                      &                                                             \\
     &                           & VarSel    & Factor profiled sure independence screening                                                   &                                                             \\
4    & 2.15                      & VarSel    & Factor profiled sure independence screening                                                   &                                                             \\
     &                           & DimRed    & Sliced regression for DimRed                                                                  &                                                             \\
5    & 1.86                      & VarSel    & Covariance regularization by thresholding                                                     &                                                             \\
     &                           & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          &                                                             \\
6    & 1.77                      & VarSel    & Asymptotic properties of bridge estimators in sparse high-dimensional regression models       &                                                             \\
     &                           & Mixed     & "Marginal asymptotics for the $''$large P                                                     & small n$''$ paradigm: with applications to microarray data" \\
7    & 1.71                      & VarSel    & A majorization-minimization approach to VarSel using spike and slab priors                    &                                                             \\
     &                           & Mixed     & Empirical \{B\}ayes selection of wavelet thresholds                                           &                                                             \\
8    & 1.66                      & VarSel    & Spades and mixture models                                                                     &                                                             \\
     &                           & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          &                                                             \\
9    & 1.61                      & DimRed    & A constructive approach to the estimation of DimRed directions                                &                                                             \\
     &                           & VarSel    & Factor profiled sure independence screening                                                   &                                                             \\
10   & 1.54                      & VarSel    & A majorization-minimization approach to VarSel using spike and slab priors                    &                                                             \\
     &                           & Mixed     & Spike and slab VarSel: frequentist and \{B\}ayesian strategies                                &                                                             \\
11   & 1.53                      & VarSel    & VarSel in nonparametric additive models                                                       &                                                             \\
     &                           & Mixed     & Nonparametric estimation of an additive model with a link function                            &                                                             \\
12   & 1.39                      & Mixed     & Nonparametric inferences for additive models                                                  &                                                             \\
     &                           & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models         &                                                             \\
13   & 1.29                      & Mixed     & Bayesian VarSel in structured high-dimensional covariate spaces with applications in genomics &                                                             \\
     &                           & VarSel    & Model selection and estimation in regression with grouped variables                           &                                                             \\
14   & 1.20                      & VarSel    & The sparsity and bias of the \{LASSO\} selection in high-dimensional linear regression        &                                                             \\
     &                           & Mixed     & Tests for high-dimensional covariance matrices                                                &                                                             \\
15   & 1.19                      & FuncAn    & Empirical dynamics for longitudinal data                                                      &                                                             \\
     &                           & Mixed     & VarSel in nonparametric varying-coefficient models for analysis of repeated measurements      &                                                            
\end{tabular}
\end{table}
\end{center}

### 2019-04-19 Manuscript Tex file/Texfile/manuscript.tex
Init Commit

\documentclass{article}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage[nottoc]{tocbibind}
\usepackage[nohead, nomarginpar, margin=1in, foot=.25in]{geometry}
\usepackage{mathtools}
\usepackage{bbm}

\usepackage{amsmath}
\usepackage{lscape} 
\usepackage{graphicx}
\graphicspath{ {./images/} }

%\usepackage{nips10submit_e}
\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
%\usepackage{epstopdf}
\usepackage{natbib}
%\usepackage{mathbbold}
\usepackage{bm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{array}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{property}[theorem]{Property}
\newtheorem{result}[theorem]{Result}
\newtheorem{example}[theorem]{Example}

\newtheorem*{remark*}{Remark}
\DeclareGraphicsExtensions{.eps}

\renewcommand{\baselinestretch}{1} % 2.0 or 3.0 would do.
\renewcommand*\labelenumi{(\theenumi)}
\renewcommand\theequation{\arabic{section}.\arabic{equation}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[linesnumbered,ruled]{algorithm2e}
\RestyleAlgo{boxruled}

\topmargin 0pt \advance \topmargin by -\headheight \advance \topmargin by
-\headsep \textheight 8.9in \oddsidemargin 0pt \evensidemargin
\oddsidemargin \marginparwidth 0.5in \textwidth 6.5in

\begin{document}
\bibliographystyle{plainnat}
\bibliography{name-of-your-bib-file-here}

\title{Factor Analysis on Report Citations, Using a Combined Latent and logistic Model}
\author{Namjoon Suh, Xiaoming Huo, Eric Heim, Timothy Van Slyke, and Lee Seversky}

\date{\today}
\maketitle

\begin{abstract}
% To be added later...
We propose a combined latent and logistic model for the citation network, where either a latent model or a logistic model alone is often insufficient to capture the structure of the data.
The proposed model has a latent (i.e., factor analysis) model to represents the main technological trends (aka factors), and adds a sparse logistic component that captures the remaining ad hoc dependence. Parameter estimation are carried out through construction of a joint-likelihood function of edges and properly chosen penalty terms. The convexity of the likelihood function allows us to develop an efficient algorithm, while the penalty terms generate a low-dimensional latent component and a sparse graphical structure. Simulation results are reported that show the new method works well in practical situations. The proposed method has been applied to a real application in citation network of statistician data set (Ji and Jin).
\end{abstract}

\noindent{\sc KEY WORDS}: citation network, matrix decomposition, latent variable model,  logistic model, convex optimization

\section{Introduction}\label{sec:intro}
We study a citation network, where each node (i.e., item) can be a technical report or a publication. A node may cite another node. Associated with a pair of nodes $i$ and $j$, we denote a binary random variable $X_{ij}$, where $1 \le i,j \le n$ and $n$ is the total number of nodes. We have $X_{ij}=1$ if and only if either node $i$ cites node $j$ or vice versa; otherwise $X_{ij}=0$. For each node $i$, we assume that there is an associated binary vector $f_{i} \in \mathbb{R}^K$, such that the $k$th entry of $f_{i}$, $f_{ik} = 1$, if and only if node $i$ is related to topic (i.e., factor) $k, 1\le k \le K$. Here $K$ is the total number of underlying topics (i.e., factors, or trends). We assume a logistic model for $X_{ij}$'s: for $1\le i,j \le n$,

\begin{equation} 
\label{eq:logistic01}
\mathbb{P}(X_{ij}=1) = \frac{e^{\alpha + f_i^T D f_j }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
here $\alpha \in \mathbb{R}$ is a parameter and matrix $D \in \mathbb{R}^{K \times K}$ is a diagonal matrix: $D = \mbox{diag}\{d_{1},d_{2},\ldots,d_{K}\}$. We assume $d_{ii} > 0$ for $1 \le i \le K$.
Another way to put \eqref{eq:logistic01} is
\begin{equation}
\label{eq:logistic02}
\mathbb{P}(X_{ij}=1) = \frac{\exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}}{1 + \exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}},
\end{equation}
A justification of the above model is that when both node $i$ and node $j$ are related to topic $k$, they have a higher chance to cite one way or the other. We have assumed a common strengthen coefficient $d_k$ ($1\le k \le K$) for factor $k$, despite different nodes. We denote a matrix $F = \{f_1, f_2, \ldots, f_n\} \in \mathbb{R}^{K \times n}$. Each column $i$ in matrix $F$ contains the factor loadings associated with the node $i$ ($1\le i \le n$). Given the diagonal matrix $D$ and the factor loading matrix $F$, we assume that $X_{ij}$'s are independent; therefore we have the total conditional probability function as follows: 
\begin{equation}
\label{eq:logistic03}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \prod_{1\le i<j \le n} \mathbb{P}(X_{ij})
= \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha + f_i^T D f_j) }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\mathbb{P}(X_{ij})$ is given in \eqref{eq:logistic02}.
The last equation holds because $X_{ij}$ only takes binary (i.e., $0$ or $1$) values.
Recall that the dot product of two matrices with same dimensionality, $A,B\in \mathbb{R}^{a \times b}$, is defined as $A\bullet B=\mbox{trace}(A^T B) = \sum_{i=1}^a\sum_{j=1}^b a_{ij}b_{ij}$.
The above \eqref{eq:logistic03} can be further rewritten as
\begin{equation}
\label{eq:logistic04}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{f_i^T D f_j }},
\end{equation}
where we assume $X_{ii}=0$ for all $i$ ($1\le i \le n$) and $X_{ij} = X_{ji}$ for all $i$ and $j$ ($1\le i,j \le n$), i.e., the matrix $X$ is symmetric.
The above delivers a factor analysis model. Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g., \cite{joreskog1969general,mcdonald1985factor, harman1976modern,rasch1960probabilistic,lord1968statistical,karl1973general}).

Our work is inspired from Fused Latent and Graphical (FLaG) model (Chen et al, 2016). They assume that majority of variation of responses can be accounted by low dimensional latent vector, and remaining dependent structure of responses can be explained by sparse graphical structure. Thus, the resulting model contains a low-dimensional latent vector and a sparse conditional graph. Their key idea is to separate these two dependent structures so that they can facilitate the statistical inference. Our model also assumes that there exist two dependent structures among citation edges in network. A low-dimensional version of the aforementioned latent vector model is largely correct and majority of the citations among the nodes are induced by these common latent vectors $f_{i}$'s (with weigh coefficients $d_{i}$'s). There is still a small remainder due to the graphical component.

Though it may seem similar to Chen et al, we work on a different model formulation in several aspects. First, FLaG is built to analyze the Eysenck’s Personality Questionnaire that consists of items designed to measure Psychoticism, Extraversion, and Neuroticism. So there are $p$ questions that need to be answered, and each questions fall into above three categories. If there are n respondents to questions, we have n independent data generated from same distribution. In our case, the observed citation network can be thought of as one realization of random graph. Second, FLaG set a collection of binary responses for each individual questions follow a joint distribution which is a combination of Item Response Theory (IRT) model and Ising model, whereas we model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of Latent Factor Analysis model and logistic model. Last but not least, FLaG approximate the original likelihood through constructing pseudo-likelihood function by taking advantage of conditional independence among the nodes, but our model’s likelihood function is directly accessible due to the conditional independence among edges given parameters.

The proposed modeling framework is also related with the analysis of decomposing a matrix into low-rank and sparse components and the statistical inference of a multivariate Gaussian model whose precision matrix admits the form of a low-rank matrix plus a sparse matrix (Chandrasekaran et al, 2012). However, the inference and optimization of the current model are different from those cases. We will construct a regularized-likelihood function, based on which estimator will be proposed for simultaneous model selection and parameter estimation. The optimization for the regularized estimator will be convex, for which we will develop an efficient algorithm through the alternating direction method of multiplier (Boyd et al, 2011).

The rest of the paper is organized as follows. In section 2 we will give a presentation on how to build a model which can encode both latent dependent structure due to the common topics and remaining ad-hoc dependent structure. In section 3, we will talk about assumptions in our model and penalization on likelihood function constructed in section 2. Section 4 gives the detailed procedure on how to compute the estimator of the optimization problem in Section 3. In Section 5, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians. We finally conclude this work in section 6 with several open questions remain to be solved and some directions for future research.

\section{Model Formulation}
\label{sec:model-form}

Recall the following graphical model that was established in \eqref{eq:logistic04}, which is essentially a factor model (latent variable model):
$$
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{f_i^T D f_j }},
$$
where
$X_{ij}, 1\le i,j \le n$, are binary random variables indicating either node $i$ cites node $j$ or vice versa,
matrix $X = \{X_{ij}\} \in \mathbb{R}^{n \times n}$ is symmetric with diagonal entries all being equal to zero,
factor loading matrix $F = [f_1,f_2,\ldots,f_n]\in \mathbb{R}^{K\times n}$ records the relation between nodes and underlying topics, $F^T$ is the transpose of $F$,
and matrix $D \in \mathbb{R}^{K \times K}$  is diagonal with entries being the weight coefficients of factors.

The above specifies a latent model (or equivalently a factor model).
We now describe a graphical model in the following.
The graphical model will complement the latent model by characterizing links that are not interpretable via common factors.
For the aforementioned binary random variable $X_{ij}$, $1\le i,j \le n$, we define
\begin{equation}
\label{eq:logistic05}
\mathbb{P}(X_{ij}=1) = \frac{e^{\alpha' + S_{ij} }}{1 + e^{\alpha' + S_{ij} }},
\end{equation}
where $S_{ij} \in \mathbb{R}$, for $1\le i,j \le n$, denotes the relation between nodes $i$ and $j$.
If we have $S_{ij}=0$, then it is less likely to have a citational relationship between nodes $i$ and $j$.
On the other hand, if $S_{ij}>0$, then it is more likely to have a citation link between nodes $i$ and $j$.
Here parameter $\alpha' \in \mathbb{R}$ plays the same role as parameter $\alpha$ does in model \eqref{eq:logistic01}.
Denote the matrix $S = \{S_{ij}, 1\le i,j \le n \} \in \mathbb{R}^{n \times n}$.
Assume that given the matrix $S$, the binary random variables
$X_{ij}$'s are independent;
consequently, we have the total conditional probability function as follows:
\begin{eqnarray}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
&=& \prod_{1\le i<j \le n} \mathbb{P}(X_{ij}) \nonumber \\
&=& \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha' + S_{ij}) }}{1 + e^{\alpha' + S_{ij} }} \nonumber \\
&=& \frac{\exp(\alpha' \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet S)}{\prod_{1\le i<j \le n}  1 + e^{\alpha' + S_{ij} }}.
\label{eq:logistic06}
\end{eqnarray}
Recall that we have assumed that $X_{ii}=0$ for all $i$ ($1\le i \le n$) and $X_{ij} = X_{ji}$ for all $i$ and $j$ ($1\le i,j \le n$), i.e., the matrix $X$ is symmetric.
In the combined model, we integrate \eqref{eq:logistic04} and
\eqref{eq:logistic06} to render the joint conditional probability function as follows:
\begin{eqnarray}
\label{eq:logistic07}
\mathbb{P}(X \mid \alpha,  F, D, S)
&=&  \prod_{1\le i<j \le n}
\frac{e^{X_{ij}(\alpha + S_{ij} + f_i^T D f_j) }}{1 + e^{\alpha + S_{ij}+ f_i^T D f_j}} \nonumber \\
&=& \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F) +\frac{1}{2} X \bullet S\right)}{\prod_{1\le i<j \le n}  \left(1 + e^{\alpha + f_i^T D f_j +S_{ij}}\right) }.
\end{eqnarray}

\section{Estimation}
\label{sec:estimate}

Note that in the model \eqref{eq:logistic07}, the log-likelihood function has the form as follows:
\begin{eqnarray}
\label{eq:logistic08}
\mathbb{L}(\alpha,  F, D, S; X)
&=& \alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F) +\frac{1}{2} X \bullet S \\
&& -\sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + f_i^T D f_j +S_{ij} }\right). \nonumber
\end{eqnarray}

If we consider maximizing the above log-likelihood function,
we will encounter several technical issues which are described below.
\begin{enumerate}
\item We would like the matrix $S \in \mathbb{R}^{n \times n}$ to have as many zero entries as possible; i.e., matrix $S$ is {\it sparse.}

\item There is an identifiability issue with the formation $F^T D F$.
More specifically, let $P \in \mathbb{R}^{K \times K}$ be a signed permutation matrix, then we have $P^T P = I_n$, where $I_n \in \mathbb{R}^{K \times K}$ is the identity matrix.
Notice that matrix $F' = PF$ is also a factor loading matrix, and
matrix $D' = P D P^T$ is still a diagonal matrix;
we have
$$
F^T D F = F^T P^T P D P^T P F = (F')^T D' F',
$$
i.e., the choice of $F$ and $D$ is not unique.

\item We would like the number of nonzeros in each column of $F$ to be small, reflecting that each node is associated with a small number of underlying topics.

\item Overall, the rank of matrix $F^T D F$ cannot be larger than $\min\{n,K\}$.
With the application that we have in mind, in this paper, we assume that $K$ is much smaller than $n$.

\end{enumerate}

Directly maximizing the objective function in \eqref{eq:logistic08} is not going to be an easy task.
Following the approaches that were mentioned in Introduction, we propose to relax $F^T D F$ to $L$, where $L$ is a low rank matrix.
Consequently, the log-likelihood function in \eqref{eq:logistic08} can be rewritten as
\begin{eqnarray}
\label{eq:logistic09}
\mathbb{L}_n(\alpha,  L, S; X)
&=& \alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet L +\frac{1}{2} X \bullet S \\
&& -\sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + L_{ij} +S_{ij}}\right). \nonumber
\end{eqnarray}

We propose a penalize likelihood estimation approach as follows:
\begin{eqnarray}
\label{eq:logistic10}
(\hat{\alpha}, \hat{L}, \hat{S})
= \mbox{arg min}_{\alpha, L, S} \left\{
-\frac{1}{n} \mathbb{L}_n(\alpha,  L, S; X) + \gamma \|S\|_1
+ \delta \|L\|_\ast\right\},
\end{eqnarray}
where $\gamma>0$ and $\delta>0$ are algorithmic parameters whose values will be discussed later,
the $L_1$ norm of matrix $S$ is defined as $\|S\|_1 = \sum_{i\neq j} S_{ij}$ (Note that we do not penalize the diagonal entries of $S$), and nuclear norm of matrix $L$ is defined as $\|L\|_\ast = {\mbox{trace}\sqrt{(L^T L)}}$. Recall that both $S$ and $L$ are symmetric matrices. The entries of matrix $S$ can either be positive or negative. Note that we have imposed the diagonal entries of the matrix $X$ to be zeros. Given that $L = F^T D F$ where matrix $D$ is diagonal with nonnegative diagonal entries, it is easy to see that matrix $L$ is positive semidefinite; which consequently leads to $\|L\|_\ast = \mbox{trace}(L)$, which is a linear functional to the matrix $L$.
The nuclear norm of $L$ penalizes the number of nonzero eigenvalues of $L$, which is the same as the rank
of $L$.
The regularization based on the nuclear norm was proposed in \cite{fazel2001rank}
and its statistical properties are studied in \cite{bach2008consistency}.

After we have obtained $\hat{S}$ in \eqref{eq:logistic10}, we can uncover the graphical model by investigating non-zero entries in $\hat{S}$.
On the other hand when we have calculated $\hat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\hat{L} = F^T D F.$
This is the price we have to pay for an amenable computational problem. The rank of estimated $\hat{L}$ will be our estimate of the number of factors (i.e., underlying common topics). For the issue on assigning the community membership of each node $i$, we will discuss this later in Section 6.

\section{ Some additional assumptions }
We are interested in verifying following optimization problem has an unique solution.

\begin{align*}
\min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
-\frac{1}{n} \log \prod_{1\le i< j\le n}\frac{exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
\end{align*}

\noindent In our problem, we are mainly interested in separating the main stream dependent structure from ad-hoc dependent structure. From the construction of our problem, $L_{ij} = F^T_{i}DF_{j}$, which encodes the positive weight when the $i$th paper and $j$th paper share $K$ common topics, and zero weight when two paper share no common topics, is always greater than or equal to zero. And $S_{ij}$, which encodes the ad-hoc dependent structure that cannot be explained by main dependent structure (induced from commonly shared topics between papers), is always greater than or equal to zero, $S_{ij} \geq 0$. Through this construction we should note that where $S_{ij}\neq0$, $L_{ij}$ should be equal to 0, and vice versa, where $L_{ij}\neq0$, $S_{ij}=0$. By incorporating these conditions, we can add following constraints to our optimization problem stated above: $L\geq 0$, $S \geq 0$, $L_{ij}*S_{ij}=0, {1\le i< j\le n}$. \\

\noindent Denote $L^*$ and $S^*$ as ground truth parameter and let $\theta^*_{ij}=\alpha+L^*_{ij}+S^*_{ij}$, $N=n(n-1)/2$. We can easily check the above logistic likelihood function's Hessian matrix is $N \times N$ diagonal matrix with each entries, $\frac{1}{n}\frac{\exp(\theta^*_{ij})}{(1+\exp(\theta^*_{ij}))^2}$. This means that our likelihood function is strictly convex in a sense that $H \succ 0$, unless $\min_{1\le i< j\le n}\theta^*_{ij}$ tends to $-\infty$. 
This is automatically guaranteed through the construction of our problem, $S_{ij} \in R, S_{ij} \geq 0$, and $L_{ij} = F^T_{i}DF_{j}$.

Once we have the unique $\Theta^* \in R^{n \times n}$, whose each entries are $\theta^*_{ij}$, we further need to confirm if it has an unique decomposition, $\Theta^*=\alpha+L^*+S^*$.
As mentioned in \cite{candes2011robust}, the decomposition is unique, and problem is well posed, as long as the low-rank matrix is not sparse, and vice versa if the sparse component is not low-rank matrix. Specifically, these conditions are guaranteed if the singular vectors of $L^*$ are not sparse and if the non-vanishing entries of $S^*$ occur at random locations. 
It is a natural question whether we can check this kind of incoherence between $L^*$ and $S^*$ by observing the given network data $X$. Since 
$X$ is a drawn data from the probability density, which is characterized by $\Theta^*$ ; $X\sim{P_{\Theta^*}}$,... (To be worked...)

\section{Computation}
\label{sec:compute}

We propose a method that takes advantage of the special structure
of the $L_1$ and nuclear norms by means of the
alternating direction method of multiplier (ADMM), which is a method
that has recently gained momentum.
An examination of the objective function in \eqref{eq:logistic10} unvails that
terms
\[
\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet L +\frac{1}{2} X \bullet S
\]
are linear in $\alpha,  L$, and $S$.
The term
\[
\sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + L_{ij} +S_{ij}}\right)
\]
is convex with respect to $\alpha,  L$, and $S$.
Functions $\|S\|_1$ and $\|L\|_\ast$ are known to be convex functions.
Therefore, the objective function in \eqref{eq:logistic10} is convex. The above convex optimization problem can be solved via ADMM as follows.

\subsection{ADMM approach}
\label{sec:ADMM}
We give a review of the alternating direction method
of multiplier (ADMM).
Consider two closed convex functions
$$
f : \chi_f \to \mathbb{R} \mbox{ and } g : \chi_g \to \mathbb{R},
$$
where the domain $\chi_f$ and $\chi_g$ of functions $f$ and $g$ are closed convex subsets of $\mathbb{R}^d$, and $\chi_f \bigcap \chi_g$ is nonempty.
Both $f$ and $g$ are possibly non-differentiable.
The alternating direction method
of multiplier is an iterative algorithm that solves the following generic optimization problem:
$$
\min_{x \in \chi_f \bigcap \chi_g} \left\{f(x) + g(x) \right\},
$$
or equivalently
\begin{eqnarray}
\label{eq:admm1}
\min_{x \in \chi_f, z\in \chi_g} & \left\{f(x) + g(z) \right\}, \\
\mbox{ subject to } & x = z. \nonumber
\end{eqnarray}
To describe the algorithm, we will need the following proximal operators
\begin{itemize}
\item $\mathbf{P}_{\lambda,f}: \mathbb{R}^d \to \chi_f$ as
$$
\mathbf{P}_{\lambda,f}(v) = \mbox{arg min}_{x \in \chi_f} \left\{
f(x) + \frac{1}{2\lambda} \|x-v\|^2_2
\right\}
$$

\item and $\mathbf{P}_{\lambda,g}: \mathbb{R}^d \to \chi_g$ as
$$
\mathbf{P}_{\lambda,g}(v) = \mbox{arg min}_{x \in \chi_g} \left\{
g(x) + \frac{1}{2\lambda} \|x-v\|^2_2
\right\},
$$
where $\|\cdot\|_2$ is the usual Euclidean norm on $\mathbb{R}^d$ and $\lambda$ is a scale parameter that is a fixed positive constant.
\end{itemize}
The algorithm starts with some initial values $x^0 \in \chi_f,
z^0 \in \chi_g, u^0 (=\lambda y^0) \in \mathbb{R}^d$.
At the $(m+1)$th iteration, $(x^m, z^m, u^m)$ is updated according to the following steps until convergence
\begin{itemize}
\item Step 1: $x^{m+1} = \mathbf{P}_{\lambda,f}(z^m - u^m)$,

\item Step 2: $z^{m+1} = \mathbf{P}_{\lambda,g}(x^{m+1} + u^m)$,

\item Step 3: $u^{m+1} = u^m + x^{m+1} - z^{m+1}$.

\end{itemize}
The convergence properties of the algorithm are summarized in the following result in \cite{boyd2011distributed}.
Let $p^\ast$ be the minimal value in \eqref{eq:admm1}.

\begin{theorem}[Boyd et al., 2011]
Assume functions $f: \chi_f \to \mathbb{R}$ and
$g: \chi_g \to \mathbb{R}$ are
closed convex functions, whose domains $\chi_f$ and $\chi_g$
are closed convex subsets of $\mathbb{R}^d$ and
$\chi_f \bigcap \chi_g \neq \emptyset$.
Assume the Lagrangian of \eqref{eq:admm1}
$$
L(x,z,y) = f(x) + g(z) + y^T(x-z)
$$
has a saddle point, that is, there exists $(x^\ast, z^\ast, y^\ast)$ (not necessarily unique) that $x^\ast \in \chi_f$ and
$z^\ast \in \chi_g$, for which
$$
L(x^\ast, z^\ast, y) \le L(x^\ast, z^\ast, y^\ast) \le
L(x, z, y^\ast), \qquad \forall x, z, y \in \mathbb{R}^d.
$$
Then the ADMM has the following convergence properties.
\begin{enumerate}
\item Residual convergence. $x^m - z^m \to 0$
as $m \to \infty$; i.e., the iterates approach feasibility.

\item Objective convergence. $f(x^m) + g(z^m) \to p^\ast$ as $m \to \infty$; i.e., the objective function of
the iterates approaches the optimal value.

\item Dual variable convergence. $y^m \to y^\ast$ as $m \to \infty$, where $y^\ast$ is a dual optimal point.

\end{enumerate}
\end{theorem}

Now we see how ADMM can be adopted to solve for our penalized likelihood estimation \eqref{eq:logistic10}.
We reparameterize $M = L + S$ and let $x = (\alpha, M, L, S)$ (viewed as a vector).
We define the following:
\begin{eqnarray*}
\chi_f &=& \{ (\alpha, M, L, S): \alpha\in\mathbb{R}, M, L, S \in \mathbb{R}^{n \times n},
L \mbox{ is positive semidefinite, }
S \mbox{ is symmetricg} \}, \\
f(x) &=&
-\frac{\alpha}{n} \sum_{1\le i< j\le n}X_{ij}
-\frac{1}{2n} X \bullet M %L - \frac{1}{2n} X \bullet S
+ \frac{1}{n}
\sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + M_{ij}}\right)
+ \gamma \|S\|_1
+ \delta \|L\|_\ast, \\
\chi_g &=& \{ (\alpha, M, L, S): \alpha\in\mathbb{R}, M, L, S \in \mathbb{R}^{n \times n},
M \mbox{ is symmetric and } M=L+S \}, \mbox{ and }\\
g(x) &=& 0, \mbox{ for } x \in \chi_g.
\end{eqnarray*}
One can verify that \eqref{eq:logistic10} can be written as
$$
\min_{x \in \chi_f \bigcap \chi_g} \left\{f(x) + g(x) \right\}.
$$

We now present each of the three steps of the ADMM algorithm and show that the proximal
operators $\mathbf{P}_{\lambda,f}$ and $\mathbf{P}_{\lambda,g}$ are easy to evaluate.
Let
$$
x^m = (x^m_\alpha, x^m_M, x^m_L, x^m_S), \quad
z^m = (z^m_\alpha, z^m_M, z^m_L, z^m_S), \quad
u^m = (u^m_\alpha, u^m_M, u^m_L, u^m_S).
$$
Step 1. We solve $x^{m+1} = \mathbf{P}_{\lambda,f}(z^m - u^m)$.
Due to the special structure of $f(\cdot)$,
$x^{m+1}_\alpha, x^{m+1}_M, x^{m+1}_L$, and $x^{m+1}_S$
can be updated separately. More precisely, we have
\begin{eqnarray}
x^{m+1}_\alpha, x^{m+1}_M &=& \mbox{arg min}_{\alpha, M} \quad
-\frac{\alpha}{n} \sum_{1\le i< j\le n}X_{ij}
-\frac{1}{2n} X \bullet M
+ \frac{1}{n} \sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + M_{ij}}\right) \nonumber \\
&& + \frac{1}{2\lambda}\left[\alpha - (z^m_\alpha - u^m_\alpha)\right]^2
+ \frac{1}{2\lambda}\|M - (z^m_M - u^m_M)\|^2_F, \label{eq:admm02} \\
x^{m+1}_L &=& \mbox{arg min}_{ L} \quad \delta \|L\|_\ast
+ \frac{1}{2\lambda}\|L - (z^m_L - u^m_L)\|^2_F,\label{eq:admm03}
\\
&& \mbox{subject to $L$ is positive semidefinite;} \nonumber \\
x^{m+1}_S &=& \mbox{arg min}_{ S} \quad  \gamma \|S\|_1
+ \frac{1}{2\lambda}\|S - (z^m_S - u^m_S)\|^2_F,
\label{eq:admm04}
\\
&& \mbox{subject to $S$ is symmetric,} \nonumber
\end{eqnarray}
where $\|\cdot\|_F$ is the matrix Frobenius norm, defined as
$\|M\|^2_F = \sum_{i,j} m^2_{ij}$ for a matrix $M = (m_{ij})$.
The problem in \eqref{eq:admm02} may not have a closed-form solution. We use a simple gradient descent to solve this step, setting the step size, $\alpha=0.1$ and stopping criteria, $\max(|x_\alpha^{m+1}-x_\alpha^{m}|,\|x_M^{m+1}-x_M^{m}\|_{\infty}) \leq 10^{-9}$. Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem. More specifically, in \eqref{eq:admm03}, suppose the eigenvalue decomposition of the symmetric matrix $(z^m_L - u^m_L)$ can be written as
$$
z^m_L - u^m_L = T \Lambda T^T,
$$
where $T$ is orthogonal ($T T^T = I_n$), then, for $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, we have
$$
x^{m+1}_L = J (T \mbox{diag}(\Lambda-\lambda \delta)_+ T^T)J^{T},
$$
and diag$(\Lambda-\lambda \delta)_+$ is a diagonal matrix with the $j$th
diagonal entry being
$$
(\Lambda_{jj}-\lambda \delta)_+ = \left\{
\begin{array}{ll}
0, & \mbox{ if } \Lambda_{jj} < \lambda \delta \\
\Lambda_{jj}-\lambda \delta, & \mbox{ if } \Lambda_{jj} \ge \lambda \delta .
\end{array}
\right.
$$
In \eqref{eq:admm04}, we have, for $i \neq j$,
\[
S_{ij} = \left\{
\begin{array}{ll}
0, & \mbox{ if } |(z^m_S - u^m_S)_{ij}| < \lambda \gamma  \\
(z^m_S - u^m_S)_{ij}-\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} > \lambda \gamma \\
(z^m_S - u^m_S)_{ij}+\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} <- \lambda \gamma
\end{array}
\right.
\]
\\

\noindent
Step 2. We solve $z^{m+1} = \mathbf{P}_{\lambda,g}(x^{m+1} + u^m)$.
A close-form solution exists here.
Denote
$
\bar{\alpha} = x^{m+1}_\alpha + u^m_\alpha,
\bar{M} = x^{m+1}_M + u^m_M,
\bar{L} = x^{m+1}_L + u^m_L$, and
$\bar{S} = x^{m+1}_S + u^m_S,
$
then evaluating $\mathbf{P}_{\lambda,g}(x^{m+1} + u^m)$ becomes
\begin{eqnarray*}
\min_{\alpha,M,L,S} & \quad
\frac{1}{2}[\alpha - \bar{\alpha}]^2
+ \frac{1}{2}\|M - \bar{M}\|^2_F
+ \frac{1}{2}\|L - \bar{L}\|^2_F
+ \frac{1}{2}\|S - \bar{S}\|^2_F  \\
\mbox{ subject to } & M \mbox{ is symmetric and } M=L+S.
\end{eqnarray*}
The above optimization problem has a close-form solution, which is as follows:
\begin{eqnarray*}
z^{m+1}_\alpha &=& \bar{\alpha}, \\
z^{m+1}_M &=&
\frac{1}{3} \bar{M} + \frac{1}{3} \bar{M}^T + \frac{1}{3} \bar{L} + \frac{1}{3} \bar{S} \\
z^{m+1}_L &=&
\frac{1}{6} \bar{M} + \frac{1}{6} \bar{M}^T + \frac{2}{3} \bar{L} - \frac{1}{3} \bar{S} \\
z^{m+1}_S &=&
\frac{1}{6} \bar{M} + \frac{1}{6} \bar{M}^T - \frac{1}{3} \bar{L} + \frac{2}{3} \bar{S}.
\end{eqnarray*}

\noindent
Step 3. We solve $u^{m+1} = u^m + x^{m+1} - z^{m+1}$, which is a simple arithmetic. \\

The most important implementation details of this algorithm are the choice of $\lambda$ and stopping criterion. In this work, we simply choose $\lambda = 0.5$. We terminate the algorithm  when in $mth$ iteration, $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^-7$.

\section{ Numerical analysis and Applications}
In this section, we have conducted a small empirical study of measuring the performance of our proposed method with artificially specified graphical structures. Also we perform a real data analysis with citation network for statisticians.

\subsection{Synthetic data} 
\textbf{Data Generation} Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P_{ij}=\frac{\exp (
\alpha+F_{i}^{T}DF_{j} +  S_{ij})}{1+\exp(\alpha+F_{i}^{T}DF_{j}+S_{ij})}$. For sparse component $S$, we generate random numbers uniformly distributed over the indices of upper triangular part (off diagonal) of matrix $S$, and make it symmetry. $F^{T}$ binary matrix has $\floor{\frac{n}{K}}$ ones in each columns, and has exactly one 1 in each rows.  
We randomly choose one of rows, fill that row with ones, and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying $I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$. Diagonal elements of $D$ are generated from $unif[7,8]$, and alpha is generated from $unif[-3,-2]$. We set $K=3,4,5$, $n=30,80,120$, and $nnz = 10, 20, 40$, where $nnz$ denotes number of non-zero component of upper-triangular part of S.\\

\noindent \textbf{Choosing tuning parameter}
We have to admit the fact that choosing good tuning parameter is an important but challenging issue in our problem. 
In our problem where the observation can be seen as one realization of random graph, it is confusing whether to define the total number of observations as $N=\frac{n(n-1)}{2}$ or 1, since in usual BIC definition, we define effective sample size "n", when we have n i.i.d. observations. Our experience shows that both BIC and AIC tend to choose the model with smallest K and no ad-hoc dependency. As an alternative, we choose a purely heuristic approach. Following the Ji and Jin[], we plot the largest 20 eigenvalues of adjacency matrix X, which can tell us the numbers of communities embedded in network. Then, we record the rank of L and number of non-zero elements in S for each tuning parameter pair on grid, and choose proper pair of tuning parameters which can give us interesting interpretation of data. \\

\begin{figure}[!h]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{\it After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\hat{L}$ matrix. (Different color represents different clusters of nodes $k$-means assign for three synthetic settings.) }
\label{fig:figure1}
\end{figure}

\noindent \textbf{Community memberships of each nodes} Given a network data, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$. We applied a simple $k$-means clustering on the fitted $L$ matrix's first $K$ eigenvectors. Furthermore, we find one interesting phenomenon. Coordinates of each rows from first two eigenvectors of estimated $\hat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well. Our experience shows that with only first two eigenvectors of $\hat{L}$, we can also cluster the nodes comparably well. \\

\noindent \textbf{Ad-hoc links} Ad-hoc links of synthetic network data can be thought of as $"$across edges$"$ between clusters of nodes. Since indices of non-zero entries of $S$ are randomly chosen, there might be some indices of non-zero $S_{ij}$ entries where $L_{ij}$ is also non-zero. In this case, this makes the edges indistinguishable if they come from $S_{ij}$ or $L_{ij}$. Some of "across

\begin{figure}[!h]
\begin{center}
\includegraphics[scale=0.75]{Fig2.pdf}
\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\hat{S}$ matrix. For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
\end{center}
\label{fig:figure2}
\end{figure}

\noindent edges" are also attributed to $\alpha$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha$ or $S_{ij}$. So the total number of across edges might not be exactly same as we set in our data generation setting. \\

\noindent \textbf{Simulation Results} Our goal in this simulation experiment is to check if our model can cluster each nodes into correct communities. Also to see if it can separate the ad-hoc links from edges which come from common topics. Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$ respectively, give us the desirable results for 3 cases. Note that different dynamics of network requires different choices of tuning parameters even the synthetic setting is same, since we are generating the random graph. However, we set the seeds in our simulation so that the results are reproducible. $Fig1$ shows us the result of clustered nodes using $k$-means algorithm on first $K(=rank(\hat{L}))$ eigenvectors. We plot the rows of first two eigenvectors on plane since it tends to visualize well the clustering behavior of nodes. Our model chooses well the ad-hoc links between clusters of nodes as can be verified in $Fig2$. We color the edges in blue whose corresponding elements of estimated $\hat{S}$ are non-zero, and black whose corresponding entries of $\hat{S}$ are zero.

\subsection{Citation and Co-authorship networks for statisticians }
Recently, Ji and Jin [] published an interesting data set on citation  and co-authorship networks of statisticians. Citation relationship over 3000 papers from 4 statistical journals, published between 2003 and 2012, were collected, and collaborative network between authors of papers is given as well. In this section, we analyze these two networks. \\

\noindent\textbf{Citation Network} This dataset is based on all published papers from 2003 to first half of 2012, in 4 of the top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association and Journal of Royal Statistical Society (Series B). Among  3248 papers, we restrict our attention on papers which have greater than or equal to 7 citations from collected papers in original dataset. We have 543 papers in our hands. The elbow points of the scree plot may be at the 3rd, 7th, or 9th largest eigenvalue, suggesting that there might be from 2 to 8 topics in network. In light of this, we performed our analysis under the assumption that there might exist 2 distinct topics and one giant component in which 3 or 4 topics mixed up. \\

\noindent $(\gamma,\delta) = (0.000912,0.0097)$ gives us $\hat{L}$ with rank 3, and $\hat{S}$ with $|supp(\hat{S})|=197$. We apply $k$-means algorithm on 3 eigenvectors of estimated $\hat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\hat{L}$ on plane in $Fig 4$. 404 papers colored in green are densely clustered nearby the origin with a short tail, $(Fig 4)$, and $k$-means classifies these papers as third topic. We list the first two topics discovered through our analysis. (Full lists of papers for each communities are provided in $\it https://sites.google.com/site/namjoonsuh/publications$)

\begin{figure}[!h]
\includegraphics[width=1\textwidth]{Fig4.png}
\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network, Co-authorship network.}
\label{fig:figure1}
\end{figure}

\begin{itemize}
  \item "Variable selection (85 papers)" 
  \item "Multiple Hypothesis Testing (54 papers)"
\end{itemize}

\noindent These two topics are classical research topics in field of statistics. Majority of papers in first community study about "Controlling False Discovery Rate" in various statistical settings. Second group talks about "Variable selection" in high-dimensional data. As expected, third group is quite hard to interpret and seems to have substructures. For further investigation on this group, after obtaining the subnetwork which is comprised only with papers in third group, we performed same analysis once again under the assumption that $K=4$. We obtain four subcommunities as follows:

\begin{itemize}
  \item "Non-parametric Bayesian Statistics (17 papers)"
  \item "Functional Data analysis (35 papers)"
  \item "Dimension Reduction (23 papers)"
  \item "Mixed topics (329 papers)"
\end{itemize}

\noindent Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction". Due to small volume of each communities, we could check that false discoveries for each community are all zero. \\

\noindent Sub-network structure has also a big chunk of papers which we refer to as "Mixed Topics". Not only could we see the papers with topics on "Learning Theory", "Non-parametric/semi-parametric statistics", "Spatial Statistics", "Theoretical Machine Learning", which does not seem to belong to any of five communities listed above, but also we could identify the papers with combinations of two or three topics. Papers like "The Bayesian Lasso (T Park, et al. 2008)", "Coordinate-independent sparse sufficient dimension reduction and variable selection (X Chen, et al. 2010)" are the examples of these papers. It is also interesting to think about a reason on papers which seem to have obvious membership in one of 5 communities other than Mixed topic classified as Mixed topic. For instance, "On the "degrees of freedom" on the LASSO (H Zou, et al. 2007)" is classified as Mixed Topic paper. We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities. Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics. \\

\noindent It is worth to note that our result is consistent with that from Ji and Jin in a sense that they also recover "Multiple Testing", "Variable selection" and "non-parametric Bayesian statistics". This is interesting since even though the dataset we consider is different from theirs, result is consistent. They focus their attentions on analyzing {\it "weakly connected giant component"} for a citation network of each paper's authors ({\it i.e. each node is an author}). We consider the citation network of papers whose node degree is greater than or equal to 7.\\

\noindent\textbf{Ad-hoc links} Non-zero components of $\hat{S}$ capture the citation relationships among papers that are not attributable to the common topics. The model we select has 197 sparse edges (9\% of total edges), and all of them are positive edges. In Table 1, we provide 15 pairs of papers that have the most positive edges. All the 15 edges come from pairs of papers from different communities. For instance, the first pair of papers comes from Functional Analysis $(\it FuncAn)$ community and Variable selection $(\it VarSel)$ community. $\it FuncAn$ paper cites $\it VarSel$ paper for borrowing a mathematical representation to build a theorem. Though it might seem to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic. Second pair comes from $\it MulT$  and $\it VarSel$ community. $\it MulT$ paper briefly mention about $\it VarSel$ paper in future work section, suggesting a possible way of combining their work and work in $\it VarSel$ paper.  And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community. \\

\begin{figure}[!t]
\includegraphics[width=1\textwidth]{Fig3.eps}
\caption{ From left to right: }
\label{fig:figure1}
\end{figure}

\section{Conclusion} 
We propose a new combined latent factor analysis and logistic model. We consider the regularized likelihood by means of $\ell 1$ and nuclear norm penalties. The computation of the regularized estimator is facilitated by developing an algorithm based on the alternating direction method of multiplier to optimize a non-smooth and convex objective function. The proposed method is applied to citation and co-authorship network of statisticians, and the estimated model renders good interpretative power. Specifically, our analysis on statistician's citation network sheds the new light on the interpretation of dataset.

However, there are still several open problems which require us to do more careful analysis. First of all, it remains unclear on how to choose the proper tuning parameters. Classical methods for choosing tuning parameters such as BIC or AIC did not work in our case, since they tend to choose the most parsimonious models. We also do not have systematic ways to do cross validation in network data. Not only because it is computationally expensive procedure, but also because if we partition the network data, we can loose fair amount of information on dependent structures among edges. This problem is also closely related with determining the number of communities in network. In lieu of using BIC or AIC, our analysis is heavily relying on heuristic approach when choosing the tuning parameter, and during this procedure, we use the screeplot for determining number of communities in network. Screeplot approach works usually well, but it does not necessarily always guarantee the correct estimate of number of communities. We need a more reliable and theoretically well understood way to determine $K$.

Secondly, we only consider the undirected case which is somewhat unrealistic assumption in real citation network, in a sense that it is not usual for two papers to cite each other at the same time. Since in our research, we were interested in separating the low rank structure of edges and ad-hoc links in network, we did not take into account the directionalities of edges in our model. However, it would be interesting to think about the way to incorporate the directed network into our matrix decomposition framework.

Last but not least, when we assign the memberships of each nodes, we use $k$-means clustering algorithm. However, $k$-means algorithm turns out that it tends to assign nodes conservatively to each communities. For example, in $Fig 4 (a)$, we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in $Fig 4 (b)$ also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community. This is probably because $k$-means does not allow overlapping membership of each nodes. It would be interesting to see what happens if we apply some clustering methods which allow the overlapped memberships of nodes in network.

\section{On non-asymptotic error bound of the estimator}
Chen et al. (2016) show that their estimator recovers the algebraic structure, that is, the conditional graph structure and the number of latent variables, with probability tending to one. However, their analysis only allows a growing number of sample points whereas they keep the number of variables fixed. Their result thus severs from the tradition to analyze the more challenging high-dimensional setting, where the number of variables is also explicitly tracked. Our analysis will focus on getting a non-asymptotic error bound of estimator in the context of where the sample size is fixed as 1, and the number of variables is growing. (More detailed descriptions on the differences between Chen et al. (2016) and our model in terms of model formulation is given in Introduction section.) We are interested in solving following optimization problem :

\begin{equation}\label{eq:1}
\min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
-\frac{1}{n} \log \prod_{1\le i< j\le n}\frac{exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
\end{equation}

Let ($\hat{\alpha},\hat{L},\hat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process. Let $\hat{\theta},\theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$ and
$\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\hat{\Delta}^{\Theta} = \hat{\Theta}-\Theta^{*}, 
\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
\hat{\Delta}^L = \hat{L}-L^{*},
\hat{\Delta}^S = \hat{L}-S^{*}.$
Throughout the proof, let $P= \Big\{\frac{\exp(\Theta_{ij})}{1+\exp(\Theta_{ij})}\Big\}_{1 \leq i,j \leq n}$. Moreover, for any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1})

\[
h(\Theta) = -\frac{1}{n}\sum_{i<j} \Big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \Big\}
\]

Observe that 
$\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$
is an optimal solution to (\ref{eq:1}), and that the ground truth parameter
$\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$ is feasible. Thus, we have the following basic inequality

\begin{equation}\label{eq:2}
    h(\hat{\Theta})-h(\Theta^{*}) 
    + \delta \|\hat{L}\|_\ast + \gamma \|\hat{S}\|_1 
    - \delta \|L^{*}\|_\ast - \gamma \|S^{*}\|_1 \leq 0
\end{equation}

We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):  
\[
\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{(1+\exp(\Theta))^{2}}
\Big)\Big) \succcurlyeq \tau I_{\frac{n(n-1)}{2}\times \frac{n(n-1)}{2}}
\]

For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal. For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite. Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on term $h(\hat{\Theta})-h(\Theta^{*})$ :

\[
h(\hat{\Theta})-h(\Theta^{*}) \geq 
\langle\, \nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*}\rangle\
+ \frac{\tau}{2}\|\Delta_{\hat{\Theta}}\|_{F}^{2}
\]

Hence, we can rearrange the term in (\ref{eq:2}) as follows:

\begin{equation}\label{eq:3}
    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} \leq 
    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*}\rangle\
    + \delta \|L^{*}\|_\ast + \gamma \|S^{*}\|_1 
    - \delta \|\hat{L}\|_\ast - \gamma \|\hat{S}\|_1
\end{equation}

Here, we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers : 
\[
\mathbb{Q}(L,S) := \|L\|_{*} + \frac{\gamma}{\delta}\|S\|_1
\]
Through the definition of $\mathbb{Q}$, we can rewrite (\ref{eq:3}) as follows:
\begin{equation}\label{eq:4}
    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} \leq 
    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*}\rangle\
    + \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\hat{\Delta}^L + L^{*},\hat{\Delta}^S + S^{*})
\end{equation}

According to Agarwal et al[2]'s second element of lemma 1, 
the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\hat{\Delta}^L + L^{*},\hat{\Delta}^S + S^{*})$ is upper-bounded by

\begin{equation}\label{eq:5}
\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) - \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^\perp}) + 2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\norm{S^*_{M^{\perp}}}_{1}
\end{equation}

Here we define $S^{*}$ to be decomposable with respect to the pair of subspace $(\mathbb{M},\mathbb{M}^{\perp})$, and let $L^{*}$ be decomposable with respect to the pair of subspace $(\mathbb{A},\mathbb{B})$.

The decomposability of elementwise $\ell 1$ norm and nuclear norm with respect to a properly chosen pair of subspace is studied at length in the paper [1]. We briefly mention the concept of decomposability here for clarification:

For arbitrary subset $S \subseteq \{1,2,..,n\} \times \{1,2,..,n\}$ of matrices indices, consider the subspace pair 
\[
    \mathbb{M}(S) := \{U\in R^{n \times n} | U_{ij} = 0, \forall (i,j) \not\in S \}
\]
and $\mathbb{M}^\perp(S)$. It is easy to verify that any pair of matrices $U\in \mathbb{M}(S)$ and $U' \in \mathbb{M}^\perp(S)$ in elementwise $\ell 1$ norm is decomposable in a sense that $\|U+U'\|_1 = \|U\|_1 + \|U'\|_1$. Similarly, in nuclear norm, if we define a pair of subspace $(\mathbb{A},\mathbb{B})$ for any matrix $L \in R^{n \times n}$, whose eigen decomposition is $UDV^{T}$, as follows:
\begin{align*}
    \mathbb{A}(L) := \{\Theta \in R^{n \times n} | row(\Theta) \subseteq V, col(\Theta) \subseteq U \} \\ 
    \mathbb{B}(L) := \{\Theta \in R^{n \times n} | row(\Theta) \subseteq V^{\perp}, col(\Theta) \subseteq U^{\perp} \} 
\end{align*}
For any pair of matrices, $U\in \mathbb{A}(L)$ and $U' \in \mathbb{B}(L)$, it is also easy to check that $\|U+U'\|_\ast = \|U\|_\ast+\|U'\|_\ast$.

First, we want to control upper bound of the term $-\langle\,\nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*} \rangle\$$
in (\ref{eq:4}).
\begin{align}
-\langle\,\nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*} \rangle\ 
&=\langle\, \frac{1}{2n} (X - P), \hat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \hat\Delta^{L} + \hat\Delta^{S} \rangle\ \\
&\leq \frac{1}{2n} \|X - P\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\hat{\Delta}^{L}\|_\ast) +  \frac{1}{2n} \|X - P\|_{\infty}\|\hat{\Delta}^{S}\|_{1} \\
&\leq \frac{1}{2n} \|X - P\|_{op}(\|\hat{\Delta}^{\alpha}\|_{F} + \|\hat{\Delta}^{L}_{A}\|_\ast + \|\hat{\Delta}^{L}_{B}\|_\ast) +
\frac{1}{2n} \|X - P\|_{\infty}(\|\hat{\Delta}^{S}_{M}\|_{1} + 
\|\hat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\ 
&\leq \frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\|_{F} + \|\hat{\Delta}^{L}_{A}\|_\ast + \|\hat{\Delta}^{L}_{B}\|_\ast) + \frac{\gamma}{2}(\|\hat{\Delta}^{S}_{M}\|_{1} + 
\|\hat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\
&= \frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\|_{F} +     \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^\perp}) ) \label{eq:10}
\end{align}

Combining the inequalities (\ref{eq:5}) and (\ref{eq:10}), we can obtain the upper bound of RHS in (\ref{eq:4}) as follows:

\begin{equation}
    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} \leq
    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F} + 
    \frac{3\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M})
    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\gamma \norm{S^{*}_{M^\perp}}_{1}
\end{equation}

Second, we wish to control the lower bound of the term  $\frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2}$ with respect to $\hat{\Delta}^{\alpha},\hat{\Delta}^{L},\hat{\Delta}^{S}$.
\begin{align}
\|\hat{\Delta}^{\Theta}\|_{F}^{2} 
&= \|\hat{\Theta}-\Theta^{*} \|_{F}^{2} \\
&= \|\hat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \hat\Delta^{L} + \hat\Delta^{S}\|_{F}^{2} \\
&= \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\hat{\Delta}^{L}+\hat{\Delta}^{S}\|_{F}^{2} + 
2 \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ \\
&=  \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\hat{\Delta}^{L}\|_{F}^{2} + \|\hat{\Delta}^{S}\|_{F}^{2} + 
2 \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
2 \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ \\
& \geq \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \|\hat{\Delta}^{L}\|_{F}^{2} + \|\hat{\Delta}^{S}\|_{F}^{2} + 
2 \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
2 \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ 
\end{align}

\begin{align}
    \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ 
    &\leq \| \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{op} 
    \|\hat{\Delta}_{L}\|_{*} + \| \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} 
    \|\hat{\Delta}_{S}\|_1 \\
    &= \|\hat{\Delta}^{\alpha}\|_{F}(\|\hat{\Delta}_{L}\|_{*} + \|\hat{\Delta}_{S}\|_1)
\end{align}

\begin{align}
    \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ 
    &\leq \|\hat{\Delta}^{L}\|_{\infty} \|\hat{\Delta}^{S}\|_1 \\
    &\leq (\|\hat{L}\|_{\infty} + \|L^{*}\|_{\infty}) \|\hat{\Delta}^{S}\|_1
\end{align}

\begin{landscape}
\begin{table}[t]
\begin{tabular}{lclclclcl}\hline

Pair & Weight & Community & Title                                                                                  &                                                             \\\hline
1    & 6.03                      & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       &                                                             \\
     &                           & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                         &                                                             \\
2    & 3.08                      & MulT      & Innovated higher criticism for detecting sparse signals in correlated noise                   &                                                             \\
     &                           & VarSel    & Regularized estimation of large covariance matrices                                           &                                                             \\
3    & 2.47                      & DimRed    & Contour projected dimension reduction                                                         &                                                             \\
     &                           & VarSel    & Factor profiled sure independence screening                                                   &                                                             \\
4    & 2.15                      & VarSel    & Factor profiled sure independence screening                                                   &                                                             \\
     &                           & DimRed    & Sliced regression for dimension reduction                                                     &                                                             \\
5    & 1.86                      & VarSel    & Covariance regularization by thresholding                                                     &                                                             \\
     &                           & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          &                                                             \\
6    & 1.77                      & VarSel    & Asymptotic properties of bridge estimators in sparse high-dimensional regression models       &                                                             \\
     &                           & Mixed     & Marginal asymptotics for the $''$large p small n$''$ paradigm: with applications to microarray data                                                 &  \\
7    & 1.71                      & VarSel    & A majorization-minimization approach to Variable Selection using spike and slab priors        &                                                             \\
     &                           & Mixed     & Empirical Bayes selection of wavelet thresholds                                           &                                                             \\
8    & 1.66                      & VarSel    & Spades and mixture models                                                                     &                                                             \\
     &                           & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          &                                                             \\
9    & 1.61                      & DimRed    & A constructive approach to the estimation of dimension reduction directions                   &                                                             \\
     &                           & VarSel    & Factor profiled sure independence screening                                                   &                                                             \\
10   & 1.54                      & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors        &                                                             \\
     &                           & Mixed     & Spike and slab variable selection: frequentist and Bayesian strategies                        &                                                             \\
11   & 1.53                      & VarSel    & variable selection in nonparametric additive models                                           &                                                             \\
     &                           & Mixed     & Nonparametric estimation of an additive model with a link function                            &                                                             \\
12   & 1.39                      & Mixed     & Nonparametric inferences for additive models                                                  &                                                             \\
     &                           & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models         &                                                             \\
13   & 1.29                      & Mixed     & Bayesian variable selection in structured high-dimensional covariate spaces with applications in genomics &                                                             \\
     &                           & VarSel    & Model selection and estimation in regression with grouped variables                           &                                                             \\
14   & 1.20                      & VarSel    & The sparsity and bias of the LASSO selection in high-dimensional linear regression            &                                                             \\
     &                           & Mixed     & Tests for high-dimensional covariance matrices                                                &                                                             \\
15   & 1.19                      & FuncAn    & Empirical dynamics for longitudinal data                                                      &                                                             \\
     &                           & Mixed     & Variable selection in nonparametric varying-coefficient models for analysis of repeated measurements      &                               \\\hline                         
\end{tabular}
\end{table}
\end{landscape}

\renewcommand\refname{Reference Cited}
\medskip

\bibliographystyle{unsrt}
\bibliography{reference}

\end{document}

### 2019-04-19 Codes & Data/Codes/ADMM_Optim.R

@@ -1,0 +1,96 @@
+ADMM <- function(X, gamma, delta){
+  N <- nrow(X)
+  source('GD.R')
+  # Initialization
+  # Initialization on X^m = (X_a, X_M, X_L, X_S)
+  X_a <- runif(1,0,1); X_M <- matrix(0,N,N);
+  X_L <- matrix(0,N,N); X_S <- matrix(0,N,N);
+  
+  # Initialization on Z^m = (Z_a, Z_M, Z_L, Z_S)
+  Z_a <- runif(1,0,1); Z_M <- matrix(0,N,N);
+  Z_L <- matrix(0,N,N); Z_S <- matrix(0,N,N);
+  
+  # Initialization on U^m = (U_a, U_M, U_L, U_S)
+  U_a <- runif(1,0,1); U_M <- matrix(0,N,N);
+  U_L <- matrix(0,N,N); U_S <- matrix(0,N,N);
+  
+  J = diag(1,N)-(1/N)*matrix(1,N,N)
+  
+  lambda <- 0.5; k <- 1;
+  Obj <- rep(0,500);
+  
+  #Obj_Val<-function(para_v){
+  #    X_a <- para_v[1]
+  #    X_M <- matrix(para_v[2:(N^2+1)],N,N)
+    
+  #    A <- log(1+exp(X_a + X_M))
+  #    (-X_a/N)*sum(X[upper.tri(X,diag=FALSE)]) + (-1/(2*N))*sum(X*X_M) + 
+  #      (1/N)*sum(A[upper.tri(A,diag=FALSE)]) + 
+  #      (1/(2*lambda))*(X_a-(Z_a-U_a))^2 + (1/(2*lambda))*sum((X_M-(Z_M-U_M))^2) 
+  #}
+  
+  for(k in 1:500){
+    ########## Step 1. <- Update x = ( a, M, L, S ) ##########
+    # a and M update via Gradient Descent
+    para_v <- c(N, lambda, X_a, Z_a, U_a, X_M, Z_M, U_M, X)
+    res <- GD(para_v)
+    X_a <- res[1]
+    X_M <- matrix(res[2:(N^2+1)],N,N)
+    
+    # a and M update via L-BFGS method
+    #para <- c(X_a, X_M)
+    #res <- optim(para, Obj_Val, method = "CG", lower = -Inf, upper = Inf)
+    #X_a <- res[[1]][1]
[…]

### 2019-04-19 Codes & Data/Codes/GD.R

@@ -1,0 +1,53 @@
+GD <- function(para_v){
+  l <- 1
+  N <- para_v[1]
+  lambda <- para_v[2]
+  
+  X_a <- para_v[3]
+  Z_a <- para_v[4]
+  U_a <- para_v[5]
+  
+  X_M <- matrix(para_v[6:((N^2)+5)],N,N)
+  Z_M <- matrix(para_v[((N^2)+6):((2*(N^2)+5))],N,N)
+  U_M <- matrix(para_v[((2*(N^2)+6)):((3*N^2)+5)],N,N)
+  
+  X <- matrix(para_v[((3*(N^2)+6)):((4*N^2)+5)],N,N)
+  
+  new_sol <- rep(0,(N^2+1))
+  old_sol <- rep(0,(N^2+1))
+  Hess_M = matrix(0, N, N)
+  
+  grad <- rep(0,(N^2+1))
+  g <- matrix(0,N,N)
+  K = (-1/N)*sum(X[upper.tri(X,diag=FALSE)])
+  P = Z_a-U_a; Q = Z_M-U_M;
+  
+  while(TRUE){
+    A = exp(X_a + X_M)/(1+exp(X_a + X_M))
+    
+    # Compute the alpha : gradient/hessian
+    grad[1] = ( K + (1/N)*sum(A[upper.tri(A,diag=FALSE)]) + (1/lambda)*(X_a-P) )
+    
+    # Compute the Gradient of M && Compute the Hessian of M
+    g = (-1/(2*N))*X + (1/lambda)*(X_M-Q)
+    g[upper.tri(g,diag = FALSE)] = g[upper.tri(g,diag = FALSE)] + (1/N)*A[upper.tri(A,diag=FALSE)]
+    grad[2:(N^2+1)] = as.vector(g)
+    
+    # Update the solution & Calculate the difference between objective function
+    old_sol = c(X_a, X_M)
+    new_sol = old_sol - 0.1*grad
+    CC<-max(abs(grad))
+    #print(CC)      
+    # Convergence Criteria
+    if(CC < 10^-9){
+      X_a <- new_sol[1]
+      X_M <- matrix(new_sol[2:(N^2+1)],N,N)
+      break
+    }
+    # Store the variable
+    X_a <- new_sol[1]
+    X_M <- matrix(new_sol[2:(N^2+1)],N,N)
+    l = l + 1
+  }
+  return(new_sol) 
+}

### 2019-04-19 Codes & Data/Codes/SynData.R

@@ -1,0 +1,17 @@
+SynData <- function(alpha,F,D,S,N){
+  # Create empty matrix for storing adjacency matrix X and Probability for 
+  X <- matrix(0,N,N); 
+  P <- matrix(0,N,N);
+  L <- F%*%D%*%t(F); 
+  P <- exp(alpha+L+S)/(1+exp(alpha+L+S));
+  
+  # Create random graph according to (a, L, S)
+  for(i in 1:(N-1)){
+    for(j in (i+1):N){
+      if(P[i,j]>runif(1,0,1))
+        X[i,j]<-1
+    }
+  }
+  X <- X + t(X)
+  return(X)
+}

### 2019-04-19 Codes & Data/Codes/Synthetic Data.R

@@ -1,0 +1,404 @@
+####################  preparation  ####################
+rm(list=ls())
+setwd('C:/Users/nsuh3/Desktop/Citation Network/FLag/Codes & Data/Codes')
+library('Matrix')      ## For matrix computation on BIC
+library('igraph')      ## For drawing graph
+source('SynData.R')    ## Function for creating binary network
+source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
+source('functions.R')
+#################### data generation N = 30, K = 3, NNZ = 10 ####################
+set.seed(1234)
+par(mfrow=c(1,3))
+N = 30; K = 3; NNZ = 10;
+### Ingredients for creating network : alpha, F, D, S                      
+### Generate alpha from random uniform distribution
+alpha = runif(1,-3,-2)
+### Create diagonal matrix D with non-negative weights
+D = diag(runif(1,7,8),K)
+### Create binary matrix F(0,1) whose columns are orthogonal with each other.
+C = floor(N/K);              # C : number of 1s for each column
+F = matrix(0,N,K);           # Create empty F matrix
+if(K>0){
+  for(l in 1:K){
+    F[((l-1)*C+1):(l*C),l] <- 1
+  }
+  if(N%%C!=0)
+    F[(K*C+1):N,K] <- 1      # In last column of F, we fill the last remaining entries with 1s, 
+  # when N is not divided by K.
+}
+if(K==0){
+  F <- matrix(0,N,K)
+}
+RR = sample(1:N, 1, replace = FALSE) 
+F[RR,] = 1
+F = (diag(N)-1/N*matrix(1,N,N))%*%F
+### Create random symmetric sparse matrix S, whose entries are greater than or equal to zero.
+S = matrix(0,N,N)
+S = rsparsematrix(N, N, nnz = NNZ, symmetric = TRUE, rand.x = runif)
+S[which(S!=0,arr.ind=TRUE)] = runif(1,6,7)
+diag(S) = 0
+### call function to generate the adjacency matrix
+X1 <- SynData(alpha,F,D,S,N)
+### generate the figure to illustrate the network
[…]

### 2019-04-19 Codes & Data/Codes/citation_network_analysis.R

@@ -1,0 +1,288 @@
+####################  preparation  ####################
+rm(list=ls())
+setwd('C:/Users/nsuh3/Desktop/Citation Network/FLag/Codes & Data')
+library('Matrix')      ## For matrix computation on BIC
+library('igraph')      ## For drawing graph
+source('SynData.R')    ## Function for creating binary network
+source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
+source('functions.R')
+################### Load the Citation Network Data ###################
+paperCitAdj = as.matrix(read.table("paperCitAdj.txt", header=FALSE))
+G <- graph.adjacency(paperCitAdj, mode="undirected", weighted=NULL) # For directed networks
+X <- as_adjacency_matrix(G,type="both",names=TRUE,sparse=FALSE,attr=NULL)
+Node_deg <- rep(0,nrow(X))
+for (i in 1:sqrt(length(X))){
+  Node_deg[i]<-sum(X[i,])
+}
+###### Get a network whose degree is greater than or equal to 7 ######
+ind <- which(Node_deg>=7,arr.ind=TRUE)
+X_new <- X[ind,ind]
+N <- ncol(X_new)
+
+X_draw <- graph_from_adjacency_matrix(X_new, mode = c("undirected"))
+plot(X_draw)
+plotScree(X_new)
+X = X_new
+
+################### Model Selection ###################
+gamma = seq(from=0.0009,to=0.00093,by=0.000003);
+delta = seq(from=0.009,to=0.01,by=0.0001);
+lambda = 1; Count = 1;
+AIC <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
+BIC <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
+
+non_zeroS <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
+L_Rank <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
+Like <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
+N = ncol(X_new)
+
+source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
+for(g in 1:length(gamma)){
+  for(d in 1:length(delta)) {
+    ### Use the ADMM method to estimate the parameters ###
[…]

### 2019-04-19 Codes & Data/Codes/coauthor_network_analysis.R

@@ -1,0 +1,248 @@
+setwd('C:/Users/nsuh3/Desktop/Citation Network/FLag/Codes & Data')
+rm(list=ls())
+require(igraph) # version 0.7.1. Note there are many changes in version 1.0.0
+source('functions.R') #set the working directory
+
+# read the data
+authorPaperBiadj = as.matrix(read.table(file="authorPaperBiadj.txt",sep="\t", header=F))
+authorList = as.matrix(read.table(file="authorList.txt",sep="\t", header=F, stringsAsFactors=F))
+paperCitAdj = as.matrix(read.table("paperCitAdj.txt", header=F))
+paperList = read.table("paperList.txt", sep=",", stringsAsFactors=F, header=T)
+
+# compute adjacency matrix of the coauthorship network
+coauthorAdjWeighted = authorPaperBiadj %*% t(authorPaperBiadj) 
+coauthorAdj = (coauthorAdjWeighted >= 1) -0 
+diag(coauthorAdj) = 0  
+
+# construct the network (A)
+thresh = 2  # the minimum number of coauthored papers for two authors to have an edge
+# compute the adjacency matrix of the network (A)
+coauthorAdjThresh = (coauthorAdjWeighted >= thresh) 
+diag(coauthorAdjThresh) = 0
+# find and label all components
+ix = clusters(graph.adjacency(coauthorAdjThresh))
+componentLabel = ix$membership
+# find the labels for the largest 8 components
+order(ix$csize, decreasing=T)[1:12] #output:  [1]   38  113  309  278  382  223 1036   42  175  725  996  117
+# find their sizes
+sort(ix$csize, decreasing=T)[1:12] #output:  [1] 236  18  14  13  10   9   9   8   8   8   8   7
+#write.table(componentLabel, "data/coauthorThresh2ComponentLabel.txt", col.names=F, row.names=F)
+
+# analyze the giant component (labeled as 38)
+adj = coauthorAdjThresh[componentLabel == 38, componentLabel == 38]
+author = authorList[componentLabel == 38]
+# list 15 high-degree nodes
[…]

### 2019-04-19 Codes & Data/Codes/functions.R

@@ -1,0 +1,248 @@
+require(igraph)
+
+dscore = function(adj, K)
+{
+  # implementation of the D-SCORE (Ji and Jin, 2014). 
+  # Note: When the adjacency matrix is symmetric, SCORE (2014) will be used.
+  #
+  # input: 
+  #    adj - adjacency matrix of a connected network/graph, either
+  #          symmtric (for undirected networks) or asymmtric (for directed networks)
+  #    K   - the number of communities
+  #
+  # output:  the community lables, starting from 1, 2, ...
+  # 
+  # depends: igraph
+  #
+  # authors: Pengsheng Ji and Jiashun Jin
+  
+  #require(igraph)
+  
+  # check connectivity
+  if(!is.connected(graph.adjacency(adj))) stop("The network based on the adjacency matrix is not weakly connected. Use the clusters function in the igraph package to extract the (weakly connected) giant component.")
+  # make sure K > 1
+  if(K < 2) stop("K must be bigger than 1.")
+  
+  
+  # if the adj is symmetric, run SCORE
+  if(sum(adj != t(adj))==0){
+    x = eigen(adj, symmetric=T)$vectors
+    r = x[,2:K]/x[,1]
+    
+    m = nrow(adj)
+    threshold = log(m) 
+    r[r > threshold] =  threshold
+    r[r < -threshold] = -threshold
+    label = kmeans(r, centers=K, nstart=20, iter=100)$cluster
+    
+    return(label)
+  }
+  else{
+    # D-SCORE
+    SVD = svd(adj)
+    rU = as.matrix((SVD$u[,2:K]) / (SVD$u[,1]) )
+    rV = as.matrix((SVD$v[,2:K]) / (SVD$v[,1]) )
+    
+    # indicator for the support
+    a = clusters(graph.adjacency(adj %*% t(adj)))
+    supU = (a$membership == which.max(a$csize))
+    b = clusters(graph.adjacency(t(adj) %*% adj))
+    supV = (b$membership == which.max(b$csize))
+    
+    # threshold the values
+    m = nrow(adj)
+    threshold = log(m) *1
+    rU[!supU, ] = NA
+    rU[rU > threshold]  = threshold
+    rU[rU < -threshold] = -threshold
+    
+    rV[!supV, ] = NA
+    rV[rV > threshold]  = threshold
+    rV[rV < -threshold] = -threshold
+    
[…]

### 2019-04-19 Codes & Data/Codes/Synthetic Data.R
Second Commit

@@ -44,6 +44,7 @@ X_draw <- graph_from_adjacency_matrix(X1, mode = c("undirected"))
 plot(X_draw)
 
 #################### Choose proper tuning parameter #########################
+plotScree(X1)
 gamma = seq(from=0.01,to=0.1,by=0.01);
 delta = seq(from=0.01,to=0.1,by=0.01);
 lambda = 1; Count = 1;
@@ -175,6 +176,7 @@ X_draw2 <- graph_from_adjacency_matrix(X2, mode = c("undirected"))
 plot(X_draw2)
 
 #################### Choose proper tuning parameter #########################
+plotScree(X2)
 gamma = seq(from=0.001,to=0.01,by=0.001);
 delta = seq(from=0.01,to=0.02,by=0.001);
 lambda = 1; Count = 1;
@@ -185,7 +187,7 @@ non_zeroS2 <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
 L_Rank2 <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
 Like2 <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
 
-for(g in 5:length(gamma)){
+for(g in 1:length(gamma)){
   for(d in 1:length(delta)) {
     ### Use the ADMM method to estimate the parameters ###
     result <- ADMM(X2, gamma[g], delta[d])
@@ -226,6 +228,7 @@ for(g in 5:length(gamma)){
 }
 
 ################## Assign memberships to each nodes ##################
+plotScree(X2)
 result2 <- ADMM(X2, 0.004, 0.014) ## gamma : 0.004, delta : 0.014 ##
 a2<-result2[[1]]
 M2<-result2[[2]]
@@ -307,6 +310,7 @@ X_draw3 <- graph_from_adjacency_matrix(X3, mode = c("undirected"))
 plot(X_draw3)
 
 #################### Choose proper tuning parameter #########################
+plotScree(X3)
 gamma = seq(from=0.001,to=0.01,by=0.001);
 delta = seq(from=0.01,to=0.02,by=0.001);
 lambda = 1; Count = 1;
@@ -317,7 +321,7 @@ non_zeroS3 <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
 L_Rank3 <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
 Like3 <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
 
[…]

### 2019-04-20 Manuscript Tex file/Manuscipt/manuscript.tex
Third message

--- 2019-04-19 Manuscript Tex file/Texfile/manuscript.tex
@@
 \usepackage{mathtools}
-\usepackage{natbib}
 \usepackage[nottoc]{tocbibind}
@@
 \usepackage{bbm}
+\usepackage{amssymb}
 
@@
 \begin{document}
-\bibliographystyle{plainnat}
-\bibliography{name-of-your-bib-file-here}
-
 \title{Factor Analysis on Report Citations, Using a Combined Latent and logistic Model}
@@
 Simulation results are reported that show the new method works well in practical situations.
-The proposed method has been applied to a real application in citation network of statistician data set (Ji and Jin).
+The proposed method has been applied to a real application in citation network of statistician data set (Ji and Jin, 2016 \cite{ji2016coauthorship}).
 \end{abstract}
@@
 The above delivers a factor analysis model.
-Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g., \cite{joreskog1969general,mcdonald1985factor, harman1976modern,rasch1960probabilistic,lord1968statistical,karl1973general}).
+Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g.,\cite{joreskog1969general, mcdonald2014factor,lord2008statistical, rasch1980probabilistic, harman1960modern, joreskog1970general}).
 
-Our work is inspired from Fused Latent and Graphical (FLaG) model (Chen et al, 2016).
+Our work is motivated from a recent work {\it Fused Latent and Graphical (FLaG) model} (Chen et al, 2016, \cite{chen2016fused}).
 They assume that majority of variation of responses can be accounted by low dimensional latent vector, and remaining dependent structure of responses can be explained by sparse graphical structure.
@@
 
-Though it may seem similar to Chen et al, we work on a different model formulation in several aspects.
+Though it may seem similar to Chen et al \cite{chen2016fused}, we work on a different model formulation in several aspects.
 First, FLaG is built to analyze the Eysenck’s Personality Questionnaire that consists of items designed to measure Psychoticism, Extraversion, and Neuroticism.
@@
 
-The proposed modeling framework is also related with the analysis of decomposing a matrix into low-rank and sparse components and the statistical inference of a multivariate Gaussian model whose precision matrix admits the form of a low-rank matrix plus a sparse matrix (Chandrasekaran et al, 2012).
+The proposed modeling framework is also related with the analysis of decomposing a matrix into low-rank and sparse components and the statistical inference of a multivariate Gaussian model whose precision matrix admits the form of a low-rank matrix plus a sparse matrix (\cite{chandrasekaran2010latent, candes2011robust, zhou2010stable}).
 However, the inference and optimization of the current model are different from those cases.
 We will construct a regularized-likelihood function, based on which estimator will be proposed for simultaneous model selection and parameter estimation.
-The optimization for the regularized estimator will be convex, for which we will develop an efficient algorithm through the alternating direction method of multiplier (Boyd et al, 2011).
+The optimization for the regularized estimator will be convex, for which we will develop an efficient algorithm through the alternating direction method of multiplier (ADMM : \cite{boyd2011distributed, gabay1975dual, glowinski1975solution}).
 
@@
 
-\section{ Some additional assumptions }
+\section{ Theoretical Properties }
 We are interested in verifying following optimization problem has an unique solution.
 
-\begin{align*}
+\begin{align}
 \min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
@@
 L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
-\end{align*}
+\end{align}
 
-\noindent In our problem, we are mainly interested in separating the main stream dependent structure from ad-hoc dependent structure.
-From the construction of our problem, $L_{ij} = F^T_{i}DF_{j}$, which encodes the positive weight when the $i$th paper and $j$th paper share $K$ common topics, and zero weight when two paper share no common topics, is always greater than or equal to zero.
-And $S_{ij}$, which encodes the ad-hoc dependent structure that cannot be explained by main dependent structure (induced from commonly shared topics between papers), is always greater than or equal to zero, $S_{ij} \geq 0$.
-Through this construction we should note that where $S_{ij}\neq0$, $L_{ij}$ should be equal to 0, and vice versa, where $L_{ij}\neq0$, $S_{ij}=0$.
-By incorporating these conditions, we can add following constraints to our optimization problem stated above: $L\geq 0$, $S \geq 0$, $L_{ij}*S_{ij}=0, {1\le i< j\le n}$.
-\\
-
-\noindent Denote $L^*$ and $S^*$ as ground truth parameter and let $\theta^*_{ij}=\alpha+L^*_{ij}+S^*_{ij}$, $N=n(n-1)/2$.
+\noindent \textbf{Strong convexity} Denote $L^*$ and $S^*$ as ground truth parameter and let $\theta^*_{ij}=\alpha+L^*_{ij}+S^*_{ij}$, $N=n(n-1)/2$.
 We can easily check the above logistic likelihood function's Hessian matrix is $N \times N$ diagonal matrix with each entries, $\frac{1}{n}\frac{\exp(\theta^*_{ij})}{(1+\exp(\theta^*_{ij}))^2}$.
@@
 $X$ is a drawn data from the probability density, which is characterized by $\Theta^*$ ; $X\sim{P_{\Theta^*}}$,... (To be worked...)
+
+I believe we can establish the the non-asymptotic error bound between optimal estimator and ground truth parameter,
+\[
+    \|\alpha^*-\hat{\alpha}\|_{F}^{2} + 
+    \|M^*-\hat{M}\|_{F}^{2} +
+    \|S^*-\hat{S}\|_{F}^{2} \leq  ?
+\]
 
@@
 As an alternative, we choose a purely heuristic approach.
-Following the Ji and Jin[], we plot the largest 20 eigenvalues of adjacency matrix X, which can tell us the numbers of communities embedded in network.
+Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest 20 eigenvalues of adjacency matrix X, which can tell us the numbers of communities embedded in network.
 Then, we record the rank of L and number of non-zero elements in S for each tuning parameter pair on grid, and choose proper pair of tuning parameters which can give us interesting interpretation of data.
@@
 \subsection{Citation and Co-authorship networks for statisticians }
-Recently, Ji and Jin [] published an interesting data set on citation  and co-authorship networks of statisticians.
+Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting data set on citation  and co-authorship networks of statisticians.
 Citation relationship over 3000 papers from 4 statistical journals, published between 2003 and 2012, were collected, and collaborative network between authors of papers is given as well.
@@
 (2016) and our model in terms of model formulation is given in Introduction section.) We are interested in solving following optimization problem :
-
 \begin{equation}\label{eq:1}
@@
 \hat{\Delta}^S = \hat{L}-S^{*}.$
-Throughout the proof, let $P= \Big\{\frac{\exp(\Theta_{ij})}{1+\exp(\Theta_{ij})}\Big\}_{1 \leq i,j \leq n}$.
-Moreover, for any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1})
+Throughout the proof, let $P=\frac{\exp(\Theta_{ij})}{1+\exp(\Theta_{ij})}$. Moreover, for any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1})
 
@@
 \begin{equation}\label{eq:5}
-\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) - \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^\perp}) + 2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\norm{S^*_{M^{\perp}}}_{1}
+    \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) - \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^\perp})
+    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
 \end{equation}
@@
     \frac{3\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M})
-    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\gamma \norm{S^{*}_{M^\perp}}_{1}
+    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\gamma \|S^*_{M^\perp}\|_{1}
+    \label{eq:11}
 \end{equation}
@@
 2 \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ \\
-& \geq \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \|\hat{\Delta}^{L}\|_{F}^{2} + \|\hat{\Delta}^{S}\|_{F}^{2} + 
+&\geq \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \|\hat{\Delta}^{L}\|_{F}^{2} + \|\hat{\Delta}^{S}\|_{F}^{2} + 
 2 \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
@@
 
+To get the further lower bound on trace inner product terms, 
+$ \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ $, we use a definition of dual norm, and the assumption...,
 \begin{align}
-    \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ 
-    &\leq \| \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{op} 
-    \|\hat{\Delta}_{L}\|_{*} + \| \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} 
-    \|\hat{\Delta}_{S}\|_1 \\
-    &= \|\hat{\Delta}^{\alpha}\|_{F}(\|\hat{\Delta}_{L}\|_{*} + \|\hat{\Delta}_{S}\|_1)
+    | \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ |
+    &= | \langle\,\hat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\
+    &\leq \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\hat{\Delta}^{S}\|_1 \\
+    &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\hat{\Delta}^{S}\|_1\\
+    &\leq 2\kappa\|\hat{\Delta}^{S}\|_1
 \end{align}
@@
 \begin{align}
-    \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ 
-    &\leq \|\hat{\Delta}^{L}\|_{\infty} \|\hat{\Delta}^{S}\|_1 \\
-    &\leq (\|\hat{L}\|_{\infty} + \|L^{*}\|_{\infty}) \|\hat{\Delta}^{S}\|_1
+    | \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ |
+    &\leq \|\hat{\Delta}^{L}\|_{\infty} \|\hat{\Delta}^{S}\|_1\\
+    &\leq (\|\hat{L}\|_{\infty} + \|L^{*}\|_{\infty})
+    \|\hat{\Delta}^{S} \|_{1}\\
+    &\leq \big(\frac{2\kappa}{n}\big)\|\hat{\Delta}^{S} \|_{1}
 \end{align}
+
+\begin{align}
+    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} 
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} 
+    - 2\kappa\tau(\frac{n+1}{n})\|\hat{\Delta}^{S}\|_{1} \\
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\hat{\Delta}^{S}\|_{1}\\
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S) \label{eq:26}
+\end{align}
+
+By combining the relations (\ref{eq:11}) and (\ref{eq:26}), we can get following inequality, 
+\[
+    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S)\\
+    \leq \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F} + 
+    \frac{3\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 2\gamma \|S^{*}_{M^\perp}\|_{1}
+\]
+Further, rearrange the terms, apply triangular inequality, $\mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S)\leq \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^{\perp}})$, and Agarwal et al[2]’s third element of lemma 1, we get
+\[
+    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} -
+    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F} 
+    \leq 
+    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}
+\]
+Noting that $\hat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\hat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
+\begin{align}
+    \delta\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) 
+    \leq \sqrt{2k}\delta\|\hat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S_\mathbb{M}\|_{F}\\
+    \leq \sqrt{2k}\delta\|\hat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S\|_{F}
+\end{align}
+
+Our goal is to get the non-asymptotic error bound between optimal estimator and ground truth parameter,
+\[
+    \|\alpha^*-\hat{\alpha}\|_{F}^{2} + 
+    \|M^*-\hat{M}\|_{F}^{2} +
+    \|S^*-\hat{S}\|_{F}^{2} \leq  ?
+\]
+I am stuck at how to reorganize the terms in
 
@@
 
-\renewcommand\refname{Reference Cited}
-\medskip
-
-\bibliographystyle{unsrt}
-\bibliography{reference}
+\bibliographystyle{plain}
+\bibliography{references.bib}
 

### 2019-05-09 Manuscript Tex file/Manuscript/manuscript.tex
Third Upload

--- 2019-04-20 Manuscript Tex file/Manuscipt/manuscript.tex
@@
 \usepackage{amssymb}
+\usepackage{float}  % For fixing the image in draft
 
@@
 
+\item To ensure unique separation of $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that eigen-vector of $L$ is centered, that is,
+\[
+    JLJ = L \quad where \quad
+    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T
+\]
+This condition uniquely identifies F up to a common orthogonal transformation of its columns.
+
 \end{enumerate}
@@
 For the issue on assigning the community membership of each node $i$, we will discuss this later in Section 6.
-
-\section{ Theoretical Properties }
-We are interested in verifying following optimization problem has an unique solution.
-
-\begin{align}
-\min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
--\frac{1}{n} \log \prod_{1\le i< j\le n}\frac{exp\left(X_{ij}\left(\alpha+
-L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
-L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
-\end{align}
-
-\noindent \textbf{Strong convexity} Denote $L^*$ and $S^*$ as ground truth parameter and let $\theta^*_{ij}=\alpha+L^*_{ij}+S^*_{ij}$, $N=n(n-1)/2$.
-We can easily check the above logistic likelihood function's Hessian matrix is $N \times N$ diagonal matrix with each entries, $\frac{1}{n}\frac{\exp(\theta^*_{ij})}{(1+\exp(\theta^*_{ij}))^2}$.
-This means that our likelihood function is strictly convex in a sense that $H \succ 0$, unless $\min_{1\le i< j\le n}\theta^*_{ij}$ tends to $-\infty$.
-This is automatically guaranteed through the construction of our problem, $S_{ij} \in R, S_{ij} \geq 0$, and $L_{ij} = F^T_{i}DF_{j}$.
-
-Once we have the unique $\Theta^* \in R^{n \times n}$, whose each entries are $\theta^*_{ij}$, we further need to confirm if it has an unique decomposition, $\Theta^*=\alpha+L^*+S^*$.
-As mentioned in \cite{candes2011robust}, the decomposition is unique, and problem is well posed, as long as the low-rank matrix is not sparse, and vice versa if the sparse component is not low-rank matrix.
-Specifically, these conditions are guaranteed if the singular vectors of $L^*$ are not sparse and if the non-vanishing entries of $S^*$ occur at random locations.
-It is a natural question whether we can check this kind of incoherence between $L^*$ and $S^*$ by observing the given network data $X$. Since 
-$X$ is a drawn data from the probability density, which is characterized by $\Theta^*$ ; $X\sim{P_{\Theta^*}}$,... (To be worked...)
-
-I believe we can establish the the non-asymptotic error bound between optimal estimator and ground truth parameter,
-\[
-    \|\alpha^*-\hat{\alpha}\|_{F}^{2} + 
-    \|M^*-\hat{M}\|_{F}^{2} +
-    \|S^*-\hat{S}\|_{F}^{2} \leq  ?
-\]
 
@@
 The problem in \eqref{eq:admm02} may not have a closed-form solution.
-We use a simple gradient descent to solve this step, setting the step size, $\alpha=0.1$ and stopping criteria, $\max(|x_\alpha^{m+1}-x_\alpha^{m}|,\|x_M^{m+1}-x_M^{m}\|_{\infty}) \leq 10^{-9}$.
+We use a simple gradient descent to solve this step, setting the step size, $\alpha=0.1$ and stopping criteria, $\max(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}) \leq 10^{-9}$.
 Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem.
@@
 In this work, we simply choose $\lambda = 0.5$.
-We terminate the algorithm  when in $mth$ iteration, $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^-7$.
+We terminate the algorithm  when in $mth$ iteration, $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^{-7}$.
 
@@
 
-\begin{figure}[!h]
+\begin{figure}[h]
 \includegraphics[width=1\textwidth]{Fig1.pdf}
@@
 
-\begin{figure}[!h]
-\begin{center}
-\includegraphics[scale=0.75]{Fig2.pdf}
-\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\hat{S}$ matrix.
-For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
-\end{center}
-\label{fig:figure2}
-\end{figure}
-
 \noindent edges" are also attributed to $\alpha$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha$ or $S_{ij}$.
@@
 
+\begin{figure}[b]
+\begin{center}
+\includegraphics[scale=0.75]{Fig2.pdf}
+\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\hat{S}$ matrix.
+For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
+\end{center}
+\label{fig:figure2}
+\end{figure}
+
 \subsection{Citation and Co-authorship networks for statisticians }
@@
 Citation relationship over 3000 papers from 4 statistical journals, published between 2003 and 2012, were collected, and collaborative network between authors of papers is given as well.
-In this section, we analyze these two networks.
+In this section, we analyze the citation network.
 \\
@@
 
-\begin{figure}[!h]
-\includegraphics[width=1\textwidth]{Fig4.png}
-\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network, Co-authorship network.}
-\label{fig:figure1}
-\end{figure}
-
 \begin{itemize}
@@
 \noindent These two topics are classical research topics in field of statistics.
-Majority of papers in first community study about "Controlling False Discovery Rate" in various statistical settings.
-Second group talks about "Variable selection" in high-dimensional data.
+First group talks about "Variable selection" in high-dimensional data.
+Majority of papers in second community study about "Controlling False Discovery Rate" in various statistical settings.
 As expected, third group is quite hard to interpret and seems to have substructures.
-For further investigation on this group, after obtaining the subnetwork which is comprised only with papers in third group, we performed same analysis once again under the assumption that $K=4$.
-We obtain four subcommunities as follows:
+For further investigation on this group, after obtaining the sub-network which is comprised only with papers in third group, we performed same analysis once again under the assumption that $K=4$.
+We obtain four sub-communities as follows:
 
@@
 
+\begin{figure}[b]
+\includegraphics[width=1\textwidth]{Fig4.eps}
+\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
+\label{fig:figure4}
+\end{figure}
+
 \noindent Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction".
-Due to small volume of each communities, we could check that false discoveries for each community are all zero.
-\\
+Due to small volume of each communities, we could check that false discoveries for each community are all zero.\\
 
@@
 \includegraphics[width=1\textwidth]{Fig3.eps}
-\caption{ From left to right: }
+\caption{Illustration of first two eigenvectors of estimated $\hat{L}$ matrix for original
+citation network with 543 papers(left) and sub-network graph(right). Presentation
+on clustering results of k-means algorithm with different colors.}
 \label{fig:figure1}
@@
 
-\section{On non-asymptotic error bound of the estimator}
-Chen et al.
-(2016) show that their estimator recovers the algebraic structure, that is, the conditional graph structure and the number of latent variables, with probability tending to one.
+\section{ On non-asymptotic error bound of the estimator }
+Chen et al.\cite{chen2016fused} show that their estimator recovers the algebraic structure, that is, the conditional graph structure and the number of latent variables, with probability tending to one.
 However, their analysis only allows a growing number of sample points whereas they keep the number of variables fixed.
 Their result thus severs from the tradition to analyze the more challenging high-dimensional setting, where the number of variables is also explicitly tracked.
-Our analysis will focus on getting a non-asymptotic error bound of estimator in the context of where the sample size is fixed as 1, and the number of variables is growing.
-(More detailed descriptions on the differences between Chen et al.
-(2016) and our model in terms of model formulation is given in Introduction section.) We are interested in solving following optimization problem :
+Our analysis will focus on getting a non-asymptotic error bound of estimator in the context of where the sample size is fixed as 1, and the number of nodes is growing.
+Readers can find more detailed descriptions on the differences between Chen et al.
+\cite{chen2016fused} and our model in terms of model formulation in Introduction section.
+We are interested in solving following optimization problem :
+
 \begin{equation}\label{eq:1}
 \min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
--\frac{1}{n} \log \prod_{1\le i< j\le n}\frac{exp\left(X_{ij}\left(\alpha+
+-\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{exp\left(X_{ij}\left(\alpha+
 L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
@@
 
+Astute readers might notice the slight difference of first term in objective function between (\ref{eq:logistic10})
+and (\ref{eq:1}).
+(\ref{eq:1}) sums over the all $(i,j)$ pairs.
+Due to the symmetry of $X$ and $\Theta=\alpha\mathbbm{1}\mathbbm{1}^T+L+S$, after scaling, the only difference lies in the inclusion of diagonal term of $\Theta$.
+It should be noted that this slight modification neither leads to theoretical consequences nor noticeable difference in practice.
+Rather, this formulation allows us to simplify the theoretical investigation in a direction to which we want to pursue \cite{ma2017exploration}.
 Let ($\hat{\alpha},\hat{L},\hat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process.
-Let $\hat{\theta},\theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$ and
-$\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
+Let $\hat{\Theta},\Theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
 And denote the error term for each parameter as $\hat{\Delta}^{\Theta} = \hat{\Theta}-\Theta^{*}, 
@@
 \hat{\Delta}^L = \hat{L}-L^{*},
-\hat{\Delta}^S = \hat{L}-S^{*}.$
-Throughout the proof, let $P=\frac{\exp(\Theta_{ij})}{1+\exp(\Theta_{ij})}$. Moreover, for any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1})
+\hat{\Delta}^S = \hat{S}-S^{*}.$
+Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
+We impose following assumptions for theoretical guarantees.
 
+\begin{assumption} (\textbf{Strong convexity})
+For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):
 \[
-h(\Theta) = -\frac{1}{n}\sum_{i<j} \Big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \Big\}
+\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
+\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
+\]
+For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal. For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite.
+\end{assumption}
+
+\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L})
+To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
+We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
+We would also note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
+\end{assumption}
+
+With these assumptions we present the behavior of non-asymptotic error bound of our estimator through following theorem.
+In our result, we measure error using the squared Frobenius norm summed across both matrices:
+\[
+    e^{2}(\hat{\alpha}.\hat{L},\hat{S}):=\|\alpha^{*}-\hat{\alpha}\|_{F}^{2} + \|L^{*}-\hat{L}\|_{F}^{2} + \|S^{*}-\hat{S}\|_{F}^{2}
 \]
 
-Observe that 
-$\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$
-is an optimal solution to (\ref{eq:1}), and that the ground truth parameter
-$\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$ is feasible. Thus, we have the following basic inequality
+\begin{theorem}
+Under the assumptions (4.1) and (4.2),
+if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying 
+\begin{align}
+\delta \geq 4\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 4\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
+\end{align}
+There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, where $k = rank(L^{*}), s= |supp(S^{*})|$, we have following upper bound on $e^{2}(\hat{\alpha}.\hat{L},\hat{S})$
+\begin{align}
+    e^{2}(\hat{\alpha},\hat{L},\hat{S}) \leq
+    c_{1}\frac{\delta^{2}}{\tau^{2}} +
+    c_{2}\frac{\delta^{2}}{\tau^{2}}
+    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\} +
+    c_{3}\frac{\gamma^{2}}{\tau^{2}}
+    \bigg\{s + \frac{\tau}{\gamma}\|S^*_{M^\perp}\|_{1}\bigg\}
+\end{align}
+\end{theorem}
 
-\begin{equation}\label{eq:2}
-    h(\hat{\Theta})-h(\Theta^{*}) 
-    + \delta \|\hat{L}\|_\ast + \gamma \|\hat{S}\|_1 
-    - \delta \|L^{*}\|_\ast - \gamma \|S^{*}\|_1 \leq 0
-\end{equation}
-
-We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):  
-\[
-\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{(1+\exp(\Theta))^{2}}
-\Big)\Big) \succcurlyeq \tau I_{\frac{n(n-1)}{2}\times \frac{n(n-1)}{2}}
-\]
-
-For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal.
-For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite.
+\begin{proof}
 Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on term $h(\hat{\Theta})-h(\Theta^{*})$ :
@@
 
-According to Agarwal et al[2]'s second element of lemma 1, 
+According to Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1, 
 the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\hat{\Delta}^L + L^{*},\hat{\Delta}^S + S^{*})$ is upper-bounded by
@@
     &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\hat{\Delta}^{S}\|_1\\
-    &\leq 2\kappa\|\hat{\Delta}^{S}\|_1
+    &\leq 2C\kappa\|\hat{\Delta}^{S}\|_1
 \end{align}
@@
     &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} 
-    - 2\kappa\tau(\frac{n+1}{n})\|\hat{\Delta}^{S}\|_{1} \\
+    - 2\kappa\tau(\frac{Cn+1}{n})\|\hat{\Delta}^{S}\|_{1} \\
     &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\hat{\Delta}^{S}\|_{1}\\
@@
 \]
-Further, rearrange the terms, apply triangular inequality, $\mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S)\leq \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^{\perp}})$, and Agarwal et al[2]’s third element of lemma 1, we get
-\[
+Further, rearrange the terms, apply triangular inequality, $\mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S)\leq \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^{\perp}})$, and Agarwal et al[\cite{agarwal2012noisy}]’s third element of lemma 1, we get
+\begin{align}
     \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} -
@@
     \leq 
-    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}
-\]
+    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}  \label{eq:42}
+\end{align}
 Noting that $\hat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\hat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
@@
     \leq \sqrt{2k}\delta\|\hat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S_\mathbb{M}\|_{F}\\
-    \leq \sqrt{2k}\delta\|\hat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S\|_{F}
+    \leq \sqrt{2k}\delta\|\hat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S\|_{F} \label{eq:44}
 \end{align}
 
-Our goal is to get the non-asymptotic error bound between optimal estimator and ground truth parameter,
-\[
-    \|\alpha^*-\hat{\alpha}\|_{F}^{2} + 
-    \|M^*-\hat{M}\|_{F}^{2} +
-    \|S^*-\hat{S}\|_{F}^{2} \leq  ?
-\]
-I am stuck at how to reorganize the terms in
+Plug (\ref{eq:44}) in (\ref{eq:42}) and rearrange the terms,
+\begin{align}
+    \bigg\{\frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} -
+    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F}\bigg\} + 
+    \bigg\{\frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2}
+    -\frac{7}{2}\sqrt{2k}\delta\|\hat{\Delta}^{L}\|_{F}\bigg\} +
+    \bigg\{\frac{\tau}{2}\|\hat{\Delta}^{S}\|_{F}^{2} - 
+    \frac{7}{2}\Psi(\mathbb{M})\gamma\|\hat{\Delta}^S\|_{F}\bigg\}\\
+    \leq 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1} \label{eq:46}
+\end{align}
+
+Rearrange the term (\ref{eq:46}) again, and yields the claim,
+\begin{align}
+    \bigg\{\|\hat{\Delta}^{\alpha}\|_{F}-\frac{\delta}{2\tau} \bigg\}^{2} + \bigg\{\|\hat{\Delta}^{L}\|_{F}-\frac{7\delta}{2\tau}\sqrt{2k}\bigg\}^{2} + \bigg\{\|\hat{\Delta}^{S}\|_{F}-\frac{7\delta}{2\tau}\Psi(\mathbb{M})\bigg\}^{2} \\
+    \leq \frac{\delta^{2}}{4\tau^{2}} + \bigg\{\frac{8\delta}{\tau}\sum_{j=r+1}^{n}\sigma_{j}(L^{*}) + 
+    \frac{49\delta^{2}}{4\tau^{2}}(2k)\bigg\} +
+    \bigg\{\frac{8\gamma}{\tau}\|S^*_{M^\perp}\|_{1} + 
+    \frac{49\gamma^{2}}{4\tau^{2}}\Psi^{2}(\mathbb{M})\bigg\}
+\end{align}
+\end{proof}
 

### 2019-05-09 Codes & Data/Codes/GD.R

@@ -20,6 +20,7 @@ GD <- function(para_v){
   grad <- rep(0,(N^2+1))
   g <- matrix(0,N,N)
   K = (-1/N)*sum(X[upper.tri(X,diag=FALSE)])
+  #K = (-1/N)*sum(X)
   P = Z_a-U_a; Q = Z_M-U_M;
   
   while(TRUE){
@@ -27,17 +28,19 @@ GD <- function(para_v){
     
     # Compute the alpha : gradient/hessian
     grad[1] = ( K + (1/N)*sum(A[upper.tri(A,diag=FALSE)]) + (1/lambda)*(X_a-P) )
+    # grad[1] = ( K + (1/N)*sum(A) + (1/lambda)*(X_a-P) )
     
     # Compute the Gradient of M && Compute the Hessian of M
     g = (-1/(2*N))*X + (1/lambda)*(X_M-Q)
     g[upper.tri(g,diag = FALSE)] = g[upper.tri(g,diag = FALSE)] + (1/N)*A[upper.tri(A,diag=FALSE)]
+    #g = (-1/N)*X + (1/lambda)*(X_M-Q) + (1/N)*A
     grad[2:(N^2+1)] = as.vector(g)
     
     # Update the solution & Calculate the difference between objective function
     old_sol = c(X_a, X_M)
     new_sol = old_sol - 0.1*grad
     CC<-max(abs(grad))
-    #print(CC)      
+    # print(CC)
     # Convergence Criteria
     if(CC < 10^-9){
       X_a <- new_sol[1]

### 2019-05-09 Codes & Data/Codes/Synthetic Data.R

@@ -8,7 +8,7 @@ source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
 source('functions.R')
 #################### data generation N = 30, K = 3, NNZ = 10 ####################
 set.seed(1234)
-par(mfrow=c(1,3))
+par(mfrow=c(1,5))
 N = 30; K = 3; NNZ = 10;
 ### Ingredients for creating network : alpha, F, D, S                      
 ### Generate alpha from random uniform distribution

### 2019-05-13 manuscript.tex
Fourth Update

--- 2019-05-09 Manuscript Tex file/Manuscript/manuscript.tex
@@
-\documentclass{article}
+\documentclass[AMS,STIX1COL]{WileyNJD-v2}
+%\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
+%\usepackage{amsmath,amsfonts}
+\usepackage{bbm}
 \usepackage{mathtools}
-\usepackage[nottoc]{tocbibind}
-\usepackage[nohead, nomarginpar, margin=1in, foot=.25in]{geometry}
-\usepackage{mathtools}
-\usepackage{bbm}
-\usepackage{amssymb}
 \usepackage{float}  % For fixing the image in draft
+\usepackage{lscape} 
+%\usepackage[nottoc,notlot,notlof]{tocbibind}
 
-\usepackage{amsmath}
-\usepackage{lscape} 
-\usepackage{graphicx}
-\graphicspath{ {./images/} }
-
-%\usepackage{nips10submit_e}
-\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
-%\usepackage{epstopdf}
-\usepackage{natbib}
-%\usepackage{mathbbold}
-\usepackage{bm}
-\usepackage{enumerate}
-\usepackage{mathrsfs}
-\usepackage{epsfig}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{verbatim}
-\usepackage{multirow}
-\usepackage{array}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{property}[theorem]{Property}
-\newtheorem{result}[theorem]{Result}
-\newtheorem{example}[theorem]{Example}
-
-\newtheorem*{remark*}{Remark}
-\DeclareGraphicsExtensions{.eps}
-
-\renewcommand{\baselinestretch}{1} % 2.0 or 3.0 would do.
-\renewcommand*\labelenumi{(\theenumi)}
-\renewcommand\theequation{\arabic{section}.\arabic{equation}}
 \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
@@
 
-%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage[linesnumbered,ruled]{algorithm2e}
-\RestyleAlgo{boxruled}
+\articletype{Article Type}%
 
-\topmargin 0pt \advance \topmargin by -\headheight \advance \topmargin by
--\headsep \textheight 8.9in \oddsidemargin 0pt \evensidemargin
-\oddsidemargin \marginparwidth 0.5in \textwidth 6.5in
+\received{13 May 2019}
+\revised{13 May 2019}
+\accepted{13 May 2019}
+
+\raggedbottom
 
 \begin{document}
-\title{Factor Analysis on Report Citations, Using a Combined Latent and logistic Model}
-\author{Namjoon Suh, Xiaoming Huo, Eric Heim, Timothy Van Slyke, and Lee Seversky}
 
-\date{\today}
-\maketitle
+\title{Factor Analysis on Report Citations, using a Combined Latent and logistic Model}
 
-\begin{abstract}
-% To be added later...
-We propose a combined latent and logistic model for the citation network, where either a latent model or a logistic model alone is often insufficient to capture the structure of the data.
+\author[1]{Namjoon Suh*}
+
+\author[1]{Xiaoming Huo}
+
+\author[3]{Eric Heim}
+
+\author[3]{Timothy Van Slyke}
+
+\author[3]{Lee Seversky}
+
+\authormark{AUTHOR ONE \textsc{et al}}
+
+\address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
+
+\address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
+
+\address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
+
+\corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}
+
+\presentaddress{This is sample for present address text this is sample for present address text}
+
+\abstract[Summary]{We propose a combined latent and logistic model for the citation network, where either a latent model or a logistic model alone is often insufficient to capture the structure of the data.
 The proposed model has a latent (i.e., factor analysis) model to represents the main technological trends (aka factors), and adds a sparse logistic component that captures the remaining ad hoc dependence.
@@
 The proposed method has been applied to a real application in citation network of statistician data set (Ji and Jin, 2016 \cite{ji2016coauthorship}).
-\end{abstract}
+}
 
-\noindent{\sc KEY WORDS}: citation network, matrix decomposition, latent variable model,  logistic model, convex optimization
+\keywords{citation network, matrix decomposition, latent variable model,  logistic model, convex optimization}
+
+\jnlcitation{\cname{%
+\author{Williams K.}, 
+\author{B. Hoskins}, 
+\author{R. Lee}, 
+\author{G. Masato}, and 
+\author{T. Woollings}} (\cyear{2016}), 
+\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
+
+\maketitle
+
+\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
 
@@
 
-\bibliographystyle{plain}
-\bibliography{references.bib}
+\nocite{*}
+\bibliography{References}%
+
+%\backmatter
 

### 2019-05-13 Manuscript for submission/manuscript.tex
latex works

--- 2019-05-13 manuscript.tex
@@
 
-\author[3]{Eric Heim}
+\author[2]{Eric Heim}
 
-\author[3]{Timothy Van Slyke}
+\author[2]{Timothy Van Slyke}
 
-\author[3]{Lee Seversky}
+\author[2]{Lee Seversky}
 
@@
 \address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
-
-\address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
 
@@
 
-\section{Introduction}\label{sec:intro}
+\section{Introduction}
+\label{sec:intro}
 We study a citation network, where each node (i.e., item) can be a technical report or a publication. 
@@
 \end{equation}
-here $\alpha \in \mathbb{R}$ is a parameter and matrix $D \in \mathbb{R}^{K \times K}$ is a diagonal matrix: $D = \mbox{diag}\{d_{1},d_{2},\ldots,d_{K}\}$. We assume $d_{ii} > 0$ for $1 \le i \le K$.
+where $\alpha \in \mathbb{R}$ is a parameter and matrix $D \in \mathbb{R}^{K \times K}$ is a diagonal matrix: $D = \mbox{diag}\{d_{1},d_{2},\ldots,d_{K}\}$. 
+We assume $d_{ii} > 0$ for $1 \le i \le K$.
 Another way to put \eqref{eq:logistic01} is
@@
 \label{eq:logistic02}
-\mathbb{P}(X_{ij}=1) = \frac{\exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}}{1 + \exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}},
+\mathbb{P}(X_{ij}=1) = \frac{\exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}}{1 + \exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}}. 
 \end{equation}
@@
 Functions $\|S\|_1$ and $\|L\|_\ast$ are known to be convex functions.
-Therefore, the objective function in \eqref{eq:logistic10} is convex. The above convex optimization problem can be solved via ADMM as follows.
+Therefore, the objective function in \eqref{eq:logistic10} is convex. 
+The above convex optimization problem can be solved via ADMM as follows.
 
@@
 $x^{m+1}_\alpha, x^{m+1}_M, x^{m+1}_L$, and $x^{m+1}_S$
-can be updated separately. More precisely, we have
+can be updated separately. 
+More precisely, we have
 \begin{eqnarray}
@@
 \]
-\\
 
@@
 Coordinates of each rows from first two eigenvectors of estimated $\hat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well. 
-Our experience shows that with only first two eigenvectors of $\hat{L}$, we can also cluster the nodes comparably well.
-\\
+Our experience shows that with only first two eigenvectors of $\hat{L}$, we can also cluster the nodes comparably well. \\
 
@@
 In this case, this makes the edges indistinguishable if they come from $S_{ij}$ or $L_{ij}$. 
-Some of "across
-
-\noindent edges" are also attributed to $\alpha$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha$ or $S_{ij}$.
-So the total number of across edges might not be exactly same as we set in our data generation setting.
-\\
+Some of ``across edges" are also attributed to $\alpha$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha$ or $S_{ij}$. 
+So the total number of across edges might not be exactly same as we set in our data generation setting. \\
 
@@
 Citation relationship over 3000 papers from 4 statistical journals, published between 2003 and 2012, were collected, and collaborative network between authors of papers is given as well. 
-In this section, we analyze the citation network.
-\\
+In this section, we analyze the citation network. \\
 
@@
 The elbow points of the scree plot may be at the 3rd, 7th, or 9th largest eigenvalue, suggesting that there might be from 2 to 8 topics in network. 
-In light of this, we performed our analysis under the assumption that there might exist 2 distinct topics and one giant component in which 3 or 4 topics mixed up.
-\\
+In light of this, we performed our analysis under the assumption that there might exist 2 distinct topics and one giant component in which 3 or 4 topics mixed up. \\
 
@@
 Not only could we see the papers with topics on "Learning Theory", "Non-parametric/semi-parametric statistics", "Spatial Statistics", "Theoretical Machine Learning", which does not seem to belong to any of five communities listed above, but also we could identify the papers with combinations of two or three topics.
-Papers like "The Bayesian Lasso (T Park, et al.
-2008)", "Coordinate-independent sparse sufficient dimension reduction and variable selection (X Chen, et al.
-2010)" are the examples of these papers.
+Papers like "The Bayesian Lasso (T Park, et al. 2008)", "Coordinate-independent sparse sufficient dimension reduction and variable selection (X Chen, et al. 2010)" are the examples of these papers. 
 It is also interesting to think about a reason on papers which seem to have obvious membership in one of 5 communities other than Mixed topic classified as Mixed topic. 
-For instance, "On the "degrees of freedom" on the LASSO (H Zou, et al.
-2007)" is classified as Mixed Topic paper.
+For instance, "On the "degrees of freedom" on the LASSO (H Zou, et al. 2007)" is classified as Mixed Topic paper. 
 We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities. 
-Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics.
-\\
+Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics. \\
 
@@
 This is interesting since even though the dataset we consider is different from theirs, result is consistent. 
-They focus their attentions on analyzing {\it "weakly connected giant component"} for a citation network of each paper's authors ({\it i.e.
-each node is an author}).
+They focus their attentions on analyzing {\it "weakly connected giant component"} for a citation network of each paper's authors ({\it i.e. each node is an author}). 
 We consider the citation network of papers whose node degree is greater than or equal to 7.\\
@@
 $\it MulT$ paper briefly mention about $\it VarSel$ paper in future work section, suggesting a possible way of combining their work and work in $\it VarSel$ paper. 
-And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community.
-\\
+And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community. \\
 
@@
 on clustering results of k-means algorithm with different colors.}
-\label{fig:figure1}
+\label{fig:figure3}
 \end{figure}
@@
 Our analysis will focus on getting a non-asymptotic error bound of estimator in the context of where the sample size is fixed as 1, and the number of nodes is growing. 
-Readers can find more detailed descriptions on the differences between Chen et al.
-\cite{chen2016fused} and our model in terms of model formulation in Introduction section.
+Readers can find more detailed descriptions on the differences between Chen et al. \cite{chen2016fused} and our model in terms of model formulation in Introduction section. 
 We are interested in solving following optimization problem :
@@
 \]
-For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal. For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite.
+For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal. 
+For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite.
 \end{assumption}
@@
 
-\[
+\begin{equation}
+\label{eq:2}
 h(\hat{\Theta})-h(\Theta^{*}) \geq
@@
 + \frac{\tau}{2}\|\Delta_{\hat{\Theta}}\|_{F}^{2}
-\]
-
-Hence, we can rearrange the term in (\ref{eq:2}) as follows:
-
+\end{equation}
+Consequently, we can rearrange the term in (\ref{eq:2}) as follows:
 \begin{equation}\label{eq:3}
@@
 
-Here, we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers : 
+Here we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers :
 \[

### 2019-05-16 Manuscript for submission/manuscript.tex
Latest

@@
 
+One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, where
+\[
+\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \frac{n(n-1)}{2},
+\]
+and
+\[
+\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|,
+\]
+
+where $M$ is the current model,
+$\mathbb{L}_n( \hat{\beta}(M))$ is the maximal log-likelihood for a given model $M$,
+and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $S$ and the low-rank matrix $L$.
+If rank$(L)=K$, we can establish the following
+\[
+|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1
+\]
+Because the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors. 
+Additionally 1 in last is due to $\alpha$.
+We want to find a M which minimizes BIC($M$) or AIC($M$) as a function of M. 
+However these traditional methods seem to entail a serious problem. 
+The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
+Our experience shows that both BIC and AIC tend to choose the most parsimonious model with the smallest K and no ad-hoc dependency among all the estimated ($\hat{L}$,$\hat{S}$) with a pair of tuning parameters from given range of grid.
+We evaluate the model selected  
+with following three evaluation metrics.
+Table \ref{tab:table1}
+
 \begin{figure}[h]
@@
 \end{figure}
+
+\begin{table}[h]
+\centering
+\begin{tabular}{c|ccc|ccc|ccc}
+   & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\ \cline{2-10} 
+   & SC        & AIC    & BIC    & SC        & AIC    & BIC    & SC        & AIC    & BIC   \\ \hline
+M1 & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
+M2 & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
+M3 & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0    
+\end{tabular}
+\caption{}
+\label{tab:table1}
+\end{table}
 

### 2019-05-16 Manuscript for submission/manuscript.tex
latex work
latex work 3

@@
 \author[1]{Namjoon Suh*}
-
 \author[1]{Xiaoming Huo}
-
 \author[2]{Eric Heim}
-
 \author[2]{Timothy Van Slyke}
-
 \author[2]{Lee Seversky}
@@
 \jnlcitation{\cname{%
-\author{Williams K.},
-\author{B. Hoskins},
-\author{R. Lee},
-\author{G. Masato}, and
-\author{T. Woollings}} (\cyear{2016}),
-\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
+\author{Suh Namjoon.},
+\author{Xiaoming Huo},
+\author{Eric Heim},
+\author{Timothy Van Slyke}, and
+\author{Lee Seversky}} (\cyear{2019}),
+\ctitle{xxx}, \cjournal{journal.}, \cvol{2019;00:1--6}.}
 
@@
 
-\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
+\footnotetext{\textbf{Abbreviations:} fused factor analysis and logistic graphical models, ADMM, network model}
 
@@
 
-\item To ensure unique separation of $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that eigen-vector of $L$ is centered, that is,
+\item To ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that the eigen-vector of $L$ is centered, that is,
 \[
-    JLJ = L \quad where \quad
-    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T
+    JLJ = L \quad \mbox{where} \quad
+    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T. 
 \]
@@
 \label{eq:logistic10}
-(\hat{\alpha}, \hat{L}, \hat{S})
+(\hat{\alpha}, \widehat{L}, \widehat{S})
 = \mbox{arg min}_{\alpha, L, S} \left\{
@@
 
-After we have obtained $\hat{S}$ in \eqref{eq:logistic10}, we can uncover the graphical model by investigating non-zero entries in $\hat{S}$.
-On the other hand when we have calculated $\hat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\hat{L} = F^T D F.$
+After we have obtained $\widehat{S}$ in \eqref{eq:logistic10}, we can uncover the graphical model by investigating non-zero entries in $\widehat{S}$.
+On the other hand when we have calculated $\widehat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\widehat{L} = F^T D F.$
 This is the price we have to pay for an amenable computational problem.
-The rank of estimated $\hat{L}$ will be our estimate of the number of factors (i.e., underlying common topics). 
+The rank of estimated $\widehat{L}$ will be our estimate of the number of factors (i.e., underlying common topics).
 For the issue on assigning the community membership of each node $i$, we will discuss this later in Section 6.
@@
 \subsection{Synthetic data}
-\textbf{Data Generation} Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P_{ij}=\frac{\exp (
+\textbf{Data Generation}. 
+Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P_{ij}=\frac{\exp (
 \alpha+F_{i}^{T}DF_{j} +  S_{ij})}{1+\exp(\alpha+F_{i}^{T}DF_{j}+S_{ij})}$.
@@
 $F^{T}$ binary matrix has $\floor{\frac{n}{K}}$ ones in each columns, and has exactly one 1 in each rows.
-We randomly choose one of rows, fill that row with ones, and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying $I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$.
-Diagonal elements of $D$ are generated from $unif[7,8]$, and alpha is generated from $unif[-3,-2]$. 
-We set $K=3,4,5$, $n=30,80,120$, and $nnz = 10, 20, 40$, where $nnz$ denotes number of non-zero component of upper-triangular part of S.\\
+We randomly choose one of rows, fill that row with ones, and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying the aforementioned $J = I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$.
+Diagonal elements of $D$ are generated from Unif$[7,8]$ (uniform distribution on $[7,8]$), and alpha is generated from Unif$[-3,-2]$.
+We set $K=3,4,5$, $n=30,80,120$, and $nnz = 10, 20, 40$, where $nnz$ denotes number of non-zero component of the upper-triangular part of S.
 
-\noindent \textbf{Choosing tuning parameter}
-We have to admit the fact that choosing good tuning parameter is an important but challenging issue in our problem.
-In our problem where the observation can be seen as one realization of random graph, it is confusing whether to define the total number of observations as $N=\frac{n(n-1)}{2}$ or 1, since in usual BIC definition, we define effective sample size "n", when we have n i.i.d.
+\textbf{Choosing the tuning parameters}.
+We have to admit the fact that choosing a good tuning parameter is an important but challenging issue in our problem.
+In our problem where the observation can be seen as one realization of random graph, it is confusing whether to define the total number of observations as $N=\frac{n(n-1)}{2}$ or 1, since in usual BIC definition, we define effective sample size ``$n$,'' when we have $n$ i.i.d.
 observations.
-Our experience shows that both BIC and AIC tend to choose the model with smallest K and no ad-hoc dependency. 
+Our experience shows that both BIC and AIC tend to choose the model with smallest $K$ and no ad-hoc dependency.
 As an alternative, we choose a purely heuristic approach.
-Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest 20 eigenvalues of adjacency matrix X, which can tell us the numbers of communities embedded in network. 
-Then, we record the rank of L and number of non-zero elements in S for each tuning parameter pair on grid, and choose proper pair of tuning parameters which can give us interesting interpretation of data.
-\\
+Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of adjacency matrix $X$, which can tell us the numbers of communities embedded in network.
+Then, we record the rank of $L$ and number of non-zero elements in S for each tuning parameter pair on grid, and choose proper pair of tuning parameters which can give us interesting interpretation of data.
 
@@
 \]
-
 where $M$ is the current model,
@@
 Because the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
-Additionally 1 in last is due to $\alpha$.
-We want to find a M which minimizes BIC($M$) or AIC($M$) as a function of M. 
+Additionally $1$ in the last is due to $\alpha$.
+We want to find an $M$ which minimizes BIC($M$) or AIC($M$) as a function of M.
 However these traditional methods seem to entail a serious problem.
 The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
-Our experience shows that both BIC and AIC tend to choose the most parsimonious model with the smallest K and no ad-hoc dependency among all the estimated ($\hat{L}$,$\hat{S}$) with a pair of tuning parameters from given range of grid.
+Our experience shows that both BIC and AIC tend to choose the most parsimonious model with the smallest K and no ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$) with a pair of tuning parameters from given range of grid.
 We evaluate the model selected
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
 \includegraphics[width=1\textwidth]{Fig1.pdf}
-\caption{\it After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\hat{L}$ matrix.
+\caption{\it After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\widehat{L}$ matrix.
 (Different color represents different clusters of nodes $k$-means assign for three synthetic settings.) }
@@
 \end{tabular}
-\caption{}
+\caption{xxx}
 \label{tab:table1}
@@
 
-\noindent \textbf{Community memberships of each nodes} Given a network data, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$.
+\textbf{Community memberships of each nodes}. 
+Given a network data, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$.
 We applied a simple $k$-means clustering on the fitted $L$ matrix's first $K$ eigenvectors.
 Furthermore, we find one interesting phenomenon.
-Coordinates of each rows from first two eigenvectors of estimated $\hat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well. 
-Our experience shows that with only first two eigenvectors of $\hat{L}$, we can also cluster the nodes comparably well. \\
+Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
+Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
 
-\noindent \textbf{Ad-hoc links} Ad-hoc links of synthetic network data can be thought of as $"$across edges$"$ between clusters of nodes. 
+\textbf{Ad-hoc links}. 
+Ad-hoc links of synthetic network data can be thought of as ``across edges'' between clusters of nodes.
 Since indices of non-zero entries of $S$ are randomly chosen, there might be some indices of non-zero $S_{ij}$ entries where $L_{ij}$ is also non-zero.
@@
 Some of ``across edges" are also attributed to $\alpha$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha$ or $S_{ij}$.
-So the total number of across edges might not be exactly same as we set in our data generation setting. \\
+So the total number of across edges might not be exactly same as we set in our data generation setting.
 
-\noindent \textbf{Simulation Results} Our goal in this simulation experiment is to check if our model can cluster each nodes into correct communities. 
+\textbf{Simulation Results}. 
+Our goal in this simulation experiment is to check if our model can cluster each nodes into correct communities.
 Also to see if it can separate the ad-hoc links from edges which come from common topics.
-Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$ respectively, give us the desirable results for 3 cases. 
+Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$, respectively, give us the desirable results for the three cases.
 Note that different dynamics of network requires different choices of tuning parameters even the synthetic setting is same, since we are generating the random graph.
 However, we set the seeds in our simulation so that the results are reproducible.
-$Fig1$ shows us the result of clustered nodes using $k$-means algorithm on first $K(=rank(\hat{L}))$ eigenvectors. 
-We plot the rows of first two eigenvectors on plane since it tends to visualize well the clustering behavior of nodes. 
-Our model chooses well the ad-hoc links between clusters of nodes as can be verified in $Fig2$. 
-We color the edges in blue whose corresponding elements of estimated $\hat{S}$ are non-zero, and black whose corresponding entries of $\hat{S}$ are zero.
+Fig. \ref{fig:figure1} shows us the result of clustered nodes using the $k$-means algorithm on the first $K(=\mbox{rank}(\widehat{L}))$ eigenvectors.
+We plot the rows of first two eigenvectors on the cartesian plane since it visualizes well the clustering behavior of the nodes.
+Our model chooses well the ad-hoc links between clusters of nodes as can be verified in Fig. \ref{fig:figure2}.
+We color the edges in blue whose corresponding elements of estimated $\widehat{S}$ are non-zero, and black whose corresponding entries of $\widehat{S}$ are zero.
 
-\begin{figure}[b]
+\begin{figure}[htbp]
 \begin{center}
 \includegraphics[scale=0.75]{Fig2.pdf}
-\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\hat{S}$ matrix. 
+\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\widehat{S}$ matrix.
 For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
+\label{fig:figure2}
 \end{center}
-\label{fig:figure2}
 \end{figure}
@@
 
-\noindent $(\gamma,\delta) = (0.000912,0.0097)$ gives us $\hat{L}$ with rank 3, and $\hat{S}$ with $|supp(\hat{S})|=197$. 
-We apply $k$-means algorithm on 3 eigenvectors of estimated $\hat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\hat{L}$ on plane in $Fig 4$. 
+\noindent $(\gamma,\delta) = (0.000912,0.0097)$ gives us $\widehat{L}$ with rank 3, and $\widehat{S}$ with $|supp(\widehat{S})|=197$.
+We apply $k$-means algorithm on 3 eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in $Fig 4$xxxx.
 404 papers colored in green are densely clustered nearby the origin with a short tail, $(Fig 4)$, and $k$-means classifies these papers as third topic.
@@
 \begin{itemize}
-  \item "Variable selection (85 papers)"
+  \item "Variable selection (85 papers)" xxxxx
   \item "Multiple Hypothesis Testing (54 papers)"
@@
 
-\begin{figure}[b]
+\begin{figure}[htbp]
 \includegraphics[width=1\textwidth]{Fig4.eps}
@@
 
-\noindent Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction". 
-Due to small volume of each communities, we could check that false discoveries for each community are all zero.\\
+Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction".
+Due to small volume of each communities, we could check that false discoveries for each community are all zero.
 
-\noindent Sub-network structure has also a big chunk of papers which we refer to as "Mixed Topics". 
+Sub-network structure has also a big chunk of papers which we refer to as "Mixed Topics".
 Not only could we see the papers with topics on "Learning Theory", "Non-parametric/semi-parametric statistics", "Spatial Statistics", "Theoretical Machine Learning", which does not seem to belong to any of five communities listed above, but also we could identify the papers with combinations of two or three topics.
-Papers like "The Bayesian Lasso (T Park, et al. 2008)", "Coordinate-independent sparse sufficient dimension reduction and variable selection (X Chen, et al. 2010)" are the examples of these papers. 
-It is also interesting to think about a reason on papers which seem to have obvious membership in one of 5 communities other than Mixed topic classified as Mixed topic. 
-For instance, "On the "degrees of freedom" on the LASSO (H Zou, et al. 2007)" is classified as Mixed Topic paper. 
+Papers like "The Bayesian Lasso (T. Park, et al. 2008)", "Coordinate-independent sparse sufficient dimension reduction and variable selection (X. Chen, et al. 2010)" are the examples of these papers.
+It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed topic classified as Mixed topic.
+For instance, "On the "degrees of freedom" on the LASSO (H. Zou, et al. 2007)" is classified as Mixed Topic paper.
 We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities.
-Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics. \\
+Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics.
 
-\noindent It is worth to note that our result is consistent with that from Ji and Jin in a sense that they also recover "Multiple Testing", "Variable selection" and "non-parametric Bayesian statistics".
+It is worth to note that our result is consistent with that from Ji and Jin in a sense that they also recover "Multiple Testing", "Variable selection" and "non-parametric Bayesian statistics".
 This is interesting since even though the dataset we consider is different from theirs, result is consistent.
-They focus their attentions on analyzing {\it "weakly connected giant component"} for a citation network of each paper's authors ({\it i.e. each node is an author}). 
-We consider the citation network of papers whose node degree is greater than or equal to 7.\\
+They focus their attentions on analyzing {\it "weakly connected giant component"} for a citation network of each paper's authors ({i.e., each node is an author}).
+We consider the citation network of papers whose node degree is greater than or equal to 7.
 
-\noindent\textbf{Ad-hoc links} Non-zero components of $\hat{S}$ capture the citation relationships among papers that are not attributable to the common topics. 
+\textbf{Ad-hoc links}. 
+Non-zero components of $\widehat{S}$ capture the citation relationships among papers that are not attributable to the common topics.
 The model we select has 197 sparse edges (9\% of total edges), and all of them are positive edges.
@@
 All the 15 edges come from pairs of papers from different communities.
-For instance, the first pair of papers comes from Functional Analysis $(\it FuncAn)$ community and Variable selection $(\it VarSel)$ community. 
+For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable selection $(\it VarSel)$ community. xxxx 
 $\it FuncAn$ paper cites $\it VarSel$ paper for borrowing a mathematical representation to build a theorem.
@@
 $\it MulT$ paper briefly mention about $\it VarSel$ paper in future work section, suggesting a possible way of combining their work and work in $\it VarSel$ paper.
-And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community. \\
+And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community.
 
-\begin{figure}[!t]
+\begin{figure}[htbp]
 \includegraphics[width=1\textwidth]{Fig3.eps}
-\caption{Illustration of first two eigenvectors of estimated $\hat{L}$ matrix for original
+\caption{Illustration of first two eigenvectors of estimated $\widehat{L}$ matrix for original
 citation network with 543 papers(left) and sub-network graph(right). Presentation
@@
 Rather, this formulation allows us to simplify the theoretical investigation in a direction to which we want to pursue \cite{ma2017exploration}.
-Let ($\hat{\alpha},\hat{L},\hat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process. 
-Let $\hat{\Theta},\Theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
+Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process.
+Let $\hat{\Theta},\Theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
 And denote the error term for each parameter as $\hat{\Delta}^{\Theta} = \hat{\Theta}-\Theta^{*},
 \hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
-\hat{\Delta}^L = \hat{L}-L^{*},
-\hat{\Delta}^S = \hat{S}-S^{*}.$
+\hat{\Delta}^L = \widehat{L}-L^{*},
+\hat{\Delta}^S = \widehat{S}-S^{*}.$
 Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
@@
 \[
-    e^{2}(\hat{\alpha}.\hat{L},\hat{S}):=\|\alpha^{*}-\hat{\alpha}\|_{F}^{2} + \|L^{*}-\hat{L}\|_{F}^{2} + \|S^{*}-\hat{S}\|_{F}^{2}
+    e^{2}(\hat{\alpha}.\widehat{L},\widehat{S}):=\|\alpha^{*}-\hat{\alpha}\|_{F}^{2} + \|L^{*}-\widehat{L}\|_{F}^{2} + \|S^{*}-\widehat{S}\|_{F}^{2}
 \]
@@
 \end{align}
-There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, where $k = rank(L^{*}), s= |supp(S^{*})|$, we have following upper bound on $e^{2}(\hat{\alpha}.\hat{L},\hat{S})$
+There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, where $k = rank(L^{*}), s= |supp(S^{*})|$, we have following upper bound on $e^{2}(\hat{\alpha}.\widehat{L},\widehat{S})$
 \begin{align}
-    e^{2}(\hat{\alpha},\hat{L},\hat{S}) \leq
+    e^{2}(\hat{\alpha},\widehat{L},\widehat{S}) \leq
     c_{1}\frac{\delta^{2}}{\tau^{2}} +
@@
     + \delta \|L^{*}\|_\ast + \gamma \|S^{*}\|_1
-    - \delta \|\hat{L}\|_\ast - \gamma \|\hat{S}\|_1
+    - \delta \|\widehat{L}\|_\ast - \gamma \|\widehat{S}\|_1
 \end{equation}
@@
     &\leq \|\hat{\Delta}^{L}\|_{\infty} \|\hat{\Delta}^{S}\|_1\\
-    &\leq (\|\hat{L}\|_{\infty} + \|L^{*}\|_{\infty})
+    &\leq (\|\widehat{L}\|_{\infty} + \|L^{*}\|_{\infty})
     \|\hat{\Delta}^{S} \|_{1}\\
@@
 
-\nocite{*}
+%\nocite{*}
 \bibliography{References}%

### 2019-06-24 Manuscript for submission/manuscript.tex
Update-June.24.
Revise some part on theorem,
add additional experiment in numerical experiment part

@@
 
-\textbf{Choosing the tuning parameters}.
-We have to admit the fact that choosing a good tuning parameter is an important but challenging issue in our problem.
-In our problem where the observation can be seen as one realization of random graph, it is confusing whether to define the total number of observations as $N=\frac{n(n-1)}{2}$ or 1, since in usual BIC definition, we define effective sample size ``$n$,'' when we have $n$ i.i.d.
-observations.
-Our experience shows that both BIC and AIC tend to choose the model with smallest $K$ and no ad-hoc dependency.
-As an alternative, we choose a purely heuristic approach.
-Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of adjacency matrix $X$, which can tell us the numbers of communities embedded in network.
-Then, we record the rank of $L$ and number of non-zero elements in S for each tuning parameter pair on grid, and choose proper pair of tuning parameters which can give us interesting interpretation of data.
+\textbf{Choosing the tuning parameters and evaluation criteria}.
+We have to admit the fact that choosing a good pair of tuning parameter is an important but challenging issue in our problem.
+We here present a purely heuristic approach.
+Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest 20 eigenvalues of adjacency matrix $X$, which can tell us the numbers of communities embedded in network.
+Then, we record the rank of L and number of non-zero elements in S for each tuning parameter pair on grid, and choose a proper pair which can give us interesting interpretation of data.
 
-One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, where
+One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, work where
 \[
-\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \frac{n(n-1)}{2},
+\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \bigg(\frac{n(n-1)}{2}\bigg),
 \]
@@
 \]
-Because the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
-Additionally $1$ in the last is due to $\alpha$.
-We want to find an $M$ which minimizes BIC($M$) or AIC($M$) as a function of M.
-However these traditional methods seem to entail a serious problem.
-The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
-Our experience shows that both BIC and AIC tend to choose the most parsimonious model with the smallest K and no ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$) with a pair of tuning parameters from given range of grid.
-We evaluate the model selected
-with following three evaluation metrics.
-Table \ref{tab:table1}
 
@@
 \includegraphics[width=1\textwidth]{Fig1.pdf}
-\caption{\it After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\widehat{L}$ matrix.
+\caption{After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\widehat{L}$ matrix.
 (Different color represents different clusters of nodes $k$-means assign for three synthetic settings.) }
@@
 
-\begin{table}[h]
+Because the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
+Additionally $1$ in the last is due to $\alpha$.
+We want to find an $M$ which minimizes BIC($M$) or AIC($M$) as a function of $M$.
+However these traditional methods seem to entail a serious problem.
+The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
+Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest K and smallest cardinality of ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$) from a pair of tuning parameters over the given range of grid.
+We evaluate the models selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.
+
+\begin{eqnarray*}
+M1 &=& \mathbbm{1}\big\{rank(\widehat{L}) = rank(L^{*})\big\} \\
+M2 &=& \frac{|\big\{(i,j):i<j:S^{*}_{i,j} \neq0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}|}{|\big\{(i,j):i<j:S^{*}_{i,j}\neq0\big\}|} \\
+M3 &=& \frac{|\big\{(i,j):i<j:S^{*}_{i,j} = 0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}|}{|\big\{(i,j):i<j:S^{*}_{i,j}=0\big\}|}
+\end{eqnarray*}
+
+$M1$ is a metric on whether selected model recovers true low rank structure of network,
+$M2$ evaluates the positive selection rate of sparse network structure,
+and lastly $M3$ evaluates the false discovery rate.
+With properly selected tuning parameter, $M1$ will be 1, $M2$ will be close to 1, and $M3$ will get close to 0.
+Evaluated results of models selected via three criteria are presented in Table 1.
+
+\begin{table}[htbp]
 \centering
@@
    & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\ \cline{2-10}
-   & SC        & AIC    & BIC    & SC        & AIC    & BIC    & SC        & AIC    & BIC   \\ \hline
-M1 & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
-M2 & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
-M3 & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0
+   & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC   \\ \hline
+$M1$ & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
+$M2$ & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
+$M3$ & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0
 \end{tabular}
-\caption{xxx}
+\caption{ Both AIC and BIC choose the model $\widehat{S}=0$ with no ad-hoc structure, and $\widehat{L}$ with the lowest rank among all estimators via a pair of tuning parameter over the grid of search region.
+Our heuristic method correctly choose the model with $\widehat{L}$ with true rank and $\widehat{S}=0$ catching all the ''across edges'' of network.
+Note that }
 \label{tab:table1}
@@
 \textbf{Community memberships of each nodes}.
-Given a network data, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$.
+Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$.
 We applied a simple $k$-means clustering on the fitted $L$ matrix's first $K$ eigenvectors.
@@
 \includegraphics[scale=0.75]{Fig2.pdf}
-\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\widehat{S}$ matrix.
+\caption{Edges colored with blue correspond to non-zero entries of estimated $\widehat{S}$ matrix.
 For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
@@
 
-\subsection{Citation and Co-authorship networks for statisticians }
+\subsection{Citation networks for statisticians }
 Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting data set on citation  and co-authorship networks of statisticians.
@@
 \noindent $(\gamma,\delta) = (0.000912,0.0097)$ gives us $\widehat{L}$ with rank 3, and $\widehat{S}$ with $|supp(\widehat{S})|=197$.
-We apply $k$-means algorithm on 3 eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in $Fig 4$xxxx.
+We apply $k$-means algorithm on 3 eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in $Fig 4$.
 404 papers colored in green are densely clustered nearby the origin with a short tail, $(Fig 4)$, and $k$-means classifies these papers as third topic.
 We list the first two topics discovered through our analysis.
-(Full lists of papers for each communities are provided in $\it https://sites.google.com/site/namjoonsuh/publications$)
+(Full lists of papers for each communities are provided in ($\emph{https://sites.google.com/site/namjoonsuh/publications}$)
 
 \begin{itemize}
-  \item "Variable selection (85 papers)" xxxxx
-  \item "Multiple Hypothesis Testing (54 papers)"
+  \item Variable selection (85 papers)
+  \item Multiple Hypothesis Testing (54 papers)
 \end{itemize}
@@
 \begin{itemize}
-  \item "Non-parametric Bayesian Statistics (17 papers)"
-  \item "Functional Data analysis (35 papers)"
-  \item "Dimension Reduction (23 papers)"
-  \item "Mixed topics (329 papers)"
+  \item Non-parametric Bayesian Statistics (17 papers)
+  \item Functional Data analysis (35 papers)
+  \item Dimension Reduction (23 papers)
+  \item Mixed topics (329 papers)
 \end{itemize}
@@
 This is interesting since even though the dataset we consider is different from theirs, result is consistent.
-They focus their attentions on analyzing {\it "weakly connected giant component"} for a citation network of each paper's authors ({i.e., each node is an author}).
+They focus their attentions on analyzing \emph{"weakly connected giant component"} for a citation network of each paper's authors ({i.e., each node is an author}).
 We consider the citation network of papers whose node degree is greater than or equal to 7.
@@
 All the 15 edges come from pairs of papers from different communities.
-For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable selection $(\it VarSel)$ community. xxxx 
-$\it FuncAn$ paper cites $\it VarSel$ paper for borrowing a mathematical representation to build a theorem.
+For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable selection $(\emph{VarSel})$ community. 
+$\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
 Though it might seem to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
-Second pair comes from $\it MulT$  and $\it VarSel$ community.
-$\it MulT$ paper briefly mention about $\it VarSel$ paper in future work section, suggesting a possible way of combining their work and work in $\it VarSel$ paper.
+Second pair comes from $\emph{MulT}$  and $\emph{VarSel}$ community.
+$\emph{MulT}$ paper briefly mention about $\emph{VarSel}$ paper in future work section, suggesting a possible way of combining their work and work in $\emph{VarSel}$ paper.
 And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community.
@@
 \section{ On non-asymptotic error bound of the estimator }
-Chen et al.\cite{chen2016fused} show that their estimator recovers the algebraic structure, that is, the conditional graph structure and the number of latent variables, with probability tending to one.
-However, their analysis only allows a growing number of sample points whereas they keep the number of variables fixed.
-Their result thus severs from the tradition to analyze the more challenging high-dimensional setting, where the number of variables is also explicitly tracked.
-Our analysis will focus on getting a non-asymptotic error bound of estimator in the context of where the sample size is fixed as 1, and the number of nodes is growing.
-Readers can find more detailed descriptions on the differences between Chen et al. \cite{chen2016fused} and our model in terms of model formulation in Introduction section.
+In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the sample size is fixed as 1, and the number of variables in model is explicitly tracked.
 We are interested in solving following optimization problem :
@@
 
+Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process.
+Let $\widehat{\Theta},\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
+And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*}, 
+\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
+\widehat{\Delta}^L = \widehat{L}-L^{*},
+\widehat{\Delta}^S = \widehat{S}-S^{*}.$
+Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
 Astute readers might notice the slight difference of first term in objective function between (\ref{eq:logistic10})
 and (\ref{eq:1}). 
-(\ref{eq:1}) sums over the all $(i,j)$ pairs.
-Due to the symmetry of $X$ and $\Theta=\alpha\mathbbm{1}\mathbbm{1}^T+L+S$, after scaling, the only difference lies in the inclusion of diagonal term of $\Theta$.
-It should be noted that this slight modification neither leads to theoretical consequences nor noticeable difference in practice.
-Rather, this formulation allows us to simplify the theoretical investigation in a direction to which we want to pursue \cite{ma2017exploration}.
-Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process.
-Let $\hat{\Theta},\Theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
-And denote the error term for each parameter as $\hat{\Delta}^{\Theta} = \hat{\Theta}-\Theta^{*},
-\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
-\hat{\Delta}^L = \widehat{L}-L^{*},
-\hat{\Delta}^S = \widehat{S}-S^{*}.$
-Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
-We impose following assumptions for theoretical guarantees.
+Justification of this modification is well explained in \emph{remark 3.1} of the paper \cite{ma2017exploration}. 
+We further impose several assumptions for theoretical guarantees of our estimator.
 
-\begin{assumption} (\textbf{Strong convexity})
+\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
 For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):
@@
 \]
-For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal.
-For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite.
+For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal. For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite.
 \end{assumption}
 
-\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L})
+\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
 To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
 We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
-We would also note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
+We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
 \end{assumption}
@@
 With these assumptions we present the behavior of non-asymptotic error bound of our estimator through following theorem.
-In our result, we measure error using the squared Frobenius norm summed across both matrices:
+In our result, we measure error using squared Frobenius norm summed across three matrices:
 \[
-    e^{2}(\hat{\alpha}.\widehat{L},\widehat{S}):=\|\alpha^{*}-\hat{\alpha}\|_{F}^{2} + \|L^{*}-\widehat{L}\|_{F}^{2} + \|S^{*}-\widehat{S}\|_{F}^{2}
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\widehat{\Delta}^{\alpha\mathbbm{1}\mathbbm{1}^T}\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
 \]
@@
 \begin{theorem}
-Under the assumptions (4.1) and (4.2),
+Under the assumptions \ref{Ass:1} and \ref{Ass:2},
 if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying 
 \begin{align}
-\delta \geq 4\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 4\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
+\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
 \end{align}
-There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, where $k = rank(L^{*}), s= |supp(S^{*})|$, we have following upper bound on $e^{2}(\hat{\alpha}.\widehat{L},\widehat{S})$
+There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
 \begin{align}
-    e^{2}(\hat{\alpha},\widehat{L},\widehat{S}) \leq
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
     c_{1}\frac{\delta^{2}}{\tau^{2}} +
@@
     c_{3}\frac{\gamma^{2}}{\tau^{2}}
-    \bigg\{s + \frac{\tau}{\gamma}\|S^*_{M^\perp}\|_{1}\bigg\}
+    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin \mathbb{M}}|S^*_{ij}|\bigg\}
 \end{align}
+where $\mathbb{M}$ is an arbitrary subset of matrix indices of cardinality at most s.
 \end{theorem}
@@
 \begin{proof}
-Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on term $h(\hat{\Theta})-h(\Theta^{*})$ :
+Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal and feasible (respectively) for the convex program (\ref{eq:1}), we have
+\begin{equation}\label{eq:2}
+    h(\widehat{\Theta}) + \delta\|\widehat{L}\|_{*} + \gamma\|\widehat{S}\|_{1} \leq  
+     h(\Theta^{*}) + \delta\|{L^{*}}\|_{*} + \gamma\|{S}^{*}\|_{1}
+\end{equation}
 
-\begin{equation}
-\label{eq:2}
-h(\hat{\Theta})-h(\Theta^{*}) \geq
-\langle\, \nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*}\rangle\
-+ \frac{\tau}{2}\|\Delta_{\hat{\Theta}}\|_{F}^{2}
-\end{equation}
-Consequently, we can rearrange the term in (\ref{eq:2}) as follows:
+Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on term $h(\widehat{\Theta})-h(\Theta^{*})$ :
+\[
+h(\widehat{\Theta})-h(\Theta^{*}) \geq 
+\langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ + \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}
+\]
+
+By rearranging the term in (\ref{eq:2}) and plugging in above inequality relation, we get:
+
 \begin{equation}\label{eq:3}
-    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*}\rangle\
+    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq 
+    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
     + \delta \|L^{*}\|_\ast + \gamma \|S^{*}\|_1 
@@
 
-Here we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers :
+Here, we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers : 
 \[
@@
 \begin{equation}\label{eq:4}
-    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*}\rangle\
-    + \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\hat{\Delta}^L + L^{*},\hat{\Delta}^S + S^{*})
+    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq 
+    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
+    + \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
 \end{equation}
@@
 According to Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1, 
-the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\hat{\Delta}^L + L^{*},\hat{\Delta}^S + S^{*})$ is upper-bounded by
+the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ is upper-bounded by
 
 \begin{equation}\label{eq:5}
-    \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) - \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^\perp})
+    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
     +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
@@
 
-Here we define $S^{*}$ to be decomposable with respect to the pair of subspace $(\mathbb{M},\mathbb{M}^{\perp})$, and let $L^{*}$ be decomposable with respect to the pair of subspace $(\mathbb{A},\mathbb{B})$.
-
-The decomposability of elementwise $\ell 1$ norm and nuclear norm with respect to a properly chosen pair of subspace is studied at length in the paper [1].
-We briefly mention the concept of decomposability here for clarification:
-
-For arbitrary subset $S \subseteq \{1,2,..,n\} \times \{1,2,..,n\}$ of matrices indices, consider the subspace pair
-\[
-    \mathbb{M}(S) := \{U\in R^{n \times n} | U_{ij} = 0, \forall (i,j) \not\in S \}
-\]
-and $\mathbb{M}^\perp(S)$.
-It is easy to verify that any pair of matrices $U\in \mathbb{M}(S)$ and $U' \in \mathbb{M}^\perp(S)$ in elementwise $\ell 1$ norm is decomposable in a sense that $\|U+U'\|_1 = \|U\|_1 + \|U'\|_1$.
-Similarly, in nuclear norm, if we define a pair of subspace $(\mathbb{A},\mathbb{B})$ for any matrix $L \in R^{n \times n}$, whose eigen decomposition is $UDV^{T}$, as follows:
-\begin{align*}
-    \mathbb{A}(L) := \{\Theta \in R^{n \times n} | row(\Theta) \subseteq V, col(\Theta) \subseteq U \} \\
-    \mathbb{B}(L) := \{\Theta \in R^{n \times n} | row(\Theta) \subseteq V^{\perp}, col(\Theta) \subseteq U^{\perp} \}
-\end{align*}
-For any pair of matrices, $U\in \mathbb{A}(L)$ and $U' \in \mathbb{B}(L)$, it is also easy to check that $\|U+U'\|_\ast = \|U\|_\ast+\|U'\|_\ast$.
-
-First, we want to control upper bound of the term $-\langle\,\nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*} \rangle\$$
+First, we want to control upper bound of the term $-\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\,$
 in (\ref{eq:4}).
 \begin{align}
--\langle\,\nabla_{\Theta}h(\Theta^{*}),\hat{\Theta}-\Theta^{*} \rangle\
-&=\langle\, \frac{1}{2n} (X - P), \hat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \hat\Delta^{L} + \hat\Delta^{S} \rangle\ \\
-&\leq \frac{1}{2n} \|X - P\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\hat{\Delta}^{L}\|_\ast) +  \frac{1}{2n} \|X - P\|_{\infty}\|\hat{\Delta}^{S}\|_{1} \\
-&\leq \frac{1}{2n} \|X - P\|_{op}(\|\hat{\Delta}^{\alpha}\|_{F} + \|\hat{\Delta}^{L}_{A}\|_\ast + \|\hat{\Delta}^{L}_{B}\|_\ast) +
-\frac{1}{2n} \|X - P\|_{\infty}(\|\hat{\Delta}^{S}_{M}\|_{1} +
+-\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\  \nonumber
+&=\langle\, \frac{1}{n} (X - P), \widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S} \rangle\ \\ \nonumber
+&\leq \frac{1}{n} \|X - P\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
+&\leq \frac{1}{n} \|X - P\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) +
+\frac{1}{n} \|X - P\|_{\infty}(\|\widehat{\Delta}^{S}_{M}\|_{1} + 
+\|\widehat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\ \nonumber
+&\leq \frac{\delta}{2}(n\|\hat{\Delta}^{\alpha}\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) + \frac{\gamma}{2}(\|\widehat{\Delta}^{S}_{M}\|_{1} + 
 \|\hat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\ 
-&\leq \frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\|_{F} + \|\hat{\Delta}^{L}_{A}\|_\ast + \|\hat{\Delta}^{L}_{B}\|_\ast) + \frac{\gamma}{2}(\|\hat{\Delta}^{S}_{M}\|_{1} +
-\|\hat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\
-&= \frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\|_{F} +     \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^\perp}) ) \label{eq:10}
+&= \frac{\delta}{2}n\|\hat{\Delta}^{\alpha}\|_{F} +     \frac{\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \frac{\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^\perp})  \label{eq:10}
 \end{align}
@@
 \begin{equation}
-    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F} +
-    \frac{3\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M})
+    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
+    \frac{\delta}{2}n\|\hat{\Delta}^{\alpha}\|_{F} + 
+    \frac{3\delta}{2}\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M})
     +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\gamma \|S^*_{M^\perp}\|_{1}
@@
 \begin{align}
-\|\hat{\Delta}^{\Theta}\|_{F}^{2}
-&= \|\hat{\Theta}-\Theta^{*} \|_{F}^{2} \\
-&= \|\hat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \hat\Delta^{L} + \hat\Delta^{S}\|_{F}^{2} \\
-&= \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\hat{\Delta}^{L}+\hat{\Delta}^{S}\|_{F}^{2} +
-2 \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ \\
-&=  \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\hat{\Delta}^{L}\|_{F}^{2} + \|\hat{\Delta}^{S}\|_{F}^{2} +
-2 \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
-2 \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ \\
-&\geq \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \|\hat{\Delta}^{L}\|_{F}^{2} + \|\hat{\Delta}^{S}\|_{F}^{2} +
-2 \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
-2 \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\
+\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
+&= \|\widehat{\Theta}-\Theta^{*} \|_{F}^{2} \\ \nonumber
+&= \|\widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S}\|_{F}^{2} \\ \nonumber
+&= \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}+\widehat{\Delta}^{S}\|_{F}^{2} + 
+2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ \\ \nonumber
+&=  \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2} + 
+2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
+2 \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ \\ 
+&= n^{2}\|\hat{\Delta}^{\alpha}\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2} + 
+2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
+2 \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ \label{eq:12}
 \end{align}
 
-To get the further lower bound on trace inner product terms,
-$ \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ $, we use a definition of dual norm, and the assumption...,
+We want to get the further lower bound on trace inner product terms, 
+$ \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $.
+To control the first trace inner product term, we use the relation $\widehat{\Delta}^{L}\mathbbm{1}=0$, apply the definition of dual norm on inner product term, triangular inequality on $\hat{\Delta}^\alpha$, and lastly we apply the constraint imposed on $|\alpha|$ stated in Assumption \ref{Ass:2}.
+
 \begin{align}
-    | \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ |
-    &= | \langle\,\hat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\
-    &\leq \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\hat{\Delta}^{S}\|_1 \\
-    &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\hat{\Delta}^{S}\|_1\\
-    &\leq 2C\kappa\|\hat{\Delta}^{S}\|_1
+    | \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \nonumber
+    &= | \langle\,\widehat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\ \nonumber
+    &\leq \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\widehat{\Delta}^{S}\|_1 \\ \nonumber
+    &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\widehat{\Delta}^{S}\|_1\\ 
+    &\leq 2C\kappa\|\widehat{\Delta}^{S}\|_1  \label{eq:13}
 \end{align}
 
+To control the term $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $, we first apply the definition of dual norm on trace inner product term, then apply triangular inequality on $\widehat{\Delta}^{L}$ and spikiness condition.
+
 \begin{align}
-    | \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ |
-    &\leq \|\hat{\Delta}^{L}\|_{\infty} \|\hat{\Delta}^{S}\|_1\\
+    | \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ | \nonumber
+    &\leq \|\widehat{\Delta}^{L}\|_{\infty} \|\widehat{\Delta}^{S}\|_1\\ \nonumber
     &\leq (\|\widehat{L}\|_{\infty} + \|L^{*}\|_{\infty})
-    \|\hat{\Delta}^{S} \|_{1}\\
-    &\leq \big(\frac{2\kappa}{n}\big)\|\hat{\Delta}^{S} \|_{1}
+    \|\widehat{\Delta}^{S} \|_{1}\\
+    &\leq \big(\frac{2\kappa}{n}\big)\|\widehat{\Delta}^{S} \|_{1} \label{eq:14}
 \end{align}
 
+We can combine the inequality (\ref{eq:12}), (\ref{eq:13}) and (\ref{eq:14}).
+Then applying the assumption on regularization parameter $\gamma$, and the fact $\|\widehat{\Delta}^{L}\|_{\ast}\geq0$ sequentially, we can get,
+
 \begin{align}
-    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2}
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2}
-    - 2\kappa\tau(\frac{Cn+1}{n})\|\hat{\Delta}^{S}\|_{1} \\
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\hat{\Delta}^{S}\|_{1}\\
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S) \label{eq:26}
+    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
+    &\geq \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} 
+    - 2\kappa\tau(\frac{Cn+1}{n})\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
+    &\geq \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\widehat{\Delta}^{S}\|_{1}\\
+    &\geq \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S) \label{eq:26}
 \end{align}
 
-By combining the relations (\ref{eq:11}) and (\ref{eq:26}), we can get following inequality,
+By combining the relations (\ref{eq:11}) and (\ref{eq:26}), applying triangular inequality, $\mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S)\leq \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) + \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^{\perp}})$, and rearranging the term, we can get following inequality,
 \[
-    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S)\\
-    \leq \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F} +
-    \frac{3\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 2\gamma \|S^{*}_{M^\perp}\|_{1}
+    \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} \\
+    \leq \frac{\delta}{2} n \|\hat{\Delta}^{\alpha}\|_{F} + 
+    2\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) +  \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) + 
+    2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 2\gamma   
+    \|S^{*}_{M^\perp}\|_{1}
 \]
-Further, rearrange the terms, apply triangular inequality, $\mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S)\leq \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^{\perp}})$, and Agarwal et al[\cite{agarwal2012noisy}]’s third element of lemma 1, we get
+
+Further, by plugging in lemma 1 to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows: 
 \begin{align}
-    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} -
-    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F}
+    \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} -
+    \frac{\delta}{2} n \|\hat{\Delta}^{\alpha}\|_{F} 
     \leq 
@@
 \end{align}
-Noting that $\hat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\hat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
-\begin{align}
-    \delta\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M})
-    \leq \sqrt{2k}\delta\|\hat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S_\mathbb{M}\|_{F}\\
-    \leq \sqrt{2k}\delta\|\hat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S\|_{F} \label{eq:44}
-\end{align}
+Noting that $\widehat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\widehat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
+\begin{align*}
+    \delta\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) 
+    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S_\mathbb{M}\|_{F}\\
+    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S\|_{F} 
+\end{align*}
 
-Plug (\ref{eq:44}) in (\ref{eq:42}) and rearrange the terms,
-\begin{align}
-    \bigg\{\frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} -
-    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F}\bigg\} +
-    \bigg\{\frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2}
-    -\frac{7}{2}\sqrt{2k}\delta\|\hat{\Delta}^{L}\|_{F}\bigg\} +
-    \bigg\{\frac{\tau}{2}\|\hat{\Delta}^{S}\|_{F}^{2} -
-    \frac{7}{2}\Psi(\mathbb{M})\gamma\|\hat{\Delta}^S\|_{F}\bigg\}\\
-    \leq 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1} \label{eq:46}
-\end{align}
-
-Rearrange the term (\ref{eq:46}) again, and yields the claim,
-\begin{align}
-    \bigg\{\|\hat{\Delta}^{\alpha}\|_{F}-\frac{\delta}{2\tau} \bigg\}^{2} + \bigg\{\|\hat{\Delta}^{L}\|_{F}-\frac{7\delta}{2\tau}\sqrt{2k}\bigg\}^{2} + \bigg\{\|\hat{\Delta}^{S}\|_{F}-\frac{7\delta}{2\tau}\Psi(\mathbb{M})\bigg\}^{2} \\
-    \leq \frac{\delta^{2}}{4\tau^{2}} + \bigg\{\frac{8\delta}{\tau}\sum_{j=r+1}^{n}\sigma_{j}(L^{*}) +
-    \frac{49\delta^{2}}{4\tau^{2}}(2k)\bigg\} +
-    \bigg\{\frac{8\gamma}{\tau}\|S^*_{M^\perp}\|_{1} +
-    \frac{49\gamma^{2}}{4\tau^{2}}\Psi^{2}(\mathbb{M})\bigg\}
-\end{align}
+Substituting the above inequality into equation ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$ yields the claim.
 \end{proof}
@@
 %\nocite{*}
-\bibliography{References}%
+\bibliography{References}
 

### 2019-07-18 Manuscript for submission/manuscript.tex
Update
Update

@@
 %\usepackage[nottoc,notlot,notlof]{tocbibind}
+
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{proposition}[theorem]{Proposition}
+%\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{remark}[theorem]{Remark}
+%\newtheorem{condition}[theorem]{Condition}
+%\newtheorem{assumption}[theorem]{Assumption}
+%\newtheorem{property}[theorem]{Property}
+%\newtheorem{result}[theorem]{Result}
+%\newtheorem{example}[theorem]{Example}
 
@@
 
-\section{ On non-asymptotic error bound of the estimator }
+\section{Auxiliary result on non-asymptotic error bound of the estimator}
 In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the sample size is fixed as 1, and the number of variables in model is explicitly tracked.
 We are interested in solving following optimization problem :
-
 \begin{equation}\label{eq:1}
@@
 \[
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\widehat{\Delta}^{\alpha\mathbbm{1}\mathbbm{1}^T}\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
 \]
 
-\begin{theorem}
+\begin{theorem} \label{Th:th1}
 Under the assumptions \ref{Ass:1} and \ref{Ass:2},
@@
     e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
-    c_{1}\frac{\delta^{2}}{\tau^{2}} +
-    c_{2}\frac{\delta^{2}}{\tau^{2}}
-    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\} +
-    c_{3}\frac{\gamma^{2}}{\tau^{2}}
-    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin \mathbb{M}}|S^*_{ij}|\bigg\}
+    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
+    _{\mathcal{K}_{\alpha^*}} +
+    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
+    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
+    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
+    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin \mathbb{M}}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
 \end{align}
@@
 
+Our result provides the upper-bound on non-asymptotic Frobenius norm between estimator $\hat{\alpha}\mathbbm{1}\mathbbm{1}^T$, $\widehat{L}$ and $\widehat{S}$, and ground truth $\alpha^*\mathbbm{1}\mathbbm{1}^T$, $L^*$ and $S^*$, where matrices $L^*$ that can be either approximately or exactly low rank, and matrices $S^*$ that also can be either approximately or exactly sparse.
+A close observation on terms in upper-bound reveals that error bounds associated with $\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2}$, $\|\widehat{\Delta}^{L}\|_{F}^{2}$, and $\|\widehat{\Delta}^{S}\|_{F}^{2}$ are represented in the form of $\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$, and $\mathcal{K}_{S^*}$ respectively.
+More specifically, terms $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ are comprised of two types of errors, \emph{Estimation error} and \emph{Approximation error}.
+''\emph{Estimation error}'' represents statistical cost of estimating a parameter belong to the model subspace $\mathbb{M}$
+
+This result helps us to understand the behavior of our proposed estimator both in practice and in ideal cases.
+In real-world, large scale citation network analysis, it is difficult to expect exactly $k(\ll n)$ number of topics embedded in network. There must be
+
+Specifically, when $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $\mathbb{M}$ (i.e., $|supp(S^*)|=s$), then we have Frobenius error bound as follows:
+\[
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim (\delta^2+1)k+\gamma^2s
+\]
+
+\emph{\textbf{Comparison to Agarwal et al, \cite{agarwal2012noisy}}}
+We would like to refer readers that result presented in \textbf{Theorem \ref{Th:th1}} is similar with that of Theorem 1 presented in paper \cite{agarwal2012noisy}. 
+However, it should be noted that the convex program we consider is distinct from \cite{agarwal2012noisy}.
+\cite{agarwal2012noisy} considers matrix decomposition problem, where the observations are noisy realization of linear transformation $\Xi$ of the sum of (approximately) low rank and (approximately) sparse matrices.
+They used the notions of Restricted Strong Convexity of quadratic loss function and decomposable regularizer to prove their claims. In our work, we consider a convex problem, whose logistic loss 
+For the completeness of paper, we provide the proof of theorem in appendix section.
+
+\section{Appendix}
 \begin{proof}
@@
 -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\  \nonumber
-&=\langle\, \frac{1}{n} (X - P), \widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S} \rangle\ \\ \nonumber
-&\leq \frac{1}{n} \|X - P\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
-&\leq \frac{1}{n} \|X - P\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) +
-\frac{1}{n} \|X - P\|_{\infty}(\|\widehat{\Delta}^{S}_{M}\|_{1} + 
-\|\widehat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\ \nonumber
-&\leq \frac{\delta}{2}(n\|\hat{\Delta}^{\alpha}\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) + \frac{\gamma}{2}(\|\widehat{\Delta}^{S}_{M}\|_{1} + 
-\|\hat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\ 
-&= \frac{\delta}{2}n\|\hat{\Delta}^{\alpha}\|_{F} +     \frac{\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \frac{\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^\perp})  \label{eq:10}
+&=\langle\, \frac{1}{n} (X - P^*), \widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S} \rangle\ \\ \nonumber
+&\leq \frac{1}{n} \|X - P^*\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
+&\leq \frac{1}{n} \|X - P^*\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) +
+\frac{1}{n} \|X - P^*\|_{\infty}(\|\widehat{\Delta}^{S}_{M}\|_{1} + 
+\|\widehat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\ 
+&\leq \frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) + \frac{\gamma}{2}(\|\widehat{\Delta}^{S}_{M}\|_{1} +
+\|\hat{\Delta}^{S}_{M^{\perp}}\|_{1})  \label{eq:10}
 \end{align}
@@
     \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    \frac{\delta}{2}n\|\hat{\Delta}^{\alpha}\|_{F} + 
+    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
     \frac{3\delta}{2}\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M})
@@
 &= \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}+\widehat{\Delta}^{S}\|_{F}^{2} + 
-2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ \\ \nonumber
+2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ \\ 
 &=  \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2} + 
-2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
-2 \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ \\ 
-&= n^{2}\|\hat{\Delta}^{\alpha}\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2} + 
 2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
@@
     \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
-    &\geq \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} 
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} 
     - 2\kappa\tau(\frac{Cn+1}{n})\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
-    &\geq \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\widehat{\Delta}^{S}\|_{1}\\
-    &\geq \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S) \label{eq:26}
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\widehat{\Delta}^{S}\|_{1}\\
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S) \label{eq:26}
 \end{align}
@@
 \[
-    \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} \\
-    \leq \frac{\delta}{2} n \|\hat{\Delta}^{\alpha}\|_{F} + 
+    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} \\
+    \leq \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
     2\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) +  \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) + 
@@
 
-Further, by plugging in lemma 1 to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows: 
+Further, by plugging in Lemma 1 to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows:
 \begin{align}
-    \frac{\tau}{2} n^{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} -
-    \frac{\delta}{2} n \|\hat{\Delta}^{\alpha}\|_{F} 
+    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} -
+    \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} 
     \leq 
@@
 Noting that $\widehat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\widehat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
-\begin{align*}
+\begin{align}
+    \nonumber 
     \delta\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) 
     \leq \sqrt{2k}\delta\|\widehat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S_\mathbb{M}\|_{F}\\
-    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S\|_{F} 
+    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S\|_{F}  \label{eq:43}
+\end{align}
+Here $\Psi(\mathbb{M})$ measures the compatibility between Frobenius norm and component-wise $\ell_{1}$ regularizer, where $\mathbb{M}$ is an arbitrary subset of matrix indices of cardinality at most s.
+\[
+    \Psi(\mathbb{M}):=\sup\limits_{U\in\mathbb{M},U\neq0}\frac{\|U\|_{1}}{\|U\|_{F}}
+\]
+Using Cauchy-Schwarz inequality, we can easily check the quantity $\Psi(\mathbb{M})$ is bounded by at most $\sqrt{s}$.
+Plugging in the relation ($\ref{eq:43}$) into ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$ yield the claim.
+\end{proof}
+
+\subsection{Proof of Lemma 1}
+\begin{proof}
+Through the application of basic inequality by using optimality of $\widehat{\Theta}$ and feasibility of $\Theta^{*}$ to convex program (\ref{eq:1}), we have
+\begin{equation}
+    h(\widehat{\Theta}) - h(\Theta^{*})
+    \leq \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
+\end{equation}
+By using convexity of $h(\Theta)$, we can write
+\begin{align}
+    h(\widehat{\Theta})-h(\Theta^{*}) &\geq 
+    \langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ \nonumber \\
+    &= - \langle\,\frac{1}{n} (X-P^{*}), \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \rangle\ \nonumber \\
+    &\geq -\frac{1}{n} \|X - P^*\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \nonumber \\
+    &\geq -\frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) - \frac{\delta}{2} (\|\widehat{\Delta}^{S}_{\mathbb{M}}\|_{1} +
+    \|\widehat{\Delta}^{S}_{\mathbb{M^\perp}}\|_{1}) \label{eq:27}
+\end{align}
+
+One more round of application on Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1, 
+we can get an upper bound of difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ as follows:
+
+\begin{equation} \label{eq:28}
+    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
+    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
+\end{equation}
+
+By combining relations (\ref{eq:27}) and (\ref{eq:28}), we can get the upper bound of $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$ : 
+\begin{align*}
+    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq 
+    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
+    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}   
+    \|S^{*}_{M^\perp}\|_{1}
 \end{align*}
 
-Substituting the above inequality into equation ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$ yields the claim.
 \end{proof}

### 2019-07-19 Manuscript for submission/manuscript.tex
Update

@@
 if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying 
-\begin{align}
+\begin{align} \label{eq:49}
 \delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
@@
 
-Our result provides the upper-bound on non-asymptotic Frobenius norm between estimator $\hat{\alpha}\mathbbm{1}\mathbbm{1}^T$, $\widehat{L}$ and $\widehat{S}$, and ground truth $\alpha^*\mathbbm{1}\mathbbm{1}^T$, $L^*$ and $S^*$, where matrices $L^*$ that can be either approximately or exactly low rank, and matrices $S^*$ that also can be either approximately or exactly sparse.
-A close observation on terms in upper-bound reveals that error bounds associated with $\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2}$, $\|\widehat{\Delta}^{L}\|_{F}^{2}$, and $\|\widehat{\Delta}^{S}\|_{F}^{2}$ are represented in the form of $\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$, and $\mathcal{K}_{S^*}$ respectively.
-More specifically, terms $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ are comprised of two types of errors, \emph{Estimation error} and \emph{Approximation error}.
-''\emph{Estimation error}'' represents statistical cost of estimating a parameter belong to the model subspace $\mathbb{M}$
-
-This result helps us to understand the behavior of our proposed estimator both in practice and in ideal cases.
-In real-world, large scale citation network analysis, it is difficult to expect exactly $k(\ll n)$ number of topics embedded in network. There must be
-
-Specifically, when $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $\mathbb{M}$ (i.e., $|supp(S^*)|=s$), then we have Frobenius error bound as follows:
-\[
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim (\delta^2+1)k+\gamma^2s
-\]
-
-\emph{\textbf{Comparison to Agarwal et al, \cite{agarwal2012noisy}}}
-We would like to refer readers that result presented in \textbf{Theorem \ref{Th:th1}} is similar with that of Theorem 1 presented in paper \cite{agarwal2012noisy}. 
-However, it should be noted that the convex program we consider is distinct from \cite{agarwal2012noisy}.
-\cite{agarwal2012noisy} considers matrix decomposition problem, where the observations are noisy realization of linear transformation $\Xi$ of the sum of (approximately) low rank and (approximately) sparse matrices.
-They used the notions of Restricted Strong Convexity of quadratic loss function and decomposable regularizer to prove their claims. In our work, we consider a convex problem, whose logistic loss 
-For the completeness of paper, we provide the proof of theorem in appendix section.
+We would first like to note readers that the result presented in \textbf{Theorem \ref{Th:th1}} can be thought of as an extension of Theorem 1 presented in paper \cite{agarwal2012noisy} to generalized linear model.
+Our work considers a logistic loss function whose parameters are characterized by sparse plus low rank matrices, whereas \cite{agarwal2012noisy} works on quadratic loss of noisy realization of linear transformation of sum of low rank and sparse matrices.
+We show that similar proof techniques can be applied in our case, giving us similar results.
+%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.
+
+Result of Theorem provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $\mathbb{M}$, and rank parameter $k$.
+This family of upper-bounds helps us to understand the behavior of our proposed estimator both in practice and in ideal cases.
+In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.
+In this case, our theorem provides the intuition on the rate on how fast the error bound $\mathcal{K}_{L^*}$ will grow.  
+In ideal cases where $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $\mathbb{M}$ (i.e., $|supp(S^*)|=s$), we can easily verify ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ (i.e., $\tau\sum_{j=k+1}^{n}\sigma_j(L^*)$) and in $\mathcal{K}_{S^*}$ (i.e., $\tau\sum_{(i,j)\notin \mathbb{M}}|S_{ij}^*|$) disappear, giving us Frobenius error bound as follows:
+\[
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s
+\]
+where $\lesssim$ denotes that we ignore constant factors.
 
 \section{Appendix}
+\subsection{Proof of Theorem \ref{Th:th1}}
+
+In proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}.
+Let $(\mathbb{M},\mathbb{M}^{\perp})$ denote arbitrary subspace pair for which component-wise $\ell_{1}$ norm is decomposable.
+Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $\mathbb{M}$ as $P_{\mathbb{M}}$.
+And also note that proof relies on following lemma:
+
+\begin{lemma} \label{le:le1}
+If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we have
+\[
+    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq 
+    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
+    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}   
+    \|S^{*}_{M^\perp}\|_{1}
+\]
+\end{lemma}
+
+\noindent\textbf{proof of Theorem \ref{Th:th1}}
 \begin{proof}
@@
 
-Further, by plugging in Lemma 1 to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows:
+Further, by plugging in Lemma \ref{le:le1} to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows:
 \begin{align}
@@
 
-\subsection{Proof of Lemma 1}
+\subsection{Proof of Lemma \ref{le:le1}}
+
 \begin{proof}

### 2019-08-18 Manuscript for submission/manuscript.tex
Update 8.18.19

@@
 \documentclass[AMS,STIX1COL]{WileyNJD-v2}
-%\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
-%\usepackage{amsmath,amsfonts}
+\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
+\usepackage{amsmath,amsfonts}
 \usepackage{bbm}
@@
 \usepackage{lscape}
-%\usepackage[nottoc,notlot,notlof]{tocbibind}
+\usepackage[nottoc,notlot,notlof]{tocbibind}
 
@@
 
-\title{Factor Analysis on Report Citations, using a Combined Latent and logistic Model}
-
-\author[1]{Namjoon Suh*}
-\author[1]{Xiaoming Huo}
+\title{Factor Analysis on Citations, using a Combined Latent and Logistic Regression Model}
+
+\author[1]{Namjoon Suh}
+\author[1]{Xiaoming Huo*}
 \author[2]{Eric Heim}
@@
 
-\authormark{AUTHOR ONE \textsc{et al}}
-
-\address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
-
-\address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
-
-\corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}
-
-\presentaddress{This is sample for present address text this is sample for present address text}
-
-\abstract[Summary]{We propose a combined latent and logistic model for the citation network, where either a latent model or a logistic model alone is often insufficient to capture the structure of the data.
-The proposed model has a latent (i.e., factor analysis) model to represents the main technological trends (aka factors), and adds a sparse logistic component that captures the remaining ad hoc dependence.
-Parameter estimation are carried out through construction of a joint-likelihood function of edges and properly chosen penalty terms.
-The convexity of the likelihood function allows us to develop an efficient algorithm, while the penalty terms generate a low-dimensional latent component and a sparse graphical structure.
-Simulation results are reported that show the new method works well in practical situations.
-The proposed method has been applied to a real application in citation network of statistician data set (Ji and Jin, 2016 \cite{ji2016coauthorship}).
+\authormark{Namjoon Suh \textsc{et al}}
+
+\address[1]{\orgdiv{School of Industrial and Systems Engineering}, \orgname{Georgia Institute of Technology}, \orgaddress{755 Ferst Dr, Atlanta, \state{GA}, \country{USA}}}
+
+\address[2]{\orgdiv{Information System Division (AFRL/RIS)}, \orgname{the Air Force Research Laboratory}, \orgaddress{Department of the Air Force, Air Force Materiel Command, AFRL/RIK - Rome, 26 Electronic Parkway, Rome,  \state{New York}, \country{USA}}}
+
+\corres{*Xiaoming Huo, Georgia Institute of Technology, \email{huo@gatech.edu}}
+
+\presentaddress{755 Ferst Dr, Atlanta, GA, USA.}
+
+\abstract[Summary]{We propose a combined model, which integrates the latent factor model and the logistic regression model, for the citation network.
+It is noticed that neither a latent factor model nor a logistic regression model alone is sufficient to capture the structure of the data.
+The proposed model has a latent (i.e., factor analysis) model to represents the main technological trends (a.k.a., factors), and adds a sparse component that captures the remaining ad-hoc dependence.
+Parameter estimation are carried out through the construction of a joint-likelihood function of edges and properly chosen penalty terms.
+The convexity of the objective function allows us to develop an efficient algorithm, while the penalty terms push towards a low-dimensional latent component and a sparse graphical structure.
+Simulation results show that the proposed method works well in practical situations.
+The proposed method has been applied to a real application, which contains a citation network of statisticians (Ji and Jin, 2016 \cite{ji2016coauthorship}).
+Some interesting findings are reported.
 }
 
-\keywords{citation network, matrix decomposition, latent variable model,  logistic model, convex optimization}
+\keywords{citation network, matrix decomposition, latent variable model, logistic regression model, convex optimization, ADMM}
 
@@
 \author{Lee Seversky}} (\cyear{2019}),
-\ctitle{xxx}, \cjournal{journal.}, \cvol{2019;00:1--6}.}
-
+\ctitle{Citation network}, \cjournal{journal.}, \cvol{2019;00:1--6}.}
 \maketitle
-
 \footnotetext{\textbf{Abbreviations:} fused factor analysis and logistic graphical models, ADMM, network model}
@@
 Our model also assumes that there exist two dependent structures among citation edges in network.
-A low-dimensional version of the aforementioned latent vector model is largely correct and majority of the citations among the nodes are induced by these common latent vectors $f_{i}$'s (with weigh coefficients $d_{i}$'s).
+A low-dimensional version of the aforementioned latent vector model is largely correct and majority of the citations among the nodes are induced by these common latent vectors $f_{i}$'s (with weight coefficients $d_{i}$'s).
 There is still a small remainder due to the graphical component.
@@
 Though it may seem similar to Chen et al \cite{chen2016fused}, we work on a different model formulation in several aspects.
-First, FLaG is built to analyze the Eysenck’s Personality Questionnaire that consists of items designed to measure Psychoticism, Extraversion, and Neuroticism.
+We summarize the differences as follows.
+\begin{enumerate}
+\item FLaG is built to analyze the Eysenck's Personality Questionnaire that consists of items designed to measure Psychoticism, Extraversion, and Neuroticism.
 So there are $p$ questions that need to be answered, and each questions fall into above three categories.
-If there are n respondents to questions, we have n independent data generated from same distribution.
-In our case, the observed citation network can be thought of as one realization of random graph.
-Second, FLaG set a collection of binary responses for each individual questions follow a joint distribution which is a combination of Item Response Theory (IRT) model and Ising model, whereas we model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of Latent Factor Analysis model and logistic model.
-Last but not least, FLaG approximate the original likelihood through constructing pseudo-likelihood function by taking advantage of conditional independence among the nodes, but our model’s likelihood function is directly accessible due to the conditional independence among edges given parameters.
+If there are $n$ respondents to questions, we have $n$ independent data generated from same distribution.
+In our case, the observed citation network can be thought of as one realization of a random graph.
+
+\item FLaG sets a collection of binary responses for each individual questions follow a joint distribution which is a combination of Item Response Theory (IRT) model and the Ising model, whereas we model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of Latent Factor Analysis model and the logistic regression model.
+
+\item FLaG approximates the original likelihood through constructing pseudo-likelihood function by taking advantage of conditional independence among the nodes, but our model's likelihood function is directly accessible due to the conditional independence among edges given parameters.
+
+\end{enumerate}
 
 The proposed modeling framework is also related with the analysis of decomposing a matrix into low-rank and sparse components and the statistical inference of a multivariate Gaussian model whose precision matrix admits the form of a low-rank matrix plus a sparse matrix (\cite{chandrasekaran2010latent, candes2011robust, zhou2010stable}).
-However, the inference and optimization of the current model are different from those cases.
+The inference and optimization of the current model are different from the aforementioned cases.
 We will construct a regularized-likelihood function, based on which estimator will be proposed for simultaneous model selection and parameter estimation.
-The optimization for the regularized estimator will be convex, for which we will develop an efficient algorithm through the alternating direction method of multiplier (ADMM : \cite{boyd2011distributed, gabay1975dual, glowinski1975solution}).
+The optimization for the regularized estimator will be convex, for which we will develop an efficient algorithm through the alternating direction method of multiplier (ADMM, \cite{boyd2011distributed, gabay1975dual, glowinski1975solution}).
 
 The rest of the paper is organized as follows.
-In section 2 we will give a presentation on how to build a model which can encode both latent dependent structure due to the common topics and remaining ad-hoc dependent structure.
-In section 3, we will talk about assumptions in our model and penalization on likelihood function constructed in section 2.
-Section 4 gives the detailed procedure on how to compute the estimator of the optimization problem in Section 3.
-In Section 5, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians.
-We finally conclude this work in section 6 with several open questions remain to be solved and some directions for future research.
+In Section \ref{sec:model-form} we will give a presentation on how to build a model which can encode both latent dependent structure due to the common topics and remaining ad-hoc dependent structure.
+In section \ref{sec:estimate}, we will discuss about the assumptions in our model and penalization on likelihood function constructed in section \ref{sec:model-form}.
+Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem formulated in Section \ref{sec:estimate}.
+In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians.
+We finally conclude this work in section \ref{sec:Con} with several open questions remain to be solved and some directions for future research.
 
@@
 matrix $X = \{X_{ij}\} \in \mathbb{R}^{n \times n}$ is symmetric with diagonal entries all being equal to zero,
-factor loading matrix $F = [f_1,f_2,\ldots,f_n]\in \mathbb{R}^{K\times n}$ records the relation between nodes and underlying topics, $F^T$ is the transpose of $F$,
+factor loading matrix $F = [f_1,f_2,\ldots,f_n]\in \mathbb{R}^{K\times n}$ records the relation between nodes and the underlying topics, $F^T$ is the transpose of $F$,
 and matrix $D \in \mathbb{R}^{K \times K}$  is diagonal with entries being the weight coefficients of factors.
@@
 The above specifies a latent model (or equivalently a factor model).
-We now describe a graphical model in the following.
+We now describe a graphical model as follows.
 The graphical model will complement the latent model by characterizing links that are not interpretable via common factors.
@@
 where $S_{ij} \in \mathbb{R}$, for $1\le i,j \le n$, denotes the relation between nodes $i$ and $j$.
-If we have $S_{ij}=0$, then it is less likely to have a citational relationship between nodes $i$ and $j$.
+Note that the matrix $S$ is introduced to capture the ad-hoc links in the graph.
+If we have $S_{ij}\leq0$, then it is less likely to have a citational relationship between nodes $i$ and $j$.
 On the other hand, if $S_{ij}>0$, then it is more likely to have a citation link between nodes $i$ and $j$.
@@
 If we consider maximizing the above log-likelihood function,
-we will encounter several technical issues which are described below.
+we will encounter several technical issues that are described below.
 \begin{enumerate}
@@
     JLJ = L \quad \mbox{where} \quad
-    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T. 
-\]
-This condition uniquely identifies F up to a common orthogonal transformation of its columns.
+    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T,
+\]
+where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$s. This condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.
 
@@
 
-We propose a penalize likelihood estimation approach as follows:
+We propose a penalized likelihood estimation approach as follows:
 \begin{eqnarray}
@@
 The rank of estimated $\widehat{L}$ will be our estimate of the number of factors (i.e., underlying common topics).
-For the issue on assigning the community membership of each node $i$, we will discuss this later in Section 6.
+For the issue on assigning the community membership of each node $i$, we will discuss this later in Section \ref{sec:Num-anal}.
 
@@
 The problem in \eqref{eq:admm02} may not have a closed-form solution.
-We use a simple gradient descent to solve this step, setting the step size, $\alpha=0.1$ and stopping criteria, $\max(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}) \leq 10^{-9}$.
+We use a simple gradient descent to solve this step, setting the step size equal to $0.1$ and stopping criteria as $\max(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}) \leq 10^{-9}$.
 Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem.
@@
 $$
-where $T$ is orthogonal ($T T^T = I_n$), then, for $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, we have
+where $T$ is orthogonal ($T T^T = I_n$). Then, for $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, we have
 $$
@@
 \begin{array}{ll}
-0, & \mbox{ if } \Lambda_{jj} < \lambda \delta \\
+0, & \mbox{ if } \Lambda_{jj} < \lambda \delta, \\
 \Lambda_{jj}-\lambda \delta, & \mbox{ if } \Lambda_{jj} \ge \lambda \delta .
@@
 \begin{array}{ll}
-0, & \mbox{ if } |(z^m_S - u^m_S)_{ij}| < \lambda \gamma  \\
+0, & \mbox{ if } |(z^m_S - u^m_S)_{ij}| < \lambda \gamma,  \\
 (z^m_S - u^m_S)_{ij}-\lambda\gamma , &
-\mbox{ if } (z^m_S - u^m_S)_{ij} > \lambda \gamma \\
+\mbox{ if } (z^m_S - u^m_S)_{ij} > \lambda \gamma, \\
 (z^m_S - u^m_S)_{ij}+\lambda\gamma , &
-\mbox{ if } (z^m_S - u^m_S)_{ij} <- \lambda \gamma
+\mbox{ if } (z^m_S - u^m_S)_{ij} <- \lambda \gamma.
 \end{array}
@@
 z^{m+1}_M &=&
-\frac{1}{3} \bar{M} + \frac{1}{3} \bar{M}^T + \frac{1}{3} \bar{L} + \frac{1}{3} \bar{S} \\
+\frac{1}{3} \bar{M} + \frac{1}{3} \bar{M}^T + \frac{1}{3} \bar{L} + \frac{1}{3} \bar{S}, \\
 z^{m+1}_L &=&
-\frac{1}{6} \bar{M} + \frac{1}{6} \bar{M}^T + \frac{2}{3} \bar{L} - \frac{1}{3} \bar{S} \\
+\frac{1}{6} \bar{M} + \frac{1}{6} \bar{M}^T + \frac{2}{3} \bar{L} - \frac{1}{3} \bar{S},
+\quad \text{and} \\
 z^{m+1}_S &=&
@@
 In this work, we simply choose $\lambda = 0.5$.
-We terminate the algorithm  when in $mth$ iteration, $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^{-7}$.
+We terminate the algorithm  when in $m$th iteration, $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^{-7}$.
 
 \section{ Numerical analysis and Applications}
-In this section, we have conducted a small empirical study of measuring the performance of our proposed method with artificially specified graphical structures.
-Also we perform a real data analysis with citation network for statisticians.
-
+\label{sec:Num-anal}
+In this section, we have conducted a small empirical study of measuring the performance of our proposed method with artificially specified graphical structures,\ref{sec:Syn-dat}.
+Also we perform a real data analysis with citation network for statisticians,\ref{sec:citation_network}.
 \subsection{Synthetic data}
+\label{sec:Syn-dat}
 \textbf{Data Generation}.
-Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P_{ij}=\frac{\exp (
-\alpha+F_{i}^{T}DF_{j} +  S_{ij})}{1+\exp(\alpha+F_{i}^{T}DF_{j}+S_{ij})}$.
-For sparse component $S$, we generate random numbers uniformly distributed over the indices of upper triangular part (off diagonal) of matrix $S$, and make it symmetry.
-$F^{T}$ binary matrix has $\floor{\frac{n}{K}}$ ones in each columns, and has exactly one 1 in each rows.
-We randomly choose one of rows, fill that row with ones, and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying the aforementioned $J = I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$.
-Diagonal elements of $D$ are generated from Unif$[7,8]$ (uniform distribution on $[7,8]$), and alpha is generated from Unif$[-3,-2]$.
-We set $K=3,4,5$, $n=30,80,120$, and $nnz = 10, 20, 40$, where $nnz$ denotes number of non-zero component of the upper-triangular part of S.
+Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P^{*}_{ij}=\frac{\exp (
+\alpha^{*}+F^{*T}_{i}D^{*}F^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+F^{*T}_{i}D^{*}F^{*}_{j} +  S^{*}_{ij})}$.
+We set the model parameters randomly following these steps:
+\begin{enumerate}
+    \item Generate $\alpha^*$ from Unif$[-3,-2]$ (i.e., $\alpha^*\sim \text{Unif}[-3,-2]$).
+    \item For the binary factor loading matrix $F^*(\in \mathbb{R}^{n \times K})$, first fill in each row of the matrix with $\floor{\frac{n}{K}}$ ones,
+     and make sure that each column of $F^{*}$ has only one $1$.
+     In last row of $F^*$, fill in the last remaining $n-K\floor{\frac{n}{K}}$ entries with $1$s.
+     Then, we randomly choose one of columns, and fill that column with ones.
+     Lastly, set $F^*=F^*J$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$.
+     %and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying the aforementioned $J = I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$.
+    \item Each element of diagonal matrix $D^{*}$ are generated from Unif$[7,8]$.
+    \item For the sparse component $S^*$, first draw $nnz$ distinct random pairs of indices that are uniformly distributed over the indices of upper triangular part (off diagonal) of matrix $S^*$.
+For each drawn pair of indices $(i,j)$, draw random number from Unif$[7,8]$ (i.e., $S^*_{ij}\sim\text{Unif}[7,8]$).
+$nnz$ denotes the number of non-zero component of the upper-triangular part of $S^{*}$.
+\end{enumerate}
+
+We consider following three scenarios: $\{(n^{(i)},K^{(i)},nnz^{(i)})\}_{i=1}^{3}=\{(30,3,10),(80,4,20),(120,5,40)\}$.
 
 \textbf{Choosing the tuning parameters and evaluation criteria}.
-We have to admit the fact that choosing a good pair of tuning parameter is an important but challenging issue in our problem.
-We here present a purely heuristic approach.
+We have to admit the fact that choosing a good pair of tuning parameters is an important but challenging issue in our problem.
+Here we present a purely heuristic approach.
 Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest 20 eigenvalues of adjacency matrix $X$, which can tell us the numbers of communities embedded in network.
-Then, we record the rank of L and number of non-zero elements in S for each tuning parameter pair on grid, and choose a proper pair which can give us interesting interpretation of data.
-
-One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, work where
+Then, we record the rank of $\widehat{L}$ and number of non-zero elements in $\widehat{S}$ for each tuning parameter pair on grid, and choose a proper pair that give us interesting interpretations of data.
+
+One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, work where we define BIC and AIC as follows:
 \[
@@
 \[
-|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1
-\]
-
-\begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig1.pdf}
-\caption{After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\widehat{L}$ matrix.
-(Different color represents different clusters of nodes $k$-means assign for three synthetic settings.) }
-\label{fig:figure1}
-\end{figure}
-
-Because the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
+|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1,
+\]
+since the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
 Additionally $1$ in the last is due to $\alpha$.
@@
 Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest K and smallest cardinality of ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$) from a pair of tuning parameters over the given range of grid.
-We evaluate the models selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.
+For clarification on this argument, we evaluate the models selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.
 
 \begin{eqnarray*}
-M1 &=& \mathbbm{1}\big\{rank(\widehat{L}) = rank(L^{*})\big\} \\
-M2 &=& \frac{|\big\{(i,j):i<j:S^{*}_{i,j} \neq0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}|}{|\big\{(i,j):i<j:S^{*}_{i,j}\neq0\big\}|} \\
-M3 &=& \frac{|\big\{(i,j):i<j:S^{*}_{i,j} = 0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}|}{|\big\{(i,j):i<j:S^{*}_{i,j}=0\big\}|}
+M_1 &=& \mathbbm{1}\big\{rank(\widehat{L}) = rank(L^{*})\big\}, \\
+M_2 &=& \frac{\left|\big\{(i,j):i<j:S^{*}_{i,j} \neq0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}\right|}{\left|\big\{(i,j):i<j:S^{*}_{i,j}\neq0\big\}\right|}, \\
+M_3 &=& \frac{\left|\big\{(i,j):i<j:S^{*}_{i,j} = 0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}\right|}{\left|\big\{(i,j):i<j:S^{*}_{i,j}=0\big\}\right|},
 \end{eqnarray*}
-
-$M1$ is a metric on whether selected model recovers true low rank structure of network,
-$M2$ evaluates the positive selection rate of sparse network structure,
-and lastly $M3$ evaluates the false discovery rate.
-With properly selected tuning parameter, $M1$ will be 1, $M2$ will be close to 1, and $M3$ will get close to 0.
-Evaluated results of models selected via three criteria are presented in Table 1.
+where $M_1$ is a metric on whether the selected model recovers true low rank structure of network,
+$M_2$ evaluates the positive selection rate of the sparse ad-hoc structure in network,
+and $M_3$ evaluates the false discovery rate of ad-hoc edges.
+With properly selected tuning parameter, $M_1$ will be 1, $M_2$ will be close to 1, and $M_3$ will get close to 0.
+We present the evaluation results of three scenarios via these three criteria in Table \ref{tab:table1}.
 
@@
    & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC   \\ \hline
-$M1$ & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
-$M2$ & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
-$M3$ & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0
+$M_1$ & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
+$M_2$ & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
+$M_3$ & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0
 \end{tabular}
-\caption{ Both AIC and BIC choose the model $\widehat{S}=0$ with no ad-hoc structure, and $\widehat{L}$ with the lowest rank among all estimators via a pair of tuning parameter over the grid of search region.
-Our heuristic method correctly choose the model with $\widehat{L}$ with true rank and $\widehat{S}=0$ catching all the ''across edges'' of network.
-Note that }
+\caption{ For three scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
+Note that both AIC and BIC choose the model with no ad-hoc structure (i.e., $\widehat{S}=0$),
+and $\widehat{L}$ with the lowest rank among all estimators via a pair of tuning parameter over the grid of search region.}
 \label{tab:table1}
@@
 
+\begin{figure}[htbp]
+\includegraphics[width=1\textwidth]{Fig1.pdf}
+\caption{Illustrations of assignment results via $k$-means algorithm on $K$ eigenvectors of the estimated $\widehat{L}$ matrix.}
+\label{fig:figure1}
+\end{figure}
+
 \textbf{Community memberships of each nodes}.
 Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$.
-We applied a simple $k$-means clustering on the fitted $L$ matrix's first $K$ eigenvectors.
-Furthermore, we find one interesting phenomenon.
-Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
-Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
+We applied a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
+For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig \ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2D$ plane.
+%Furthermore, we find one interesting phenomenon.
+%Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
+%Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
 
@@
 Ad-hoc links of synthetic network data can be thought of as ``across edges'' between clusters of nodes.
-Since indices of non-zero entries of $S$ are randomly chosen, there might be some indices of non-zero $S_{ij}$ entries where $L_{ij}$ is also non-zero.
-In this case, this makes the edges indistinguishable if they come from $S_{ij}$ or $L_{ij}$.
-Some of ``across edges" are also attributed to $\alpha$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha$ or $S_{ij}$.
-So the total number of across edges might not be exactly same as we set in our data generation setting.
+Since indices of non-zero entries of $S^{*}$ are randomly chosen, there might be some indices of positive $S^{*}_{ij}$ entries where $L^{*}_{ij}$ is also positive.
+In this case, this makes the edges indistinguishable if they come from $S^{*}_{ij}$ or $L^{*}_{ij}$.
+%Some of ``across edges" are also attributed to $\alpha^{*}$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha^{*}$ or $S^{*}_{ij}$.
+So the total number of ``across edges'' might not be exactly same as ``$nnz$'' as we set in our data generation setting.
 
@@
 Also to see if it can separate the ad-hoc links from edges which come from common topics.
-Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$, respectively, give us the desirable results for the three cases.
-Note that different dynamics of network requires different choices of tuning parameters even the synthetic setting is same, since we are generating the random graph.
-However, we set the seeds in our simulation so that the results are reproducible.
-Fig. \ref{fig:figure1} shows us the result of clustered nodes using the $k$-means algorithm on the first $K(=\mbox{rank}(\widehat{L}))$ eigenvectors.
+Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$, respectively, give us the desirable results for the three scenarios.
+For first scenario, both $\gamma$ and $\delta$ are searched over $\{0.01,0.02,\dots,0.1\}$.
+For second and third scenarios, parameters are searched over $100$ points, equidistant, from the interval $[0.001,0.01]$ for $\gamma$, and $[0.01,0.02]$ for $\delta$.
+%Note that different dynamics of network requires different choices of tuning parameters even the synthetic setting is same, since we are generating the random graph.
+%In order to avoid this problem, we set the seeds in our simulation so that the results are reproducible. (Code is provided in $\emph{https://sites.google.com/site/namjoonsuh/publications}$.)
+Fig. \ref{fig:figure1} shows us the result of clustered nodes using $k$-means algorithm on the first $K(=\mbox{rank}(\widehat{L}))$ eigenvectors.
 We plot the rows of first two eigenvectors on the cartesian plane since it visualizes well the clustering behavior of the nodes.
 Our model chooses well the ad-hoc links between clusters of nodes as can be verified in Fig. \ref{fig:figure2}.
-We color the edges in blue whose corresponding elements of estimated $\widehat{S}$ are non-zero, and black whose corresponding entries of $\widehat{S}$ are zero.
+We color the edges in blue whose corresponding elements of estimated $\widehat{S}$ are non-zero, and color the edges in black whose corresponding entries of $\widehat{S}$ are zero.
 
@@
 \includegraphics[scale=0.75]{Fig2.pdf}
+%\includegraphics[scale=1,bb=0 0 30 30]{Fig2.pdf}
 \caption{Edges colored with blue correspond to non-zero entries of estimated $\widehat{S}$ matrix.
-For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
+For all three cases, our algorithm correctly separates the ``across edges'' from edges coming from low-rank matrix structure.}
 \label{fig:figure2}
@@
 
-\subsection{Citation networks for statisticians }
+\subsection{Citation networks for statisticians}
+\label{sec:citation_network}
 Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting data set on citation  and co-authorship networks of statisticians.
-Citation relationship over 3000 papers from 4 statistical journals, published between 2003 and 2012, were collected, and collaborative network between authors of papers is given as well.
-In this section, we analyze the citation network. \\
-
-\noindent\textbf{Citation Network} This dataset is based on all published papers from 2003 to first half of 2012, in 4 of the top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association and Journal of Royal Statistical Society (Series B).
-Among  3248 papers, we restrict our attention on papers which have greater than or equal to 7 citations from collected papers in original dataset.
-We have 543 papers in our hands.
-The elbow points of the scree plot may be at the 3rd, 7th, or 9th largest eigenvalue, suggesting that there might be from 2 to 8 topics in network.
-In light of this, we performed our analysis under the assumption that there might exist 2 distinct topics and one giant component in which 3 or 4 topics mixed up. \\
-
-\noindent $(\gamma,\delta) = (0.000912,0.0097)$ gives us $\widehat{L}$ with rank 3, and $\widehat{S}$ with $|supp(\widehat{S})|=197$.
-We apply $k$-means algorithm on 3 eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in $Fig 4$.
-404 papers colored in green are densely clustered nearby the origin with a short tail, $(Fig 4)$, and $k$-means classifies these papers as third topic.
+Citational relationships over $3000$ papers from $4$ statistical journals were collected, and collaborative network among authors of the papers is also given.
+In our work, we only analyze the citation network of papers.
+\begin{figure}[htbp]
+\includegraphics[width=1\textwidth]{Fig3.eps}
+\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
+\label{fig:figure3}
+\end{figure}
+This dataset is based on all papers published from $2003$ to first half of $2012$, in $4$ of the top statistical journals: ``Annals of Statistics'', ``Biometrika'', ``Journal of American Statistical Association'' and ``Journal of Royal Statistical Society (Series B)''.
+Among  $3248$ papers in total, we restrict our attention on papers which have greater than or equal to $7$ citations from the collected papers in original dataset.
+We have $543$ papers in our hands.
+The elbow points of the scree plot may be at the $3$rd, $7$th, or $9$th largest eigenvalue, suggesting that there might be from $2$ to $8$ topics in network (See $Fig \ref{fig:figure3}, left$).
+In light of this, we performed our analysis under the assumption that there might exist $2$ distinct topics and one giant component in which $3$ or $4$ topics are mixed up.
+
+A pair of parameters, $(\gamma,\delta) = (0.000912,0.0097)$, gives us $\widehat{L}$ with rank $3$, and $\widehat{S}$ with $|supp(\widehat{S})|/2=197$.
+We apply $k$-means algorithm on $3$ eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in $Fig \ref{fig:figure4}$.
+$404$ papers colored in green are densely clustered nearby the origin with a short tail, $(Fig \ref{fig:figure4})$, and $k$-means classifies these papers as third topic.
 We list the first two topics discovered through our analysis.
-(Full lists of papers for each communities are provided in ($\emph{https://sites.google.com/site/namjoonsuh/publications}$)
+Full lists of papers for each communities are provided in $\emph{https://sites.google.com/site/namjoonsuh/publications}$.
 
 \begin{itemize}
-  \item Variable selection (85 papers)
-  \item Multiple Hypothesis Testing (54 papers)
+  \item Variable selection ($85$ papers)
+  \item Multiple Hypothesis Testing ($54$ papers)
 \end{itemize}
@@
 \noindent These two topics are classical research topics in field of statistics.
-First group talks about "Variable selection" in high-dimensional data.
-Majority of papers in second community study about "Controlling False Discovery Rate" in various statistical settings.
+First group talks about ``Variable selection'' in high-dimensional data.
+Majority of papers in second community study about ``Controlling False Discovery Rate'' in various statistical settings.
 As expected, third group is quite hard to interpret and seems to have substructures.
-For further investigation on this group, after obtaining the sub-network which is comprised only with papers in third group, we performed same analysis once again under the assumption that $K=4$.
+For further investigation on this group, after obtaining the sub-network which is comprised only with papers in third group, we performed same analysis once again under the assumption that $K=4$ (See $Fig \ref{fig:figure3},right$).
 We obtain four sub-communities as follows:
@@
 \begin{itemize}
-  \item Non-parametric Bayesian Statistics (17 papers)
-  \item Functional Data analysis (35 papers)
-  \item Dimension Reduction (23 papers)
-  \item Mixed topics (329 papers)
+  \item Non-parametric Bayesian Statistics ($17$ papers)
+  \item Functional Data analysis ($35$ papers)
+  \item Dimension Reduction ($23$ papers)
+  \item Mixed topics ($329$ papers)
 \end{itemize}
+
+Out of this one big chunk, we got three small, but meaningful topics: ``Bayesian Statistics'', ``Functional/longitudinal data analysis'', ``Dimension Reduction''.
+Due to small volume of each communities, we could manually check that false discoveries for each community are all zero.
+
+Sub-network structure has also a big chunk of papers which we refer to as ``Mixed Topics''.
+Not only could we see the papers with topics on ``Learning Theory'', ``Non-parametric/semi-parametric statistics'', ``Spatial Statistics'', ``Theoretical Machine Learning'', which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
+Papers like ``The Bayesian Lasso (T.
+Park, et al.
+2008)'', ``Coordinate-independent sparse sufficient dimension reduction and variable selection (X.
+Chen, et al.
+2010)'' are the examples of these papers.
+It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed topic classified as Mixed topic.
+For instance, ``On the "degrees of freedom" on the LASSO (H. Zou, et al. 2007)'' is classified as Mixed Topic paper.
+We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities.
+Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics.
+
+Furthermore, it is worth to note that our result is consistent with that from Ji and Jin \cite{ji2016coauthorship} in a sense that they also recover ``Multiple Testing'', ``Variable selection'' and ``non-parametric Bayesian statistics''.
+This is interesting since even though the dataset we consider is different from theirs, the results are consistent.
+They focus their attentions on analyzing \emph{"weakly connected giant component"} for a citation network of each paper's authors ({i.e., each node is an author}).
+We consider the citation network of papers whose node degree is greater than or equal to 7.
+
+Non-zero components of $\widehat{S}$ capture the citation relationships among papers that are not attributable to the common topics.
+The model we select has 197 sparse edges ($9\%$ of total edges), and all of them are positive edges.
+In Table \ref{tab:table2}, we provide 15 pairs of papers that have the largest estimated $\widehat{S}_{ij}$.
+All the 15 edges come from pairs of papers from different communities.
+For instance, the first pair of papers comes from the ``Functional Analysis'' community (denoted by \emph{FuncAn}) and ``Variable selection'' $(\emph{VarSel})$ community.
+$\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
+Though it might seem to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
+Second pair comes from ``Multiple Testing'' (denoted as $\emph{MulT}$) and ``Variable Selection'' ($\emph{VarSel}$) community.
+$\emph{MulT}$ paper briefly mentions about $\emph{VarSel}$ paper in future work section, suggesting a possible way of combining their work and work in $\emph{VarSel}$ paper.
+And we also observe that as the estimated weight of sparse edges (i.e., $\widehat{S}_{ij}$) decreases, the number of pairs of papers that come from "Mixed topics" community increases.
 
@@
 \includegraphics[width=1\textwidth]{Fig4.eps}
-\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
+\caption{Illustration of first two eigenvectors of estimated $\widehat{L}$ matrix for original
+citation network with 543 papers (left) and sub-network graph (right). We present
+the results of assignment of each paper to each topic via $k$-means algorithm with different colors.}
 \label{fig:figure4}
@@
 
-Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction".
-Due to small volume of each communities, we could check that false discoveries for each community are all zero.
-
-Sub-network structure has also a big chunk of papers which we refer to as "Mixed Topics".
-Not only could we see the papers with topics on "Learning Theory", "Non-parametric/semi-parametric statistics", "Spatial Statistics", "Theoretical Machine Learning", which does not seem to belong to any of five communities listed above, but also we could identify the papers with combinations of two or three topics.
-Papers like "The Bayesian Lasso (T. Park, et al. 2008)", "Coordinate-independent sparse sufficient dimension reduction and variable selection (X. Chen, et al. 2010)" are the examples of these papers.
-It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed topic classified as Mixed topic.
-For instance, "On the "degrees of freedom" on the LASSO (H. Zou, et al. 2007)" is classified as Mixed Topic paper.
-We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities.
-Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics.
-
-It is worth to note that our result is consistent with that from Ji and Jin in a sense that they also recover "Multiple Testing", "Variable selection" and "non-parametric Bayesian statistics".
-This is interesting since even though the dataset we consider is different from theirs, result is consistent.
-They focus their attentions on analyzing \emph{"weakly connected giant component"} for a citation network of each paper's authors ({i.e., each node is an author}).
-We consider the citation network of papers whose node degree is greater than or equal to 7.
-
-\textbf{Ad-hoc links}. 
-Non-zero components of $\widehat{S}$ capture the citation relationships among papers that are not attributable to the common topics.
-The model we select has 197 sparse edges (9\% of total edges), and all of them are positive edges.
-In Table 1, we provide 15 pairs of papers that have the most positive edges.
-All the 15 edges come from pairs of papers from different communities.
-For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable selection $(\emph{VarSel})$ community. 
-$\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
-Though it might seem to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
-Second pair comes from $\emph{MulT}$  and $\emph{VarSel}$ community.
-$\emph{MulT}$ paper briefly mention about $\emph{VarSel}$ paper in future work section, suggesting a possible way of combining their work and work in $\emph{VarSel}$ paper.
-And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community.
-
-\begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig3.eps}
-\caption{Illustration of first two eigenvectors of estimated $\widehat{L}$ matrix for original
-citation network with 543 papers(left) and sub-network graph(right). Presentation
-on clustering results of k-means algorithm with different colors.}
-\label{fig:figure3}
-\end{figure}
-
-\section{Conclusion}
-We propose a new combined latent factor analysis and logistic model.
-We consider the regularized likelihood by means of $\ell 1$ and nuclear norm penalties.
-The computation of the regularized estimator is facilitated by developing an algorithm based on the alternating direction method of multiplier to optimize a non-smooth and convex objective function.
-The proposed method is applied to citation and co-authorship network of statisticians, and the estimated model renders good interpretative power.
-Specifically, our analysis on statistician's citation network sheds the new light on the interpretation of dataset.
-
-However, there are still several open problems which require us to do more careful analysis.
-First of all, it remains unclear on how to choose the proper tuning parameters.
-Classical methods for choosing tuning parameters such as BIC or AIC did not work in our case, since they tend to choose the most parsimonious models.
-We also do not have systematic ways to do cross validation in network data.
-Not only because it is computationally expensive procedure, but also because if we partition the network data, we can loose fair amount of information on dependent structures among edges.
-This problem is also closely related with determining the number of communities in network.
-In lieu of using BIC or AIC, our analysis is heavily relying on heuristic approach when choosing the tuning parameter, and during this procedure, we use the screeplot for determining number of communities in network.
-Screeplot approach works usually well, but it does not necessarily always guarantee the correct estimate of number of communities.
-We need a more reliable and theoretically well understood way to determine $K$.
-
-Secondly, we only consider the undirected case which is somewhat unrealistic assumption in real citation network, in a sense that it is not usual for two papers to cite each other at the same time.
-Since in our research, we were interested in separating the low rank structure of edges and ad-hoc links in network, we did not take into account the directionalities of edges in our model.
-However, it would be interesting to think about the way to incorporate the directed network into our matrix decomposition framework.
-
-Last but not least, when we assign the memberships of each nodes, we use $k$-means clustering algorithm.
-However, $k$-means algorithm turns out that it tends to assign nodes conservatively to each communities.
-For example, in $Fig 4 (a)$, we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in $Fig 4 (b)$ also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
-This is probably because $k$-means does not allow overlapping membership of each nodes.
-It would be interesting to see what happens if we apply some clustering methods which allow the overlapped memberships of nodes in network.
-
-\section{Auxiliary result on non-asymptotic error bound of the estimator}
-In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the sample size is fixed as 1, and the number of variables in model is explicitly tracked.
-We are interested in solving following optimization problem :
-\begin{equation}\label{eq:1}
-\min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
--\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{exp\left(X_{ij}\left(\alpha+
-L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
-L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
-\end{equation}
-
-Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process.
-Let $\widehat{\Theta},\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
-And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*}, 
-\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
-\widehat{\Delta}^L = \widehat{L}-L^{*},
-\widehat{\Delta}^S = \widehat{S}-S^{*}.$
-Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
-Astute readers might notice the slight difference of first term in objective function between (\ref{eq:logistic10})
-and (\ref{eq:1}). 
-Justification of this modification is well explained in \emph{remark 3.1} of the paper \cite{ma2017exploration}. 
-We further impose several assumptions for theoretical guarantees of our estimator.
-
-\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
-For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):
-\[
-\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
-\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
-\]
-For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal. For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite.
-\end{assumption}
-
-\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
-To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
-We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
-We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
-\end{assumption}
-
-With these assumptions we present the behavior of non-asymptotic error bound of our estimator through following theorem.
-In our result, we measure error using squared Frobenius norm summed across three matrices:
-\[
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
-\]
-
-\begin{theorem} \label{Th:th1}
-Under the assumptions \ref{Ass:1} and \ref{Ass:2},
-if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying 
-\begin{align} \label{eq:49}
-\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
-\end{align}
-There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
-\begin{align}
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
-    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
-    _{\mathcal{K}_{\alpha^*}} +
-    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
-    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
-    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
-    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin \mathbb{M}}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
-\end{align}
-where $\mathbb{M}$ is an arbitrary subset of matrix indices of cardinality at most s.
-\end{theorem}
-
-We would first like to note readers that the result presented in \textbf{Theorem \ref{Th:th1}} can be thought of as an extension of Theorem 1 presented in paper \cite{agarwal2012noisy} to generalized linear model.
-Our work considers a logistic loss function whose parameters are characterized by sparse plus low rank matrices, whereas \cite{agarwal2012noisy} works on quadratic loss of noisy realization of linear transformation of sum of low rank and sparse matrices.
-We show that similar proof techniques can be applied in our case, giving us similar results.
-%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.
-
-Result of Theorem provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $\mathbb{M}$, and rank parameter $k$.
-This family of upper-bounds helps us to understand the behavior of our proposed estimator both in practice and in ideal cases.
-In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.
-In this case, our theorem provides the intuition on the rate on how fast the error bound $\mathcal{K}_{L^*}$ will grow.  
-In ideal cases where $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $\mathbb{M}$ (i.e., $|supp(S^*)|=s$), we can easily verify ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ (i.e., $\tau\sum_{j=k+1}^{n}\sigma_j(L^*)$) and in $\mathcal{K}_{S^*}$ (i.e., $\tau\sum_{(i,j)\notin \mathbb{M}}|S_{ij}^*|$) disappear, giving us Frobenius error bound as follows:
-\[
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s
-\]
-where $\lesssim$ denotes that we ignore constant factors.
-
-\section{Appendix}
-\subsection{Proof of Theorem \ref{Th:th1}}
-
-In proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}.
-Let $(\mathbb{M},\mathbb{M}^{\perp})$ denote arbitrary subspace pair for which component-wise $\ell_{1}$ norm is decomposable.
-Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $\mathbb{M}$ as $P_{\mathbb{M}}$.
-And also note that proof relies on following lemma:
-
-\begin{lemma} \label{le:le1}
-If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we have
-\[
-    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq 
-    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
-    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}   
-    \|S^{*}_{M^\perp}\|_{1}
-\]
-\end{lemma}
-
-\noindent\textbf{proof of Theorem \ref{Th:th1}}
-\begin{proof}
-Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal and feasible (respectively) for the convex program (\ref{eq:1}), we have
-\begin{equation}\label{eq:2}
-    h(\widehat{\Theta}) + \delta\|\widehat{L}\|_{*} + \gamma\|\widehat{S}\|_{1} \leq  
-     h(\Theta^{*}) + \delta\|{L^{*}}\|_{*} + \gamma\|{S}^{*}\|_{1}
-\end{equation}
-
-Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on term $h(\widehat{\Theta})-h(\Theta^{*})$ :
-\[
-h(\widehat{\Theta})-h(\Theta^{*}) \geq 
-\langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ + \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}
-\]
-
-By rearranging the term in (\ref{eq:2}) and plugging in above inequality relation, we get:
-
-\begin{equation}\label{eq:3}
-    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
-    + \delta \|L^{*}\|_\ast + \gamma \|S^{*}\|_1 
-    - \delta \|\widehat{L}\|_\ast - \gamma \|\widehat{S}\|_1
-\end{equation}
-
-Here, we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers : 
-\[
-\mathbb{Q}(L,S)   := \|L\|_{*} + \frac{\gamma}{\delta}\|S\|_1
-\]
-Through the definition of $\mathbb{Q}$, we can rewrite (\ref{eq:3}) as follows:
-\begin{equation}\label{eq:4}
-    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
-    + \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
-\end{equation}
-
-According to Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1, 
-the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ is upper-bounded by
-
-\begin{equation}\label{eq:5}
-    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
-    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
-\end{equation}
-
-First, we want to control upper bound of the term $-\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\,$
-in (\ref{eq:4}).
-\begin{align}
--\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\  \nonumber
-&=\langle\, \frac{1}{n} (X - P^*), \widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S} \rangle\ \\ \nonumber
-&\leq \frac{1}{n} \|X - P^*\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
-&\leq \frac{1}{n} \|X - P^*\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) +
-\frac{1}{n} \|X - P^*\|_{\infty}(\|\widehat{\Delta}^{S}_{M}\|_{1} + 
-\|\widehat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\ 
-&\leq \frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) + \frac{\gamma}{2}(\|\widehat{\Delta}^{S}_{M}\|_{1} +
-\|\hat{\Delta}^{S}_{M^{\perp}}\|_{1})  \label{eq:10}
-\end{align}
-
-Combining the inequalities (\ref{eq:5}) and (\ref{eq:10}), we can obtain the upper bound of RHS in (\ref{eq:4}) as follows:
-
-\begin{equation}
-    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
-    \frac{3\delta}{2}\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M})
-    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\gamma \|S^*_{M^\perp}\|_{1}
-    \label{eq:11}
-\end{equation}
-
-Second, we wish to control the lower bound of the term  $\frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2}$ with respect to $\hat{\Delta}^{\alpha},\hat{\Delta}^{L},\hat{\Delta}^{S}$.
-\begin{align}
-\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
-&= \|\widehat{\Theta}-\Theta^{*} \|_{F}^{2} \\ \nonumber
-&= \|\widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S}\|_{F}^{2} \\ \nonumber
-&= \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}+\widehat{\Delta}^{S}\|_{F}^{2} + 
-2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ \\ 
-&=  \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2} + 
-2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
-2 \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\  \label{eq:12}
-\end{align}
-
-We want to get the further lower bound on trace inner product terms, 
-$ \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $.
-To control the first trace inner product term, we use the relation $\widehat{\Delta}^{L}\mathbbm{1}=0$, apply the definition of dual norm on inner product term, triangular inequality on $\hat{\Delta}^\alpha$, and lastly we apply the constraint imposed on $|\alpha|$ stated in Assumption \ref{Ass:2}.
-
-\begin{align}
-    | \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \nonumber
-    &= | \langle\,\widehat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\ \nonumber
-    &\leq \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\widehat{\Delta}^{S}\|_1 \\ \nonumber
-    &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\widehat{\Delta}^{S}\|_1\\ 
-    &\leq 2C\kappa\|\widehat{\Delta}^{S}\|_1  \label{eq:13}
-\end{align}
-
-To control the term $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $, we first apply the definition of dual norm on trace inner product term, then apply triangular inequality on $\widehat{\Delta}^{L}$ and spikiness condition.
-
-\begin{align}
-    | \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ | \nonumber
-    &\leq \|\widehat{\Delta}^{L}\|_{\infty} \|\widehat{\Delta}^{S}\|_1\\ \nonumber
-    &\leq (\|\widehat{L}\|_{\infty} + \|L^{*}\|_{\infty})
-    \|\widehat{\Delta}^{S} \|_{1}\\
-    &\leq \big(\frac{2\kappa}{n}\big)\|\widehat{\Delta}^{S} \|_{1} \label{eq:14}
-\end{align}
-
-We can combine the inequality (\ref{eq:12}), (\ref{eq:13}) and (\ref{eq:14}).
-Then applying the assumption on regularization parameter $\gamma$, and the fact $\|\widehat{\Delta}^{L}\|_{\ast}\geq0$ sequentially, we can get,
-
-\begin{align}
-    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} 
-    - 2\kappa\tau(\frac{Cn+1}{n})\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\widehat{\Delta}^{S}\|_{1}\\
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S) \label{eq:26}
-\end{align}
-
-By combining the relations (\ref{eq:11}) and (\ref{eq:26}), applying triangular inequality, $\mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S)\leq \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) + \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^{\perp}})$, and rearranging the term, we can get following inequality,
-\[
-    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} \\
-    \leq \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
-    2\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) +  \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) + 
-    2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 2\gamma   
-    \|S^{*}_{M^\perp}\|_{1}
-\]
-
-Further, by plugging in Lemma \ref{le:le1} to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows:
-\begin{align}
-    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} -
-    \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} 
-    \leq 
-    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}  \label{eq:42}
-\end{align}
-Noting that $\widehat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\widehat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
-\begin{align}
-    \nonumber 
-    \delta\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) 
-    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S_\mathbb{M}\|_{F}\\
-    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S\|_{F}  \label{eq:43}
-\end{align}
-Here $\Psi(\mathbb{M})$ measures the compatibility between Frobenius norm and component-wise $\ell_{1}$ regularizer, where $\mathbb{M}$ is an arbitrary subset of matrix indices of cardinality at most s.
-\[
-    \Psi(\mathbb{M}):=\sup\limits_{U\in\mathbb{M},U\neq0}\frac{\|U\|_{1}}{\|U\|_{F}}
-\]
-Using Cauchy-Schwarz inequality, we can easily check the quantity $\Psi(\mathbb{M})$ is bounded by at most $\sqrt{s}$.
-Plugging in the relation ($\ref{eq:43}$) into ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$ yield the claim.
-\end{proof}
-
-\subsection{Proof of Lemma \ref{le:le1}}
-
-\begin{proof}
-Through the application of basic inequality by using optimality of $\widehat{\Theta}$ and feasibility of $\Theta^{*}$ to convex program (\ref{eq:1}), we have
-\begin{equation}
-    h(\widehat{\Theta}) - h(\Theta^{*})
-    \leq \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
-\end{equation}
-By using convexity of $h(\Theta)$, we can write
-\begin{align}
-    h(\widehat{\Theta})-h(\Theta^{*}) &\geq 
-    \langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ \nonumber \\
-    &= - \langle\,\frac{1}{n} (X-P^{*}), \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \rangle\ \nonumber \\
-    &\geq -\frac{1}{n} \|X - P^*\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \nonumber \\
-    &\geq -\frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) - \frac{\delta}{2} (\|\widehat{\Delta}^{S}_{\mathbb{M}}\|_{1} +
-    \|\widehat{\Delta}^{S}_{\mathbb{M^\perp}}\|_{1}) \label{eq:27}
-\end{align}
-
-One more round of application on Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1, 
-we can get an upper bound of difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ as follows:
-
-\begin{equation} \label{eq:28}
-    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
-    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
-\end{equation}
-
-By combining relations (\ref{eq:27}) and (\ref{eq:28}), we can get the upper bound of $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$ : 
-\begin{align*}
-    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq 
-    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
-    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}   
-    \|S^{*}_{M^\perp}\|_{1}
-\end{align*}
-
-\end{proof}
-
 \begin{landscape}
-\begin{table}[t]
+\begin{table}[htbp]
+\centering
 \begin{tabular}{lclclclcl}\hline
@@
 \end{tabular}
+\caption{15 pairs of papers that have the largest estimated $\widehat{S}_{ij}$.
+Note that all the 15 edges come from pairs of papers from different communities. }
 \end{table}
+\label{tab:table2}
 \end{landscape}
+
+\section{Conclusion}
+\label{sec:Con}
+
+We propose a new combined latent factor and logistic regression model.
+We consider the regularized likelihood by means of $L_1$ and nuclear norm penalties.
+The computation of the regularized estimator is facilitated by developing an algorithm based on the alternating direction method of multiplier to optimize a non-smooth and convex objective function.
+The proposed method is applied to citation network of statisticians, and the estimated model renders good interpretative power.
+Specifically, our analysis on statistician's citation network sheds the new light on the interpretation of dataset.
+
+Nonetheless, there are still several open questions remaining to be answered.
+First of all, it remains unclear on how to choose the proper tuning parameters.
+Classical methods for choosing tuning parameters such as BIC or AIC did not work in our case, since they tend to choose the most parsimonious models.
+We also do not have systematic ways to do cross validation in network data.
+Not only because it is computationally expensive procedure, but also because if we partition the network data, we can loose fair amount of information on dependent structures among edges.
+This problem is also closely related with determining the number of communities in network.
+In lieu of using BIC or AIC, our analysis is heavily relying on heuristic approach when choosing the tuning parameter, and during this procedure, we use the screeplot for determining number of communities in network.
+Screeplot approach works usually well, but it does not necessarily always guarantee the correct estimate of number of communities.
+We need a more reliable and theoretically well understood way to determine $K$.
+
+Secondly, we only consider the undirected case which is somewhat unrealistic assumption for citation network in real world, in a sense that it is not usual for two papers to cite each other at the same time.
+Since, in our research, we were interested in separating the low rank structure of edges and ad-hoc links in network, we did not take into account the directions of edges in our model.
+However, it would be interesting to consider incorporating the directed network into our matrix decomposition framework.
+
+Last but not least, when we assign the memberships of each nodes, we use $k$-means clustering algorithm.
+However, $k$-means algorithm turns out that it tends to assign nodes conservatively to each communities.
+For example, in $Fig \ref{fig:figure4}(left)$, we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in $Fig \ref{fig:figure4}(right)$ also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
+This is probably because $k$-means does not allow overlapping membership of each nodes.
+It would be interesting to see what happens if we apply some clustering methods which allow the overlapped memberships of nodes in network.
+
+\section{Auxiliary result on non-asymptotic error bound of the estimator}
+In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the sample size is fixed as 1, and the number of variables in model is explicitly tracked.
+We are interested in solving following optimization problem :
+\begin{equation}\label{eq:1}
+\min\limits_{\alpha \in R, S = S^T \atop L \succcurlyeq 0}
+-\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{exp\left(X_{ij}\left(\alpha+
+L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
+L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
+\end{equation}
+
+Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process.
+Let $\widehat{\Theta},\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
+And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*},
+\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
+\widehat{\Delta}^L = \widehat{L}-L^{*},
+\widehat{\Delta}^S = \widehat{S}-S^{*}.$
+Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
+Astute readers might notice the slight difference of first term in objective function between (\ref{eq:logistic10})
+and (\ref{eq:1}).
+Justification of this modification is well explained in \emph{remark 3.1} of the paper \cite{ma2017exploration}.
+We then impose several assumptions for theoretical guarantees of our estimator.
+
+\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
+For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):
+\[
+\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
+\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
+\]
+For any vector $a$, $diag(a)$ is the diagonal matrix with elements of $a$ on its diagonal. For any square matrix $A$ and $B$, $ A \succcurlyeq B $ if and only if $A-B$ is positive semi-definite.
+\end{assumption}
+
+\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
+To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
+We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
+We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
+\end{assumption}
+
+With these assumptions we present the behavior of non-asymptotic error bound of our estimator through following theorem.
+In our result, we measure error using squared Frobenius norm summed across three matrices:
+\[
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
+\]
+
+\begin{theorem} \label{Th:th1}
+Under the assumptions \ref{Ass:1} and \ref{Ass:2},
+if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
+\begin{align} \label{eq:49}
+\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
+\end{align}
+There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
+\begin{align}
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
+    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
+    _{\mathcal{K}_{\alpha^*}} +
+    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
+    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
+    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
+    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
+\end{align}
+where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
+\end{theorem}
+
+We would first like to note readers that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to generalized linear model.
+Our work considers a logistic loss function whose parameters are characterized by sparse matrix plus low rank matrix, whereas \cite{agarwal2012noisy} works on quadratic loss of noisy realization of linear transformation of sum of low rank and sparse matrices.
+We show that similar proof techniques can be applied in our case, giving us similar results.
+%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.
+
+Result of the Theorem \ref{Th:th1} provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $M$, and rank parameter $k$, helping us to understand the behavior of our proposed estimator both in practice and in ideal cases.
+In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.
+In this case, our theorem provides the intuition on the rate on how fast the error bound $\mathcal{K}_{L^*}$ will grow.
+In ideal cases where $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $M$ (i.e., $|supp(S^*)|=s$), we can easily verify ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ (i.e., $\tau\sum_{j=k+1}^{n}\sigma_j(L^*)$) and in $\mathcal{K}_{S^*}$ (i.e., $\tau\sum_{(i,j)\notin M}|S_{ij}^*|$) disappear, giving us Frobenius error bound as follows:
+\[
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s
+\]
+where $\lesssim$ denotes that we ignore constant factors.
+
+\section{Appendix}
+\subsection{Proof of Theorem \ref{Th:th1}}
+
+In proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}.
+Let $(M,M^{\perp})$ denote arbitrary subspace pair for which component-wise $L_{1}$ norm is decomposable.
+Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $M$ as $P_{M}$.
+And also note that proof relies on following lemma:
+
+\begin{lemma} \label{le:le1}
+If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we have
+\[
+    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq
+    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
+    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
+    \|S^{*}_{M^\perp}\|_{1}
+\]
+\end{lemma}
+
+\noindent\textbf{proof of Theorem \ref{Th:th1}}.
+\begin{proof}
+Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal and feasible (respectively) for the convex program (\ref{eq:1}), we have
+\begin{equation}\label{eq:2}
+    h(\widehat{\Theta}) + \delta\|\widehat{L}\|_{*} + \gamma\|\widehat{S}\|_{1} \leq
+     h(\Theta^{*}) + \delta\|{L^{*}}\|_{*} + \gamma\|{S}^{*}\|_{1}
+\end{equation}
+
+Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on the term $h(\widehat{\Theta})-h(\Theta^{*})$ :
+\[
+h(\widehat{\Theta})-h(\Theta^{*}) \geq
+\langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ + \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}
+\]
+
+By rearranging the term in (\ref{eq:2}) and plugging in above inequality relation, we get:
+
+\begin{equation}\label{eq:3}
+    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
+    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
+    + \delta \|L^{*}\|_\ast + \gamma \|S^{*}\|_1
+    - \delta \|\widehat{L}\|_\ast - \gamma \|\widehat{S}\|_1
+\end{equation}
+
+Here, we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers :
+\[
+\mathbb{Q}(L,S)   := \|L\|_{*} + \frac{\gamma}{\delta}\|S\|_1
+\]
+Through the definition of $\mathbb{Q}$, we can rewrite (\ref{eq:3}) as follows:
+\begin{equation}\label{eq:4}
+    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
+    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
+    + \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
+\end{equation}
+
+According to Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1,
+the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ is upper-bounded by
+
+\begin{equation}\label{eq:5}
+    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
+    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
+\end{equation}
+
+First, we want to control upper bound of the term $-\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\,$
+in (\ref{eq:4}).
+\begin{align}
+-\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\  \nonumber
+&=\langle\, \frac{1}{n} (X - P^*), \widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S} \rangle\ \\ \nonumber
+&\leq \frac{1}{n} \|X - P^*\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
+&\leq \frac{1}{n} \|X - P^*\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) +
+\frac{1}{n} \|X - P^*\|_{\infty}(\|\widehat{\Delta}^{S}_{M}\|_{1} +
+\|\widehat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\
+&\leq \frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) + \frac{\gamma}{2}(\|\widehat{\Delta}^{S}_{M}\|_{1} +
+\|\widehat{\Delta}^{S}_{M^{\perp}}\|_{1})  \label{eq:10}
+\end{align}
+
+Combining the inequalities (\ref{eq:5}) and (\ref{eq:10}), we can obtain the upper bound of RHS in (\ref{eq:4}) as follows:
+
+\begin{equation}
+    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
+    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
+    \frac{3\delta}{2}\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M})
+    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\gamma \|S^*_{M^\perp}\|_{1}
+    \label{eq:11}
+\end{equation}
+
+Second, we wish to control the lower bound of the term  $\frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}$ with respect to $\hat{\Delta}^{\alpha},\widehat{\Delta}^{L},\widehat{\Delta}^{S}$.
+\begin{align}
+\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
+&= \|\widehat{\Theta}-\Theta^{*} \|_{F}^{2} \\ \nonumber
+&= \|\widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S}\|_{F}^{2} \\ \nonumber
+&= \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}+\widehat{\Delta}^{S}\|_{F}^{2} +
+2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ \\
+&=  \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2} +
+2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
+2 \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\  \label{eq:12}
+\end{align}
+
+We want to get the further lower bound on trace inner product terms,
+$ \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $.
+To control the first trace inner product term, we use the relation $\widehat{\Delta}^{L}\mathbbm{1}=0$, apply the definition of dual norm on inner product term, apply triangular inequality on $\hat{\Delta}^\alpha$, and lastly we apply the constraint imposed on $|\alpha|$ stated in Assumption \ref{Ass:2}.
+
+\begin{align}
+    | \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \nonumber
+    &= | \langle\,\widehat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\ \nonumber
+    &\leq \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\widehat{\Delta}^{S}\|_1 \\ \nonumber
+    &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\widehat{\Delta}^{S}\|_1\\
+    &\leq 2C\kappa\|\widehat{\Delta}^{S}\|_1  \label{eq:13}
+\end{align}
+
+To control the term $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $, we first apply the definition of dual norm on trace inner product term, then apply triangular inequality on $\widehat{\Delta}^{L}$ and spikiness condition.
+
+\begin{align}
+    | \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ | \nonumber
+    &\leq \|\widehat{\Delta}^{L}\|_{\infty} \|\widehat{\Delta}^{S}\|_1\\ \nonumber
+    &\leq (\|\widehat{L}\|_{\infty} + \|L^{*}\|_{\infty})
+    \|\widehat{\Delta}^{S} \|_{1}\\
+    &\leq \big(\frac{2\kappa}{n}\big)\|\widehat{\Delta}^{S} \|_{1} \label{eq:14}
+\end{align}
+
+We can combine the inequality (\ref{eq:12}), (\ref{eq:13}) and (\ref{eq:14}).
+Then applying the assumption on regularization parameter $\gamma$, and the fact $\|\widehat{\Delta}^{L}\|_{\ast}\geq0$ sequentially, we can get,
+
+\begin{align}
+    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2}
+    - 2\kappa\tau(\frac{Cn+1}{n})\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\widehat{\Delta}^{S}\|_{1}\\
+    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S) \label{eq:26}
+\end{align}
+
+By combining the relations (\ref{eq:11}) and (\ref{eq:26}), applying triangular inequality, $\mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S)\leq \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) + \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^{\perp}})$, and rearranging the term, we can get following inequality,
+\[
+    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} \\
+    \leq \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
+    2\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) +  \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) +
+    2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 2\gamma
+    \|S^{*}_{M^\perp}\|_{1}
+\]
+
+Further, by plugging in Lemma 1 to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows:
+\begin{align}
+    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} -
+    \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}
+    \leq
+    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}  \label{eq:42}
+\end{align}
+Noting that $\widehat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\widehat{\Delta}^{S}_{M}$ lies in the model space $M$, we find that
+\begin{align}
+    \nonumber
+    \delta\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M})
+    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L_{A}\|_{F} + \Psi(M)\gamma\|\widehat{\Delta}^S_M\|_{F}\\
+    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L\|_{F} + \Psi(M)\gamma\|\widehat{\Delta}^S\|_{F}  \label{eq:43}
+\end{align}
+Here $\Psi(M)$ measures the compatibility between Frobenius norm and component-wise $L_{1}$ regularizer, where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
+\[
+    \Psi(M):=\sup\limits_{U\in M,U\neq0}\frac{\|U\|_{1}}{\|U\|_{F}}
+\]
+Using Cauchy-Schwarz inequality, we can easily check the quantity $\Psi(M)$ is bounded by at most $\sqrt{s}$.
+Plugging in the relation ($\ref{eq:43}$) into ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$ yield the claim.
+\end{proof}
+
+\subsection{Proof of Lemma \ref{le:le1}}
+
+\begin{proof}
+Through the application of basic inequality by using optimality of $\widehat{\Theta}$ and feasibility of $\Theta^{*}$ to convex program (\ref{eq:1}), we have
+\begin{equation}
+    h(\widehat{\Theta}) - h(\Theta^{*})
+    \leq \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
+\end{equation}
+By using convexity of $h(\Theta)$, we can write
+\begin{align}
+    h(\widehat{\Theta})-h(\Theta^{*}) &\geq
+    \langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ \nonumber \\
+    &= - \langle\,\frac{1}{n} (X-P^{*}), \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \rangle\ \nonumber \\
+    &\geq -\frac{1}{n} \|X - P^*\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \nonumber \\
+    &\geq -\frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) - \frac{\delta}{2} (\|\widehat{\Delta}^{S}_{M}\|_{1} +
+    \|\widehat{\Delta}^{S}_{M^\perp}\|_{1}) \label{eq:27}
+\end{align}
+
+One more round of application on Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1,
+we can get an upper bound of difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ as follows:
+
+\begin{equation} \label{eq:28}
+    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
+    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
+\end{equation}
+
+By combining relations (\ref{eq:27}) and (\ref{eq:28}), we can get the upper bound of $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$ :
+\begin{align*}
+    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq
+    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
+    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
+    \|S^{*}_{M^\perp}\|_{1}
+\end{align*}
+
+\end{proof}
 

### 2019-08-18 Codes & Data/Codes/Synthetic Data.R

@@ -138,8 +138,6 @@ par(mfrow=c(1,3))
 plot(X_draw,main="N=30,K=3,NNZ=10")
 
 
-
-
 #################### data generation N = 80, K = 4, NNZ = 20 ####################
 N = 80; K = 4; NNZ = 20;
 ### Ingredients for creating network : alpha, F, D, S                      
@@ -268,9 +266,6 @@ for(i in 1:length(B[,1])){
 E(X_draw2)$color <- "black"
 E(X_draw2)[list]$color <- "blue"
 plot(X_draw2,main="N=80,K=4,NNZ=20")
-
-
-
 
 
 #################### data generation N = 120, K = 5, NNZ = 40 ###########################

### 2019-08-20 Manuscript for submission/manuscript.tex
Update
minor changes

@@
 \documentclass[AMS,STIX1COL]{WileyNJD-v2}
-\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
+%\documentclass[AMS]{WileyNJD-v2}
+\usepackage{graphicx,times,verbatim,amsmath,amsthm}
+%\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
 \usepackage{amsmath,amsfonts}
@@
 
-\title{Factor Analysis on Citations, using a Combined Latent and Logistic Regression Model}
+\title{Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model}
 
@@
 Given that $L = F^T D F$ where matrix $D$ is diagonal with nonnegative diagonal entries, it is easy to see that matrix $L$ is positive semidefinite; which consequently leads to $\|L\|_\ast = \mbox{trace}(L)$, which is a linear functional to the matrix $L$.
-The nuclear norm of $L$ penalizes the number of nonzero eigenvalues of $L$, which is the same as the rank
+The nuclear norm of $L$ mimicks the number of nonzero eigenvalues of $L$, which is the same as the rank
 of $L$.
@@
      and make sure that each column of $F^{*}$ has only one $1$.
-     In last row of $F^*$, fill in the last remaining $n-K\floor{\frac{n}{K}}$ entries with $1$s.
+     In last row of $F^*$, fill in the last remaining $n-K\floor{\frac{n}{K}}$ entries with $1$'s.
      Then, we randomly choose one of columns, and fill that column with ones.

### 2019-08-22 Manuscript for submission/manuscript.tex
Update

@@
 \mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
-= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{f_i^T D f_j }},
+= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
 \end{equation}
@@
 
-Our work is motivated from a recent work {\it Fused Latent and Graphical (FLaG) model} (Chen et al, 2016, \cite{chen2016fused}).
+Our work is motivated from a recent work {\emph{Fused Latent and Graphical (FLaG) model} (Chen et al, 2016, \cite{chen2016fused}).
 They assume that majority of variation of responses can be accounted by low dimensional latent vector, and remaining dependent structure of responses can be explained by sparse graphical structure.
@@
 Their key idea is to separate these two dependent structures so that they can facilitate the statistical inference.
-Our model also assumes that there exist two dependent structures among citation edges in network.
+In our model, we also assume that there exist two dependent structures among citation edges in a network.
 A low-dimensional version of the aforementioned latent vector model is largely correct and majority of the citations among the nodes are induced by these common latent vectors $f_{i}$'s (with weight coefficients $d_{i}$'s).
-There is still a small remainder due to the graphical component.
+There is still a small remainder due to the sparse graphical component.
 
@@
 
-\item FLaG sets a collection of binary responses for each individual questions follow a joint distribution which is a combination of Item Response Theory (IRT) model and the Ising model, whereas we model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of Latent Factor Analysis model and the logistic regression model.
-
-\item FLaG approximates the original likelihood through constructing pseudo-likelihood function by taking advantage of conditional independence among the nodes, but our model's likelihood function is directly accessible due to the conditional independence among edges given parameters.
-
+\item In FLaG model, a collection of binary responses for each question in the questionnaire follows a joint distribution, which is a combination of the Item Response Theory (IRT) model and the Ising model.
+    We model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of the Latent Factor Analysis model and the sparse graphical model.
+
+\item FLaG approximates the original likelihood through constructing pseudo-likelihood function by taking advantage of conditional independence among the nodes.
+    In our model, likelihood function is directly accessible due to the conditional independence among edges given parameters.
 \end{enumerate}
 
-The proposed modeling framework is also related with the analysis of decomposing a matrix into low-rank and sparse components and the statistical inference of a multivariate Gaussian model whose precision matrix admits the form of a low-rank matrix plus a sparse matrix (\cite{chandrasekaran2010latent, candes2011robust, zhou2010stable}).
+The proposed modeling framework is also related with the analysis of decomposing a matrix into low-rank and sparse components (\cite{agarwal2012noisy,candes2011robust,chandrasekaran2010latent, zhou2010stable}).
+Specifically, \cite{chandrasekaran2010latent} studies statistical inference of a multivariate Gaussian model whose precision matrix admits the form of a low-rank matrix plus a sparse matrix.
 The inference and optimization of the current model are different from the aforementioned cases.
 We will construct a regularized-likelihood function, based on which estimator will be proposed for simultaneous model selection and parameter estimation.
-The optimization for the regularized estimator will be convex, for which we will develop an efficient algorithm through the alternating direction method of multiplier (ADMM, \cite{boyd2011distributed, gabay1975dual, glowinski1975solution}).
+The objective function in the optimization problem for the regularized estimator is convex, for which we will develop an efficient algorithm through the alternating direction method of multiplier (ADMM, \cite{boyd2011distributed, gabay1975dual, glowinski1975solution}).
 
 The rest of the paper is organized as follows.
-In Section \ref{sec:model-form} we will give a presentation on how to build a model which can encode both latent dependent structure due to the common topics and remaining ad-hoc dependent structure.
-In section \ref{sec:estimate}, we will discuss about the assumptions in our model and penalization on likelihood function constructed in section \ref{sec:model-form}.
+In Section \ref{sec:model-form}, we will give a presentation on how to build a model, which can encode both the latent dependent structure due to the common topics and the remaining sparse ad-hoc dependent structure.
+In Section \ref{sec:estimate}, we will discuss the assumptions in our model and penalization on likelihood function that is constructed in Section \ref{sec:model-form}.
 Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem formulated in Section \ref{sec:estimate}.
 In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians.
-We finally conclude this work in section \ref{sec:Con} with several open questions remain to be solved and some directions for future research.
+We finally conclude this work in Section \ref{sec:Con} with several open questions and some directions for future research.
 
@@
 \mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
-= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{f_i^T D f_j }},
+= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
 $$
@@
 \label{sec:estimate}
-
 Note that in the model \eqref{eq:logistic07}, the log-likelihood function has the form as follows:
@@
 where $\gamma>0$ and $\delta>0$ are algorithmic parameters whose values will be discussed later,
-the $L_1$ norm of matrix $S$ is defined as $\|S\|_1 = \sum_{i\neq j} S_{ij}$ (Note that we do not penalize the diagonal entries of $S$), and nuclear norm of matrix $L$ is defined as $\|L\|_\ast = {\mbox{trace}\sqrt{(L^T L)}}$.
+the $L_1$ norm of matrix $S$ is defined as $\|S\|_1 = \sum_{i\neq j} |S_{ij}|$ (Note that we do not penalize the diagonal entries of $S$), and nuclear norm of matrix $L$ is defined as $\|L\|_\ast = {\mbox{trace}\sqrt{(L^T L)}}$.
 Recall that both $S$ and $L$ are symmetric matrices.
@@
 On the other hand when we have calculated $\widehat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\widehat{L} = F^T D F.$
-This is the price we have to pay for an amenable computational problem.
-The rank of estimated $\widehat{L}$ will be our estimate of the number of factors (i.e., underlying common topics).
+This is the price we have to pay for an amenable computational approach.
+The rank of estimated $\widehat{L}$ will be our estimate of the number of factors (i.e., the number of underlying common topics).
 For the issue on assigning the community membership of each node $i$, we will discuss this later in Section \ref{sec:Num-anal}.
+
+\section{Non-asymptotic error bound of the estimator}
+In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the number of papers in network is explicitly tracked.
+We are interested in solving the following optimization problem :
+\begin{equation}\label{eq:Modified}
+\min\limits_{\alpha \in R, S = S^T \atop L \succcurlyeq 0}
+-\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{\exp\left(X_{ij}\left(\alpha+
+L_{ij}+S_{ij}\right)\right)}{1+\exp\left(\alpha+
+L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
+\end{equation}
+
+%Astute readers might notice the slight difference of the first term in objective function between (\ref{eq:logistic10}) and (\ref{eq:Modified}).
+For the convenience of theoretical investigation, we slightly modify the first term in the objective function summing over all $(i,j)$ pairs.
+After scaling, due to symmetry of $X$,$L$, and $S$, the only difference between (\ref{eq:logistic10}) and (\ref{eq:Modified}) is in the inclusion of terms in diagonal pairs $(i,i),\forall i=1,\dots,n$.
+%the first term in the objective function in (\ref{eq:Modified}) sums over all $(i,j)$ pairs.
+This slight modification leads to neither theoretical consequence nor noticeable difference in practice.
+Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:Modified}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth, which governs the data generating process.
+Let $\widehat{\Theta},\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
+And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*},
+\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
+\widehat{\Delta}^L = \widehat{L}-L^{*},
+\widehat{\Delta}^S = \widehat{S}-S^{*}.$
+Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
+We then impose several assumptions for theoretical guarantees of our estimator.
+
+\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
+For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):
+\[
+\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
+\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
+\]
+For any vector $a$, $diag(a)$ is the diagonal matrix with elements of $a$ on its diagonal. For any square matrix $A$ and $B$, $ A \succcurlyeq B $ if and only if $A-B$ is positive semi-definite.
+\end{assumption}
+
+\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
+To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
+We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
+We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
+\end{assumption}
+
+With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through following theorem.
+In our result, we measure error using squared Frobenius norm summed across three matrices:
+\[
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
+\]
+
+\begin{theorem} \label{Th:th1}
+Under the assumptions \ref{Ass:1} and \ref{Ass:2},
+if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
+\begin{align} \label{eq:49}
+\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
+\end{align}
+There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
+\begin{align}
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
+    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
+    _{\mathcal{K}_{\alpha^*}} +
+    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
+    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
+    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
+    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
+\end{align}
+where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
+\end{theorem}
+
+We would first like to note readers that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to generalized linear model.
+Our work considers a logistic loss function whose parameters are characterized by sparse matrix plus low rank matrix, whereas \cite{agarwal2012noisy} works on quadratic loss of noisy realization of linear transformation of sum of low rank and sparse matrices.
+We show that similar proof techniques can be applied in our case, giving us similar results.
+%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.
+
+Result of the Theorem \ref{Th:th1} provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $M$, and rank parameter $k$, helping us to understand the behavior of our proposed estimator both in practice and in ideal cases.
+In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.
+In this case, our theorem provides the intuition on the rate on how fast the error bound $\mathcal{K}_{L^*}$ will grow.
+In ideal cases where $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $M$ (i.e., $|supp(S^*)|=s$), we can easily verify ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ (i.e., $\tau\sum_{j=k+1}^{n}\sigma_j(L^*)$) and in $\mathcal{K}_{S^*}$ (i.e., $\tau\sum_{(i,j)\notin M}|S_{ij}^*|$) disappear, giving us Frobenius error bound as follows:
+\[
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s
+\]
+where $\lesssim$ denotes that we ignore constant factors.
 
@@
 We propose a method that takes advantage of the special structure
-of the $L_1$ and nuclear norms by means of the
+of the $L_1$ and the nuclear norm by means of the
 alternating direction method of multiplier (ADMM), which is a method
@@
 The problem in \eqref{eq:admm02} may not have a closed-form solution.
-We use a simple gradient descent to solve this step, setting the step size equal to $0.1$ and stopping criteria as $\max(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}) \leq 10^{-9}$.
+We use a simple gradient descent to solve in this step, setting the step size equal to $0.05$ and stopping criteria as $\max(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}) \leq 10^{-9}$.
 Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem.
@@
 In this work, we simply choose $\lambda = 0.5$.
-We terminate the algorithm  when in $m$th iteration, $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^{-7}$.
+We terminate the algorithm  when in the $m$th iteration, we have $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^{-7}$.
 
@@
 \label{sec:Num-anal}
-In this section, we have conducted a small empirical study of measuring the performance of our proposed method with artificially specified graphical structures,\ref{sec:Syn-dat}.
-Also we perform a real data analysis with citation network for statisticians,\ref{sec:citation_network}.
-\subsection{Synthetic data}
+Section \ref{sec:Num-anal} is divided into two parts.
+In subsection \ref{sec:Syn-dat}, we conduct an empirical study of measuring the performance of our proposed method with artificially specified graphical structures.
+In subsection \ref{sec:citation_network}, we perform a real data analysis with citation network for statisticians.
+
+\begin{remark}
+Throughout the Section, we add $*$ to the superscript of parameters when they govern a data-generating process.
+$\alpha^*$ is an intercept term in logistic regression model.
+$f^*_j$ is the $j$th column of factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in network, and $n$ denotes the number of papers in a network.
+Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote weight coefficient of factors. 
+$S_{ij}^*$ denotes an ad-hoc citational relation between $i$th and $j$th paper.
+We use the notation $|S^*|$ to denote the cardinality of non-zero components of upper-triangular part of $S^*$ matrix 
+(i.e., $|S^*|=|\{(i,j) : S_{ij}^{*}\neq 0, 1 \leq i<j \leq n\}|$).
+We will use $X \sim \text{Unif}[a,b]$ to denote
+$X$ is drawn from uniform distribution supported on the interval $[a,b]$.
+\end{remark}
+
+\subsection{Numerical experiments with synthetic data}
 \label{sec:Syn-dat}
-\textbf{Data Generation}.
+In this subsection, after a brief introduction on several synthetic scenarios that we want to explore, we will discuss how to set ground truth parameters for generating synthetic networks from pre-specified scenarios.
+Then, three model selection criteria and related evaluation metrics for the selected model will be introduced.
+Lastly, several interesting findings from the experiments will be presented.
+
+\subsubsection{Synthetic Setting}
+We consider following three scenarios: $\{(n^{(i)},K^{(i)},nnz^{(i)})\}_{i=1}^{3}=\{(30,3,10),(80,4,20),(120,5,40)\}$.
+
+\subsubsection{Data Generation}
 Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P^{*}_{ij}=\frac{\exp (
@@
      %and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying the aforementioned $J = I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$.
-    \item Each element of diagonal matrix $D^{*}$ are generated from Unif$[7,8]$.
-    \item For the sparse component $S^*$, first draw $nnz$ distinct random pairs of indices that are uniformly distributed over the indices of upper triangular part (off diagonal) of matrix $S^*$.
+    \item Each element of diagonal matrix $D^{*}$ is generated from uniform distribution supported on $[7,8]$.
+    \item For the sparse component $S^*$, first draw $|S^*|$ sparsity pattern
+    first draw $nnz$ distinct random pairs of indices that are uniformly distributed over the indices of upper triangular part (off diagonal) of matrix $S^*$.
 For each drawn pair of indices $(i,j)$, draw random number from Unif$[7,8]$ (i.e., $S^*_{ij}\sim\text{Unif}[7,8]$).
-$nnz$ denotes the number of non-zero component of the upper-triangular part of $S^{*}$.
 \end{enumerate}
 
-We consider following three scenarios: $\{(n^{(i)},K^{(i)},nnz^{(i)})\}_{i=1}^{3}=\{(30,3,10),(80,4,20),(120,5,40)\}$.
-
-\textbf{Choosing the tuning parameters and evaluation criteria}.
-We have to admit the fact that choosing a good pair of tuning parameters is an important but challenging issue in our problem.
-Here we present a purely heuristic approach.
-Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest 20 eigenvalues of adjacency matrix $X$, which can tell us the numbers of communities embedded in network.
-Then, we record the rank of $\widehat{L}$ and number of non-zero elements in $\widehat{S}$ for each tuning parameter pair on grid, and choose a proper pair that give us interesting interpretations of data.
-
-One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, work where we define BIC and AIC as follows:
+\subsubsection{Choosing the tuning parameters and evaluation criteria}
+We observe that choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
+Here we present a heuristic approach.
+Following the approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of adjacency matrix $X$, which can tell us the number of communities embedded in network.
+Then, we record the rank of $\widehat{L}$ and number of non-zero elements in $\widehat{S}$ for each tuning parameter pair on a given grid, and choose a proper pair that give us interesting interpretations of data.
+
+One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) and the AIC, work where we recall that BIC and AIC are defined as follows:
 \[
@@
 and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $S$ and the low-rank matrix $L$.
-If rank$(L)=K$, we can establish the following
-\[
-|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1,
+If we have $\text{rank}(L)=K$, we can establish the following
+\[
+|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1 ;
 \]
@@
 Additionally $1$ in the last is due to $\alpha$.
-We want to find an $M$ which minimizes BIC($M$) or AIC($M$) as a function of $M$.
+We want to find an $M$, which minimizes BIC($M$) or AIC($M$) as a function of $M$.
 However these traditional methods seem to entail a serious problem.
-The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
-Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest K and smallest cardinality of ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$) from a pair of tuning parameters over the given range of grid.
-For clarification on this argument, we evaluate the models selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.
+%The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
+Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\text{supp}(\widehat{S})|/2)$ of ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$)s'.
+We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.
 
@@
 \caption{ For three scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
-Note that both AIC and BIC choose the model with no ad-hoc structure (i.e., $\widehat{S}=0$),
-and $\widehat{L}$ with the lowest rank among all estimators via a pair of tuning parameter over the grid of search region.}
+Note that, for all three scenarios, both AIC and BIC choose the model with no ad-hoc structure (i.e., $\widehat{S}=0$), and $\widehat{L}$ with rank $1$ (i.e.,$\text{rank}(\widehat{L})=1$).}
 \label{tab:table1}
@@
 
-\textbf{Community memberships of each nodes}.
+\subsubsection{Findings}
 Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$.
 We applied a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
-For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig \ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2D$ plane.
+For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
 %Furthermore, we find one interesting phenomenon.
@@
 
-\textbf{Simulation Results}.
-Our goal in this simulation experiment is to check if our model can cluster each nodes into correct communities.
-Also to see if it can separate the ad-hoc links from edges which come from common topics.
-Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$, respectively, give us the desirable results for the three scenarios.
-For first scenario, both $\gamma$ and $\delta$ are searched over $\{0.01,0.02,\dots,0.1\}$.
-For second and third scenarios, parameters are searched over $100$ points, equidistant, from the interval $[0.001,0.01]$ for $\gamma$, and $[0.01,0.02]$ for $\delta$.
+%\textbf{Simulation Results}.
+%Our goal in this simulation experiment is to check if our model can cluster each nodes into correct communities.
+%Also to see if it can separate the ad-hoc links from edges which come from common topics.
+%Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$, respectively, give us the desirable results for the three scenarios.
+%For first scenario, both $\gamma$ and $\delta$ are searched over $\{0.01,0.02,\dots,0.1\}$.
+%For second and third scenarios, parameters are searched over $100$ points, equidistant, from the interval $[0.001,0.01]$ for $\gamma$, and $[0.01,0.02]$ for $\delta$.
 %Note that different dynamics of network requires different choices of tuning parameters even the synthetic setting is same, since we are generating the random graph.
 %In order to avoid this problem, we set the seeds in our simulation so that the results are reproducible. (Code is provided in $\emph{https://sites.google.com/site/namjoonsuh/publications}$.)
-Fig. \ref{fig:figure1} shows us the result of clustered nodes using $k$-means algorithm on the first $K(=\mbox{rank}(\widehat{L}))$ eigenvectors.
-We plot the rows of first two eigenvectors on the cartesian plane since it visualizes well the clustering behavior of the nodes.
-Our model chooses well the ad-hoc links between clusters of nodes as can be verified in Fig. \ref{fig:figure2}.
-We color the edges in blue whose corresponding elements of estimated $\widehat{S}$ are non-zero, and color the edges in black whose corresponding entries of $\widehat{S}$ are zero.
+%Fig. \ref{fig:figure1} shows us the result of clustered nodes using $k$-means algorithm on the first $K(=\mbox{rank}(\widehat{L}))$ eigenvectors.
+%We plot the rows of first two eigenvectors on the cartesian plane since it visualizes well the clustering behavior of the nodes.
+%Our model chooses well the ad-hoc links between clusters of nodes as can be verified in Fig. \ref{fig:figure2}.
+%We color the edges in blue whose corresponding elements of estimated $\widehat{S}$ are non-zero, and color the edges in black whose corresponding entries of $\widehat{S}$ are zero.
 
@@
 \end{figure}
-This dataset is based on all papers published from $2003$ to first half of $2012$, in $4$ of the top statistical journals: ``Annals of Statistics'', ``Biometrika'', ``Journal of American Statistical Association'' and ``Journal of Royal Statistical Society (Series B)''.
-Among  $3248$ papers in total, we restrict our attention on papers which have greater than or equal to $7$ citations from the collected papers in original dataset.
-We have $543$ papers in our hands.
-The elbow points of the scree plot may be at the $3$rd, $7$th, or $9$th largest eigenvalue, suggesting that there might be from $2$ to $8$ topics in network (See $Fig \ref{fig:figure3}, left$).
-In light of this, we performed our analysis under the assumption that there might exist $2$ distinct topics and one giant component in which $3$ or $4$ topics are mixed up.
-
-A pair of parameters, $(\gamma,\delta) = (0.000912,0.0097)$, gives us $\widehat{L}$ with rank $3$, and $\widehat{S}$ with $|supp(\widehat{S})|/2=197$.
-We apply $k$-means algorithm on $3$ eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in $Fig \ref{fig:figure4}$.
+This dataset is based on all papers published from $2003$ to first half of $2012$, in $4$ of the top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association and Journal of Royal Statistical Society (Series B).
+Among  $3248$ papers in total, we restrict our attention on papers, which have greater than or equal to $7$ citations from the collected papers.
+Consequently, we have $543$ papers in total.
+The elbow points of the eigen-value scree plot  from  may be at the $3$rd, $7$th, or $9$th largest eigenvalue, suggesting that there might be from $2$ to $8$ topics embedded in network (See Fig$ \ref{fig:figure3}$).
+In light of this, we performed our analysis under the assumption that there might exist $2$ distinct topics and one giant component, in which $3$ or $4$ topics are mixed up.
+
+A pair of parameters, $(\gamma,\delta) = (0.000912,0.0097)$, gives us $\widehat{L}$ with rank $3$, and $\widehat{S}$ with $|\widehat{S}|=197$.
+We apply $k$-means algorithm on $3$ eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in Fig $\ref{fig:figure4}$.
 $404$ papers colored in green are densely clustered nearby the origin with a short tail, $(Fig \ref{fig:figure4})$, and $k$-means classifies these papers as third topic.
 We list the first two topics discovered through our analysis.
-Full lists of papers for each communities are provided in $\emph{https://sites.google.com/site/namjoonsuh/publications}$.
+%Full lists of papers for each communities are provided in $\emph{https://sites.google.com/site/namjoonsuh/publications}$.
 
@@
 \noindent These two topics are classical research topics in field of statistics.
-First group talks about ``Variable selection'' in high-dimensional data.
-Majority of papers in second community study about ``Controlling False Discovery Rate'' in various statistical settings.
+First group talks about Variable Selection in high-dimensional data.
+Majority of papers in second community study about Controlling False Discovery Rate in various statistical settings.
 As expected, third group is quite hard to interpret and seems to have substructures.
-For further investigation on this group, after obtaining the sub-network which is comprised only with papers in third group, we performed same analysis once again under the assumption that $K=4$ (See $Fig \ref{fig:figure3},right$).
+For further investigation on this group, after obtaining the sub-network which is comprised only with the papers in the third group, we performed same analysis once again under the assumption that $K=4$ (See $Fig \ref{fig:figure3},right$).
 We obtain four sub-communities as follows:
@@
 
-Out of this one big chunk, we got three small, but meaningful topics: ``Bayesian Statistics'', ``Functional/longitudinal data analysis'', ``Dimension Reduction''.
+Out of this one big chunk, we got three small, but meaningful topics: Bayesian Statistics, Functional / Longitudinal Data Analysis, Dimension Reduction.
 Due to small volume of each communities, we could manually check that false discoveries for each community are all zero.
 
-Sub-network structure has also a big chunk of papers which we refer to as ``Mixed Topics''.
-Not only could we see the papers with topics on ``Learning Theory'', ``Non-parametric/semi-parametric statistics'', ``Spatial Statistics'', ``Theoretical Machine Learning'', which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
-Papers like ``The Bayesian Lasso (T.
+Sub-network structure has also a big chunk of papers which we refer to as Mixed Topics.
+Not only could we see the papers with topics on Learning Theory, Non-parametric/Semi-parametric Statistics, Spatial Statistics, Theoretical Machine Learning, which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
+Papers, such as The Bayesian Lasso (T.
 Park, et al.
-2008)'', ``Coordinate-independent sparse sufficient dimension reduction and variable selection (X.
+$2008$), Coordinate-independent sparse sufficient dimension reduction and variable selection (X.
 Chen, et al.
-2010)'' are the examples of these papers.
+$2010$), are the examples of these papers.
 It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed topic classified as Mixed topic.
-For instance, ``On the "degrees of freedom" on the LASSO (H. Zou, et al. 2007)'' is classified as Mixed Topic paper.
+For instance, ``On the "degrees of freedom" on the LASSO (H. Zou, et al. $2007$)'' is classified as Mixed Topic paper.
 We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities.
-Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics.
-
-Furthermore, it is worth to note that our result is consistent with that from Ji and Jin \cite{ji2016coauthorship} in a sense that they also recover ``Multiple Testing'', ``Variable selection'' and ``non-parametric Bayesian statistics''.
+Actually, out of $19$ citation relationships it has with other papers, $12$ of them came from the relationships with papers from Mixed topics.
+
+Furthermore, it is worth to note that our result is consistent with that from Ji and Jin \cite{ji2016coauthorship} in a sense that they also recover topics such as Multiple Testing, Variable Selection and Non-parametric Bayesian statistics.
 This is interesting since even though the dataset we consider is different from theirs, the results are consistent.
@@
 Non-zero components of $\widehat{S}$ capture the citation relationships among papers that are not attributable to the common topics.
-The model we select has 197 sparse edges ($9\%$ of total edges), and all of them are positive edges.
-In Table \ref{tab:table2}, we provide 15 pairs of papers that have the largest estimated $\widehat{S}_{ij}$.
-All the 15 edges come from pairs of papers from different communities.
-For instance, the first pair of papers comes from the ``Functional Analysis'' community (denoted by \emph{FuncAn}) and ``Variable selection'' $(\emph{VarSel})$ community.
+The model we select has $197$ sparse edges ($9\%$ of total edges), and all of them are positive edges.
+In Table \ref{tab:table2}, we provide $15$ pairs of papers that have the largest estimated $\widehat{S}_{ij}$.
+All the $15$ edges come from pairs of papers from different communities.
+For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable Selection $(\emph{VarSel})$ community.
 $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
 Though it might seem to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
-Second pair comes from ``Multiple Testing'' (denoted as $\emph{MulT}$) and ``Variable Selection'' ($\emph{VarSel}$) community.
+Second pair comes from Multiple Testing (denoted as $\emph{MulT}$) and Variable Selection ($\emph{VarSel}$) community.
 $\emph{MulT}$ paper briefly mentions about $\emph{VarSel}$ paper in future work section, suggesting a possible way of combining their work and work in $\emph{VarSel}$ paper.
-And we also observe that as the estimated weight of sparse edges (i.e., $\widehat{S}_{ij}$) decreases, the number of pairs of papers that come from "Mixed topics" community increases.
+And we also observe that as the estimated weight of sparse edges (i.e., $\widehat{S}_{ij}$) decreases, the number of pairs of papers that come from Mixed topics community increases.
 
@@
 \caption{Illustration of first two eigenvectors of estimated $\widehat{L}$ matrix for original
-citation network with 543 papers (left) and sub-network graph (right). We present
+citation network with $543$ papers (left) and sub-network graph (right). We present
 the results of assignment of each paper to each topic via $k$-means algorithm with different colors.}
@@
 \end{tabular}
-\caption{15 pairs of papers that have the largest estimated $\widehat{S}_{ij}$.
+\caption{15 pairs of papers that have the largest $\widehat{S}_{ij}$ among the 197 non-zero component of $\widehat{S}$.
 Note that all the 15 edges come from pairs of papers from different communities. }
@@
 
-We propose a new combined latent factor and logistic regression model.
+We propose a new combined latent factor and sparse graphical model.
 We consider the regularized likelihood by means of $L_1$ and nuclear norm penalties.
@@
 
-Nonetheless, there are still several open questions remaining to be answered.
+Nonetheless, there are still several questions remaining to be answered.
 First of all, it remains unclear on how to choose the proper tuning parameters.
@@
 In lieu of using BIC or AIC, our analysis is heavily relying on heuristic approach when choosing the tuning parameter, and during this procedure, we use the screeplot for determining number of communities in network.
-Screeplot approach works usually well, but it does not necessarily always guarantee the correct estimate of number of communities.
+Screeplot approach works well in general situation, but it does not necessarily always guarantee the correct estimate of number of communities.
 We need a more reliable and theoretically well understood way to determine $K$.
@@
 However, $k$-means algorithm turns out that it tends to assign nodes conservatively to each communities.
-For example, in $Fig \ref{fig:figure4}(left)$, we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in $Fig \ref{fig:figure4}(right)$ also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
+For example, in Fig$\ref{fig:figure4}(left)$, we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in Fig$\ref{fig:figure4}(right)$ also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
 This is probably because $k$-means does not allow overlapping membership of each nodes.
 It would be interesting to see what happens if we apply some clustering methods which allow the overlapped memberships of nodes in network.
-
-\section{Auxiliary result on non-asymptotic error bound of the estimator}
-In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the sample size is fixed as 1, and the number of variables in model is explicitly tracked.
-We are interested in solving following optimization problem :
-\begin{equation}\label{eq:1}
-\min\limits_{\alpha \in R, S = S^T \atop L \succcurlyeq 0}
--\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{exp\left(X_{ij}\left(\alpha+
-L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
-L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
-\end{equation}
-
-Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process.
-Let $\widehat{\Theta},\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
-And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*},
-\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
-\widehat{\Delta}^L = \widehat{L}-L^{*},
-\widehat{\Delta}^S = \widehat{S}-S^{*}.$
-Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
-Astute readers might notice the slight difference of first term in objective function between (\ref{eq:logistic10})
-and (\ref{eq:1}).
-Justification of this modification is well explained in \emph{remark 3.1} of the paper \cite{ma2017exploration}.
-We then impose several assumptions for theoretical guarantees of our estimator.
-
-\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
-For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):
-\[
-\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
-\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
-\]
-For any vector $a$, $diag(a)$ is the diagonal matrix with elements of $a$ on its diagonal. For any square matrix $A$ and $B$, $ A \succcurlyeq B $ if and only if $A-B$ is positive semi-definite.
-\end{assumption}
-
-\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
-To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
-We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
-We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
-\end{assumption}
-
-With these assumptions we present the behavior of non-asymptotic error bound of our estimator through following theorem.
-In our result, we measure error using squared Frobenius norm summed across three matrices:
-\[
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
-\]
-
-\begin{theorem} \label{Th:th1}
-Under the assumptions \ref{Ass:1} and \ref{Ass:2},
-if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
-\begin{align} \label{eq:49}
-\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
-\end{align}
-There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
-\begin{align}
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
-    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
-    _{\mathcal{K}_{\alpha^*}} +
-    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
-    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
-    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
-    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
-\end{align}
-where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
-\end{theorem}
-
-We would first like to note readers that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to generalized linear model.
-Our work considers a logistic loss function whose parameters are characterized by sparse matrix plus low rank matrix, whereas \cite{agarwal2012noisy} works on quadratic loss of noisy realization of linear transformation of sum of low rank and sparse matrices.
-We show that similar proof techniques can be applied in our case, giving us similar results.
-%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.
-
-Result of the Theorem \ref{Th:th1} provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $M$, and rank parameter $k$, helping us to understand the behavior of our proposed estimator both in practice and in ideal cases.
-In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.
-In this case, our theorem provides the intuition on the rate on how fast the error bound $\mathcal{K}_{L^*}$ will grow.
-In ideal cases where $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $M$ (i.e., $|supp(S^*)|=s$), we can easily verify ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ (i.e., $\tau\sum_{j=k+1}^{n}\sigma_j(L^*)$) and in $\mathcal{K}_{S^*}$ (i.e., $\tau\sum_{(i,j)\notin M}|S_{ij}^*|$) disappear, giving us Frobenius error bound as follows:
-\[
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s
-\]
-where $\lesssim$ denotes that we ignore constant factors.
 

### 2019-08-22 Codes & Data/Codes/ADMM_Optim.R

@@ -83,7 +83,7 @@ ADMM <- function(X, gamma, delta){
     res <- sqrt(sum((X_M-X_L-X_S)^2))
     print(res)
     # Convergence Check
-    if(res < 10^-5 ){
+    if(res < 10^-4 ){
       result <- list(X_a, X_M, X_L, X_S)
       break
     }

### 2019-08-22 Codes & Data/Codes/GD.R

@@ -38,7 +38,7 @@ GD <- function(para_v){
     
     # Update the solution & Calculate the difference between objective function
     old_sol = c(X_a, X_M)
-    new_sol = old_sol - 0.1*grad
+    new_sol = old_sol - 0.05*grad
     CC<-max(abs(grad))
     # print(CC)
     # Convergence Criteria

### 2019-08-22 Manuscript for submission/manuscript.tex
Update

@@
 $f^*_j$ is the $j$th column of factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in network, and $n$ denotes the number of papers in a network.
+Here, we introduce another notation, $n_{l}$, denoting the number of papers, which share $l$ common topics.
 Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote weight coefficient of factors.
@@
 \subsubsection{Synthetic Setting}
-We consider following three scenarios: $\{(n^{(i)},K^{(i)},nnz^{(i)})\}_{i=1}^{3}=\{(30,3,10),(80,4,20),(120,5,40)\}$.
+In first scenario, we consider following three cases: $\{(n_{1}^{(i)},K^{(i)},|S^*|^{(i)})\}_{i=1}^{3}$ $=\{(30,3,10),
+(80,4,20),(120,5,40)\}$.
+For example,  $(n_{1}^{(3)},K^{(3)},|S^*|^{(3)})$ means that we generate a network with $120$ papers, $5$ topics embedded, and $40$ arbitrary indexed ad-hoc links.
+Note $n_{1}^{(3)}=120$ means that each paper in the network has only one topic.
+In second scenario, we consider a case where we have 
+$(n,n_{2},n_{3},K,|S^{*}|)=(200,70,7,3,20)$.
+Here, we generate a network with $200$ papers in total, which is comprised of $70$ papers with $2$ topics, $7$ papers with $3$ topics.
+The network has $3$ topics, and $20$ arbitrary indexed ad-hoc links.
+In third scenario, we consider a case:
+$(n,n_{3},K,|S^{*}|)=(200,20,3,20)$.
+In this scenario, we have a network with $200$ papers with $3$ topics. Among $200$ papers, there are $20$ papers, which are related with all the $3$ topics.
+These $20$ papers have citational relationships with three clusters of papers via $20$ ad-hoc links, where papers in each cluster deals with only $1$ topic.
 
@@
 %The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
-Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\text{supp}(\widehat{S})|/2)$ of ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$)s'.
+Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\widehat{S}|)$ of ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$)s'.
 We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.

### 2019-09-05 Manuscript for submission/manuscript.tex
Update

--- 2019-08-22 Manuscript for submission/manuscript.tex
@@
 \begin{remark}
-Throughout the Section, we add $*$ to the superscript of parameters when they govern a data-generating process.
-$\alpha^*$ is an intercept term in logistic regression model.
-$f^*_j$ is the $j$th column of factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in network, and $n$ denotes the number of papers in a network.
-Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote weight coefficient of factors. 
+Throughout the Section, we add $*$ to the superscript of parameters to denote that they are ground truth parameters.
+We use $\alpha^*$ as an intercept term in logistic regression model, and
+$f^*_j$ as $j$th column of factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in network, and $n$ denotes the number of papers in the network.
+Here, we introduce another notation, $n_{l}$, denoting the number of papers, which share $l$ common topics.
+Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote weight coefficient of factors, and
 $S_{ij}^*$ denotes an ad-hoc citational relation between $i$th and $j$th paper.
@@
 (i.e., $|S^*|=|\{(i,j) : S_{ij}^{*}\neq 0, 1 \leq i<j \leq n\}|$).
-We will use $X \sim \text{Unif}[a,b]$ to denote
-$X$ is drawn from uniform distribution supported on the interval $[a,b]$.
+%We will use $X \sim \text{Unif}[a,b]$ to denote
+%the random variable $X$ is drawn from uniform distribution supported on the interval $[a,b]$.
 \end{remark}
@@
 \label{sec:Syn-dat}
-In this subsection, after a brief introduction on several synthetic scenarios that we want to explore, we will discuss how to set ground truth parameters for generating synthetic networks from pre-specified scenarios.
-Then, three model selection criteria and related evaluation metrics for the selected model will be introduced.
-Lastly, several interesting findings from the experiments will be presented.
+After a brief introduction on several synthetic scenarios that we want to explore, we will discuss how to set ground truth parameters for generating synthetic networks from pre-specified scenarios.
+Subsequently, three model selection criteria and three evaluation metrics for the selected model will be introduced.
+Lastly, several interesting observations from the experiments will be presented.
+
+\begin{figure}[htbp]
+\includegraphics[width=1\textwidth]{Fig1.pdf}
+\caption{Illustrations of assignment results via $k$-means algorithm on $K$ eigenvectors of the estimated $\widehat{L}$ matrix.}
+\label{fig:figure1}
+\end{figure}
 
 \subsubsection{Synthetic Setting}
-We consider following three scenarios: $\{(n^{(i)},K^{(i)},nnz^{(i)})\}_{i=1}^{3}=\{(30,3,10),(80,4,20),(120,5,40)\}$.
-
-\subsubsection{Data Generation}
-Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P^{*}_{ij}=\frac{\exp (
-\alpha^{*}+F^{*T}_{i}D^{*}F^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+F^{*T}_{i}D^{*}F^{*}_{j} +  S^{*}_{ij})}$.
-We set the model parameters randomly following these steps:
+In this subsection, we consider $3$ scenarios.
+In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
+In second scenario, we study a slightly more complicated situation than the first one where each paper in the network can possibly have more than one topic.
+%It is worth noting that different clusters of papers, where each cluster is comprised of papers with same topic, are connected via ad-hoc links.
+
+More concretely, in first scenario, when there is a network of $n$ papers with $K$ topics, there are $K$ clusters of papers, where each of which deals with $1$ specific topic out of $K$ topics.
+And each cluster is comprised of $\frac{n}{K}$ non-overlapping papers.
+Moreover, these $K$ clusters are connected with each other via $|S^*|$ random ad-hoc links.
+Specifically, we assume $|S^*|/\binom{K}{2}$ ad-hoc links connect $2$ different clusters of papers.
+For example, suppose that we have a network of $120$ papers with $5$ topics and with $30$ random ad-hoc links.
+Then, there are $5$ clusters, each of which has $24$ papers, and each of $10(=\binom{5}{2})$ pairs of clusters is connected through $3(=30/\binom{5}{2})$ random ad-hoc links.
+%(See Fig$\ref{fig:figure1}$
+
+Based upon the settings mentioned in the first scenario, additionally in second scenario, we suppose that there are $n_{l}$ papers, which share $l(\leq K)$ common topics in the network.
+For instance, if we have a network of $210$ papers with $3$ topics, and
+$n_2=50$, then $n_2=50$ means that there are $50$ papers out of $210$ papers, which have $2$ shared topics out of $3$ topics.
+Here, we want to note the readers that ad-hoc links are not used either to connect the clusters of papers that share $l$ common topics, or to connect a cluster of $1$ topic and a cluster that share $l$ common topics.
+In order to represent this notion in a generated network,
+first, we randomly pick $n_{l}$ indices from the set $\Omega_{n_{l}} = \{1,2,\dots,n\} \setminus \Omega_{S^*}$, where $\Omega_{S^*}$ denotes a set of indices of papers for formulating $|S^*|$ ad-hoc links.
+Next, $\forall j \in \Omega_{n_{l}}$, fill in arbitrary $l$ positions of $f_j^*$ with $1$s.
+
+With these settings in mind, we construct $3$ cases of networks for scenarios $1$, $2$, and $3$ respectively. Specifically;
+
 \begin{enumerate}
-    \item Generate $\alpha^*$ from Unif$[-3,-2]$ (i.e., $\alpha^*\sim \text{Unif}[-3,-2]$).
-    \item For the binary factor loading matrix $F^*(\in \mathbb{R}^{n \times K})$, first fill in each row of the matrix with $\floor{\frac{n}{K}}$ ones,
-     and make sure that each column of $F^{*}$ has only one $1$.
-     In last row of $F^*$, fill in the last remaining $n-K\floor{\frac{n}{K}}$ entries with $1$'s.
-     Then, we randomly choose one of columns, and fill that column with ones.
-     Lastly, set $F^*=F^*J$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$.
+    \item In the first scenario, we consider following three cases: $\{(n^{(i)},n_{1}^{(i)},K^{(i)},|S^*|^{(i)})\}_{i=1}^{3}$ $=\{(30,30,3,9), (80,80,4,18),$ $(120,120,5,30)\}$.
+        If we take an example, the notation  $(n^{(1)},n_{1}^{(1)},K^{(1)},|S^*|^{(1)})=(30,30,3,9)$ means that we generate a network with $30$ papers.
+There are $3$ topics embedded in the network, and $9$ random ad-hoc links connect $3$ clusters of papers, where each cluster represents a collection of papers with same topic.
+        Note that every paper in three networks, which are considered in this scenario, studies only about $1$ topic among $K$ topics.
+    \item In the second scenario, we consider three cases where we have
+        $\{(n^{(i)},n_{2}^{(i)},n_{3}^{(i)},K^{(i)},|S^{*}|^{(i)})\}_{i=1}^{3}=
+        \{(120,0,10,3,18),$ $(210,50,0,3,18),(210,10,10,3,18)\}$.
+        For instance, in the third case, we have a network with $210$ papers in total. There are $3$ topics commonly shared across the network.
+        Among $210$ papers, $10$ papers randomly share $2$ topics out of $3$, other $10$ papers have $3$ mixed topics, whereas remaining $190$ papers only discuss $1$ topic.
+        Note that $3$ clusters from these $190$ papers are connected through $18$ random ad-hoc links.
+        % For all $3$ cases, networks considered in this scenario have $3$ topics, and $3$ clusters of papers are connected via $18$ random ad-hoc links.
+        % In the first case, we generate a network with $120$ papers in total, which is comprised of $110$ papers with $1$ topic, and $10$ papers with $3$ mixed topics.
+        % In the second case, we have a network with $210$ papers in total.
+        % Among them, $50$ papers randomly share $2$ topics out of $3$ topics.
+        % And remaining $160$ papers talk about only $1$ topic.
+        % Lastly, in the third case, the network to be considered has $210$ papers in total.
+        % Among them, $10$ papers randomly share $2$ topics out of $3$, other $10$ papers have $3$ mixed topics, whereas remaining $190$ papers only discuss $1$ topic.
+    \item adsfasdf
+\end{enumerate}
+
+All $9$ networks that are elaborated in scenarios $1$, $2$ and $3$ are visualized in Fig\ref{fig:figure1}.
+Note that ad-hoc links, which connect clusters of papers with $1$ topic, are colored in green.
+For more detailed descriptions on parametric settings for generating networks in Fig\ref{fig:figure1}, readers can refer the R code provided in $\dots$.
+%In next subsection, we provide detailed ground truth parameters settings for generating the networks in Fig\ref{fig:figure1}.
+
+%\subsubsection{Data Generation}
+%Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P^{*}_{ij}=\frac{\exp (
+%\alpha^{*}+F^{*T}_{i}D^{*}F^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+F^{*T}_{i}D^{*}F^{*}_{j} +  S^{*}_{ij})}$.
+%Here, we describe a procedure on how to set the model parameters, $\alpha^*, S^*, D^*, F^*$, to define the probability $P^*_{ij}$ for generating the random networks in Fig\ref{fig:figure1}.
+
+%\begin{enumerate}
+%    \item Generate $\alpha^*$ from uniform distribution supported on $[-11,-10]$. Only for the case $4$, we draw $\alpha^* \sim \text{Unif}[-4,-3]$.
+
+%    \item We assume that the ad-hoc links, induced from non-zero entries of $S^*$ matrix, can complement the latent model
+%        the link structure that cannot be explained by common topics.
+%        Based on this assumption, we make the ad-hoc links connect the clusters with $K$ distinct topics.
+
+%    \item Each element of diagonal matrix $D^{*}$ is generated from uniform distribution supported on $[19,20]$. (i.e., $D_{ii} \sim \text{Unif}[19,20], \forall 1\leq i \leq K$)
+
+%    \item For factor loading matrix $F^*(\in \mathbb{R}^{K \times n})$, first fill in each row of the matrix with $\floor{\frac{n}{K}}$ ones,
+%        and make sure that each column of $F^{*}$ has only one $1$.
+%        In last row of $F^*$, fill in the last remaining $n-K\floor{\frac{n}{K}}$ entries with $1$'s.
+%        Then, we randomly choose one of columns, and fill that column with ones.
+%        Lastly, set $F^*=F^*J$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$.
         %and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying the aforementioned $J = I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$.
-    \item Each element of diagonal matrix $D^{*}$ is generated from uniform distribution supported on $[7,8]$.
-    \item For the sparse component $S^*$, first draw $|S^*|$ sparsity pattern
-    first draw $nnz$ distinct random pairs of indices that are uniformly distributed over the indices of upper triangular part (off diagonal) of matrix $S^*$.
-For each drawn pair of indices $(i,j)$, draw random number from Unif$[7,8]$ (i.e., $S^*_{ij}\sim\text{Unif}[7,8]$).
-\end{enumerate}
+%\end{enumerate}
 
 \subsubsection{Choosing the tuning parameters and evaluation criteria}
+
 We observe that choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
 Here we present a heuristic approach.
-Following the approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of adjacency matrix $X$, which can tell us the number of communities embedded in network.
-Then, we record the rank of $\widehat{L}$ and number of non-zero elements in $\widehat{S}$ for each tuning parameter pair on a given grid, and choose a proper pair that give us interesting interpretations of data.
+Following the approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of adjacency matrix $X$, which can tell us the number of communities embedded in the network
+(See Fig\ref{fig:figure2} to check for the cases of $6$ aforementioned synthetic networks).
+Then, we record the rank of $\widehat{L}$ and number of non-zero elements in $\widehat{S}$ for each tuning parameter pair on a given grid, and choose a proper pair that gives us interesting interpretations of data.
 
@@
 %The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
-Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\text{supp}(\widehat{S})|/2)$ of ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$)s'.
+Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\widehat{S}|)$ of ad-hoc links among all the estimated ($\widehat{L}$,$\widehat{S}$)s' over the given grid.
 We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.
 
+\begin{figure}[htbp]
+\includegraphics[width=1\textwidth]{Fig2.pdf}
+\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
+\label{fig:figure2}
+\end{figure}
+
 \begin{eqnarray*}
-M_1 &=& \mathbbm{1}\big\{rank(\widehat{L}) = rank(L^{*})\big\}, \\
+M_1 &=& \mathbbm{1}\big\{\text{rank}(\widehat{L}) = \text{rank}(L^{*})\big\}, \\
 M_2 &=& \frac{\left|\big\{(i,j):i<j:S^{*}_{i,j} \neq0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}\right|}{\left|\big\{(i,j):i<j:S^{*}_{i,j}\neq0\big\}\right|}, \\
@@
 With properly selected tuning parameter, $M_1$ will be 1, $M_2$ will be close to 1, and $M_3$ will get close to 0.
-We present the evaluation results of three scenarios via these three criteria in Table \ref{tab:table1}.
-
-\begin{table}[htbp]
-\centering
-\begin{tabular}{c|ccc|ccc|ccc}
-   & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\ \cline{2-10}
-   & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC   \\ \hline
-$M_1$ & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
-$M_2$ & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
-$M_3$ & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0
-\end{tabular}
-\caption{ For three scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
-Note that, for all three scenarios, both AIC and BIC choose the model with no ad-hoc structure (i.e., $\widehat{S}=0$), and $\widehat{L}$ with rank $1$ (i.e.,$\text{rank}(\widehat{L})=1$).}
-\label{tab:table1}
-\end{table}
-
-\begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig1.pdf}
-\caption{Illustrations of assignment results via $k$-means algorithm on $K$ eigenvectors of the estimated $\widehat{L}$ matrix.}
-\label{fig:figure1}
-\end{figure}
-
-\subsubsection{Findings}
-Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$.
+We present the evaluation results of $9$ cases via these $3$ criteria in Table \ref{tab:table1}.
+
+\subsubsection{Several Observations}
+Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
 We applied a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
@@
 %Some of ``across edges" are also attributed to $\alpha^{*}$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha^{*}$ or $S^{*}_{ij}$.
-So the total number of ``across edges'' might not be exactly same as ``$nnz$'' as we set in our data generation setting.
+So the total number of ``across edges'' might not be exactly same as $|S^*|$ as we set in our data generation setting.
+
+\begin{table}[htbp]
+%\centering
+%\begin{tabular}{c|ccc|ccc|ccc}
+%   & \multicolumn{9}{c|}{Scenario 1}
+%   & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\ %\cline{2-10}
+%   & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC   \\ \hline
+%$M_1$ & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
+%$M_2$ & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
+%$M_3$ & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0
+%\end{tabular}
+%\begin{table}[htbp]
+
+\centering
+\begin{tabular}{c|ccc|ccc|ccc}
+            & \multicolumn{9}{c}{\textbf{Scenario 1}}                                              \\
+            \cline{2-10}
+            & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\
+            \cline{2-10}
+            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
+            \hline
+$M_{1}$          &             &       &      &             &       &      &             &       &      \\
+$M_{2}$          &             &       &      &             &       &      &             &       &      \\
+$M_{3}$          &             &       &      &             &       &      &             &       &      \\
+Grid Region &    &       &      &             &       &      &             &       &      \\
+            \hline
+\end{tabular}
+
+\begin{tabular}{c|ccc|ccc|ccc}
+            & \multicolumn{9}{c}{\textbf{Scenario 2}}                                              \\
+            \cline{2-10}
+            & \multicolumn{3}{c|}{Case 4} & \multicolumn{3}{c|}{Case 5} & \multicolumn{3}{c}{Case 6} \\
+            \cline{2-10}
+            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
+            \hline
+$M_{1}$          &             &       &      &             &       &      &             &       &      \\
+$M_{2}$        &             &       &      &             &       &      &             &       &      \\
+$M_{3}$       &             &       &      &             &       &      &             &       &  \\
+Grid Region &             &       &      &             &       &      &             &       &      \\
+\end{tabular}
+
+\begin{tabular}{c|ccc|ccc|ccc}
+            & \multicolumn{9}{c}{\textbf{Scenario 3}}                                              \\
+            \cline{2-10}
+            & \multicolumn{3}{c|}{Case 7} & \multicolumn{3}{c|}{Case 8} & \multicolumn{3}{c}{Case 9} \\
+            \cline{2-10}
+            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
+            \hline
+$M_{1}$          &             &       &      &             &       &      &             &       &      \\
+$M_{2}$        &             &       &      &             &       &      &             &       &      \\
+$M_{3}$       &             &       &      &             &       &      &             &       &  \\
+Grid Region &             &       &      &             &       &      &             &       &      \\
+\end{tabular}
+
+\caption{ For three scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
+Note that, for all three scenarios, both AIC and BIC choose the model with no ad-hoc structure (i.e., $\widehat{S}=0$), and $\widehat{L}$ with rank $1$ (i.e.,$\text{rank}(\widehat{L})=1$).}
+\label{tab:table1}
+\end{table}
+
+\begin{figure}[htbp]
+\includegraphics[width=1\textwidth]{Fig3.pdf}
+\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
+\label{fig:figure3}
+\end{figure}
 
@@
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[scale=0.75]{Fig2.pdf}
+%\begin{figure}[htbp]
+%\begin{center}
+%\includegraphics[scale=0.75]{Fig2.pdf}
 %\includegraphics[scale=1,bb=0 0 30 30]{Fig2.pdf}
-\caption{Edges colored with blue correspond to non-zero entries of estimated $\widehat{S}$ matrix.
-For all three cases, our algorithm correctly separates the ``across edges'' from edges coming from low-rank matrix structure.}
-\label{fig:figure2}
-\end{center}
-\end{figure}
+%\caption{Edges colored with blue correspond to non-zero entries of estimated $\widehat{S}$ matrix.
+%For all three cases, our algorithm correctly separates the ``across edges'' from edges coming from low-rank matrix structure.}
+%\label{fig:figure2}
+%\end{center}
+%\end{figure}
 
@@
 
-Sub-network structure has also a big chunk of papers which we refer to as Mixed Topics.
+Sub-network structure has also a big chunk of papers which we refer it as Mixed Topics cluster.
 Not only could we see the papers with topics on Learning Theory, Non-parametric/Semi-parametric Statistics, Spatial Statistics, Theoretical Machine Learning, which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
@@
 
-\begin{landscape}
+%\begin{landscape}
 \begin{table}[htbp]
 \centering
-\begin{tabular}{lclclclcl}\hline
-
-Pair & Weight & Community & Title                                                                                  & \\\hline
-1    & 6.03                      & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       & \\
-     &                           & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                         & \\
-2    & 3.08                      & MulT      & Innovated higher criticism for detecting sparse signals in correlated noise                   & \\
-     &                           & VarSel    & Regularized estimation of large covariance matrices & \\
-3    & 2.47                      & DimRed    & Contour projected dimension reduction & \\
-     &                           & VarSel    & Factor profiled sure independence screening & \\
-4    & 2.15                      & VarSel    & Factor profiled sure independence screening & \\
-     &                           & DimRed    & Sliced regression for dimension reduction & \\
-5    & 1.86                      & VarSel    & Covariance regularization by thresholding & \\
-     &                           & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
-6    & 1.77                      & VarSel    & Asymptotic properties of bridge estimators in sparse high-dimensional regression models       & \\
-     &                           & Mixed     & Marginal asymptotics for the $''$large p small n$''$ paradigm: with applications to microarray data &  \\
-7    & 1.71                      & VarSel    & A majorization-minimization approach to Variable Selection using spike and slab priors        & \\
-     &                           & Mixed     & Empirical Bayes selection of wavelet thresholds & \\
-8    & 1.66                      & VarSel    & Spades and mixture models & \\
-     &                           & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
-9    & 1.61                      & DimRed    & A constructive approach to the estimation of dimension reduction directions                   & \\
-     &                           & VarSel    & Factor profiled sure independence screening & \\
-10   & 1.54                      & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors        & \\
-     &                           & Mixed     & Spike and slab variable selection: frequentist and Bayesian strategies                        & \\
-11   & 1.53                      & VarSel    & variable selection in nonparametric additive models & \\
-     &                           & Mixed     & Nonparametric estimation of an additive model with a link function                            & \\
-12   & 1.39                      & Mixed     & Nonparametric inferences for additive models & \\
-     &                           & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models         & \\
-13   & 1.29                      & Mixed     & Bayesian variable selection in structured high-dimensional covariate spaces with applications in genomics & \\
-     &                           & VarSel    & Model selection and estimation in regression with grouped variables                           & \\
-14   & 1.20                      & VarSel    & The sparsity and bias of the LASSO selection in high-dimensional linear regression            & \\
-     &                           & Mixed     & Tests for high-dimensional covariance matrices & \\
-15   & 1.19                      & FuncAn    & Empirical dynamics for longitudinal data & \\
-     &                           & Mixed     & Variable selection in nonparametric varying-coefficient models for analysis of repeated measurements   &       \\\hline
+\begin{tabular}{lclclcl}\hline
+Pair & Community & Title & \\\hline
+1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       & \\
+     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                         & \\
+2    & MulT      & Innovated higher criticism for detecting sparse signals in correlated noise                   & \\
+     & VarSel    & Regularized estimation of large covariance matrices & \\
+3    & DimRed    & Contour projected dimension reduction & \\
+     & VarSel    & Factor profiled sure independence screening & \\
+4    & VarSel    & Factor profiled sure independence screening & \\
+     & DimRed    & Sliced regression for dimension reduction & \\
+5    & VarSel    & Covariance regularization by thresholding & \\
+     & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
+6    & VarSel    & Asymptotic properties of bridge estimators in sparse high-dimensional regression models       & \\
+     & Mixed     & Marginal asymptotics for the $''$large p small n$''$ paradigm: with applications to microarray data &  \\
+7    & VarSel    & A majorization-minimization approach to Variable Selection using spike and slab priors        & \\
+     & Mixed     & Empirical Bayes selection of wavelet thresholds & \\
+8    & VarSel    & Spades and mixture models & \\
+     & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
+9    & DimRed    & A constructive approach to the estimation of dimension reduction directions                   & \\
+     & VarSel    & Factor profiled sure independence screening & \\
+10   & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors        & \\
+     & Mixed     & Spike and slab variable selection: frequentist and Bayesian strategies                        & \\
+11   & VarSel    & variable selection in nonparametric additive models & \\
+     & Mixed     & Nonparametric estimation of an additive model with a link function                            & \\
+12   & Mixed     & Nonparametric inferences for additive models & \\
+     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models         & \\
+13   & Mixed     & Bayesian variable selection in structured high-dimensional covariate spaces with applications in genomics & \\
+     & VarSel    & Model selection and estimation in regression with grouped variables                           & \\
+14   & VarSel    & The sparsity and bias of the LASSO selection in high-dimensional linear regression            & \\
+     & Mixed     & Tests for high-dimensional covariance matrices & \\
+15   & FuncAn    & Empirical dynamics for longitudinal data & \\
+     & Mixed     & Variable selection in nonparametric varying-coefficient models for analysis of repeated measurements   &       \\\hline
 \end{tabular}
@@
 \label{tab:table2}
-\end{landscape}
+%\end{landscape}
 

### 2019-09-05 Codes & Data/Codes/ADMM_Optim.R

@@ -83,11 +83,10 @@ ADMM <- function(X, gamma, delta){
     res <- sqrt(sum((X_M-X_L-X_S)^2))
     print(res)
     # Convergence Check
-    if(res < 10^-4 ){
+    if(res < 10^-4){
       result <- list(X_a, X_M, X_L, X_S)
       break
     }
-    
     k <- k + 1
   }
   

### 2019-09-05 Codes & Data/Codes/Synthetic Data Scenario.R

@@ -1,0 +1,82 @@
+####################  preparation  ####################
+rm(list=ls())
+setwd('C:/Users/namjo/Documents/GitHub/Citation-Network/Codes & Data/Codes')
+library('Matrix')      ## For matrix computation on BIC
+library('igraph')      ## For drawing graph
+source('SynData.R')    ## Function for creating binary network
+source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
+source('functions.R')
+source('Synthetic Networks.R')
+#################### data generation N = 30, K = 3, NNZ = 10 ####################
+set.seed(123)
+par(mfrow=c(3,3),mar = c(1, 1.5, 1.5, 1.5)) # ??? ??? ??? ??? # 
+######## First Scenario ########
+set.seed(123); Net1 <- Network1(30,3,9,1)
+set.seed(123); Net2 <- Network1(80,4,18,2)
+set.seed(123); Net3 <- Network1(120,5,30,3)
+######## Second Scenario ########
+set.seed(123); Net4 <- Network2(120,10,0,3,20,4)
+set.seed(123); Net5 <- Network2(210,0,50,3,18,5)
+set.seed(123); Net6 <- Network2(210,10,10,3,18,6)
+######## Third Scenario ########
+set.seed(123); Net7 <- Network3(120,10,0,3,20,7)
+set.seed(123); Net8 <- Network3(210,0,50,3,18,8)
+set.seed(123); Net9 <- Network3(210,10,10,3,18,9)
+par(mfrow=c(1,1))
+
+######## Plot Scree ########
+par(mfrow=c(3,3),mar = c(2, 2, 1, 1))
+plotScree(Net1); plotScree(Net2); plotScree(Net3);
+plotScree(Net4); plotScree(Net5); plotScree(Net6);
+plotScree(Net7); plotScree(Net8); plotScree(Net9);
+par(mfrow=c(1,1))
+
+################ Scenario 1 ################
+gamma = seq(from=0.01,to=0.02,by=0.001);
+delta = seq(from=0.02,to=0.03,by=0.001);
+Res1 <- Model_Sel(Net1,gamma,delta) ## gamma : 0.011, delta : 0.023 
+
+gamma = seq(from=0.004,to=0.005,by=0.0001);
[…]

### 2019-09-05 Codes & Data/Codes/Synthetic Data.R

@@ -8,11 +8,10 @@ source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
 source('functions.R')
 #################### data generation N = 30, K = 3, NNZ = 10 ####################
 set.seed(1234)
-par(mfrow=c(1,5))
 N = 30; K = 3; NNZ = 10;
 ### Ingredients for creating network : alpha, F, D, S                      
 ### Generate alpha from random uniform distribution
-alpha = runif(1,-3,-2)
+alpha = runif(1,-6,-5)
 ### Create diagonal matrix D with non-negative weights
 D = diag(runif(1,7,8),K)
 ### Create binary matrix F(0,1) whose columns are orthogonal with each other.
@@ -142,7 +141,7 @@ plot(X_draw,main="N=30,K=3,NNZ=10")
 N = 80; K = 4; NNZ = 20;
 ### Ingredients for creating network : alpha, F, D, S                      
 ### Generate alpha from random uniform distribution
-alpha = runif(1,-3,-2)
+alpha = runif(1,-6,-5)
 ### Create diagonal matrix D with non-negative weights
 D = diag(runif(1,7,8),K)
 ### Create binary matrix F(0,1) whose columns are orthogonal with each other.
@@ -159,9 +158,15 @@ if(K>0){
 if(K==0){
   F <- matrix(0,N,K)
 }
-RR = sample(1:N, 1, replace = FALSE) 
+RR = sample(1:N, 7, replace = FALSE) 
 F[RR,] = 1
+TT = sample(setdiff(1:N, RR),10,replace=FALSE)
+F[TT,] = 0 
+for(i in 1:length(TT)){
+  F[TT[i],][c(sample(1:K,K-1,replace=FALSE))] = 1
+}
 F = (diag(N)-1/N*matrix(1,N,N))%*%F
+
 ### Create random symmetric sparse matrix S, whose entries are greater than or equal to zero.
 S = matrix(0,N,N)
 S = rsparsematrix(N, N, nnz = NNZ, symmetric = TRUE, rand.x = runif)
@@ -235,6 +240,7 @@ S2<-result2[[4]]
 
 K = qr(L2)$rank
 
+K = 5
 N = ncol(X2)
 First_eigen1 = eigen(L2)$vectors[,1]
 Second_eigen1 = eigen(L2)$vectors[,2]
[…]

### 2019-09-05 Codes & Data/Codes/Synthetic Networks.R

@@ -1,0 +1,347 @@
+library(latex2exp)
+library("plot3D")
+Network1 <- function(N,K,NNZ, case){
+  ### Ingredients for creating network : alpha, F, D, S                      
+  ### Generate alpha from uniform distribution
+  alpha = runif(1,-11,-10)
+  ### Create diagonal matrix D with non-negative weights
+  D = diag(runif(1,19,20),K)
+  ### Create binary matrix F(0,1) whose columns are orthogonal with each other.
+  C = floor(N/K);              # C : number of 1s for each column
+  F = matrix(0,N,K);           # Create empty F matrix
+  if(K>0){
+    for(l in 1:K){
+      F[((l-1)*C+1):(l*C),l] <- 1
+    }
+    if(N%%C!=0)
+      F[(K*C+1):N,K] <- 1      # In last column of F, we fill the last remaining entries with 1s, 
+    # when N is not divided by K.
+  }
+  if(K==0){
+    F <- matrix(0,N,K)
+  }
+  F = (diag(N)-1/N*matrix(1,N,N))%*%F
+  
+  ad_hoc_ind = c();  A = choose(K,2);
+  for(i in 1:(K-1)){
+    for(j in i:(K-1)){
+      ind = cbind( sample( ((N/K)*(i-1)+1):((N/K)*i), floor(NNZ/A), replace = FALSE),
+                   sample( ((N/K)*(j)+1):((N/K)*(j+1)), floor(NNZ/A), replace = FALSE ) )
+      ad_hoc_ind = rbind(ad_hoc_ind,ind)
+    }
+  }
+  
+  S = matrix(0,N,N)
+  S[ad_hoc_ind]=runif(1,19,20)
+  S = S + t(S)
+  diag(S) = 0
+  
+  ### Create random symmetric sparse matrix S, whose entries are greater than or equal to zero.
+  #S = matrix(0,N,N)
+  #S = rsparsematrix(N, N, nnz = NNZ, symmetric = TRUE, rand.x = runif)
+  #S[which(S!=0,arr.ind=TRUE)] = runif(1,6,7)
+  #diag(S) = 0
+  
+  ### call function to generate the adjacency matrix
+  X1 <- SynData(alpha,F,D,S,N)
+  
+  ### generate the figure to illustrate the network
[…]

### 2019-09-05 Codes & Data/Codes/functions.R

@@ -1,4 +1,5 @@
 require(igraph)
+library(latex2exp)
 
 dscore = function(adj, K)
 {
@@ -158,14 +159,13 @@ score = function(adj, K)
 
 
 
-
-plotScree=function(adj)
+plotScree=function(adj,case)
 {
   #adj can be symmetric or asymmetric
   m = dim(adj)
   values = eigen(adj %*% t(adj))$values 
-  plot(sqrt(values[1:20]), cex=2, pch=22, type="b", lty=2, lwd=3, col="red", bg="red", xlab="", ylab="")
-  
+  plot(sqrt(values[1:20]), cex=2, pch=22, type="b", lty=2, lwd=3, col="red", bg="red", xlab="", ylab="",
+       main=TeX(sprintf("$\\textbf{Case  %d}$", case)))
 }
 
 

### 2019-09-09 Manuscript for submission/manuscript.tex
Update

@@
 $f^*_j$ as $j$th column of factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in network, and $n$ denotes the number of papers in the network.
-Here, we introduce another notation, $n_{l}$, denoting the number of papers, which share $l$ common topics.
+We also introduce a notation, $n_{l}$, denoting the number of papers, which share $l$ common topics.
 Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote weight coefficient of factors, and
 $S_{ij}^*$ denotes an ad-hoc citational relation between $i$th and $j$th paper.
-We use the notation $|S^*|$ to denote the cardinality of non-zero components of upper-triangular part of $S^*$ matrix
-(i.e., $|S^*|=|\{(i,j) : S_{ij}^{*}\neq 0, 1 \leq i<j \leq n\}|$).
-%We will use $X \sim \text{Unif}[a,b]$ to denote
-%the random variable $X$ is drawn from uniform distribution supported on the interval $[a,b]$.
+We use the notation $|(\bullet)|$ to denote the cardinality of non-zero components of upper-triangular part of $(\bullet)$ matrix
+(e.g., $|S^*|=|\{(i,j) : S_{ij}^{*}\neq 0, 1 \leq i<j \leq n\}|$).
+We will use $X \sim \text{Unif}[a,b]$ to denote
+the random variable $X$ is drawn from uniform distribution supported on the interval $[a,b]$.
 \end{remark}
@@
 \label{sec:Syn-dat}
-After a brief introduction on several synthetic scenarios that we want to explore, we will discuss how to set ground truth parameters for generating synthetic networks from pre-specified scenarios.
-Subsequently, three model selection criteria and three evaluation metrics for the selected model will be introduced.
-Lastly, several interesting observations from the experiments will be presented.
+After an introduction on three synthetic scenarios that we want to explore, three model selection criteria and three evaluation metrics for the selected model will be suggested.
+Experimental results from the synthetic networks and several interesting findings from those results will be elaborated subsequently.
 
@@
 \includegraphics[width=1\textwidth]{Fig1.pdf}
-\caption{Illustrations of assignment results via $k$-means algorithm on $K$ eigenvectors of the estimated $\widehat{L}$ matrix.}
+\caption{Graphical illustrations of $9$ synthetic networks. Note the links that are drawn from $S^*_{ij} \neq 0$ are colored in green. }
 \label{fig:figure1}
@@
 \subsubsection{Synthetic Setting}
-In this subsection, we consider $3$ scenarios.
-In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
-In second scenario, we study a slightly more complicated situation than the first one where each paper in the network can possibly have more than one topic.
+In this subsection, we consider following $3$ scenarios:
+%In this subsection, we consider $3$ scenarios.
+%In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
+%In second scenario, we study a more complicated situation than the first one where each paper in the network can possibly have more than one topic.
 %It is worth noting that different clusters of papers, where each cluster is comprised of papers with same topic, are connected via ad-hoc links.
-
-More concretely, in first scenario, when there is a network of $n$ papers with $K$ topics, there are $K$ clusters of papers, where each of which deals with $1$ specific topic out of $K$ topics.
+%In third scenario, we consider a situation
+\begin{itemize}
+    \item \textbf{First scenario.} When there is a network of $n$ papers with $K$ topics, there are $K$ clusters of papers, where each of which deals with $1$ specific topic out of $K$ topics.
         And each cluster is comprised of $\frac{n}{K}$ non-overlapping papers.
@@
         For example, suppose that we have a network of $120$ papers with $5$ topics and with $30$ random ad-hoc links.
-Then, there are $5$ clusters, each of which has $24$ papers, and each of $10(=\binom{5}{2})$ pairs of clusters is connected through $3(=30/\binom{5}{2})$ random ad-hoc links.
+Then, there are $5$ clusters, each of which has $24$ papers, and each of $10 (=\binom{5}{2})$ pairs of clusters is connected through $3 (=30/\binom{5}{2})$ random ad-hoc links.
 %(See Fig$\ref{fig:figure1}$
 
-Based upon the settings mentioned in the first scenario, additionally in second scenario, we suppose that there are $n_{l}$ papers, which share $l(\leq K)$ common topics in the network.
+    \item \textbf{Second scenario.} Based upon the settings mentioned in the first scenario, we suppose that there are $n_{l}$ papers, which share $l(\leq K)$ common topics in the network.
         For instance, if we have a network of $210$ papers with $3$ topics, and
-$n_2=50$, then $n_2=50$ means that there are $50$ papers out of $210$ papers, which have $2$ shared topics out of $3$ topics.
-Here, we want to note the readers that ad-hoc links are not used either to connect the clusters of papers that share $l$ common topics, or to connect a cluster of $1$ topic and a cluster that share $l$ common topics.
-In order to represent this notion in a generated network,
-first, we randomly pick $n_{l}$ indices from the set $\Omega_{n_{l}} = \{1,2,\dots,n\} \setminus \Omega_{S^*}$, where $\Omega_{S^*}$ denotes a set of indices of papers for formulating $|S^*|$ ad-hoc links.
-Next, $\forall j \in \Omega_{n_{l}}$, fill in arbitrary $l$ positions of $f_j^*$ with $1$s.
+        $n_2$ is equal to $50$, then this means that there are $50$ papers out of $210$ papers, which have $2$ shared topics out of $3$ topics.
+        %Here, we want to note the readers that ad-hoc links are not used either to connect the clusters of papers that share $l$ common topics, or to connect a cluster of $1$ topic and a cluster that share $l$ common topics.
+        %In order to represent this notion in a generated network,
+        %first, we randomly pick $n_{l}$ indices from the set $\Omega_{n_{l}} = \{1,2,\dots,n\} \setminus \Omega_{S^*}$, where $\Omega_{S^*}$ denotes a set of indices of papers for formulating $|S^*|$ ad-hoc links.
+        %Next, $\forall j \in \Omega_{n_{l}}$, fill in arbitrary $l$ positions of $f_j^*$ with $1$s.
+
+     \item \textbf{Third scenario.} In this scenario, we want to study a role of $\alpha^*$ in the network.
+        In the first and second scenarios, we set $\alpha^* \sim \text{Unif}[-11,-10]$, so that it has little effect on creating random edges in the network.
+        In the third scenario, we set $\alpha^* \sim \text{Unif}[-4,-3]$, whereas other parametric settings for $D^*, F^*$ and $S^*$ are same with those from the first and second scenarios.
+        This setting has an effect on increasing the number of edges connecting the clusters of papers with $l$ topics and those with $1$ topic.
+\end{itemize}
 
@@
         Among $210$ papers, $10$ papers randomly share $2$ topics out of $3$, other $10$ papers have $3$ mixed topics, whereas remaining $190$ papers only discuss $1$ topic.
-        Note that $3$ clusters from these $190$ papers are connected through $18$ random ad-hoc links.
-        % For all $3$ cases, networks considered in this scenario have $3$ topics, and $3$ clusters of papers are connected via $18$ random ad-hoc links.
-        % In the first case, we generate a network with $120$ papers in total, which is comprised of $110$ papers with $1$ topic, and $10$ papers with $3$ mixed topics.
-        % In the second case, we have a network with $210$ papers in total.
-        % Among them, $50$ papers randomly share $2$ topics out of $3$ topics.
-        % And remaining $160$ papers talk about only $1$ topic.
-        % Lastly, in the third case, the network to be considered has $210$ papers in total.
-        % Among them, $10$ papers randomly share $2$ topics out of $3$, other $10$ papers have $3$ mixed topics, whereas remaining $190$ papers only discuss $1$ topic.
-    \item adsfasdf
+        Note that the $3$ clusters from these $190$ papers are connected through $18$ random ad-hoc links.
+    \item In the third scenario, we basically study the same $3$ cases with those from the second scenario.
+        (i.e., $\{(n^{(i)},n_{2}^{(i)},n_{3}^{(i)},K^{(i)},|S^{*}|^{(i)})
+        \}_{i=1}^{3}=\{(120,0,10,3,18), (210,50,0,3,18),(210,10,10,3,18)\}$)
+        The only difference between these two scenarios comes from the random setting of $\alpha^*$. (i.e.,$\alpha^* \sim \text{Unif}[-4,-3]$)
 \end{enumerate}
@@
 Note that ad-hoc links, which connect clusters of papers with $1$ topic, are colored in green.
-For more detailed descriptions on parametric settings for generating networks in Fig\ref{fig:figure1}, readers can refer the R code provided in $\dots$.
-%In next subsection, we provide detailed ground truth parameters settings for generating the networks in Fig\ref{fig:figure1}.
+Readers can refer the R code provided in $\dots$, for more detailed descriptions on parametric settings for generating networks in Fig\ref{fig:figure1}.
 
@@
 \subsubsection{Choosing the tuning parameters and evaluation criteria}
-
 We observe that choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
-Here we present a heuristic approach.
-Following the approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of adjacency matrix $X$, which can tell us the number of communities embedded in the network
-(See Fig\ref{fig:figure2} to check for the cases of $6$ aforementioned synthetic networks).
-Then, we record the rank of $\widehat{L}$ and number of non-zero elements in $\widehat{S}$ for each tuning parameter pair on a given grid, and choose a proper pair that gives us interesting interpretations of data.
-
+Here we present a heuristic procedure for choosing a good pair of tuning parameters $(\gamma,\delta)$.
+Following the scree-plot approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of the adjacency matrix $X$, and find an ``elbow'' point where the eigenvalues seem to level off.
+An index of the point, which is to the left of this elbow point, is considered as the number of the topics embedded in the network.
+(We will denote this number as $\hat{K}^{\text{Scree}}$.)
+We want to note the readers that the scree-plot analysis serves as a good guideline for determining the range of grids to search over.
+With the estimate of the number of topics in the network in mind, we record the $\text{rank}(\widehat{L}^{\gamma,\delta})$ and $|\widehat{S}^{\gamma,\delta}|$ for each tuning parameter pair on a given grid.
+We need to go through several iterations of this recording procedure to find a proper range of grid, in which we can get $\text{rank}(\widehat{L}^{\gamma,\delta})=\hat{K}^{\text{Scree}}$
+and $10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X|$, via adjusting the range of grid for $\gamma$ and $\delta$ repeatedly.
+Once we find a grid, which satisfies above constraints, we choose a pair of tuning parameters: %($\gamma^{\text{Heu}},\delta^{\text{Heu}}$):
+\[
+    (\gamma^{\text{Heu}},\delta^{\text{Heu}}):=
+    \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\hat{K}^{\text{Scree}},
+    \quad \mbox{mode} |\widehat{S}^{\gamma,\delta}| \quad
+    \text{s.t.} \quad 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 0.05|X| \big\}
+\]
 One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) and the AIC, work where we recall that BIC and AIC are defined as follows:
@@
 \[
-\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|,
-\]
-where $M$ is the current model,
-$\mathbb{L}_n( \hat{\beta}(M))$ is the maximal log-likelihood for a given model $M$,
-and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $S$ and the low-rank matrix $L$.
-If we have $\text{rank}(L)=K$, we can establish the following
-\[
-|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1 ;
-\]
-since the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
-Additionally $1$ in the last is due to $\alpha$.
-We want to find an $M$, which minimizes BIC($M$) or AIC($M$) as a function of $M$.
-However these traditional methods seem to entail a serious problem.
-%The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
-Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\widehat{S}|)$ of ad-hoc links among all the estimated ($\widehat{L}$,$\widehat{S}$)s' over the given grid.
+\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|.
+\]
+Here $M$ indicates the current model, which is implicitly understood that the model is obtained from certain tuning parameter pair $(\gamma,\delta)$.
+We use $\mathbb{L}_n( \hat{\beta}(M))$ to denote the maximal log-likelihood for a given model $M$,
+and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $\widehat{S}^{\gamma,\delta}$ and the low-rank matrix $\widehat{L}^{\gamma,\delta}$.
+In detail, if we have $\text{rank}(\widehat{L}^{\gamma,\delta})=K$, we can establish the following
+\[
+|M| = \sum_{i < j}1_{\{S_{ij} \neq 0\}} + n K - \frac{K(K-1)}{2} + 1 ;
+\]
+since the number of free parameters in $\widehat{L}^{\gamma,\delta}$ is $K$ plus $nK - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
+Additional $1$ in the last term is due to $\hat{\alpha}$.
+We want to find a pair $(\gamma,\delta)$, which minimizes BIC($M$) and AIC($M$) as a function of $(\gamma,\delta)$ respectively, where we denote them as follows:
+\[
+    (\gamma^{BIC},\delta^{BIC}):= \mbox{arg min}_{\gamma, \delta}
+    \mbox{BIC}(M),
+    \quad
+    (\gamma^{AIC},\delta^{AIC}):= \mbox{arg min}_{\gamma, \delta}
+    \mbox{AIC}(M)
+\]
 We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.
@@
 \includegraphics[width=1\textwidth]{Fig2.pdf}
-\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
+\caption{ Scree plots for $9$ synthetic Networks.
+    $\hat{K}^{\text{Scree}}$ recovers the number of topics in network correctly for all $9$ cases.}
 \label{fig:figure2}
@@
 \subsubsection{Several Observations}
-Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
-We applied a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
-For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
+%Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
+%We apply a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
+%For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
 %Furthermore, we find one interesting phenomenon.
@@
 %Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
-
-\textbf{Ad-hoc links}.
-Ad-hoc links of synthetic network data can be thought of as ``across edges'' between clusters of nodes.
-Since indices of non-zero entries of $S^{*}$ are randomly chosen, there might be some indices of positive $S^{*}_{ij}$ entries where $L^{*}_{ij}$ is also positive.
-In this case, this makes the edges indistinguishable if they come from $S^{*}_{ij}$ or $L^{*}_{ij}$.
+\begin{enumerate}
+    \item \textbf{Model Selection.}
+    First and foremost, choosing a good pair of tuning parameters is of essential issue when it comes to making a good statistical inference on data.
+    As presented in Table\ref{tab:table1}, we observe that the traditional model selection methods, both BIC and AIC, perform poorly on choosing true models, whereas our heuristic approach chooses good models reasonably well for the 9 artificial cases.
+    In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics for all $9$ cases. (See Fig\ref{fig:figure2})
+    On the other hand, both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\widehat{S}|)$ of ad-hoc links among the estimated ($\widehat{L}$,$\widehat{S}$)s' over the given grid.
+
+    \item \textbf{Node Membership.}
+    After fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether the $i$th paper belongs to $k$th topic or not.
+    We apply a simple $k$-means clustering algorithm on the $\widehat{L}$ matrix’s $K(=\text{rank}(\widehat{L}))$ eigenvectors.
+    (We will denote column-wise concatenation of these $K$ eigenvectors as $\widehat{E}_{K} \in \mathbb{R}^{n\times K}$.)
+    For $3$ cases in Scenario $1$, where each paper in the network can only have $1$ topic, we confirm that $k$-means algorithm performs well on classifying papers in the network.
+    However, in Scenario $2$ and $3$ where we allow the papers in the network can have more than $1$ topic, naive implementation of $k$-means algorithm entails a problem, since it is not able to afford the overlapped membership of nodes.
+    In order to obtain a sense on how many clusters of papers exist in latent space, we project each row of the $\widehat{E}_{K}$ on the first and second principal components of data matrix $\widehat{E}_{K}$, and plot the projected points on $2$-dimensional plane.
+    We count the number of distinct clusters plotted on the plane. Subsequently, we run the $k$-means algorithm on the projected points.
+    See Fig\ref{fig:figure3} for the references on how this procedure performs on $9$ synthetic cases.
+
+    \item \textbf{Scenario $2$ vs. Scenario $3$.}
+    We empirically observe that the number of edges between clusters $\big\{ C_{i,j}:\forall 1 \leq i \neq j \leq K \big\}$ and $\big\{ C_{i}: \forall 1 \leq i \leq K \big\}$ has an effect on their clustering behaviors in latent space.
+Here $C_{i}$ is used to represent a set of papers on $i$th topic, and $C_{i,j}$ is used to denote a collection of papers that have $i$th and $j$th topics.
+    If we take a look at Fig\ref{fig:figure3}, Case $4$ in second scenario illustrates that it is difficult for us to visually distinguish the papers in $C_{1,2,3}$ and those in $\big\{ C_{i}: \forall 1 \leq i \leq 3 \big\}$ in projected space, whereas they are obviously distinguishable in Case $7$.
+    Unfortunately, we can observe similar phenomenon in Case $5$ and $6$, where the exact separations of clusters $\big\{ C_{i,j}:\forall 1 \leq i \neq j \leq 3 \big\}$ are not made.
+    %makes $k$-means algorithm difficult to distinguish the clusters of papers $C_{1,2}, C_{2,3}, C_{1,3}$ and $C_{1,2,3}$ from each other both in Case $5$ and $6$.
+    On the other hand, in third scenario, distinct separations are made between $6$ clusters $C_{1}, C_{2}, C_{3}, C_{1,2}, C_{2,3}, C_{1,3}$ in Case $8$, and between $7$ clusters $C_{1}, C_{2}, C_{3}, C_{1,2}, C_{2,3}, C_{1,3}, C_{1,2,3}$ in Case $9$, so that we can explicitly know the membership of each paper in the network.
+
+    % In fact, this observation is especially helpful for us to understand the behavior of our model with the statisticians’ citation network data, which we are going to explore in the following subsection.
+    % In the statisticians’ citation network, we also observe clusters of papers, which have more than $1$ topic, behave similarly with those from the second scenario.
+
+    \item \textbf{Ad-hoc links.}
+    In our setting, ad-hoc links of synthetic network data are considered as ``across edges'' between clusters $\big\{ C_{i}: \forall 1 \leq i \leq K \big\}$.
+    Our heuristic method works much better than either AIC or BIC in recovering the ad-hoc edges for the $6$ cases in $3$ scenarios.
+    For the three Cases (i.e., Case $2,3,9$) where both AIC and BIC work well, all the pairs of tuning parameters in the grid give the same $|\widehat{S}^{\gamma,\delta}|$.
+
+    %Since indices of non-zero entries of $S^{*}$ are randomly chosen, there might be some indices of positive $S^{*}_{ij}$ entries where $L^{*}_{ij}$ is also positive.
+    %In this case, this makes the edges indistinguishable if they come from $S^{*}_{ij}$ or $L^{*}_{ij}$.
     %Some of ``across edges" are also attributed to $\alpha^{*}$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha^{*}$ or $S^{*}_{ij}$.
-So the total number of ``across edges'' might not be exactly same as $|S^*|$ as we set in our data generation setting.
+    %So the total number of ``across edges'' might not be exactly same as $|S^*|$ as we set in our data generation setting.
+\end{enumerate}
 
@@
             \hline
-$M_{1}$          &             &       &      &             &       &      &             &       &      \\
-$M_{2}$          &             &       &      &             &       &      &             &       &      \\
-$M_{3}$          &             &       &      &             &       &      &             &       &      \\
-Grid Region &    &       &      &             &       &      &             &       &      \\
+$M_{1}$   &    1(3)  &    0(2)   &  0(2)  &    1(4)    &  0(3)   &  0(3)  &    1(5)  &   0(4)    &   0(4) \\
+$M_{2}$   &    1     &    0 &      0 &         1    &     1  &    1  &         1    &    1   &   1   \\
+$M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
+%Grid Region &    &       &      &             &       &      &             &       &      \\
             \hline
@@
             \hline
-$M_{1}$          &             &       &      &             &       &      &             &       &      \\
-$M_{2}$        &             &       &      &             &       &      &             &       &      \\
-$M_{3}$       &             &       &      &             &       &      &             &       &  \\
-Grid Region &             &       &      &             &       &      &             &       &      \\
+$M_{1}$   &   1(3)     &     1(3)  &  1(3)    &      1(3)   &   1(3)    &  1(3)    &   1(3)     &  1(3)     &   1(3)   \\
+$M_{2}$   &   $\frac{17}{18}$   &   0    &    0  &   $\frac{17}{18}$     &   0    &  0    &  $\frac{16}{18}$    &   0    &  0    \\
+$M_{3}$   &   0 &     0  &   0   &        0     &    0   &  0    &        0     &   0    & 0 \\
+%Grid Region &             &       &      &             &       &      &             &       &      \\
+            \hline
 \end{tabular}
@@
             \hline
-$M_{1}$          &             &       &      &             &       &      &             &       &      \\
-$M_{2}$        &             &       &      &             &       &      &             &       &      \\
-$M_{3}$       &             &       &      &             &       &      &             &       &  \\
-Grid Region &             &       &      &             &       &      &             &       &      \\
+$M_{1}$  &    1(3)   &   1(3)    &  1(3)    &     1(3)        &    1(3)   &  1(3)    &   1(3)          &  1(3)      &  1(3)     \\
+$M_{2}$  &     1       &   0  &    0  &    $\frac{15}{18}$         &   0  &  0  &   1   &  1    &   1     \\
+$M_{3}$  &  $\frac{1}{7122}$  &  0  &  0   &   $\frac{3}{21927}$ &     0  &  0     &  $\frac{4}{21927}$ & $\frac{4}{21927}$ & $\frac{4}{21927}$ \\
+%Grid Region &             &       &      &             &       &      &             &       &      \\
 \end{tabular}
-
 \caption{ For three scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
-Note that, for all three scenarios, both AIC and BIC choose the model with no ad-hoc structure (i.e., $\widehat{S}=0$), and $\widehat{L}$ with rank $1$ (i.e.,$\text{rank}(\widehat{L})=1$).}
+A number in the parentheses represents the rank of $\widehat{L}$ estimated from ($\gamma^{\text{Heu}},\delta^{\text{Heu}}$), ($\gamma^{\text{AIC}},\delta^{\text{AIC}}$) and ($\gamma^{\text{BIC}},\delta^{\text{BIC}}$) for each case.}
 \label{tab:table1}
@@
 \includegraphics[width=1\textwidth]{Fig3.pdf}
-\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
+\caption{ Plots of the projected points on the first (X-axis) and second (Y-axis) principal component of the data matrix $\widehat{E}_{K}$.
+Different colors represent different clusters of papers that $k$-means algorithm assigns.}
 \label{fig:figure3}
@@
 \begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig3.eps}
-\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
-\label{fig:figure3}
+\includegraphics[width=1\textwidth]{Fig4.pdf}
+\caption{ Scree plots for 543-Citation network, and Sub-network.}
+\label{fig:figure4}
 \end{figure}
@@
 Consequently, we have $543$ papers in total.
-The elbow points of the eigen-value scree plot  from  may be at the $3$rd, $7$th, or $9$th largest eigenvalue, suggesting that there might be from $2$ to $8$ topics embedded in network (See Fig$ \ref{fig:figure3}$).
+The elbow points of the eigen-value scree plot  from  may be at the $3$rd, $7$th, or $9$th largest eigenvalue, suggesting that there might be from $2$ to $8$ topics embedded in network (See Fig$\ref{fig:figure3}$).
 In light of this, we performed our analysis under the assumption that there might exist $2$ distinct topics and one giant component, in which $3$ or $4$ topics are mixed up.
 
-A pair of parameters, $(\gamma,\delta) = (0.000912,0.0097)$, gives us $\widehat{L}$ with rank $3$, and $\widehat{S}$ with $|\widehat{S}|=197$.
+A pair of parameters, $(\gamma^{\text{Heu}},\delta^{\text{Heu}}) = (0.000912,0.0097)$, gives us $\widehat{L}$ with rank $3$, and $\widehat{S}$ with $|\widehat{S}|=197$.
 We apply $k$-means algorithm on $3$ eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in Fig $\ref{fig:figure4}$.
-$404$ papers colored in green are densely clustered nearby the origin with a short tail, $(Fig \ref{fig:figure4})$, and $k$-means classifies these papers as third topic.
+$404$ papers colored in green are densely clustered nearby the origin with a short tail, (Fig $\ref{fig:figure4}$), and $k$-means classifies these papers as third topic.
 We list the first two topics discovered through our analysis.
@@
 As expected, third group is quite hard to interpret and seems to have substructures.
-For further investigation on this group, after obtaining the sub-network which is comprised only with the papers in the third group, we performed same analysis once again under the assumption that $K=4$ (See $Fig \ref{fig:figure3},right$).
+For further investigation on this group, after obtaining the sub-network which is comprised only with the papers in the third group, we performed same analysis once again under the assumption that $K=4$ (See Fig$\ref{fig:figure3}$,right).
 We obtain four sub-communities as follows:
@@
 Sub-network structure has also a big chunk of papers which we refer it as Mixed Topics cluster.
-Not only could we see the papers with topics on Learning Theory, Non-parametric/Semi-parametric Statistics, Spatial Statistics, Theoretical Machine Learning, which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
+Not only could we see the papers with topics on Learning Theory, Non-parametric / Semi-parametric Statistics, Spatial Statistics, Theoretical Machine Learning, which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
 Papers, such as The Bayesian Lasso (T.
@@
 This is interesting since even though the dataset we consider is different from theirs, the results are consistent.
-They focus their attentions on analyzing \emph{"weakly connected giant component"} for a citation network of each paper's authors ({i.e., each node is an author}).
+They focus their attentions on analyzing \emph{`weakly connected giant component'} for a citation network of each paper's authors ({i.e., each node is an author}).
 We consider the citation network of papers whose node degree is greater than or equal to 7.
@@
 \begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig4.eps}
+\includegraphics[width=1\textwidth]{Fig5.pdf}
 \caption{Illustration of first two eigenvectors of estimated $\widehat{L}$ matrix for original
@@
 the results of assignment of each paper to each topic via $k$-means algorithm with different colors.}
-\label{fig:figure4}
+\label{fig:figure5}
 \end{figure}
@@
 \begin{tabular}{lclclcl}\hline
-Pair & Community & Title & \\\hline
+Pair & Community & Title & \\
+\hline
 1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       & \\
@@
 6    & VarSel    & Asymptotic properties of bridge estimators in sparse high-dimensional regression models       & \\
-     & Mixed     & Marginal asymptotics for the $''$large p small n$''$ paradigm: with applications to microarray data &  \\
+     & Mixed     & Marginal asymptotics for the ``large p small n'' paradigm: with applications to microarray data &  \\
 7    & VarSel    & A majorization-minimization approach to Variable Selection using spike and slab priors        & \\
@@
 10   & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors        & \\
-     & Mixed     & Spike and slab variable selection: frequentist and Bayesian strategies                        & \\
+     & Mixed     & Spike and slab variable selection: Frequentist and Bayesian strategies                        & \\
 11   & VarSel    & variable selection in nonparametric additive models & \\
@@
 
-\section{Conclusion}
+\section{Discussion}
 \label{sec:Con}
@@
 However, $k$-means algorithm turns out that it tends to assign nodes conservatively to each communities.
-For example, in Fig$\ref{fig:figure4}(left)$, we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in Fig$\ref{fig:figure4}(right)$ also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
+For example, in Fig$\ref{fig:figure4}$(left), we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in Fig$\ref{fig:figure4}$(right) also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
 This is probably because $k$-means does not allow overlapping membership of each nodes.

### 2019-09-09 Codes & Data/Codes/ADMM_Optim.R

@@ -83,7 +83,7 @@ ADMM <- function(X, gamma, delta){
     res <- sqrt(sum((X_M-X_L-X_S)^2))
     print(res)
     # Convergence Check
-    if(res < 10^-4){
+    if(res < 5e-4){
       result <- list(X_a, X_M, X_L, X_S)
       break
     }

### 2019-09-09 Codes & Data/Codes/GD.R

@@ -40,7 +40,7 @@ GD <- function(para_v){
     old_sol = c(X_a, X_M)
     new_sol = old_sol - 0.05*grad
     CC<-max(abs(grad))
-    # print(CC)
+    print(CC)
     # Convergence Criteria
     if(CC < 10^-9){
       X_a <- new_sol[1]

### 2019-09-09 Codes & Data/Codes/Synthetic Data Scenario.R

@@ -21,14 +21,14 @@ set.seed(123); Net6 <- Network2(210,10,10,3,18,6)
 ######## Third Scenario ########
 set.seed(123); Net7 <- Network3(120,10,0,3,20,7)
 set.seed(123); Net8 <- Network3(210,0,50,3,18,8)
-set.seed(123); Net9 <- Network3(210,10,10,3,18,9)
+set.seed(123); Net9 <- Network3(210,10,10,3,18,9);
 par(mfrow=c(1,1))
 
 ######## Plot Scree ########
-par(mfrow=c(3,3),mar = c(2, 2, 1, 1))
-plotScree(Net1); plotScree(Net2); plotScree(Net3);
-plotScree(Net4); plotScree(Net5); plotScree(Net6);
-plotScree(Net7); plotScree(Net8); plotScree(Net9);
+par(mfrow=c(3,3),mar = c(2, 2, 2, 1))
+plotScree(Net1,1); plotScree(Net2,2); plotScree(Net3,3);
+plotScree(Net4,4); plotScree(Net5,5); plotScree(Net6,6);
+plotScree(Net7,7); plotScree(Net8,8); plotScree(Net9,9);
 par(mfrow=c(1,1))
 
 ################ Scenario 1 ################
@@ -42,41 +42,51 @@ Res2 <- Model_Sel(Net2,gamma,delta) ## gamma : 0.004, delta : 0.009 ##
 
 gamma = seq(from=0.002,to=0.003,by=0.0005);
 delta = seq(from=0.0046,to=0.0048,by=0.00005);
-Res3 <- Model_Sel(Net3,0.003,0.00475) ## gamma : 0.003, delta : 0.00475 ##
+Res3 <- Model_Sel(Net3,gamma,delta) ## gamma : 0.003, delta : 0.00475 ##
 
 ################ Scenario 2 ################
 gamma = seq(from=0.002,to=0.004,by=0.0002);
 delta = seq(from=0.015,to=0.02,by=0.0005);
-Res4 <- Model_Sel(Net4,0.0032,0.019) ## gamma : 0.0032, delta : 0.019 
-K_means(Net4,0.0032,0.019)
+Res4 <- Model_Sel(Net4[[1]],gamma,delta) ## gamma : 0.0032, delta : 0.019 
 
 gamma = seq(from=0.00204,to=0.00244,by=0.00004); 
[…]

### 2019-09-09 Codes & Data/Codes/Synthetic Networks.R

@@ -1,5 +1,7 @@
 library(latex2exp)
 library("plot3D")
+source('ADMM_Optim.R') 
+
 Network1 <- function(N,K,NNZ, case){
   ### Ingredients for creating network : alpha, F, D, S                      
   ### Generate alpha from uniform distribution
@@ -71,7 +73,9 @@ Network1 <- function(N,K,NNZ, case){
   #plot(X_draw,main=TeX(sprintf("$\\textbf{Case %d : n = %d, n_{1} = %d, K = %d,\\left|S^{*}\\right| = %d}$", case, N, N, K, NNZ)))
   plot(X_draw,main=TeX(sprintf("$\\textbf{Case  %d}$", case)))
   #plot(X_draw,main=Tex(sprintf("$\\Scenario 1 : Case (%d)$",Case)))
-  return(X1)
+  
+  Res <- list(X1,B)
+  return(Res)
 }
 
 Network2<-function(N,N_K,N_K_1,K,NNZ, case){
@@ -157,7 +161,9 @@ Network2<-function(N,N_K,N_K_1,K,NNZ, case){
   E(X_draw2)[list]$color <- "green"
   #plot(X_draw2,main=TeX(sprintf("$\\textbf{Case %d \\ n = %d, n_{1} = %d, K = %d,\\left|S^{*}\\right| = %d}$", case, N, N, K, NNZ)))
   plot(X_draw2,main=TeX(sprintf("$\\textbf{Case  %d}$", case)))
-  return(X2)
+  
+  output <- list(X2,TT,RR)
+  return(output)
 }
 
 Network3<-function(N,N_K,N_K_1,K,NNZ,case){
@@ -241,7 +247,9 @@ Network3<-function(N,N_K,N_K_1,K,NNZ,case){
   E(X_draw2)[list]$color <- "green"
   #plot(X_draw2,main=TeX(sprintf("$\\textbf{Case %d : n = %d, n_{1} = %d, K = %d,\\left|S^{*}\\right| = %d}$", case, N, N, K, NNZ)))
   plot(X_draw2,main=TeX(sprintf("$\\textbf{Case  %d}$", case)))
-  return(X2)
+  
+  output <- list(X2,TT,RR)
+  return(output)
 }
 
 SynData <- function(alpha,F,D,S,N){
[…]

### 2019-09-09 Codes & Data/Codes/functions.R

@@ -159,13 +159,13 @@ score = function(adj, K)
 
 
 
-plotScree=function(adj,case)
+plotScree=function(adj)
 {
   #adj can be symmetric or asymmetric
   m = dim(adj)
   values = eigen(adj %*% t(adj))$values 
   plot(sqrt(values[1:20]), cex=2, pch=22, type="b", lty=2, lwd=3, col="red", bg="red", xlab="", ylab="",
-       main=TeX(sprintf("$\\textbf{Case  %d}$", case)))
+       main=TeX(sprintf("$\\textbf{Sub-Network}$")))
 }
 
 

### 2019-09-17 Manuscript for submission/manuscript.tex
Update

@@
 \usepackage[nottoc,notlot,notlof]{tocbibind}
-
+\newcommand{\block}[1]{
+  \underbrace{\begin{matrix}1 & \cdots & 1\end{matrix}}_{#1}
+}
 %\newtheorem{theorem}{Theorem}[section]
@@
 \label{eq:logistic02}
-\mathbb{P}(X_{ij}=1) = \frac{\exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}}{1 + \exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}}.
+\mathbb{P}(X_{ij}=1) = \frac{\exp\left(\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right)}{1 + \exp\left(\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right)}.
 \end{equation}
@@
 \mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
-= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
+= \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F)\right)}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
 \end{equation}
@@
 
-Our work is motivated from a recent work {\emph{Fused Latent and Graphical (FLaG) model} (Chen et al, 2016, \cite{chen2016fused}).
+Our work is motivated from a recent work named {\emph{Fused Latent and Graphical (FLaG) model} (Chen et al, 2016, \cite{chen2016fused}).
 They assume that majority of variation of responses can be accounted by low dimensional latent vector, and remaining dependent structure of responses can be explained by sparse graphical structure.
@@
 \item In FLaG model, a collection of binary responses for each question in the questionnaire follows a joint distribution, which is a combination of the Item Response Theory (IRT) model and the Ising model.
-    We model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of the Latent Factor Analysis model and the sparse graphical model.
+    We model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of the Latent Factor Analysis model and the Sparse Graphical model.
 
@@
 In Section \ref{sec:estimate}, we will discuss the assumptions in our model and penalization on likelihood function that is constructed in Section \ref{sec:model-form}.
-Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem formulated in Section \ref{sec:estimate}.
+In Section \ref{sec:theorem}, we provide a non-asymptotic error bound of the estimator.
+Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem that is formulated in Section \ref{sec:estimate}.
 In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians.
@@
 $$
-\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
-= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
+\mathbb{P}\left(\{X_{ij}, 1\le i,j \le n\}\right)
+= \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F)\right)}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
 $$
@@
 &=& \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha' + S_{ij}) }}{1 + e^{\alpha' + S_{ij} }} \nonumber \\
-&=& \frac{\exp(\alpha' \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet S)}{\prod_{1\le i<j \le n}  1 + e^{\alpha' + S_{ij} }}.
+&=& \frac{\exp\left(\alpha' \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet S\right)}{\prod_{1\le i<j \le n}  1 + e^{\alpha' + S_{ij} }}.
 \label{eq:logistic06}
@@
 
-\item To ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that the eigen-vector of $L$ is centered, that is,
+\item To ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and an arbitrary matrix $L$, we assume that the eigen-vector of $L$ is centered, that is,
 \[
@@
 \]
-where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$s. This condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.
+where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$'s. If we have $L=F^TDF$, this condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.
 
@@
 \section{Non-asymptotic error bound of the estimator}
-In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the number of papers in network is explicitly tracked.
+\label{sec:theorem}
+In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the number of papers in a network is explicitly tracked.
 We are interested in solving the following optimization problem :
@@
 \begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
-For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):
-\[
-\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
+For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of the log-likelihood function is bounded away from zero ($\tau > 0$):
+\[
+\nabla^{2}h(\Theta) = \mbox{diag}\Big(\mbox{vec}\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
 \Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
 \]
-For any vector $a$, $diag(a)$ is the diagonal matrix with elements of $a$ on its diagonal. For any square matrix $A$ and $B$, $ A \succcurlyeq B $ if and only if $A-B$ is positive semi-definite.
+For any vector $a$, $\mbox{diag}(a)$ is the diagonal matrix with elements of $a$ on its diagonal.
+For any square matrix $A$ and $B$, we have $ A \succcurlyeq B $ if and only if matrix $A-B$ is positive semi-definite.
 \end{assumption}
@@
 \begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
-To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
+To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
 We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
@@
 
-With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through following theorem.
+With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through the following theorem.
 In our result, we measure error using squared Frobenius norm summed across three matrices:
@@
 \begin{align} \label{eq:49}
-\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
+\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
 \end{align}
-There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
+then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, we have the following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
 \begin{align}
@@
     \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
-    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
+    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}},
 \end{align}
@@
 
-We would first like to note readers that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to generalized linear model.
-Our work considers a logistic loss function whose parameters are characterized by sparse matrix plus low rank matrix, whereas \cite{agarwal2012noisy} works on quadratic loss of noisy realization of linear transformation of sum of low rank and sparse matrices.
+We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
+Our work considers a logistic loss function whose parameters are characterized by a sparse matrix plus a low rank matrix, whereas Agarwal, et al.\cite{agarwal2012noisy} work on a quadratic loss of a noisy realization of a linear transformation of sum of a low rank matrix and a sparse matrix.
 We show that similar proof techniques can be applied in our case, giving us similar results.
@@
 f(x) + \frac{1}{2\lambda} \|x-v\|^2_2
-\right\}
+\right\},
 $$
@@
 \end{itemize}
-The convergence properties of the algorithm are summarized in the following result in \cite{boyd2011distributed}.
+The convergence properties of the algorithm are summarized in the following result as in \cite{boyd2011distributed}.
 Let $p^\ast$ be the minimal value in \eqref{eq:admm1}.
@@
 
-Now we see how ADMM can be adopted to solve for our penalized likelihood estimation \eqref{eq:logistic10}.
+Now we describe how ADMM can be adopted to solve for our penalized likelihood estimation problem in \eqref{eq:logistic10}.
 We reparameterize $M = L + S$ and let $x = (\alpha, M, L, S)$ (viewed as a vector).
@@
 
-\begin{remark}
-Throughout the Section, we add $*$ to the superscript of parameters to denote that they are ground truth parameters.
-We use $\alpha^*$ as an intercept term in logistic regression model, and
-$f^*_j$ as $j$th column of factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in network, and $n$ denotes the number of papers in the network.
-We also introduce a notation, $n_{l}$, denoting the number of papers, which share $l$ common topics.
-Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote weight coefficient of factors, and
-$S_{ij}^*$ denotes an ad-hoc citational relation between $i$th and $j$th paper.
-We use the notation $|(\bullet)|$ to denote the cardinality of non-zero components of upper-triangular part of $(\bullet)$ matrix
-(e.g., $|S^*|=|\{(i,j) : S_{ij}^{*}\neq 0, 1 \leq i<j \leq n\}|$).
-We will use $X \sim \text{Unif}[a,b]$ to denote
-the random variable $X$ is drawn from uniform distribution supported on the interval $[a,b]$.
-\end{remark}
+%\begin{remark}
+%Throughout the Section, we add $*$ to the superscript of parameters to denote that they are ground truth.
+%We use $\alpha^*$ as an intercept term in the logistic regression model, and
+%$f^*_j$ as the $j$th column of the factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in a network, and $n$ denotes the number of papers in the network.
+%We also introduce a notation, $n_{l}$, denoting the number of papers, which share $l$ common topics.
+%Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote the weight coefficients of factors, and
+%$S_{ij}^*$ denotes an ad-hoc citational relation between $i$th and $j$th paper.
+%We use the notation $|M|$ to denote the cardinality of non-zero components of the upper-triangular part of an arbitrary matrix $M$.
+%We will use $X \sim \text{Unif}[a,b]$ to denote
+%the random variable $X$ is drawn from the uniform distribution that is supported on the interval $[a,b]$.
+%\end{remark}
 
@@
 \label{sec:Syn-dat}
-After an introduction on three synthetic scenarios that we want to explore, three model selection criteria and three evaluation metrics for the selected model will be suggested.
-Experimental results from the synthetic networks and several interesting findings from those results will be elaborated subsequently.
-
-\begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig1.pdf}
-\caption{Graphical illustrations of $9$ synthetic networks. Note the links that are drawn from $S^*_{ij} \neq 0$ are colored in green. }
-\label{fig:figure1}
-\end{figure}
+After an introduction on two synthetic scenarios that we want to explore, we describe three model selection criteria and four evaluation metrics for the selected model.
+Subsequently, we elaborate experimental results from the synthetic networks and several interesting findings from those results.
 
 \subsubsection{Synthetic Setting}
-In this subsection, we consider following $3$ scenarios:
+%In this subsection, we consider the following $3$ scenarios:
 %In this subsection, we consider $3$ scenarios.
@@
 %In third scenario, we consider a situation
-\begin{itemize}
-    \item \textbf{First scenario.} When there is a network of $n$ papers with $K$ topics, there are $K$ clusters of papers, where each of which deals with $1$ specific topic out of $K$ topics.
-        And each cluster is comprised of $\frac{n}{K}$ non-overlapping papers.
-        Moreover, these $K$ clusters are connected with each other via $|S^*|$ random ad-hoc links.
-        Specifically, we assume $|S^*|/\binom{K}{2}$ ad-hoc links connect $2$ different clusters of papers.
-        For example, suppose that we have a network of $120$ papers with $5$ topics and with $30$ random ad-hoc links.
-Then, there are $5$ clusters, each of which has $24$ papers, and each of $10 (=\binom{5}{2})$ pairs of clusters is connected through $3 (=30/\binom{5}{2})$ random ad-hoc links.
+Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of procedures for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.
+
+\begin{enumerate}
+    \item We draw an intercept term $\alpha^*$ in the logistic regression model from the uniform distribution that is supported on [-11,-10].
+        %In this way, we can make $\alpha^*$ have the least effects in creating edges in the network.
+
+    \item Recall that the binary factor loading matrix $F^*$ encodes the relation between topics and papers
+        (i.e., if $i$th paper studies about $k$th topic, we denote $F^*_{ki}=1$, otherwise $F^*_{ki}=0$).
+        First, we simply set there exists $K$ topics in the network with $n$ papers, and each of them consists of $\frac{n}{K}$ papers.
+        This can be expressed in $F^*$ as follows:
+        \[
+            F^* =
+               \begin{bmatrix}
+                 \smash[b]{\block{n/K}} \\
+                 && \smash[b]{\block{n/K}} \\
+                 &&&& \ddots \\
+                 &&&&& \block{n/K}
+                \end{bmatrix}
+              \in R^{K \times n},
+        \]
+        where each row of $F^*$ has $\frac{n}{K}$ $1$s and each column has only one $1$.
+        Then, we assume that $n_{l}$ papers share $l$ topics and $n_{m}$ papers share $m$ topics ($1 < l < m \leq K$).
+        This can be represented in the $F^*$ in following steps:
+        $1)$ Pick distinct $n_{l}$ indices randomly from $\{1,2,\dots,n\}$.
+        We will denote the set of the indices as $\Omega_{n_l}$.
+        $2)$ Choose $n_{m}$ indices from the set $\{1,2,\dots,n\}\setminus \Omega_{n_{l}}$ and denote the set of those indices as $\Omega_{n_{m}}$.
+        $3)$ Make the columns of $F^*$ with corresponding indices in set $\Omega_{n_{l}} \cup \Omega_{n_{m}}$ zeros.
+        $4)$ We use a notation $f^*_j$ to denote the $j$th column of the matrix $F^*$.
+        Fill arbitrary $l$ entries of $f^*_j$ for $j \in \Omega_{n_l}$ with $1$s, and also fill arbitrary $m$ entries of $f^*_j$ for $j \in \Omega_{n_m}$ with $1$s.
+        Lastly, we set $F^*=JF^*$ where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$.
+
+    \item Generate weight coefficients of the factors $D^*_{ii}$ from the uniform distribution that is supported on $[19,20]$ $ \forall 1 \leq i \leq K$.
+
+    \item Remind that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
+        In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
+        Specifically, we assume that there are $\frac{|S^*|}{_KC_{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
+        This can be implemented via following steps:
+        1) We construct $K$ sets $C^*_1,\dots,C^*_K$ that are defined as follows:
+        \begin{align*}
+           &C^*_{1} \subseteq \big\{1, 2, \dots, \frac{n}{K} \big\} \setminus \big\{ \Omega_{n_l}
+           \cup \Omega_{n_m} \big\} \\
+           &C^*_{2} \subseteq \big\{\frac{n}{K}+1, \dots, \frac{2n}{K} \big\} \setminus \big\{ \Omega_{n_l} \cup \Omega_{n_m} \big\}  \\
+           &\vdots \\
+           &C^*_{K} \subseteq \big\{\frac{(K-1)n}{K}+1, \dots, n \big\} \setminus \big\{ \Omega_{n_l}
+           \cup \Omega_{n_m} \big\}
+        \end{align*}
+        where each of them has arbitrary $\frac{|S^*|}{_KC_{2}}$ elements.
+        2) Create a set $I_{S^*}$ whose elements are pairs of indices such that
+        \[
+            I_{S^*} =
+            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{_KC_{2}} \bigg\},
+        \]
+        where we use $i_r$ to indicate $r$th element $i$ in the set.
+        3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
+        4) Lastly, make it symmetric by setting $S^*={S^*}^{T}$.
+    \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
+        The distribution's parameter is parametrized by a probability, $P^{*}_{ij}=\frac{\exp (\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}$.
+        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X=X^T$.
+\end{enumerate}
+
+%\begin{itemize}
+%    \item \textbf{First scenario.}
+        %We consider a network of $n$ papers with $K$ topics, as represented by $K$ clusters.
+        %There are $K$ clusters of papers, where each of which deals with $1$ specific topic out of $K$ topics.
+        %Each cluster consists of $\frac{n}{K}$ non-overlapping papers.
+        %Moreover, these $K$ clusters are connected with each other via $|S^*|$ random ad-hoc links.
+        %Specifically, we assume $|S^*|/\binom{K}{2}$ ad-hoc links connect two different clusters of papers.
+        %For example, suppose that we have a network of $120$ papers with five topics and with $30$ random ad-hoc links.
+Then, there are five clusters for $24$ papers, and each $10(=\binom{5}{2})$ pairs of clusters are connected by $3 (=30/\binom{5}{2})$ random ad-hoc links.
         %(See Fig$\ref{fig:figure1}$
-
-    \item \textbf{Second scenario.} Based upon the settings mentioned in the first scenario, we suppose that there are $n_{l}$ papers, which share $l(\leq K)$ common topics in the network.
-        For instance, if we have a network of $210$ papers with $3$ topics, and
-        $n_2$ is equal to $50$, then this means that there are $50$ papers out of $210$ papers, which have $2$ shared topics out of $3$ topics.
+        %\[\begin{bmatrix} a_{11}&a_{12}&\cdots &a_{1n} \\ a_{21}&a_{22}&\cdots &a_{2n} \\ \vdots & \vdots & \ddots & \vdots\\ a_{n1}&a_{n2}&\cdots &a_{nn} \end{bmatrix}\]
+
+%    \item \textbf{Second scenario.} Based upon the settings mentioned in the first scenario, we suppose that there are $n_{l}$ papers, which share $l(\leq K)$ common topics in the network.
+%        For instance, if we have a network of $210$ papers with $3$ topics, and
+%        $n_2$ is equal to $50$, then this means that there are $50$ papers out of $210$ papers, which have $2$ shared topics out of $3$ topics.
         %Here, we want to note the readers that ad-hoc links are not used either to connect the clusters of papers that share $l$ common topics, or to connect a cluster of $1$ topic and a cluster that share $l$ common topics.
@@
 
-     \item \textbf{Third scenario.} In this scenario, we want to study a role of $\alpha^*$ in the network.
-        In the first and second scenarios, we set $\alpha^* \sim \text{Unif}[-11,-10]$, so that it has little effect on creating random edges in the network.
-        In the third scenario, we set $\alpha^* \sim \text{Unif}[-4,-3]$, whereas other parametric settings for $D^*, F^*$ and $S^*$ are same with those from the first and second scenarios.
-        This setting has an effect on increasing the number of edges connecting the clusters of papers with $l$ topics and those with $1$ topic.
-\end{itemize}
-
-With these settings in mind, we construct $3$ cases of networks for scenarios $1$, $2$, and $3$ respectively. Specifically;
+     %\item \textbf{Third scenario.} In this scenario, we want to study a role of $\alpha^*$ in the network.
+        %In the first and second scenarios, we set $\alpha^* \sim \text{Unif}[-11,-10]$, so that it has little effect on creating random edges in the network.
+        %In the third scenario, we set $\alpha^* \sim \text{Unif}[-4,-3]$, whereas other parametric settings for $D^*, F^*$ and $S^*$ are same with those from the first and second scenarios.
+        %This setting has an effect on increasing the number of edges connecting the clusters of papers with $l$ topics and those with $1$ topic.
+%\end{itemize}
+
+With these settings in mind, we consider two scenarios, where each of them has three synthetic networks.
 
 \begin{enumerate}
-    \item In the first scenario, we consider following three cases: $\{(n^{(i)},n_{1}^{(i)},K^{(i)},|S^*|^{(i)})\}_{i=1}^{3}$ $=\{(30,30,3,9), (80,80,4,18),$ $(120,120,5,30)\}$.
+    \item In the first scenario, we consider three networks, in which each of them consists of papers with only one topic.
+        Specifically, following three networks
+        $\{(n^{(i)},n_{1}^{(i)},K^{(i)},|S^*|^{(i)})\}_{i=1}^{3}$ $=\{(30,30,3,9), (80,80,4,18),$ $(120,120,5,30)\}$ are considered.
         If we take an example, the notation  $(n^{(1)},n_{1}^{(1)},K^{(1)},|S^*|^{(1)})=(30,30,3,9)$ means that we generate a network with $30$ papers.
 There are $3$ topics embedded in the network, and $9$ random ad-hoc links connect $3$ clusters of papers, where each cluster represents a collection of papers with same topic.
-        Note that every paper in three networks, which are considered in this scenario, studies only about $1$ topic among $K$ topics.
-    \item In the second scenario, we consider three cases where we have
-        $\{(n^{(i)},n_{2}^{(i)},n_{3}^{(i)},K^{(i)},|S^{*}|^{(i)})\}_{i=1}^{3}=
+
+    \item In the second scenario, we consider three networks, in which each of them has some papers that have more than one topic.
+        In particular, we consider $\{(n^{(i)},n_{2}^{(i)},n_{3}^{(i)},K^{(i)},|S^{*}|^{(i)})\}_{i=1}^{3}=
         \{(120,0,10,3,18),$ $(210,50,0,3,18),(210,10,10,3,18)\}$.
@@
         Note that the $3$ clusters from these $190$ papers are connected through $18$ random ad-hoc links.
-    \item In the third scenario, we basically study the same $3$ cases with those from the second scenario.
-        (i.e., $\{(n^{(i)},n_{2}^{(i)},n_{3}^{(i)},K^{(i)},|S^{*}|^{(i)})
-        \}_{i=1}^{3}=\{(120,0,10,3,18), (210,50,0,3,18),(210,10,10,3,18)\}$)
-        The only difference between these two scenarios comes from the random setting of $\alpha^*$. (i.e.,$\alpha^* \sim \text{Unif}[-4,-3]$)
 \end{enumerate}
 
-All $9$ networks that are elaborated in scenarios $1$, $2$ and $3$ are visualized in Fig\ref{fig:figure1}.
-Note that ad-hoc links, which connect clusters of papers with $1$ topic, are colored in green.
-Readers can refer the R code provided in $\dots$, for more detailed descriptions on parametric settings for generating networks in Fig\ref{fig:figure1}.
+\begin{figure}[htbp]
+\includegraphics[width=1\textwidth]{Fig1.pdf}
+\caption{Graphical illustrations of six synthetic networks.
+Nodes that share the common factors are clustered. The cross cluster links are ad-hoc Citations.}
+\label{fig:figure1}
+\end{figure}
+
+All six networks that are elaborated in scenarios $1$ and $2$ are visualized in Fig\ref{fig:figure1}.
+Notice that the nodes that share the common topics are clustered,
+and the cross clustered links are ad-hoc citations.
+%ad-hoc links, which connect clusters of papers with $1$ topic, are colored in green.
+%Readers can refer the R code provided in $\dots$, for more detailed descriptions on parametric settings for generating networks in Fig\ref{fig:figure1}.
 
@@
 Here we present a heuristic procedure for choosing a good pair of tuning parameters $(\gamma,\delta)$.
-Following the scree-plot approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of the adjacency matrix $X$, and find an ``elbow'' point where the eigenvalues seem to level off.
+Following the scree-plot approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $15$ eigenvalues of the adjacency matrix $X$, and find an ``elbow'' point where the eigenvalues seem to level off.
 An index of the point, which is to the left of this elbow point, is considered as the number of the topics embedded in the network.
-(We will denote this number as $\hat{K}^{\text{Scree}}$.)
+(We will denote this number as $\widehat{K}^{\text{Scree}}$.)
 We want to note the readers that the scree-plot analysis serves as a good guideline for determining the range of grids to search over.
 With the estimate of the number of topics in the network in mind, we record the $\text{rank}(\widehat{L}^{\gamma,\delta})$ and $|\widehat{S}^{\gamma,\delta}|$ for each tuning parameter pair on a given grid.
-We need to go through several iterations of this recording procedure to find a proper range of grid, in which we can get $\text{rank}(\widehat{L}^{\gamma,\delta})=\hat{K}^{\text{Scree}}$
+We need to go through several iterations of this recording procedure to find a proper range of grid, in which we can get $\text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}}$
 and $10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X|$, via adjusting the range of grid for $\gamma$ and $\delta$ repeatedly.
@@
     (\gamma^{\text{Heu}},\delta^{\text{Heu}}):=
-    \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\hat{K}^{\text{Scree}},
+    \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}},
     \quad \mbox{mode} |\widehat{S}^{\gamma,\delta}| \quad
@@
 \]
-We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.
-
-\begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig2.pdf}
-\caption{ Scree plots for $9$ synthetic Networks.
-    $\hat{K}^{\text{Scree}}$ recovers the number of topics in network correctly for all $9$ cases.}
-\label{fig:figure2}
-\end{figure}
+We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following four evaluation metrics.
 
 \begin{eqnarray*}
-M_1 &=& \mathbbm{1}\big\{\text{rank}(\widehat{L}) = \text{rank}(L^{*})\big\}, \\
+M_1 &=& \mathbbm{1}\big\{\mbox{rank}(\widehat{L}) = \mbox{rank}(L^{*})\big\}, \\
 M_2 &=& \frac{\left|\big\{(i,j):i<j:S^{*}_{i,j} \neq0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}\right|}{\left|\big\{(i,j):i<j:S^{*}_{i,j}\neq0\big\}\right|}, \\
-M_3 &=& \frac{\left|\big\{(i,j):i<j:S^{*}_{i,j} = 0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}\right|}{\left|\big\{(i,j):i<j:S^{*}_{i,j}=0\big\}\right|},
+M_3 &=& \frac{\left|\big\{(i,j):i<j:S^{*}_{i,j} = 0 \quad \& \quad \widehat{S}_{i,j} \neq 0 \big\}\right|}{\left|\big\{(i,j):i<j:S^{*}_{i,j}=0\big\}\right|}, \\
+M_4 &=& \frac{\left|\big\{\mbox{Misclassified Nodes}\big\}\right|}{n},
 \end{eqnarray*}
-where $M_1$ is a metric on whether the selected model recovers true low rank structure of network,
+where $M_1$ is a metric on whether the selected model recovers the true low rank structure of network,
 $M_2$ evaluates the positive selection rate of the sparse ad-hoc structure in network,
 and $M_3$ evaluates the false discovery rate of ad-hoc edges.
-With properly selected tuning parameter, $M_1$ will be 1, $M_2$ will be close to 1, and $M_3$ will get close to 0.
-We present the evaluation results of $9$ cases via these $3$ criteria in Table \ref{tab:table1}.
+$M_4$ calculates the proportion of mis-classified nodes to the entire nodes in the network.
+With properly selected tuning parameter, $M_1$ will be 1, $M_2$ will be close to 1, and $M_3$ and $M_4$ will get close to 0.
+We present the evaluation results of the six cases via the four criteria, $M_1,M_2,M_3$, and $M_4$ in Table \ref{tab:table1}.
 
@@
     \item \textbf{Model Selection.}
-    First and foremost, choosing a good pair of tuning parameters is of essential issue when it comes to making a good statistical inference on data.
-    As presented in Table\ref{tab:table1}, we observe that the traditional model selection methods, both BIC and AIC, perform poorly on choosing true models, whereas our heuristic approach chooses good models reasonably well for the 9 artificial cases.
-    In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics for all $9$ cases. (See Fig\ref{fig:figure2})
-    On the other hand, both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\widehat{S}|)$ of ad-hoc links among the estimated ($\widehat{L}$,$\widehat{S}$)s' over the given grid.
-
-    \item \textbf{Node Membership.}
-    After fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether the $i$th paper belongs to $k$th topic or not.
-    We apply a simple $k$-means clustering algorithm on the $\widehat{L}$ matrix’s $K(=\text{rank}(\widehat{L}))$ eigenvectors.
-    (We will denote column-wise concatenation of these $K$ eigenvectors as $\widehat{E}_{K} \in \mathbb{R}^{n\times K}$.)
-    For $3$ cases in Scenario $1$, where each paper in the network can only have $1$ topic, we confirm that $k$-means algorithm performs well on classifying papers in the network.
-    However, in Scenario $2$ and $3$ where we allow the papers in the network can have more than $1$ topic, naive implementation of $k$-means algorithm entails a problem, since it is not able to afford the overlapped membership of nodes.
-    In order to obtain a sense on how many clusters of papers exist in latent space, we project each row of the $\widehat{E}_{K}$ on the first and second principal components of data matrix $\widehat{E}_{K}$, and plot the projected points on $2$-dimensional plane.
-    We count the number of distinct clusters plotted on the plane. Subsequently, we run the $k$-means algorithm on the projected points.
-    See Fig\ref{fig:figure3} for the references on how this procedure performs on $9$ synthetic cases.
-
-    \item \textbf{Scenario $2$ vs. Scenario $3$.}
-    We empirically observe that the number of edges between clusters $\big\{ C_{i,j}:\forall 1 \leq i \neq j \leq K \big\}$ and $\big\{ C_{i}: \forall 1 \leq i \leq K \big\}$ has an effect on their clustering behaviors in latent space.
-Here $C_{i}$ is used to represent a set of papers on $i$th topic, and $C_{i,j}$ is used to denote a collection of papers that have $i$th and $j$th topics.
-    If we take a look at Fig\ref{fig:figure3}, Case $4$ in second scenario illustrates that it is difficult for us to visually distinguish the papers in $C_{1,2,3}$ and those in $\big\{ C_{i}: \forall 1 \leq i \leq 3 \big\}$ in projected space, whereas they are obviously distinguishable in Case $7$.
-    Unfortunately, we can observe similar phenomenon in Case $5$ and $6$, where the exact separations of clusters $\big\{ C_{i,j}:\forall 1 \leq i \neq j \leq 3 \big\}$ are not made.
-    %makes $k$-means algorithm difficult to distinguish the clusters of papers $C_{1,2}, C_{2,3}, C_{1,3}$ and $C_{1,2,3}$ from each other both in Case $5$ and $6$.
-    On the other hand, in third scenario, distinct separations are made between $6$ clusters $C_{1}, C_{2}, C_{3}, C_{1,2}, C_{2,3}, C_{1,3}$ in Case $8$, and between $7$ clusters $C_{1}, C_{2}, C_{3}, C_{1,2}, C_{2,3}, C_{1,3}, C_{1,2,3}$ in Case $9$, so that we can explicitly know the membership of each paper in the network.
-
-    % In fact, this observation is especially helpful for us to understand the behavior of our model with the statisticians’ citation network data, which we are going to explore in the following subsection.
-    % In the statisticians’ citation network, we also observe clusters of papers, which have more than $1$ topic, behave similarly with those from the second scenario.
-
-    \item \textbf{Ad-hoc links.}
-    In our setting, ad-hoc links of synthetic network data are considered as ``across edges'' between clusters $\big\{ C_{i}: \forall 1 \leq i \leq K \big\}$.
-    Our heuristic method works much better than either AIC or BIC in recovering the ad-hoc edges for the $6$ cases in $3$ scenarios.
-    For the three Cases (i.e., Case $2,3,9$) where both AIC and BIC work well, all the pairs of tuning parameters in the grid give the same $|\widehat{S}^{\gamma,\delta}|$.
-
-    %Since indices of non-zero entries of $S^{*}$ are randomly chosen, there might be some indices of positive $S^{*}_{ij}$ entries where $L^{*}_{ij}$ is also positive.
-    %In this case, this makes the edges indistinguishable if they come from $S^{*}_{ij}$ or $L^{*}_{ij}$.
-    %Some of ``across edges" are also attributed to $\alpha^{*}$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha^{*}$ or $S^{*}_{ij}$.
-    %So the total number of ``across edges'' might not be exactly same as $|S^*|$ as we set in our data generation setting.
-\end{enumerate}
+    First and foremost, choosing a good pair of tuning parameters is critical when it comes to making a good statistical inference on data.
+    As presented in Table\ref{tab:table1}, both BIC and AIC, which are well known for their model selection consistency in asymptotic setting, appear to under-estimate either the number of topics or the number of ad-hoc links in the networks in our synthetic settings.
+This may be caused by the fact that these traditional methods take the sample size into account, and therefore penalizes the model complexity too harshly.
+    In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics, and this strategy leads us to good model selection results for all the six cases considered in two scenarios.
+(See Fig\ref{fig:figure2}.)
 
     \begin{table}[htbp]
-%\centering
-%\begin{tabular}{c|ccc|ccc|ccc}
-%   & \multicolumn{9}{c|}{Scenario 1}
-%   & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\ %\cline{2-10}
-%   & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC    & Heuristic        & AIC    & BIC   \\ \hline
-%$M_1$ & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
-%$M_2$ & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
-%$M_3$ & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0
-%\end{tabular}
-%\begin{table}[htbp]
-
     \centering
@@
                 \hline
-$M_{1}$   &    1(3)  &    0(2)   &  0(2)  &    1(4)    &  0(3)   &  0(3)  &    1(5)  &   0(4)    &   0(4) \\
+    $M_{1}$   &    1 (3)  &    0 (2)   &  0 (2)  &    1 (4)    &  0 (3)   &  0 (3)  &    1 (5)  &   0 (4)    & 0 (4) \\
     $M_{2}$   &    1     &    0 &      0 &         1    &     1  &    1  &         1    &    1   &   1   \\
     $M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
-%Grid Region &    &       &      &             &       &      &             &       &      \\
+    $M_{4}$   &  0  &       &      &   0          &       &      &  0           &       &      \\
                 \hline
@@
                 \hline
-$M_{1}$   &   1(3)     &     1(3)  &  1(3)    &      1(3)   &   1(3)    &  1(3)    &   1(3)     &  1(3)     &   1(3)   \\
+    $M_{1}$   &   1 (3)     &     1 (3)  &  1 (3)    &      1 (3)   &   1 (3)    &  1 (3)    &   1 (3)     &  1 (3)   & 1 (3)   \\
     $M_{2}$   &   $\frac{17}{18}$   &   0    &    0  &   $\frac{17}{18}$     &   0    &  0    &  $\frac{16}{18}$    &   0    &  0    \\
     $M_{3}$   &   0 &     0  &   0   &        0     &    0   &  0    &        0     &   0    & 0 \\
-%Grid Region &             &       &      &             &       &      &             &       &      \\
+    $M_{4}$   &   0 &       &      &          0   &       &      &   $\frac{2}{210}$       &       &      \\
                 \hline
     \end{tabular}
-
-\begin{tabular}{c|ccc|ccc|ccc}
-            & \multicolumn{9}{c}{\textbf{Scenario 3}}                                              \\
-            \cline{2-10}
-            & \multicolumn{3}{c|}{Case 7} & \multicolumn{3}{c|}{Case 8} & \multicolumn{3}{c}{Case 9} \\
-            \cline{2-10}
-            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
-            \hline
-$M_{1}$  &    1(3)   &   1(3)    &  1(3)    &     1(3)        &    1(3)   &  1(3)    &   1(3)          &  1(3)      &  1(3)     \\
-$M_{2}$  &     1       &   0  &    0  &    $\frac{15}{18}$         &   0  &  0  &   1   &  1    &   1     \\
-$M_{3}$  &  $\frac{1}{7122}$  &  0  &  0   &   $\frac{3}{21927}$ &     0  &  0     &  $\frac{4}{21927}$ & $\frac{4}{21927}$ & $\frac{4}{21927}$ \\
-%Grid Region &             &       &      &             &       &      &             &       &      \\
-\end{tabular}
-\caption{ For three scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
+    \caption{ For two scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$. 
+    Also note that it chooses a model whose mis-classification rate is close to $0$.
     A number in the parentheses represents the rank of $\widehat{L}$ estimated from ($\gamma^{\text{Heu}},\delta^{\text{Heu}}$), ($\gamma^{\text{AIC}},\delta^{\text{AIC}}$) and ($\gamma^{\text{BIC}},\delta^{\text{BIC}}$) for each case.}
@@
     \begin{figure}[htbp]
+        \includegraphics[width=1\textwidth]{Fig2.pdf}
+        \caption{ Scree plots for six synthetic Networks.
+        $\hat{K}^{\mbox{Scree}}$ recovers the number of topics in the network correctly for all six cases.}
+        \label{fig:figure2}
+    \end{figure}
+
+    \item \textbf{Node Membership.}
+    After fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether the $i$th paper belongs to the $k$th topic or not.
+    We apply a simple $k$-means clustering algorithm on the $\widehat{L}$ matrix’s $K$ eigenvectors where $K$ denotes the rank of matrix $\widehat{L}$.
+    %(We will denote column-wise concatenation of these $K$ eigenvectors as $\widehat{E}_{K} \in \mathbb{R}^{n\times K}$.)
+    For three cases in Scenario $1$, where each paper in the network only has one topic, we confirm that $k$-means algorithm performs well on classifying papers in the network.
+    However, in Scenario $2$ where we allow the papers in the network can have more than one topic, naive implementation of $k$-means algorithm entails a problem, since it is not able to afford the overlapped membership of nodes.
+    Here, we create a matrix $\widehat{E}_{K}\in \mathbb{R}^{n \times K}$, whose $i$th column corresponds to the $i$th eigenvector of the $\widehat{L}$.
+    In order to obtain a sense on how many clusters of papers exist in latent space, we project each row of the $\widehat{E}_{K}$ on the first and second principal components of data matrix $\widehat{E}_{K}$, and plot the projected points on $2$-dimensional plane.
+    We count the number of distinct clusters plotted on the plane. Subsequently, we run the $k$-means algorithm on the projected points.
+    Refer Table\ref{tab:table1} and Fig\ref{fig:figure3} for the references on how this procedure performs on six synthetic cases.
+
+    \begin{figure}[htbp]
+    \centering
     \includegraphics[width=1\textwidth]{Fig3.pdf}
-\caption{ Plots of the projected points on the first (X-axis) and second (Y-axis) principal component of the data matrix $\widehat{E}_{K}$.
+    \caption{ Case $1\sim3$ : Plots of rows from the first two eigenvectors of $\widehat{L}^{\gamma^{\text{Heu}},\delta^{\text{Heu}}}$.
+    Case $4 \sim 6$ : Plots of the projected points on the first (X-axis) and second (Y-axis) principal component of the data matrix $\widehat{E}_{K}^{\gamma^{\text{Heu}},\delta^{\text{Heu}}}$.
 Different colors represent different clusters of papers that $k$-means algorithm assigns.}
@@
     \end{figure}
+
+    %\item \textbf{Scenario $2$ vs. Scenario $3$.}
+    %We empirically observe that the number of edges between clusters $\big\{ C_{i,j}:\forall 1 \leq i \neq j \leq K \big\}$ and $\big\{ C_{i}: \forall 1 \leq i \leq K \big\}$ has an effect on their clustering behaviors in latent space.
+Here $C_{i}$ is used to represent a set of papers on $i$th topic, and $C_{i,j}$ is used to denote a collection of papers that have $i$th and $j$th topics.
+    %If we take a look at Fig\ref{fig:figure3}, Case $4$ in second scenario illustrates that it is difficult for us to visually distinguish the papers in $C_{1,2,3}$ and those in $\big\{ C_{i}: \forall 1 \leq i \leq 3 \big\}$ in projected space, whereas they are obviously distinguishable in Case $7$.
+    %Unfortunately, we can observe similar phenomenon in Case $5$ and $6$, where the exact separations of clusters $\big\{ C_{i,j}:\forall 1 \leq i \neq j \leq 3 \big\}$ are not made.
+    %makes $k$-means algorithm difficult to distinguish the clusters of papers $C_{1,2}, C_{2,3}, C_{1,3}$ and $C_{1,2,3}$ from each other both in Case $5$ and $6$.
+    %On the other hand, in third scenario, distinct separations are made between $6$ clusters $C_{1}, C_{2}, C_{3}, C_{1,2}, C_{2,3}, C_{1,3}$ in Case $8$, and between $7$ clusters $C_{1}, C_{2}, C_{3}, C_{1,2}, C_{2,3}, C_{1,3}, C_{1,2,3}$ in Case $9$, so that we can explicitly know the membership of each paper in the network.
+
+    % In fact, this observation is especially helpful for us to understand the behavior of our model with the statisticians’ citation network data, which we are going to explore in the following subsection.
+    % In the statisticians’ citation network, we also observe clusters of papers, which have more than $1$ topic, behave similarly with those from the second scenario.
+
+    %\item \textbf{Ad-hoc links.}
+    %In our setting, ad-hoc links of synthetic network data are considered as ``across edges'' between clusters $\big\{ C_{i}: \forall 1 \leq i \leq K \big\}$.
+    %Our heuristic method works much better than either AIC or BIC in recovering the ad-hoc edges for the $6$ cases in $3$ scenarios.
+    %For the three Cases (i.e., Case $2,3,9$) where both AIC and BIC work well, all the pairs of tuning parameters in the grid give the same $|\widehat{S}^{\gamma,\delta}|$.
+
+    %Since indices of non-zero entries of $S^{*}$ are randomly chosen, there might be some indices of positive $S^{*}_{ij}$ entries where $L^{*}_{ij}$ is also positive.
+    %In this case, this makes the edges indistinguishable if they come from $S^{*}_{ij}$ or $L^{*}_{ij}$.
+    %Some of ``across edges" are also attributed to $\alpha^{*}$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha^{*}$ or $S^{*}_{ij}$.
+    %So the total number of ``across edges'' might not be exactly same as $|S^*|$ as we set in our data generation setting.
+\end{enumerate}
 
@@
 Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting data set on citation  and co-authorship networks of statisticians.
-Citational relationships over $3000$ papers from $4$ statistical journals were collected, and collaborative network among authors of the papers is also given.
+Citational relationships over $3000$ papers from four statistical journals were collected, and collaborative network among authors of the papers is also given.
 In our work, we only analyze the citation network of papers.
@@
 \end{figure}
-This dataset is based on all papers published from $2003$ to first half of $2012$, in $4$ of the top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association and Journal of Royal Statistical Society (Series B).
-Among  $3248$ papers in total, we restrict our attention on papers, which have greater than or equal to $7$ citations from the collected papers.
+This dataset is based on all papers published from $2003$ to the first half of $2012$, in the four top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association and Journal of Royal Statistical Society (Series B).
+Among the $3248$ papers in total, we restrict our attention on papers, which have greater than or equal to seven citations from the collected papers.
 Consequently, we have $543$ papers in total.
-The elbow points of the eigen-value scree plot  from  may be at the $3$rd, $7$th, or $9$th largest eigenvalue, suggesting that there might be from $2$ to $8$ topics embedded in network (See Fig$\ref{fig:figure3}$).
+The elbow points of the scree plot from the network
+may be at the $3$rd, $7$th, or $9$th largest eigenvalue, suggesting that there might be from $2$ to $8$ topics embedded in the network (See Fig$\ref{fig:figure4}$ for the reference).
 In light of this, we performed our analysis under the assumption that there might exist $2$ distinct topics and one giant component, in which $3$ or $4$ topics are mixed up.
@@
 A pair of parameters, $(\gamma^{\text{Heu}},\delta^{\text{Heu}}) = (0.000912,0.0097)$, gives us $\widehat{L}$ with rank $3$, and $\widehat{S}$ with $|\widehat{S}|=197$.
-We apply $k$-means algorithm on $3$ eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in Fig $\ref{fig:figure4}$.
-$404$ papers colored in green are densely clustered nearby the origin with a short tail, (Fig $\ref{fig:figure4}$), and $k$-means classifies these papers as third topic.
+We apply $k$-means algorithm on the first three eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in Fig $\ref{fig:figure5}$.
+$404$ papers colored in green are densely clustered nearby the origin with a short tail, (Fig $\ref{fig:figure5}$), and $k$-means classifies these papers as third topic.
 We list the first two topics discovered through our analysis.
@@
 \begin{itemize}
-  \item Variable selection ($85$ papers)
-  \item Multiple Hypothesis Testing ($54$ papers)
+  \item Variable selection, which includes $85$ paper.
+  \item Multiple Hypothesis Testing, which includes $54$ papers.
 \end{itemize}
@@
 \begin{itemize}
-  \item Non-parametric Bayesian Statistics ($17$ papers)
-  \item Functional Data analysis ($35$ papers)
-  \item Dimension Reduction ($23$ papers)
-  \item Mixed topics ($329$ papers)
+  \item Non-parametric Bayesian Statistics, which includes $17$ papers.
+  \item Functional Data analysis, which includes $35$ papers.
+  \item Dimension Reduction, which includes $23$ papers.
+  \item Mixed topics, which includes $329$ papers.
 \end{itemize}
@@
 Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $M$ as $P_{M}$.
-And also note that proof relies on following lemma:
+And also note that proof relies on the following lemma:
 
 \begin{lemma} \label{le:le1}
-If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we have
+If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}\left(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\right)$, we have
 \[
@@
     \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
-    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
+    3\mathbb{Q}\left(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\right)+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
     \|S^{*}_{M^\perp}\|_{1}
@@
 \begin{proof}
-Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal and feasible (respectively) for the convex program (\ref{eq:1}), we have
+Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal minimizer and feasible solution respectively for the convex program (\ref{eq:Modified}), we have
 \begin{equation}\label{eq:2}

### 2019-09-17 Codes & Data/Codes/Synthetic Data Scenario.R

@@ -9,7 +9,7 @@ source('functions.R')
 source('Synthetic Networks.R')
 #################### data generation N = 30, K = 3, NNZ = 10 ####################
 set.seed(123)
-par(mfrow=c(3,3),mar = c(1, 1.5, 1.5, 1.5)) # ??? ??? ??? ??? # 
+par(mfrow=c(2,3),mar = c(1, 1.5, 1.5, 1.5)) # ??? ??? ??? ??? # 
 ######## First Scenario ########
 set.seed(123); Net1 <- Network1(30,3,9,1)
 set.seed(123); Net2 <- Network1(80,4,18,2)
@@ -18,6 +18,8 @@ set.seed(123); Net3 <- Network1(120,5,30,3)
 set.seed(123); Net4 <- Network2(120,10,0,3,20,4)
 set.seed(123); Net5 <- Network2(210,0,50,3,18,5)
 set.seed(123); Net6 <- Network2(210,10,10,3,18,6)
+par(mfrow=c(1,1))
+
 ######## Third Scenario ########
 set.seed(123); Net7 <- Network3(120,10,0,3,20,7)
 set.seed(123); Net8 <- Network3(210,0,50,3,18,8)
@@ -40,9 +42,9 @@ gamma = seq(from=0.004,to=0.005,by=0.0001);
 delta = seq(from=0.009,to=0.01,by=0.0001);
 Res2 <- Model_Sel(Net2,gamma,delta) ## gamma : 0.004, delta : 0.009 ## 
 
-gamma = seq(from=0.002,to=0.003,by=0.0005);
-delta = seq(from=0.0046,to=0.0048,by=0.00005);
-Res3 <- Model_Sel(Net3,gamma,delta) ## gamma : 0.003, delta : 0.00475 ##
+gamma = seq(from=0.002,to=0.003,by=0.0001);
+delta = seq(from=0.0046,to=0.0048,by=0.00002);
+Res3 <- Model_Sel(Net3[[1]],gamma,delta) ## gamma : 0.003, delta : 0.00475 ##
 
 ################ Scenario 2 ################
 gamma = seq(from=0.002,to=0.004,by=0.0002);
@@ -61,6 +63,7 @@ Res6 <- Model_Sel(Net6[[1]],gamma,delta) ## gamma : 0.002, delta : 0.016
 gamma = seq(from=0.002,to=0.004,by=0.0002);
[…]

### 2019-09-17 Codes & Data/Codes/Synthetic Networks.R

@@ -38,12 +38,6 @@ Network1 <- function(N,K,NNZ, case){
   S = S + t(S)
   diag(S) = 0
   
-  ### Create random symmetric sparse matrix S, whose entries are greater than or equal to zero.
-  #S = matrix(0,N,N)
-  #S = rsparsematrix(N, N, nnz = NNZ, symmetric = TRUE, rand.x = runif)
-  #S[which(S!=0,arr.ind=TRUE)] = runif(1,6,7)
-  #diag(S) = 0
-  
   ### call function to generate the adjacency matrix
   X1 <- SynData(alpha,F,D,S,N)
   
@@ -70,10 +64,10 @@ Network1 <- function(N,K,NNZ, case){
   
   E(X_draw)$color <- "red"
   E(X_draw)[list]$color <- "green"
-  #plot(X_draw,main=TeX(sprintf("$\\textbf{Case %d : n = %d, n_{1} = %d, K = %d,\\left|S^{*}\\right| = %d}$", case, N, N, K, NNZ)))
-  plot(X_draw,main=TeX(sprintf("$\\textbf{Case  %d}$", case)))
-  #plot(X_draw,main=Tex(sprintf("$\\Scenario 1 : Case (%d)$",Case)))
   
+  plot(X_draw, family="serif", vertex.size=10, vertex.label=NA)
+  title(sprintf("Case %d",case),family="LM Roman 10")
+
   Res <- list(X1,B)
   return(Res)
 }
@@ -159,8 +153,9 @@ Network2<-function(N,N_K,N_K_1,K,NNZ, case){
   }
   E(X_draw2)$color <- "red"
   E(X_draw2)[list]$color <- "green"
-  #plot(X_draw2,main=TeX(sprintf("$\\textbf{Case %d \\ n = %d, n_{1} = %d, K = %d,\\left|S^{*}\\right| = %d}$", case, N, N, K, NNZ)))
-  plot(X_draw2,main=TeX(sprintf("$\\textbf{Case  %d}$", case)))
+  
+  plot(X_draw2, family="serif", vertex.size=10, vertex.label=NA)
+  title(sprintf("Case %d",case),family="serif")
   
   output <- list(X2,TT,RR)
   return(output)
@@ -335,18 +330,33 @@ K_means<-function(X, gamma, delta, K_clusters, case){
   FAC = eigen(L)$vectors[,1:K]
   pca <- prcomp(FAC,scale=TRUE)
 
[…]

### 2019-09-17 Codes & Data/Codes/citation_network_analysis.R

@@ -1,12 +1,14 @@
 ####################  preparation  ####################
 rm(list=ls())
-setwd('C:/Users/nsuh3/Desktop/Citation Network/FLag/Codes & Data')
+setwd('C:/Users/namjo/Documents/GitHub/Citation-Network/Codes & Data/Codes')
 library('Matrix')      ## For matrix computation on BIC
 library('igraph')      ## For drawing graph
 source('SynData.R')    ## Function for creating binary network
 source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
 source('functions.R')
+source('GD.R')
 ################### Load the Citation Network Data ###################
+setwd('C:/Users/namjo/Documents/GitHub/Citation-Network/Codes & Data/Statistician network data')
 paperCitAdj = as.matrix(read.table("paperCitAdj.txt", header=FALSE))
 G <- graph.adjacency(paperCitAdj, mode="undirected", weighted=NULL) # For directed networks
 X <- as_adjacency_matrix(G,type="both",names=TRUE,sparse=FALSE,attr=NULL)
@@ -25,8 +27,8 @@ plotScree(X_new)
 X = X_new
 
 ################### Model Selection ###################
-gamma = seq(from=0.0009,to=0.00093,by=0.000003);
-delta = seq(from=0.009,to=0.01,by=0.0001);
+gamma = seq(from=0.01,to=0.01,by=0.00000);
+delta = seq(from=0.01,to=0.01,by=0.0001);
 lambda = 1; Count = 1;
 AIC <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
 BIC <- matrix( 0, nrow=length(gamma),ncol=length(delta) )
@@ -40,7 +42,7 @@ source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
 for(g in 1:length(gamma)){
   for(d in 1:length(delta)) {
     ### Use the ADMM method to estimate the parameters ###
-    result <- ADMM(X_chunk, gamma[g], delta[d])
+    result <- ADMM(X, 1, 0.01)
     
     a<-result1[[1]]
     M<-result1[[2]]
@@ -63,8 +65,8 @@ for(g in 1:length(gamma)){
     log_sum<-log(1+exp(a + L + S))
     
     log_max <- 0;
-    log_max <- a*sum(X_chunk[upper.tri(X,diag=FALSE)]) +
[…]

### 2019-09-17 Codes & Data/Codes/functions.R

@@ -159,13 +159,14 @@ score = function(adj, K)
 
 
 
-plotScree=function(adj)
+plotScree=function(adj,case)
 {
   #adj can be symmetric or asymmetric
   m = dim(adj)
   values = eigen(adj %*% t(adj))$values 
-  plot(sqrt(values[1:20]), cex=2, pch=22, type="b", lty=2, lwd=3, col="red", bg="red", xlab="", ylab="",
-       main=TeX(sprintf("$\\textbf{Sub-Network}$")))
+  plot(sqrt(values[1:15]), cex=1, pch=22, type="b", 
+       lty=2, lwd=3, col="red", bg="red", xlab="", ylab="")
+  title(sprintf("Case %d",case),family="LM Roman 10")
 }
 
 

### 2019-09-17 Manuscript for submission/manuscript.tex
Update

@@
 For any vector $a$, $\mbox{diag}(a)$ is the diagonal matrix with elements of $a$ on its diagonal. 
+For any matrix $B=[b_1,\dots,b_n]\in\mathbb{R}^{n \times n}$, $\mbox{vex}(B)\in\mathbb{R}^{n^2}$ is obtained by stacking $ b_1,\dots, b_{n}$ in order. 
 For any square matrix $A$ and $B$, we have $ A \succcurlyeq B $ if and only if matrix $A-B$ is positive semi-definite.
@@
 As expected, third group is quite hard to interpret and seems to have substructures.
-For further investigation on this group, after obtaining the sub-network which is comprised only with the papers in the third group, we performed same analysis once again under the assumption that $K=4$ (See Fig$\ref{fig:figure3}$,right).
+For further investigation on this group, after obtaining the sub-network which is comprised only with the papers in the third group, we performed same analysis once again under the assumption that $K=4$ (See Fig$\ref{fig:figure4}$,right).
 We obtain four sub-communities as follows:

### 2019-10-01 Manuscript for submission/manuscript.tex
Update

--- 2019-09-17 Manuscript for submission/manuscript.tex
@@
 This slight modification leads to neither theoretical consequence nor noticeable difference in practice.
-Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:Modified}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth, which governs the data generating process.
-Let $\widehat{\Theta},\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
+Let ($\widehat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:Modified}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth, which governs the data generating process.
+Let $\widehat{\Theta}$ and $\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \widehat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
 And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*},
-\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
+\widehat{\Delta}^{\alpha} = \widehat{\alpha}-\alpha^{*},
 \widehat{\Delta}^L = \widehat{L}-L^{*},
@@
 For any vector $a$, $\mbox{diag}(a)$ is the diagonal matrix with elements of $a$ on its diagonal.
+For any matrix $B=[b_1,\dots,b_n]\in\mathbb{R}^{n \times n}$, $\mbox{vec}(B)\in\mathbb{R}^{n^2}$ is obtained by stacking $ b_1,\dots, b_{n}$ in order.
 For any square matrix $A$ and $B$, we have $ A \succcurlyeq B $ if and only if matrix $A-B$ is positive semi-definite.
@@
 \[
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
+    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})
+    :=\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
 \]
@@
 \end{align}
-then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, we have the following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
+then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
 \begin{align}
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
+    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
     \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
@@
 Section \ref{sec:Num-anal} is divided into two parts.
-In subsection \ref{sec:Syn-dat}, we conduct an empirical study of measuring the performance of our proposed method with artificially specified graphical structures.
-In subsection \ref{sec:citation_network}, we perform a real data analysis with citation network for statisticians.
+In Section \ref{sec:Syn-dat}, we conduct an empirical study of our proposed method with artificial graphical structures.
+In Section \ref{sec:citation_network}, we perform a real data analysis with citation network for statisticians.
 
@@
 \label{sec:Syn-dat}
-After an introduction on two synthetic scenarios that we want to explore, we describe three model selection criteria and four evaluation metrics for the selected model.
+First, we introduce two synthetic scenarios that we want to explore.
+Then, we describe three model selection criteria and four evaluation metrics for the selected model.
 Subsequently, we elaborate experimental results from the synthetic networks and several interesting findings from those results.
@@
     \item We draw an intercept term $\alpha^*$ in the logistic regression model from the uniform distribution that is supported on [-11,-10].
-        %In this way, we can make $\alpha^*$ have the least effects in creating edges in the network.
+        In this way, we can make $\alpha^*$ have the least effects in creating edges in the network.
 
@@
         (i.e., if $i$th paper studies about $k$th topic, we denote $F^*_{ki}=1$, otherwise $F^*_{ki}=0$).
-        First, we simply set there exists $K$ topics in the network with $n$ papers, and each of them consists of $\frac{n}{K}$ papers.
+        First, we assume that there are $n$ papers in the network, and $K$ topics are embedded in the network. Each of them consists of $\frac{n}{K}$ papers.
         This can be expressed in $F^*$ as follows:
@@
         \]
-        where each row of $F^*$ has $\frac{n}{K}$ $1$s and each column has only one $1$.
+        where each row of $F^*$ has $\frac{n}{K}$ $1$'s and each column has only one $1$.
         Then, we assume that $n_{l}$ papers share $l$ topics and $n_{m}$ papers share $m$ topics ($1 < l < m \leq K$).
@@
 
-    \item Generate weight coefficients of the factors $D^*_{ii}$ from the uniform distribution that is supported on $[19,20]$ $ \forall 1 \leq i \leq K$.
+    \item Generate the weight coefficients of the factors $D^*_{ii}$ from the uniform distribution that is supported on $[19,20]$ $ \forall 1 \leq i \leq K$.
+        In this way, we can let the papers with same topic cluster together.
 
@@
         3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
-        4) Lastly, make it symmetric by setting $S^*={S^*}^{T}$.
+        4) Lastly, make it symmetric by setting $S^*_{jj}=S^*_{ij},\forall 1\leq i < j \leq n$.
     \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
         The distribution's parameter is parametrized by a probability, $P^{*}_{ij}=\frac{\exp (\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}$.
-        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X=X^T$.
+        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X_{ji}=X_{ij},\forall 1 \leq i < j \leq n$.
 \end{enumerate}
@@
 
-All six networks that are elaborated in scenarios $1$ and $2$ are visualized in Fig\ref{fig:figure1}.
+All six networks that are elaborated in scenarios $1$ and $2$ are visualized in Fig.\ref{fig:figure1}.
 Notice that the nodes that share the common topics are clustered,
@@
 \subsubsection{Choosing the tuning parameters and evaluation criteria}
-We observe that choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
+Choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
 Here we present a heuristic procedure for choosing a good pair of tuning parameters $(\gamma,\delta)$.
@@
     \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}},
-    \quad \mbox{mode} |\widehat{S}^{\gamma,\delta}| \quad
-    \text{s.t.} \quad 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 0.05|X| \big\}
+    \mbox{mode} |\widehat{S}^{\gamma,\delta}|: \mbox{subject to} 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X| \big\}
 \]
@@
 With properly selected tuning parameter, $M_1$ will be 1, $M_2$ will be close to 1, and $M_3$ and $M_4$ will get close to 0.
-We present the evaluation results of the six cases via the four criteria, $M_1,M_2,M_3$, and $M_4$ in Table \ref{tab:table1}.
+We present the evaluation results of the six cases via the four criteria, $M_1,M_2,M_3$, and $M_4$ in Table.\ref{tab:table1}.
 
@@
     First and foremost, choosing a good pair of tuning parameters is critical when it comes to making a good statistical inference on data.
-    As presented in Table\ref{tab:table1}, both BIC and AIC, which are well known for their model selection consistency in asymptotic setting, appear to under-estimate either the number of topics or the number of ad-hoc links in the networks in our synthetic settings.
+    As presented in Table.\ref{tab:table1}, both BIC and AIC, which are well known for their model selection consistency in asymptotic setting, appear to under-estimate either the number of topics or the number of ad-hoc links in the networks in our synthetic settings.
 This may be caused by the fact that these traditional methods take the sample size into account, and therefore penalizes the model complexity too harshly.
     In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics, and this strategy leads us to good model selection results for all the six cases considered in two scenarios.
-(See Fig\ref{fig:figure2}.)
+(See Fig.\ref{fig:figure2})
 
@@
     $M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
-    $M_{4}$   &  0  &       &      &   0          &       &      &  0           &       &      \\
+    $M_{4}$   &  0  &   $\frac{20}{30}$    &  $\frac{20}{30}$    &   0          &   $\frac{25}{40}$    &   $\frac{25}{30}$   &  0      &  $\frac{30}{30}$     &   $\frac{30}{30}$   \\
                 \hline
@@
     $M_{3}$   &   0 &     0  &   0   &        0     &    0   &  0    &        0     &   0    & 0 \\
-    $M_{4}$   &   0 &       &      &          0   &       &      &   $\frac{2}{210}$       &       &      \\
+    $M_{4}$   &  0  &   $\frac{20}{120}$    &  $\frac{20}{120}$    &   0          &   $\frac{25}{210}$    &   $\frac{25}{210}$   &  0      &  $\frac{30}{210}$     &   $\frac{30}{210}$   \\
                 \hline
@@
     We count the number of distinct clusters plotted on the plane. Subsequently, we run the $k$-means algorithm on the projected points.
-    Refer Table\ref{tab:table1} and Fig\ref{fig:figure3} for the references on how this procedure performs on six synthetic cases.
+    Refer Table.\ref{tab:table1} and Fig.\ref{fig:figure3} for the references on how this procedure performs on six synthetic cases.
 
@@
 \label{sec:citation_network}
-Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting data set on citation  and co-authorship networks of statisticians.
-Citational relationships over $3000$ papers from four statistical journals were collected, and collaborative network among authors of the papers is also given.
-In our work, we only analyze the citation network of papers.
 \begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig4.pdf}
-\caption{ Scree plots for 543-Citation network, and Sub-network.}
+\includegraphics[width=1\textwidth]{Fig4.eps}
+\caption{From left to right : Scree plots of the adjacency matrix $X^{\mbox{orig}}$ and $X^{\mbox{sub}}$.}
 \label{fig:figure4}
 \end{figure}
-This dataset is based on all papers published from $2003$ to the first half of $2012$, in the four top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association and Journal of Royal Statistical Society (Series B).
-Among the $3248$ papers in total, we restrict our attention on papers, which have greater than or equal to seven citations from the collected papers.
-Consequently, we have $543$ papers in total.
-The elbow points of the scree plot from the network
-may be at the $3$rd, $7$th, or $9$th largest eigenvalue, suggesting that there might be from $2$ to $8$ topics embedded in the network (See Fig$\ref{fig:figure4}$ for the reference).
-In light of this, we performed our analysis under the assumption that there might exist $2$ distinct topics and one giant component, in which $3$ or $4$ topics are mixed up.
-
-A pair of parameters, $(\gamma^{\text{Heu}},\delta^{\text{Heu}}) = (0.000912,0.0097)$, gives us $\widehat{L}$ with rank $3$, and $\widehat{S}$ with $|\widehat{S}|=197$.
-We apply $k$-means algorithm on the first three eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in Fig $\ref{fig:figure5}$.
-$404$ papers colored in green are densely clustered nearby the origin with a short tail, (Fig $\ref{fig:figure5}$), and $k$-means classifies these papers as third topic.
-We list the first two topics discovered through our analysis.
-%Full lists of papers for each communities are provided in $\emph{https://sites.google.com/site/namjoonsuh/publications}$.
-
+Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting dataset on citation network of papers from statistics journals.
+Specifically, this dataset is based upon all papers published from $2003$ to the first half of $2012$, from the four top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association and Journal of Royal Statistical Society (Series B).
+Citational relationships of $3248$ papers are given in the form of adjacency matrix.
+In our analysis, we focus our attentions on the papers which have greater than or equal to $10$ citational edges in the network of Ji and Jin \cite{ji2016coauthorship}.
+After collecting papers with greater than or equal to $10$ citational edges and eliminating those that have no connecting edges from the rest, we have $232$ papers in total.
+
+We denote the adjacency matrix of these $232$ papers as $X^{\mbox{orig}}$.
+Elbow points of the scree plot from $X^{\mbox{orig}}$ may be at the $3$rd, $5$th, or $9$th largest eigenvalue, suggesting that there are from $2$ to $8$ embedded topics in the network.
+(See Fig.
+$\ref{fig:figure4}$)
+In light of this, we conduct the analysis in two steps:
+\begin{enumerate}
+    \item First, we assume that the network $X^{\mbox{orig}}$ has $2$ distinct topics and one giant mixed-component, which has a sub-network structure.
+Under this assumption, we set $\widehat{K}^{\mbox{scree}}$ as $3$, and select a proper model via our heuristic method.
+        Then, we perform a $k$-means algorithm on matrix $\widehat{E}_{3}$ treating each row of the matrix as one data point.
+        Note that we set the total number of clusters in the network as $3$ when we run the clustering algorithm.
+    \item Next, we restrict the network to the giant component ignoring all the edges to/from outside and obtain a subnetwork.
+        We denote the adjacency matrix of this subnetwork as $X^{\mbox{sub}}$. We set $\widehat{K}^{\mbox{scree}}$ as $5$, and also select a proper model through the heuristic method.
+        Here, we run the $k$-means algorithm on $\widehat{E}_{5}$ setting the number of clusters as $5$.
+\end{enumerate}
+
+In the first step, a pair of parameters, $(\gamma^{\text{Heu}},\delta^{\text{Heu}}) = (0.0021094, 0.01913)$, gives us $\widehat{L}^{\mbox{orig}}$ with rank $3$, and $\widehat{S}^{\mbox{orig}}$ with $|\widehat{S}^{\mbox{orig}}|=261$.
+We list the first two topics discovered through our analysis. Full list of papers for each community is provided in $https://sites.google.com/site/namjoonsuh/publications$.
 \begin{itemize}
-  \item Variable selection, which includes $85$ paper.
-  \item Multiple Hypothesis Testing, which includes $54$ papers.
+    \item Variable selection, which includes $43$ paper.
+    \item Multiple Hypothesis Testing, which includes $31$ papers.
 \end{itemize}
-
-\noindent These two topics are classical research topics in field of statistics.
-First group talks about Variable Selection in high-dimensional data.
-Majority of papers in second community study about Controlling False Discovery Rate in various statistical settings.
-As expected, third group is quite hard to interpret and seems to have substructures.
-For further investigation on this group, after obtaining the sub-network which is comprised only with the papers in the third group, we performed same analysis once again under the assumption that $K=4$ (See Fig$\ref{fig:figure3}$,right).
-We obtain four sub-communities as follows:
+The first topic is about Variable Selection with high-dimensional data.
+The second topic discusses Controlling False Discovery Rate in various statistical settings.
+The third group, which consists of $158$ papers, is hard to interpret and appears to have sub-network structures.
+For further investigation, we set this group as a giant component in the network, and denote the corresponding network's adjacency matrix as $X^{\mbox{sub}}$.
+As aforementioned, we perform a model selection as described in Step $2$, and obtain five sub-communities as follows:
 
 \begin{itemize}
-  \item Non-parametric Bayesian Statistics, which includes $17$ papers.
-  \item Functional Data analysis, which includes $35$ papers.
-  \item Dimension Reduction, which includes $23$ papers.
-  \item Mixed topics, which includes $329$ papers.
+    \item Non-parametric Bayesian Statistics, which includes $15$ papers.
+    \item Functional / Longitudinal Data analysis, which includes $16$ papers.
+    \item Dimension Reduction, which includes $14$ papers.
+    \item High-dimensional covariance estimation, which includes $15$ papers.
+    \item Mixed topics, which includes $98$ papers.
 \end{itemize}
-
-Out of this one big chunk, we got three small, but meaningful topics: Bayesian Statistics, Functional / Longitudinal Data Analysis, Dimension Reduction.
-Due to small volume of each communities, we could manually check that false discoveries for each community are all zero.
-
-Sub-network structure has also a big chunk of papers which we refer it as Mixed Topics cluster.
+From the sub-network $X^{\mbox{sub}}$, we got four meaningful topics: Bayesian Statistics, Functional/Longitudinal Data Analysis, Dimension Reduction, and high-dimensional covariance estimation.
+Due to the small volume of each community, we could manually check that false discovery for each community is all zero.
+
+Sub-network structure has also a big chunk of papers which we refer it as ``Mixed Topics'' cluster.
 Not only could we see the papers with topics on Learning Theory, Non-parametric / Semi-parametric Statistics, Spatial Statistics, Theoretical Machine Learning, which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
@@
 
-Furthermore, it is worth to note that our result is consistent with that from Ji and Jin \cite{ji2016coauthorship} in a sense that they also recover topics such as Multiple Testing, Variable Selection and Non-parametric Bayesian statistics.
-This is interesting since even though the dataset we consider is different from theirs, the results are consistent.
-They focus their attentions on analyzing \emph{`weakly connected giant component'} for a citation network of each paper's authors ({i.e., each node is an author}).
-We consider the citation network of papers whose node degree is greater than or equal to 7.
-
-Non-zero components of $\widehat{S}$ capture the citation relationships among papers that are not attributable to the common topics.
-The model we select has $197$ sparse edges ($9\%$ of total edges), and all of them are positive edges.
-In Table \ref{tab:table2}, we provide $15$ pairs of papers that have the largest estimated $\widehat{S}_{ij}$.
-All the $15$ edges come from pairs of papers from different communities.
+Non-zero components of $\widehat{S}^{\mbox{orig}}$ capture the citation relationships among papers that are not attributable to the common topics.
+The model we select has $261$ sparse edges ($9\%$ of total edges), and all of them are positive edges.
+In Table \ref{tab:table2}, we provide $15$ pairs of papers that have the largest estimated $\widehat{S}_{ij}^{\mbox{orig}}$.
+All the $15$ edges come from the pairs of papers from different communities.
 For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable Selection $(\emph{VarSel})$ community.
 $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
-Though it might seem to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
+Though it might appear to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
 Second pair comes from Multiple Testing (denoted as $\emph{MulT}$) and Variable Selection ($\emph{VarSel}$) community.
 $\emph{MulT}$ paper briefly mentions about $\emph{VarSel}$ paper in future work section, suggesting a possible way of combining their work and work in $\emph{VarSel}$ paper.
-And we also observe that as the estimated weight of sparse edges (i.e., $\widehat{S}_{ij}$) decreases, the number of pairs of papers that come from Mixed topics community increases.
-
-\begin{figure}[htbp]
-\includegraphics[width=1\textwidth]{Fig5.pdf}
-\caption{Illustration of first two eigenvectors of estimated $\widehat{L}$ matrix for original
-citation network with $543$ papers (left) and sub-network graph (right). We present
-the results of assignment of each paper to each topic via $k$-means algorithm with different colors.}
-\label{fig:figure5}
-\end{figure}
+And we also observe that as the estimated weight of sparse edges (i.e., $\widehat{S}_{ij}^{\mbox{orig}}$) decreases, the number of pairs of papers that come from Mixed topics community increases.
+
+%\begin{figure}[htbp]
+%\includegraphics[width=1\textwidth]{Fig5.pdf}
+%\caption{Illustration of first two eigenvectors of estimated $\widehat{L}$ matrix for original
+%citation network with $543$ papers (left) and sub-network graph (right). We present
+%the results of assignment of each paper to each topic via $k$-means algorithm with different colors.}
+%\label{fig:figure5}
+%\end{figure}
 
@@
 \end{tabular}
-\caption{15 pairs of papers that have the largest $\widehat{S}_{ij}$ among the 197 non-zero component of $\widehat{S}$.
-Note that all the 15 edges come from pairs of papers from different communities. }
+\caption{All the $15$ edges come from pairs of papers from different communities.
+For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.}
 \end{table}
@@
 However, $k$-means algorithm turns out that it tends to assign nodes conservatively to each communities.
-For example, in Fig$\ref{fig:figure4}$(left), we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in Fig$\ref{fig:figure4}$(right) also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
+For example, in Fig.$\ref{fig:figure4}$(left), we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in Fig.$\ref{fig:figure4}$(right) also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
 This is probably because $k$-means does not allow overlapping membership of each nodes.

### 2019-10-01 Codes & Data/Codes/ADMM_Optim.R

@@ -83,7 +83,7 @@ ADMM <- function(X, gamma, delta){
     res <- sqrt(sum((X_M-X_L-X_S)^2))
     print(res)
     # Convergence Check
-    if(res < 5e-4){
+    if(res < 1e-4){
       result <- list(X_a, X_M, X_L, X_S)
       break
     }

### 2019-10-01 Codes & Data/Codes/GD.R

@@ -40,7 +40,7 @@ GD <- function(para_v){
     old_sol = c(X_a, X_M)
     new_sol = old_sol - 0.05*grad
     CC<-max(abs(grad))
-    print(CC)
+    # print(CC)
     # Convergence Criteria
     if(CC < 10^-9){
       X_a <- new_sol[1]

### 2019-10-01 Codes & Data/Codes/Synthetic Data Scenario.R

@@ -9,7 +9,7 @@ source('functions.R')
 source('Synthetic Networks.R')
 #################### data generation N = 30, K = 3, NNZ = 10 ####################
 set.seed(123)
-par(mfrow=c(2,3),mar = c(1, 1.5, 1.5, 1.5)) # ??? ??? ??? ??? # 
+par(mfrow=c(2,3),mar = c(2, 2, 2, 2)) # ??? ??? ??? ??? # 
 ######## First Scenario ########
 set.seed(123); Net1 <- Network1(30,3,9,1)
 set.seed(123); Net2 <- Network1(80,4,18,2)
@@ -20,17 +20,11 @@ set.seed(123); Net5 <- Network2(210,0,50,3,18,5)
 set.seed(123); Net6 <- Network2(210,10,10,3,18,6)
 par(mfrow=c(1,1))
 
-######## Third Scenario ########
-set.seed(123); Net7 <- Network3(120,10,0,3,20,7)
-set.seed(123); Net8 <- Network3(210,0,50,3,18,8)
-set.seed(123); Net9 <- Network3(210,10,10,3,18,9);
-par(mfrow=c(1,1))
-
 ######## Plot Scree ########
-par(mfrow=c(3,3),mar = c(2, 2, 2, 1))
-plotScree(Net1,1); plotScree(Net2,2); plotScree(Net3,3);
-plotScree(Net4,4); plotScree(Net5,5); plotScree(Net6,6);
-plotScree(Net7,7); plotScree(Net8,8); plotScree(Net9,9);
+source('functions.R')
+par(mfrow=c(2,3),mar = c(2, 2, 2, 1))
+plotScree(Net1[[1]],1); plotScree(Net2[[1]],2); plotScree(Net3[[1]],3);
+plotScree(Net4[[1]],4); plotScree(Net5[[1]],5); plotScree(Net6[[1]],6);
 par(mfrow=c(1,1))
 
 ################ Scenario 1 ################
@@ -76,12 +70,12 @@ Eval9 <- Eval(Net9,Res9,gamma,delta)
   
 ############################################
 source('Synthetic Networks.R')
-par(mfrow=c(3,3),mar = c(2, 2, 2, 1))
+par(mfrow=c(2,3),mar = c(2, 2, 2, 2))
 set.seed(1234); K_means(Net1[[1]],0.011,0.024,3,1); 
[…]

### 2019-10-01 Codes & Data/Codes/citation_network_analysis.R

@@ -1,12 +1,8 @@
 ####################  preparation  ####################
 rm(list=ls())
-setwd('C:/Users/namjo/Documents/GitHub/Citation-Network/Codes & Data/Codes')
 library('Matrix')      ## For matrix computation on BIC
 library('igraph')      ## For drawing graph
-source('SynData.R')    ## Function for creating binary network
-source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
-source('functions.R')
-source('GD.R')
+
 ################### Load the Citation Network Data ###################
 setwd('C:/Users/namjo/Documents/GitHub/Citation-Network/Codes & Data/Statistician network data')
 paperCitAdj = as.matrix(read.table("paperCitAdj.txt", header=FALSE))
@@ -16,19 +12,27 @@ Node_deg <- rep(0,nrow(X))
 for (i in 1:sqrt(length(X))){
   Node_deg[i]<-sum(X[i,])
 }
-###### Get a network whose degree is greater than or equal to 7 ######
-ind <- which(Node_deg>=7,arr.ind=TRUE)
+
+################### Load Functions for analysis ###################
+setwd('C:/Users/namjo/Documents/GitHub/Citation-Network/Codes & Data/Codes')
+source('SynData.R')    ## Function for creating binary network
+source('ADMM_Optim.R') ## Function of ADMM algorithm for estimation
+source('functions.R')
+source('GD.R')
+
+###### Get a network whose degree is greater than or equal to 10 ######
+ind <- which(Node_deg>=10,arr.ind=TRUE)
 X_new <- X[ind,ind]
 N <- ncol(X_new)
+A = rowSums(X_new)
+ind = which(A==0,arr.ind=TRUE)
+X = X_new[-ind,-ind]
 
-X_draw <- graph_from_adjacency_matrix(X_new, mode = c("undirected"))
-plot(X_draw)
-plotScree(X_new)
-X = X_new
+plotScree(X)
 
 ################### Model Selection ###################
-gamma = seq(from=0.01,to=0.01,by=0.00000);
-delta = seq(from=0.01,to=0.01,by=0.0001);
+gamma = seq(from=0.0021091,to=0.0021095,by=0.00000006);
[…]

### 2019-10-01 Codes & Data/Codes/functions.R

@@ -166,7 +166,7 @@ plotScree=function(adj,case)
   values = eigen(adj %*% t(adj))$values 
   plot(sqrt(values[1:15]), cex=1, pch=22, type="b", 
        lty=2, lwd=3, col="red", bg="red", xlab="", ylab="")
-  title(sprintf("Case %d",case),family="LM Roman 10")
+  #title(sprintf("Case %d",case),family="LM Roman 10")
 }
 
 

### 2019-10-01 Manuscript for submission/manuscript.tex
Update

@@
 \caption{All the $15$ edges come from pairs of papers from different communities.
-For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.}
+For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
+But they are not related in terms of topic.}
 \end{table}
@@
 
-In proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}.
-Let $(M,M^{\perp})$ denote arbitrary subspace pair for which component-wise $L_{1}$ norm is decomposable.
+In the proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}.
+Let $(M,M^{\perp})$ denote an arbitrary subspace pair for which component-wise $L_{1}$ norm is decomposable.
 Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $M$ as $P_{M}$.
-And also note that proof relies on the following lemma:
+And also note that the proof relies on the following lemma:
 
@@
 \[
-    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq
-    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
+    \mathbb{Q}\left(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\right) \leq
+    \left\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F} +
     3\mathbb{Q}\left(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\right)+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
-    \|S^{*}_{M^\perp}\|_{1}
+    \left\|S^{*}_{M^\perp}\right\|_{1}
 \]
@@
 
-\noindent\textbf{proof of Theorem \ref{Th:th1}}.
+\noindent\textbf{Proof of Theorem \ref{Th:th1}}.
 \begin{proof}

### 2019-10-03 Manuscript for submission/manuscript.tex
Update

@@
 \[
-\nabla^{2}h(\Theta) = \mbox{diag}\Big(\mbox{vec}\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
+\nabla^{2}h(\Theta) = \mbox{diag}\Big(\mbox{vec}\Big(\frac{1}{n}\frac{\exp(\Theta)}{(1+\exp(\Theta))^{2}}
 \Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
@@
     e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})
-    :=\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
+    :=\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F}^{2} + \left\|\widehat{\Delta}^{L}\right\|_{F}^{2} + \left\|\widehat{\Delta}^{S}\right\|_{F}^{2}
 \]
@@
 \begin{align} \label{eq:49}
-\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
+\delta \geq 2 \left\|\frac{1}{n}(X-P^{*}) \right\|_{op} \quad and \quad \gamma \geq 2\left\|\frac{1}{n}(X-P^{*})\right\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
 \end{align}
 then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
-\begin{align}
+\begin{align} \label{theorem1}
     e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
@@
 
-We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
-Our work considers a logistic loss function whose parameters are characterized by a sparse matrix plus a low rank matrix, whereas Agarwal, et al.\cite{agarwal2012noisy} work on a quadratic loss of a noisy realization of a linear transformation of sum of a low rank matrix and a sparse matrix.
-We show that similar proof techniques can be applied in our case, giving us similar results.
+We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension of Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
+Specifically, our work considers a logistic loss function whose parameter is characterized by a sparse matrix plus a low rank matrix,
+whereas Agarwal, et al.\cite{agarwal2012noisy} work on a general linear observation model whose parameter is also 
+characterized by sum of a low rank matrix and a sparse matrix.
+
+%In this Section, we show that similar proof techniques can be applied in our case, giving us similar results.
 %Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.
 
-Result of the Theorem \ref{Th:th1} provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $M$, and rank parameter $k$, helping us to understand the behavior of our proposed estimator both in practice and in ideal cases.
+Astute readers might have noticed that the upper bound in \ref{theorem1} consists of three different terms, where we denote them as
+$\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$. 
+Each respective term is involved with estimating three model parameters, $\alpha, L$ and $S$.
+To be more specific, both $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ have two types of error:
+1) The first one is called as an ``estimation error''. 
+This error represents the statistical cost of estimating parameters which belong to the model subspace. 
+2) Another quantity is referred as ``approximation error''. 
+This error occurs when we only focus on estimating parameters within the model subspace, 
+and it shrinks as the model subspace becomes large.
+%=\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F}^{2} + \left\|\widehat{\Delta}^{L}\right\|_{F}^{2} + \left\|\widehat{\Delta}^{S}\right\|_{F}^{2}
+
+The result of the Theorem \ref{Th:th1} provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $M$, and rank parameter $k$.
+In other words, this means that the subset $M$ and the target rank $k$ can be adaptively chosen so as to obtain the tightest upper bound.
+In ideal case where $L^*$ is an exact low rank matrix with rank $k$ \big(i.e., $\mbox{rank}(L^*)=k$\big) and $S^*$ is a sparse matrix, whose support lies within the model subspace $M$ \big(i.e., $\mbox{supp}(S^*) \subset M$\big), we can easily see ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ \big(i.e., $\delta\sum_{j=k+1}^{n}\sigma_j(L^*)$ \big) and in $\mathcal{K}_{S^*}$ \big(i.e., $\gamma\sum_{(i,j)\notin M}|S_{ij}^*|$\big) disappear, giving us Frobenius error bound as follows:
+\[
+    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s.
+\]
+Here we use the notation $X \lesssim Y$ to denote that there exists universal absolute constant $C$ such that $X \leq CY$.
+
+%This helps us to understand the behavior of our proposed estimator both in practice and in ideal cases.
 In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.
-In this case, our theorem provides the intuition on the rate on how fast the error bound $\mathcal{K}_{L^*}$ will grow.
-In ideal cases where $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $M$ (i.e., $|supp(S^*)|=s$), we can easily verify ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ (i.e., $\tau\sum_{j=k+1}^{n}\sigma_j(L^*)$) and in $\mathcal{K}_{S^*}$ (i.e., $\tau\sum_{(i,j)\notin M}|S_{ij}^*|$) disappear, giving us Frobenius error bound as follows:
-\[
-    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s
-\]
-where $\lesssim$ denotes that we ignore constant factors.
 
@@
 where $\|\cdot\|_F$ is the matrix Frobenius norm, defined as
-$\|M\|^2_F = \sum_{i,j} m^2_{ij}$ for a matrix $M = (m_{ij})$.
+$\|M\|^2_F = \sum_{i,j} m^2_{ij}$ for a matrix $M = \{(m_{ij})\}_{i,j=1}^{n}$.
 The problem in \eqref{eq:admm02} may not have a closed-form solution.
-We use a simple gradient descent to solve in this step, setting the step size equal to $0.05$ and stopping criteria as $\max(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}) \leq 10^{-9}$.
+We use a simple gradient descent to solve in this step, setting the step size equal to $0.05$ and stopping criteria as $\max\big(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}\big) \leq 10^{-9}$.
 Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem.
@@
 $$
-x^{m+1}_L = J (T \mbox{diag}(\Lambda-\lambda \delta)_+ T^T)J^{T},
+x^{m+1}_L = J \big(T \mbox{diag}(\Lambda-\lambda \delta\big)_+ T^T)J^{T},
 $$
@@
         (i.e., if $i$th paper studies about $k$th topic, we denote $F^*_{ki}=1$, otherwise $F^*_{ki}=0$).
-        First, we assume that there are $n$ papers in the network, and $K$ topics are embedded in the network. Each of them consists of $\frac{n}{K}$ papers.
+        First, we assume that there are $n$ papers in the network, and $K$ topics are embedded in it. 
+        Each of them consists of $\frac{n}{K}$ papers.
         This can be expressed in $F^*$ as follows:
@@
         3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
-        4) Lastly, make it symmetric by setting $S^*_{jj}=S^*_{ij},\forall 1\leq i < j \leq n$.
+        4) Lastly, make it symmetric by setting $S^*_{ji}=S^*_{ij},\forall 1\leq i < j \leq n$.
     \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
@@
 \caption{Graphical illustrations of six synthetic networks.
-Nodes that share the common factors are clustered. The cross cluster links are ad-hoc Citations.}
+Nodes that share the common factors are clustered. The cross cluster links are ad-hoc Citations.
+All the graphs are drawn via R package `igraph'.}
 \label{fig:figure1}
@@
     $M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
-    $M_{4}$   &  0  &   $\frac{20}{30}$    &  $\frac{20}{30}$    &   0          &   $\frac{25}{40}$    &   $\frac{25}{30}$   &  0      &  $\frac{30}{30}$     &   $\frac{30}{30}$   \\
+    $M_{4}$   &  0  &   $\frac{10}{30}$    &  $\frac{10}{30}$    &   0          &   $\frac{20}{80}$    &   $\frac{20}{80}$   &  0      &  $\frac{24}{120}$     &   $\frac{24}{120}$   \\
                 \hline
@@
     $M_{3}$   &   0 &     0  &   0   &        0     &    0   &  0    &        0     &   0    & 0 \\
-    $M_{4}$   &  0  &   $\frac{20}{120}$    &  $\frac{20}{120}$    &   0          &   $\frac{25}{210}$    &   $\frac{25}{210}$   &  0      &  $\frac{30}{210}$     &   $\frac{30}{210}$   \\
+    $M_{4}$   &  0  &   0    &  0    &   0          &   0    &   0   &  0      &  0     &   0   \\
                 \hline
@@
 
-In the first step, a pair of parameters, $(\gamma^{\text{Heu}},\delta^{\text{Heu}}) = (0.0021094, 0.01913)$, gives us $\widehat{L}^{\mbox{orig}}$ with rank $3$, and $\widehat{S}^{\mbox{orig}}$ with $|\widehat{S}^{\mbox{orig}}|=261$.
-We list the first two topics discovered through our analysis. Full list of papers for each community is provided in $https://sites.google.com/site/namjoonsuh/publications$.
+In the first step, a pair of parameters, $(\gamma^{\text{Heu}},\delta^{\text{Heu}}) = (0.0021094, 0.01913)$, gives us $\widehat{L}$ with rank $3$, and $\widehat{S}$ with $|\widehat{S}|=51$.
+We list the first two topics discovered through our analysis.
 \begin{itemize}
@@
 \end{itemize}
-The first topic is about Variable Selection with high-dimensional data.
+The first topic studies on Variable Selection with high-dimensional data.
 The second topic discusses Controlling False Discovery Rate in various statistical settings.
 The third group, which consists of $158$ papers, is hard to interpret and appears to have sub-network structures.
-For further investigation, we set this group as a giant component in the network, and denote the corresponding network's adjacency matrix as $X^{\mbox{sub}}$.
-As aforementioned, we perform a model selection as described in Step $2$, and obtain five sub-communities as follows:
-
+For further investigation, we set this group as a giant component in the network, and denote the corresponding component's adjacency matrix as $X^{\mbox{sub}}$.
+We perform a model selection as described in aforementioned Step $2$.
+A pair of tuning parameters, $(\gamma^{\text{Heu}},\delta^{\text{Heu}}) = (0.00312, 0.0146)$, gives us the model with $\widehat{L}$ with rank $5$, and $\widehat{S}$ with $|\widehat{S}|=88$,
+and we can obtain five sub-communities as follows:
 \begin{itemize}
@@
 From the sub-network $X^{\mbox{sub}}$, we got four meaningful topics: Bayesian Statistics, Functional/Longitudinal Data Analysis, Dimension Reduction, and high-dimensional covariance estimation.
-Due to the small volume of each community, we could manually check that false discovery for each community is all zero.
-
-Sub-network structure has also a big chunk of papers which we refer it as ``Mixed Topics'' cluster.
+Due to the small volume of each community, we could manually check that the false discovery for each community is all zero.
+(Full list of papers for each community is provided in $https://sites.google.com/site/namjoonsuh/publications$.)
+
+Sub-network structure has also a big collection of papers which we refer it as ``Mixed Topics'' cluster.
 Not only could we see the papers with topics on Learning Theory, Non-parametric / Semi-parametric Statistics, Spatial Statistics, Theoretical Machine Learning, which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
@@
 It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed topic classified as Mixed topic.
-For instance, ``On the "degrees of freedom" on the LASSO (H. Zou, et al. $2007$)'' is classified as Mixed Topic paper.
+For instance, the paper, On the "degrees of freedom" on the LASSO (H. Zou, et al. $2007$), is classified as Mixed Topic paper.
 We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities.
-Actually, out of $19$ citation relationships it has with other papers, $12$ of them came from the relationships with papers from Mixed topics.
-
-Non-zero components of $\widehat{S}^{\mbox{orig}}$ capture the citation relationships among papers that are not attributable to the common topics.
-The model we select has $261$ sparse edges ($9\%$ of total edges), and all of them are positive edges.
-In Table \ref{tab:table2}, we provide $15$ pairs of papers that have the largest estimated $\widehat{S}_{ij}^{\mbox{orig}}$.
-All the $15$ edges come from the pairs of papers from different communities.
+Actually, out of $11$ citation relationships it has with other papers, $6$ of them came from the relationships with papers from Mixed topics.
+
+Non-zero components of $\widehat{S}$ capture the citation relationships among papers that are not attributable to the common topics.
+The selected model has $51$ sparse edges, and all of them are positive edges.
+In Table \ref{tab:table2}, we provide $10$ pairs of papers that have the largest estimated $\widehat{S}_{ij}$.
+All the $10$ edges come from the pairs of papers from different communities.
 For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable Selection $(\emph{VarSel})$ community.
@@
 Though it might appear to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
-Second pair comes from Multiple Testing (denoted as $\emph{MulT}$) and Variable Selection ($\emph{VarSel}$) community.
-$\emph{MulT}$ paper briefly mentions about $\emph{VarSel}$ paper in future work section, suggesting a possible way of combining their work and work in $\emph{VarSel}$ paper.
-And we also observe that as the estimated weight of sparse edges (i.e., $\widehat{S}_{ij}^{\mbox{orig}}$) decreases, the number of pairs of papers that come from Mixed topics community increases.
+The second pair of papers comes from the Mixed topics community (denoted as $\emph{Mixed}$) and the Variable Selection ($\emph{VarSel}$) community.
+This case is interesting since both papers study about variable selection problem, but they are classified in different communities and connected via an ad-hoc link.
+Specifically, the paper from $Mixed$ community study the variable selection problem under the non-parametric Bayesian framework, and compare their method with the one that is proposed in $\emph{VarSel}$ paper, ``Adaptive Lasso’’.
+
+%Second pair comes from the Mixed topics community (denoted as $\emph{Mixed}$) and the Variable Selection ($\emph{VarSel}$) community.
+%$\emph{MulT}$ paper briefly mentions about $\emph{VarSel}$ paper in future work section, suggesting a possible way of combining their work and work in $\emph{VarSel}$ paper.
+%And we also observe that as the estimated weight of sparse edges (i.e., $\widehat{S}_{ij}^{\mbox{orig}}$) decreases, the number of pairs of papers that come from Mixed topics community increases.
 
@@
 \centering
-\begin{tabular}{lclclcl}\hline
+\begin{tabular}{clclc}\hline
 Pair & Community & Title & \\
@@
      & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                         & \\
-2    & MulT      & Innovated higher criticism for detecting sparse signals in correlated noise                   & \\
-     & VarSel    & Regularized estimation of large covariance matrices & \\
+2    & VarSel      & The adaptive lasso and its oracle properties                                                  & \\
+     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection                & \\
 3    & DimRed    & Contour projected dimension reduction                                                        & \\
@@
      & DimRed    & Sliced regression for dimension reduction & \\
-5    & VarSel    & Covariance regularization by thresholding & \\
-     & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
-6    & VarSel    & Asymptotic properties of bridge estimators in sparse high-dimensional regression models       & \\
-     & Mixed     & Marginal asymptotics for the ``large p small n'' paradigm: with applications to microarray data &  \\
-7    & VarSel    & A majorization-minimization approach to Variable Selection using spike and slab priors        & \\
-     & Mixed     & Empirical Bayes selection of wavelet thresholds & \\
-8    & VarSel    & Spades and mixture models & \\
-     & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
-9    & DimRed    & A constructive approach to the estimation of dimension reduction directions                   & \\
+5    & CovEst    & Two sample tests for high-dimensional covariance matrices & \\
+     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression          & \\
+6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise       & \\
+     & CovEst     & Regularized estimation of large covariance matrices     &  \\
+7    & DimRed    & A constructive approach to the estimation of dimension reduction directions        & \\
      & VarSel     & Factor profiled sure independence screening    & \\
-10   & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors        & \\
-     & Mixed     & Spike and slab variable selection: Frequentist and Bayesian strategies                        & \\
-11   & VarSel    & variable selection in nonparametric additive models & \\
-     & Mixed     & Nonparametric estimation of an additive model with a link function                            & \\
-12   & Mixed     & Nonparametric inferences for additive models & \\
+8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors  & \\
+     & Mixed      & Empirical {B}ayes selection of wavelet thresholds                          & \\
+9    & Mixed    & Nonparametric inferences for additive models                   & \\
      & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models      & \\
-13   & Mixed     & Bayesian variable selection in structured high-dimensional covariate spaces with applications in genomics & \\
-     & VarSel    & Model selection and estimation in regression with grouped variables                           & \\
-14   & VarSel    & The sparsity and bias of the LASSO selection in high-dimensional linear regression            & \\
-     & Mixed     & Tests for high-dimensional covariance matrices & \\
-15   & FuncAn    & Empirical dynamics for longitudinal data & \\
-     & Mixed     & Variable selection in nonparametric varying-coefficient models for analysis of repeated measurements   &       \\\hline
+10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality        & \\
+     & Mixed     & Maximum likelihood estimation in semiparametric regression models with censored data                   & \\
+\hline
 \end{tabular}
-\caption{All the $15$ edges come from pairs of papers from different communities.
+\caption{All the $10$ edges come from pairs of papers from different communities.
 For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
@@
 \section{Appendix}
-\subsection{Proof of Theorem \ref{Th:th1}}
-
-In the proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}.
-Let $(M,M^{\perp})$ denote an arbitrary subspace pair for which component-wise $L_{1}$ norm is decomposable.
+In this Section, first we briefly introduce several notations, a notion on the decomposability of regularizer, and a useful lemma proved in the work \cite{agarwal2012noisy}.
+Then, we present Lemma\ref{le:le2} and its proof.
+Finally, we present the proof of our Theorem\ref{Th:th1}.
+
+\subsection{Preliminary}
 Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $M$ as $P_{M}$.
-And also note that the proof relies on the following lemma:
-
-\begin{lemma} \label{le:le1}
+We use $\langle A,B \rangle$ to denote the trace inner product of two matrices $A$ and $B$ \big(i.e.,$\langle A,B \rangle=\mbox{tr}\big(A^T B\big)$\big).
+We use $\|A\|_{\infty}$ to denote the maximum absolute entry of matrix $A$, and use $\|B\|_{op}$ to denote the largest singular value of matrix $B$.
+And we will use the notion of decomposability of $L_1$ norm with respect to a pair of subspace $(M,M^{\perp})$.
+Given an arbitrary subset $S \subseteq \{1,2,\dots,n\} \times \{1,2,\dots,n\}$ of matrix indices, $M$ is defined as follows:
+\[
+    M(S):=\{ U \in \mathbb{R}^{n \times n} | U_{ij}=0, \forall (i,j) \in S \}
+\]
+and $M^{\perp}(S):=(M(S))^{\perp}$.
+With this in mind, we recall the formal definition of the decomposability of $L_1$ norm as follows:
+\begin{definition}
+    Given a subspace $M \subset \mathbb{R}^{n \times n}$ and its orthogonal complement $M^{\perp}$, an elementwise $L_1$ norm
+    is decomposable with respect to $(M, M^{\perp})$ if
+    \[
+        \| A + B \|_{1} = \|A\|_{1} + \|B\|_{1},
+        \forall A \in M \mbox{and} B \in M^{\perp},
+    \]
+\end{definition}
+The notion of decomposability is used to penalize the perturbation from the model subspace $M$, and to obtain the tightest bound the $L_1$ norm can achieve.
+We will also use two results in our proof, which are presented and proved in the work \cite{agarwal2012noisy}.
+For the convenience of readers, we present them here as follows:
+%We will choose the model subspace $M$, which will be chosen such that the matrix $S^*$ lies within or close to $M$.
+\begin{lemma}
+(\textbf{Agarwal, et al} \cite{agarwal2012noisy})
+For any $k=1,2,\dots,n$, there is a decomposition $\widehat{\Delta}^{L} =\widehat{\Delta}^{L}_{A} + \widehat{\Delta}^{L}_{B}$ such that:
+\begin{enumerate}
+ \item The decomposition satisfies
+    \begin{equation}\label{eq:Lm1}
+        \mbox{rank}(\widehat{\Delta}^{L}_{A}) \leq 2k, \quad and \quad (\widehat{\Delta}^{L}_{A})^{T}\widehat{\Delta}^{L}_{B}
+        = (\widehat{\Delta}^{L}_{B})^{T}\widehat{\Delta}^{L}_{A} =0
+    \end{equation}
+ \item The difference $\mathbb{Q}(L^{*},S^{*}) -  \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ is upper-bounded by
+    \begin{equation} \label{eq:28}
+        \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
+        +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
+    \end{equation}
+\end{enumerate}
+\end{lemma}
+where the notation $\mathbb{Q}(L,S)$ is defined as the weighted combination of the two regularizers for any pair of positive tuning parameters $(\gamma,\delta)$:
+\[
+\mathbb{Q}\left(L,S\right)   := \left\|L\right\|_{*} + \frac{\gamma}{\delta}\left\|S\right\|_1.
+\]
+
+\subsection{Lemma \ref{le:le2}}
+\begin{lemma} \label{le:le2}
 If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}\left(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\right)$, we have
@@
 
-\noindent\textbf{Proof of Theorem \ref{Th:th1}}.
+\begin{proof}
+Through the application of basic inequality by using optimality of $\widehat{\Theta}$ and feasibility of $\Theta^{*}$ to convex program (\ref{eq:Modified}), we have
+\begin{equation}
+    h(\widehat{\Theta}) - h(\Theta^{*})
+    \leq \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
+\end{equation}
+By using convexity of $h(\Theta)$, we can write
+\begin{align}
+    h(\widehat{\Theta})-h(\Theta^{*}) &\geq
+    \langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ \nonumber \\
+    &= - \langle\,\frac{1}{n} (X-P^{*}), \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \rangle\ \nonumber \\
+    &\geq -\frac{1}{n} \|X - P^*\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \nonumber \\
+    &\geq -\frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) - \frac{\gamma}{2} (\|\widehat{\Delta}^{S}_{M}\|_{1} +
+    \|\widehat{\Delta}^{S}_{M^\perp}\|_{1}) \label{eq:27}
+\end{align}
+
+An application of Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1,
+we can get an upper bound of difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ as follows:
+
+\begin{equation} \label{eq:28}
+    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
+    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
+\end{equation}
+
+By combining relations (\ref{eq:27}) and (\ref{eq:28}), we can get the upper bound of $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$ :
+\begin{align*}
+    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq
+    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
+    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
+    \|S^{*}_{M^\perp}\|_{1}
+\end{align*}
+\end{proof}
+
+\subsection{Proof of Theorem \ref{Th:th1}}
 \begin{proof}
@@
 \begin{equation}\label{eq:2}
-    h(\widehat{\Theta}) + \delta\|\widehat{L}\|_{*} + \gamma\|\widehat{S}\|_{1} \leq
-     h(\Theta^{*}) + \delta\|{L^{*}}\|_{*} + \gamma\|{S}^{*}\|_{1}
+    h(\widehat{\Theta}) + \delta\left\|\widehat{L}\right\|_{*} + \gamma\left\|\widehat{S}\right\|_{1} \leq
+     h(\Theta^{*}) + \delta\left\|{L^{*}}\right\|_{*} + \gamma\left\|{S}^{*}\right\|_{1}
 \end{equation}
@@
 h(\widehat{\Theta})-h(\Theta^{*}) \geq
-\langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ + \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}
+\langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ + \frac{\tau}{2}\left\|\widehat{\Delta}^{\Theta}\right\|_{F}^{2}
 \]
@@
 
-Here, we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers :
-\[
-\mathbb{Q}(L,S)   := \|L\|_{*} + \frac{\gamma}{\delta}\|S\|_1
-\]
+%Here, we introduce another notation, for any pair of positive tuning parameters $(\delta,\gamma)$ which is defined as the weighted combination of the two regularizers :
+%\[
+%\mathbb{Q}\left(L,S\right)   := \left\|L\right\|_{*} + \frac{\gamma}{\delta}\left\|S\right\|_1
+%\]
 Through the definition of $\mathbb{Q}$, we can rewrite (\ref{eq:3}) as follows:
@@
     -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
-    + \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
+    + \delta \mathbb{Q}\left(L^{*},S^{*}\right) - \delta \mathbb{Q}\left(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\right)
 \end{equation}
@@
 \begin{equation}\label{eq:5}
-    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
-    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
+    \mathbb{Q}\left(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\right) - \mathbb{Q}\left(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\right)
+    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\left\|S^*_{M^\perp}\right\|_{1}
 \end{equation}
@@
 &=\langle\, \frac{1}{n} (X - P^*), \widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S} \rangle\ \\ \nonumber
-&\leq \frac{1}{n} \|X - P^*\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
-&\leq \frac{1}{n} \|X - P^*\|_{op}(\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) +
-\frac{1}{n} \|X - P^*\|_{\infty}(\|\widehat{\Delta}^{S}_{M}\|_{1} +
-\|\widehat{\Delta}^{S}_{M^{\perp}}\|_{1}) \\
-&\leq \frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) + \frac{\gamma}{2}(\|\widehat{\Delta}^{S}_{M}\|_{1} +
-\|\widehat{\Delta}^{S}_{M^{\perp}}\|_{1})  \label{eq:10}
+&\leq \frac{1}{n} \left\|X - P^*\right\|_{op}(\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_\ast + \left\|\widehat{\Delta}^{L}\right\|_\ast) +  \frac{1}{n} \left\|X - P^*\right\|_{\infty}\left\|\widehat{\Delta}^{S}\right\|_{1} \\ \nonumber
+&\leq \frac{1}{n} \left\|X - P^*\right\|_{op}(\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F} + \left\|\widehat{\Delta}^{L}_{A}\right\|_\ast + \left\|\widehat{\Delta}^{L}_{B}\right\|_\ast) +
+\frac{1}{n} \left\|X - P^*\right\|_{\infty}(\left\|\widehat{\Delta}^{S}_{M}\right\|_{1} +
+\left\|\widehat{\Delta}^{S}_{M^{\perp}}\right\|_{1}) \\
+&\leq \frac{\delta}{2}(\left\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F} + \left\|\widehat{\Delta}^{L}_{A}\right\|_\ast + \left\|\widehat{\Delta}^{L}_{B}\right\|_\ast) + \frac{\gamma}{2}(\left\|\widehat{\Delta}^{S}_{M}\right\|_{1} +
+\left\|\widehat{\Delta}^{S}_{M^{\perp}}\right\|_{1})  \label{eq:10}
 \end{align}
@@
 $ \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $.
-To control the first trace inner product term, we use the relation $\widehat{\Delta}^{L}\mathbbm{1}=0$, apply the definition of dual norm on inner product term, apply triangular inequality on $\hat{\Delta}^\alpha$, and lastly we apply the constraint imposed on $|\alpha|$ stated in Assumption \ref{Ass:2}.
+To control the first trace inner product term, we use the relation $\widehat{\Delta}^{L}\mathbbm{1}=0$, apply the definition of dual norm on inner product term, apply triangular inequality on $\widehat{\Delta}^\alpha$, and lastly we apply the constraint imposed on $|\alpha|$ stated in Assumption \ref{Ass:2}.
 
@@
     &= | \langle\,\widehat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\ \nonumber
-    &\leq \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\widehat{\Delta}^{S}\|_1 \\ \nonumber
-    &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\widehat{\Delta}^{S}\|_1\\
+    &\leq \|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\widehat{\Delta}^{S}\|_1 \\ \nonumber
+    &\leq (|\widehat{\alpha}|+|\alpha^{*}|)\|\widehat{\Delta}^{S}\|_1\\
     &\leq 2C\kappa\|\widehat{\Delta}^{S}\|_1  \label{eq:13}
@@
     &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2}
-    - 2\kappa\tau(\frac{Cn+1}{n})\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
+    - \kappa\tau\bigg(\frac{Cn+1}{n}\bigg)\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
     &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\widehat{\Delta}^{S}\|_{1}\\
@@
 
-\subsection{Proof of Lemma \ref{le:le1}}
-
-\begin{proof}
-Through the application of basic inequality by using optimality of $\widehat{\Theta}$ and feasibility of $\Theta^{*}$ to convex program (\ref{eq:1}), we have
-\begin{equation}
-    h(\widehat{\Theta}) - h(\Theta^{*})
-    \leq \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
-\end{equation}
-By using convexity of $h(\Theta)$, we can write
-\begin{align}
-    h(\widehat{\Theta})-h(\Theta^{*}) &\geq
-    \langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ \nonumber \\
-    &= - \langle\,\frac{1}{n} (X-P^{*}), \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \rangle\ \nonumber \\
-    &\geq -\frac{1}{n} \|X - P^*\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \nonumber \\
-    &\geq -\frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) - \frac{\delta}{2} (\|\widehat{\Delta}^{S}_{M}\|_{1} +
-    \|\widehat{\Delta}^{S}_{M^\perp}\|_{1}) \label{eq:27}
-\end{align}
-
-One more round of application on Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1,
-we can get an upper bound of difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ as follows:
-
-\begin{equation} \label{eq:28}
-    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
-    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
-\end{equation}
-
-By combining relations (\ref{eq:27}) and (\ref{eq:28}), we can get the upper bound of $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$ :
-\begin{align*}
-    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq
-    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
-    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
-    \|S^{*}_{M^\perp}\|_{1}
-\end{align*}
-
-\end{proof}
-
 %\nocite{*}

### 2019-10-03 Codes & Data/Codes/Synthetic Data Scenario.R

@@ -53,21 +53,6 @@ gamma = seq(from=0.002,to=0.004,by=0.0002);
 delta = seq(from=0.015,to=0.02,by=0.0005);
 Res6 <- Model_Sel(Net6[[1]],gamma,delta) ## gamma : 0.002, delta : 0.016
 
-################ Scenario 3 ################
-gamma = seq(from=0.002,to=0.004,by=0.0002);
-delta = seq(from=0.015,to=0.02,by=0.0005);
-Res7 <- Model_Sel(Net7[[1]],gamma,delta) ## gamma : 0.0032, delta : 0.019 
-Eval7 <- Eval(Net7,Res7,gamma,delta)
-
-gamma = seq(from=0.0019,to=0.002,by=0.00001);
-delta = seq(from=0.03,to=0.035,by=0.0005);
-Res8 <- Model_Sel(Net8[[1]],gamma,delta) ## gamma : 0.00212, delta : 0.048
-
-gamma = seq(from=0.001,to=0.002,by=0.0001);
-delta = seq(from=0.022,to=0.024,by=0.0002);
-Res9 <- Model_Sel(Net9[[1]],gamma,delta) ## gamma : 0.002, delta : 0.016
-Eval9 <- Eval(Net9,Res9,gamma,delta)
-  
 ############################################
 source('Synthetic Networks.R')
 par(mfrow=c(2,3),mar = c(2, 2, 2, 2))
@@ -78,37 +63,19 @@ set.seed(1234); K_means(Net3[[1]],0.003,0.00476,5,3);
 set.seed(1234); K_means(Net4[[1]],0.0032,0.019,4,4); 
 set.seed(1234); K_means(Net5[[1]],0.00212,0.048,5,5); 
 set.seed(1234); K_means(Net6[[1]],0.002,0.016,5,6);
-
-set.seed(1234); K_means(Net7[[1]],0.0032,0.019,4,7); 
-set.seed(1234); K_means(Net8[[1]],0.00192,0.0315,6,8); 
-set.seed(12345); K_means(Net9[[1]],0.0019,0.024,6,9);
 par(mfrow=c(1,1))
 
 object_list <- list(Res1,Res2,Res3,Res4,Res5,Res6,Res7,Res8,Res9)
 save(object_list,file="myfile.RData")
 
-(sum(Net1)/2)*0.03
-(sum(Net2)/2)*0.01
-(sum(Net3)/2)*0.01
 
[…]

### 2019-10-03 Codes & Data/Codes/citation_network_analysis.R

@@ -28,7 +28,12 @@ A = rowSums(X_new)
 ind = which(A==0,arr.ind=TRUE)
 X = X_new[-ind,-ind]
 
+par(mfrow=c(1,2),mar = c(2, 2, 1.5, 1.5)) # ??? ??? ??? ??? # 
 plotScree(X)
+title(TeX("$\\X^{orig}$"),cex.main=0.85)
+
+plotScree(X_chunk)
+title(TeX("$\\X^{sub}$"),cex.main=0.85)
 
 ################### Model Selection ###################
 gamma = seq(from=0.0021091,to=0.0021095,by=0.00000006);
@@ -75,7 +80,8 @@ for(g in 1:length(gamma)){
   }
 }
 #################### Choose the proper tuning parameters #######################
-result1 <- ADMM(X, gamma[6], delta[1])  ## Gamma : 0.002109, Delta : 0.0194
+N = ncol(X)
+result1 <- ADMM(X, 0.002109, 0.0194)  ## Gamma : 0.002109, Delta : 0.0194
 a1 <- result1[[1]]
 M1 <- result1[[2]]
 L1 <- result1[[3]]
@@ -97,7 +103,7 @@ non_zero_S;
 set.seed(1233)
 K = qr(L1)$rank;
 setwd('C:/Users/namjo/Documents/GitHub/Citation-Network/Codes & Data/Statistician network data')
-KMeans = kmeans(eigen(L)$vectors[,1:K], K, iter.max = 1000, nstart = 100, algorithm = "Hartigan-Wong")
+KMeans = kmeans(eigen(L1)$vectors[,1:K], K, iter.max = 1000, nstart = 100, algorithm = "Hartigan-Wong")
 Topic1 = which(KMeans$cluster == 1,arr.ind = TRUE)
 Topic2 = which(KMeans$cluster == 2,arr.ind = TRUE)
 Topic3 = which(KMeans$cluster == 3,arr.ind = TRUE)
@@ -144,7 +150,7 @@ plot(X_draw_Topic4, main = "Papers on variable selection")
 par(mfrow=c(1,2),mar = c(4, 4, 2, 1))
 
 DF <- data.frame(FE = eigen(L1)$vector[,1], SE = eigen(L1)$vector[,2], Cluster = rep(0,N))
-DF[Topic1,3]=1; DF[Topic2,3]=2; DF[Topic3,3]=3; DF[Topic4,4]=4;
[…]

### 2019-10-03 Codes & Data/Codes/functions.R

@@ -166,7 +166,7 @@ plotScree=function(adj,case)
   values = eigen(adj %*% t(adj))$values 
   plot(sqrt(values[1:15]), cex=1, pch=22, type="b", 
        lty=2, lwd=3, col="red", bg="red", xlab="", ylab="")
-  #title(sprintf("Case %d",case),family="LM Roman 10")
+  # title(sprintf("Case %d",case),family="LM Roman 10")
 }
 
 

### 2019-10-07 Manuscript for submission/manuscript.tex
Update

@@
 \widehat{\Delta}^S = \widehat{S}-S^{*}.$
-Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
+Throughout the discussion, let $P^{*}=\bigg\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\bigg\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
 We then impose several assumptions for theoretical guarantees of our estimator.
@@
 
-\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
+\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L}) \label{Ass:2}
 To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
+\end{assumption}
+
+\begin{assumption} (\textbf{Spikiness of L and Constraint on $\alpha$}) \label{Ass:3}
 We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
@@
 \[
-    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})
-    :=\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F}^{2} + \left\|\widehat{\Delta}^{L}\right\|_{F}^{2} + \left\|\widehat{\Delta}^{S}\right\|_{F}^{2}
+    e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)
+    :=\big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \big\|\widehat{\Delta}^{S}\big\|_{F}^{2}
 \]
@@
 \begin{theorem} \label{Th:th1}
-Under the assumptions \ref{Ass:1} and \ref{Ass:2},
+Under the assumptions \ref{Ass:1}, \ref{Ass:2} and \ref{Ass:3},
 if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
@@
 \end{align}
-then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
+then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)$
 \begin{align} \label{theorem1}
-    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
+    e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big) \leq
     \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
@@
 \end{align}
-where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
+where $M$ is an arbitrary subset of matrix indices of cardinality at most $s$.
 \end{theorem}
@@
 Specifically, our work considers a logistic loss function whose parameter is characterized by a sparse matrix plus a low rank matrix,
-whereas Agarwal, et al.\cite{agarwal2012noisy} work on a general linear observation model whose parameter is also 
+whereas Agarwal, et al. \cite{agarwal2012noisy} work on a general linear observation model whose parameter is also
 characterized by sum of a low rank matrix and a sparse matrix.
@@
 
-Astute readers might have noticed that the upper bound in \ref{theorem1} consists of three different terms, where we denote them as
+Astute readers might have noticed that the upper bound in \eqref{theorem1} consists of three different terms, where we denote them as
 $\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$.
@@
 To be more specific, both $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ have two types of error:
-1) The first one is called as an ``estimation error''. 
-This error represents the statistical cost of estimating parameters which belong to the model subspace. 
-2) Another quantity is referred as ``approximation error''. 
+1) The first one is called as an ``estimation error.''
+This error represents the statistical cost of estimating parameters that belong to the model subspace.
+2) Another quantity is referred as ``approximation error.''
 This error occurs when we only focus on estimating parameters within the model subspace,
@@
 \label{sec:Syn-dat}
-First, we introduce two synthetic scenarios that we want to explore.
-Then, we describe three model selection criteria and four evaluation metrics for the selected model.
-Subsequently, we elaborate experimental results from the synthetic networks and several interesting findings from those results.
-
-\subsubsection{Synthetic Setting}
+First, we introduce two synthetic scenarios that we want to explore (Section \ref{sec:Syn-set}).
+Then, we describe three model selection criteria and four evaluation metrics for the selected model
+(Section \ref{sec:Eval-crit}).
+Subsequently, we elaborate experimental results from the synthetic networks and several interesting findings from those results (Section \ref{sec:obs}).
+
+\subsubsection{Synthetic Setting} \label{sec:Syn-set}
 %In this subsection, we consider the following $3$ scenarios:
@@
            &C^*_{2} \subseteq \big\{\frac{n}{K}+1, \dots, \frac{2n}{K} \big\} \setminus \big\{ \Omega_{n_l} \cup \Omega_{n_m} \big\}  \\
-           &\vdots \\
+           & \quad \vdots \\
            &C^*_{K} \subseteq \big\{\frac{(K-1)n}{K}+1, \dots, n \big\} \setminus \big\{ \Omega_{n_l}
@@
 
-\subsubsection{Choosing the tuning parameters and evaluation criteria}
+\subsubsection{Choosing the tuning parameters and evaluation criteria} \label{sec:Eval-crit}
 Choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
@@
 
-\subsubsection{Several Observations}
+\subsubsection{Several Observations} \label{sec:obs}
 %Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
@@
     In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics, and this strategy leads us to good model selection results for all the six cases considered in two scenarios.
-(See Fig.\ref{fig:figure2})
+(See Fig.$\ref{fig:figure2}$)
 
@@
     $M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
-    $M_{4}$   &  0  &   $\frac{10}{30}$    &  $\frac{10}{30}$    &   0          &   $\frac{20}{80}$    &   $\frac{20}{80}$   &  0      &  $\frac{24}{120}$     &   $\frac{24}{120}$   \\
+    $M_{4}$   &  0  &    10/30    &  10/30     &   0   &   20/80    &   20/80   &  0      &  24/120     &   24/120    \\
                 \hline
@@
     $M_{1}$   &   1 (3)     &     1 (3)  &  1 (3)    &      1 (3)   &   1 (3)    &  1 (3)    &   1 (3)     &  1 (3)   & 1 (3)   \\
-    $M_{2}$   &   $\frac{17}{18}$   &   0    &    0  &   $\frac{17}{18}$     &   0    &  0    &  $\frac{16}{18}$    &   0    &  0    \\
+    $M_{2}$   &   17/18   &   0    &    0  &   17/18     &   0    &  0    &  16/18    &   0    &  0    \\
     $M_{3}$   &   0 &     0  &   0   &        0     &    0   &  0    &        0     &   0    & 0 \\
@@
 (See Fig.
-$\ref{fig:figure4}$)
+\ref{fig:figure4})
 In light of this, we conduct the analysis in two steps:
@@
 \begin{itemize}
-    \item Variable selection, which includes $43$ paper.
-    \item Multiple Hypothesis Testing, which includes $31$ papers.
+    \item Variable selection (VarSel), which includes $43$ paper.
+    \item Multiple Hypothesis Testing (MulT), which includes $31$ papers.
 \end{itemize}
@@
 \begin{itemize}
-    \item Non-parametric Bayesian Statistics, which includes $15$ papers.
-    \item Functional / Longitudinal Data analysis, which includes $16$ papers.
-    \item Dimension Reduction, which includes $14$ papers.
-    \item High-dimensional covariance estimation, which includes $15$ papers.
-    \item Mixed topics, which includes $98$ papers.
+    \item Non-parametric Bayesian Statistics (NonPar), which includes $15$ papers.
+    \item Functional / Longitudinal Data analysis (FuncAn), which includes $16$ papers.
+    \item Dimension Reduction (DimRed), which includes $14$ papers.
+    \item High-dimensional covariance estimation (CovEst), which includes $15$ papers.
+    \item Mixed topics (Mixed), which includes $98$ papers.
 \end{itemize}
@@
 All the $10$ edges come from the pairs of papers from different communities.
-For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable Selection $(\emph{VarSel})$ community.
+For instance, the first pair of papers comes from the Functional Analysis community and Variable Selection community.
 $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
@@
 \hline
-1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       & \\
-     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                         & \\
-2    & VarSel      & The adaptive lasso and its oracle properties                                                  & \\
-     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection                & \\
-3    & DimRed    & Contour projected dimension reduction                                                        & \\
-     & VarSel    & Factor profiled sure independence screening & \\
-4    & VarSel    & Factor profiled sure independence screening & \\
-     & DimRed    & Sliced regression for dimension reduction & \\
-5    & CovEst    & Two sample tests for high-dimensional covariance matrices & \\
-     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression          & \\
-6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise       & \\
-     & CovEst     & Regularized estimation of large covariance matrices     &  \\
-7    & DimRed    & A constructive approach to the estimation of dimension reduction directions        & \\
-     & VarSel     & Factor profiled sure independence screening    & \\
-8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors  & \\
-     & Mixed      & Empirical {B}ayes selection of wavelet thresholds                          & \\
-9    & Mixed    & Nonparametric inferences for additive models                   & \\
-     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models      & \\
-10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality        & \\
-     & Mixed     & Maximum likelihood estimation in semiparametric regression models with censored data                   & \\
+1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis (P.Hall, et al. $2006$)      & \\
+     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters (J.Fan, et al, $2004$)                       & \\
+2    & VarSel      & The adaptive lasso and its oracle properties (H.Zou, $2006$)                             & \\
+     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection (Y. Chung, et al. $2009$)    & \\
+3    & DimRed    & Contour projected dimension reduction (R.Luo, et al. $2009$)                                                     & \\
+     & VarSel    & Factor profiled sure independence screening (H.Wang, $2012$)& \\
+4    & VarSel    & Factor profiled sure independence screening (H.Wang, $2012$)& \\
+     & DimRed    & Sliced regression for dimension reduction (H.Wang, et al. $2012$) & \\
+5    & CovEst    & Two sample tests for high-dimensional covariance matrices (J.Li, et al. $2012$)& \\
+     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression (CH.Zhang, et al. $2008$)        & \\
+6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise (P.Hall, et al. $2010$)       & \\
+     & CovEst     & Regularized estimation of large covariance matrices (PJ.Bickel, et al. $2008$)    &  \\
+7    & DimRed    & A constructive approach to the estimation of dimension reduction directions (Y. Xia. $2007$)       & \\
+     & VarSel     & Factor profiled sure independence screening (H.Wang, $2012$)    & \\
+8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors (TJ.Yen, $2011$) & \\
+     & Mixed      & Empirical {B}ayes selection of wavelet thresholds (IM. Johnstone, et al. $2005$)                         & \\
+9    & Mixed    & Nonparametric inferences for additive models (J.Fan, et al, $2005$)                  & \\
+     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models 
+     (J.Fan, et al, $2011$)     & \\
+10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality    
+    (J.Fan, et al, $2010$) & \\
+     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data  & \\
 \hline
@@
 In this Section, first we briefly introduce several notations, a notion on the decomposability of regularizer, and a useful lemma proved in the work \cite{agarwal2012noisy}.
-Then, we present Lemma\ref{le:le2} and its proof.
+Then, we present Lemma \ref{le:le2} and its proof.
 Finally, we present the proof of our Theorem\ref{Th:th1}.
@@
 %We will choose the model subspace $M$, which will be chosen such that the matrix $S^*$ lies within or close to $M$.
-\begin{lemma}
+\begin{lemma} \label{eq:Lmag}
 (\textbf{Agarwal, et al} \cite{agarwal2012noisy})
@@
     \begin{equation}\label{eq:Lm1}
-        \mbox{rank}(\widehat{\Delta}^{L}_{A}) \leq 2k, \quad and \quad (\widehat{\Delta}^{L}_{A})^{T}\widehat{\Delta}^{L}_{B}
-        = (\widehat{\Delta}^{L}_{B})^{T}\widehat{\Delta}^{L}_{A} =0
-    \end{equation}
- \item The difference $\mathbb{Q}(L^{*},S^{*}) -  \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ is upper-bounded by
+        \mbox{rank}\big(\widehat{\Delta}^{L}_{A}\big) \leq 2k, \quad and \quad \big(\widehat{\Delta}^{L}_{A}\big)^{T}\widehat{\Delta}^{L}_{B}
+        = \big(\widehat{\Delta}^{L}_{B}\big)^{T}\widehat{\Delta}^{L}_{A} =0
+    \end{equation}
+ \item The difference $\mathbb{Q}\big(L^{*},S^{*}\big) -  \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big)$ is upper-bounded by
     \begin{equation} \label{eq:28}
-        \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
-        +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
+        \mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) - \mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\big)
+        +2 \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\frac{\gamma}{\delta}\left\|S^*_{M^\perp}\right\|_{1}
     \end{equation}
@@
     \left\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F} +
-    3\mathbb{Q}\left(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\right)+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
+    3\mathbb{Q}\left(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\right)+4 \sum_{j=k+1}^{n} \sigma_{j}\big(L^{*}\big) + 4\frac{\gamma}{\delta}
     \left\|S^{*}_{M^\perp}\right\|_{1}
@@
 \begin{equation}
-    h(\widehat{\Theta}) - h(\Theta^{*})
-    \leq \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
+    h\big(\widehat{\Theta}\big) - h\big(\Theta^{*}\big)
+    \leq \delta \mathbb{Q}\big(L^{*},S^{*}\big) - \delta \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big)
 \end{equation}
@@
 \begin{align}
-    h(\widehat{\Theta})-h(\Theta^{*}) &\geq
-    \langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ \nonumber \\
-    &= - \langle\,\frac{1}{n} (X-P^{*}), \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \rangle\ \nonumber \\
-    &\geq -\frac{1}{n} \|X - P^*\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \nonumber \\
-    &\geq -\frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) - \frac{\gamma}{2} (\|\widehat{\Delta}^{S}_{M}\|_{1} +
-    \|\widehat{\Delta}^{S}_{M^\perp}\|_{1}) \label{eq:27}
+    h\big(\widehat{\Theta}\big)-h\big(\Theta^{*}\big) &\geq
+    \big\langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\big\rangle\ \nonumber \\
+    &= - \big\langle\,\frac{1}{n} (X-P^{*}), \widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \big\rangle\ \nonumber \\
+    &\geq -\frac{1}{n} \|X - P^*\|_{op}\bigg(\big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_\ast + \big\|\widehat{\Delta}^{L}\big\|_\ast\bigg) +  \frac{1}{n} \|X - P^*\|_{\infty}\big\|\widehat{\Delta}^{S}\big\|_{1} \nonumber \\
+    &\geq -\frac{\delta}{2}\bigg(\big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\big\|_\ast + \big\|\widehat{\Delta}^{L}_{B}\big\|_\ast\bigg) - \frac{\gamma}{2} \bigg(\big\|\widehat{\Delta}^{S}_{M}\big\|_{1} +
+    \big\|\widehat{\Delta}^{S}_{M^\perp}\big\|_{1}\bigg) \label{eq:27}
 \end{align}
 
-An application of Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1,
-we can get an upper bound of difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ as follows:
+An application of Agarwal et al \cite{agarwal2012noisy}'s second element of lemma \ref{eq:Lmag},
+we can get an upper bound of difference $\mathbb{Q}\big(L^*,S^*\big)- \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big)$ as follows:
 
 \begin{equation} \label{eq:28}
-    \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) - \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})
-    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\|S^*_{M^\perp}\|_{1}
-\end{equation}
-
-By combining relations (\ref{eq:27}) and (\ref{eq:28}), we can get the upper bound of $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$ :
+    \mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) - \mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\big)
+    +2 \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\frac{\gamma}{\delta}\big\|S^*_{M^\perp}\big\|_{1}
+\end{equation}
+
+By combining relations (\ref{eq:27}) and (\ref{eq:28}), we can get the upper bound of $\mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\big)$ :
 \begin{align*}
-    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq
-    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
-    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
-    \|S^{*}_{M^\perp}\|_{1}
+    \mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\big) \leq
+    \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} +
+    3\mathbb{Q}\big(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\big)+4 \sum_{j=k+1}^{n} \sigma_{j}\big(L^{*}\big) + 4\frac{\gamma}{\delta}
+    \big\|S^{*}_{M^\perp}\big\|_{1}
 \end{align*}
@@
 \begin{equation}\label{eq:2}
-    h(\widehat{\Theta}) + \delta\left\|\widehat{L}\right\|_{*} + \gamma\left\|\widehat{S}\right\|_{1} \leq
-     h(\Theta^{*}) + \delta\left\|{L^{*}}\right\|_{*} + \gamma\left\|{S}^{*}\right\|_{1}
-\end{equation}
-
-Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on the term $h(\widehat{\Theta})-h(\Theta^{*})$ :
-\[
-h(\widehat{\Theta})-h(\Theta^{*}) \geq
-\langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ + \frac{\tau}{2}\left\|\widehat{\Delta}^{\Theta}\right\|_{F}^{2}
+    h\big(\widehat{\Theta}\big) + \delta\big\|\widehat{L}\big\|_{*} + \gamma\big\|\widehat{S}\big\|_{1} \leq
+     h\big(\Theta^{*}\big) + \delta\big\|{L^{*}}\big\|_{*} + \gamma\big\|{S}^{*}\big\|_{1}
+\end{equation}
+
+Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on the term $h\big(\widehat{\Theta}\big)-h\big(\Theta^{*}\big)$ :
+\[
+h\big(\widehat{\Theta}\big)-h\big(\Theta^{*}\big) \geq
+\big\langle\, \nabla_{\Theta}h\big(\Theta^{*}\big),\widehat{\Theta}-\Theta^{*}\big\rangle\ + \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2}
 \]
@@
 \begin{equation}\label{eq:3}
-    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
-    + \delta \|L^{*}\|_\ast + \gamma \|S^{*}\|_1
-    - \delta \|\widehat{L}\|_\ast - \gamma \|\widehat{S}\|_1
+    \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2} \leq
+    -\big\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\big\rangle\
+    + \delta \big\|L^{*}\big\|_\ast + \gamma \big\|S^{*}\big\|_1
+    - \delta \big\|\widehat{L}\big\|_\ast - \gamma \big\|\widehat{S}\big\|_1
 \end{equation}
@@
 \begin{equation}\label{eq:4}
-    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    -\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\
-    + \delta \mathbb{Q}\left(L^{*},S^{*}\right) - \delta \mathbb{Q}\left(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\right)
-\end{equation}
-
-According to Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1,
-the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})$ is upper-bounded by
+    \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2} \leq
+    -\big\langle\,\nabla_{\Theta}h\big(\Theta^{*}\big),\widehat{\Theta}-\Theta^{*}\big\rangle\
+    + \delta \mathbb{Q}\big(L^{*},S^{*}\big) - \delta \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big)
+\end{equation}
+
+According to Agarwal et al \cite{agarwal2012noisy}'s second element of lemma \ref{eq:Lmag},
+the difference $\mathbb{Q}\big(L^*,S^*\big)- \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big)$ is upper-bounded by
 
 \begin{equation}\label{eq:5}
-    \mathbb{Q}\left(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\right) - \mathbb{Q}\left(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\right)
-    +2 \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\frac{\gamma}{\delta}\left\|S^*_{M^\perp}\right\|_{1}
-\end{equation}
-
-First, we want to control upper bound of the term $-\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\,$
+    \mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) - \mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\big)
+    +2 \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\frac{\gamma}{\delta}\big\|S^*_{M^\perp}\big\|_{1}
+\end{equation}
+
+First, we want to control upper bound of the term $-\big\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \big\rangle\,$
 in (\ref{eq:4}).
 \begin{align}
--\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \rangle\  \nonumber
-&=\langle\, \frac{1}{n} (X - P^*), \widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S} \rangle\ \\ \nonumber
-&\leq \frac{1}{n} \left\|X - P^*\right\|_{op}(\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_\ast + \left\|\widehat{\Delta}^{L}\right\|_\ast) +  \frac{1}{n} \left\|X - P^*\right\|_{\infty}\left\|\widehat{\Delta}^{S}\right\|_{1} \\ \nonumber
-&\leq \frac{1}{n} \left\|X - P^*\right\|_{op}(\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F} + \left\|\widehat{\Delta}^{L}_{A}\right\|_\ast + \left\|\widehat{\Delta}^{L}_{B}\right\|_\ast) +
-\frac{1}{n} \left\|X - P^*\right\|_{\infty}(\left\|\widehat{\Delta}^{S}_{M}\right\|_{1} +
-\left\|\widehat{\Delta}^{S}_{M^{\perp}}\right\|_{1}) \\
-&\leq \frac{\delta}{2}(\left\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F} + \left\|\widehat{\Delta}^{L}_{A}\right\|_\ast + \left\|\widehat{\Delta}^{L}_{B}\right\|_\ast) + \frac{\gamma}{2}(\left\|\widehat{\Delta}^{S}_{M}\right\|_{1} +
-\left\|\widehat{\Delta}^{S}_{M^{\perp}}\right\|_{1})  \label{eq:10}
+-\big\langle\,\nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*} \big\rangle\  \nonumber
+&=\big\langle\, \frac{1}{n} (X - P^*), \widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S} \big\rangle\ \\ \nonumber
+&\leq \frac{1}{n} \|X - P^*\|_{op}\bigg(\big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_\ast + \big\|\widehat{\Delta}^{L}\big\|_\ast\bigg) +  \frac{1}{n} \|X - P^*\|_{\infty}\big\|\widehat{\Delta}^{S}\big\|_{1} \\ \nonumber
+&\leq \frac{1}{n} \|X - P^*\|_{op}\bigg(\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F} + \left\|\widehat{\Delta}^{L}_{A}\right\|_\ast + \left\|\widehat{\Delta}^{L}_{B}\right\|_\ast\bigg) +
+\frac{1}{n} \left\|X - P^*\right\|_{\infty}\bigg(\left\|\widehat{\Delta}^{S}_{M}\right\|_{1} +
+\left\|\widehat{\Delta}^{S}_{M^{\perp}}\right\|_{1}\bigg) \\
+&\leq \frac{\delta}{2}\bigg(\big\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} + \big\|\widehat{\Delta}^{L}_{A}\big\|_\ast + \big\|\widehat{\Delta}^{L}_{B}\big\|_\ast\bigg) + \frac{\gamma}{2}\bigg(\left\|\widehat{\Delta}^{S}_{M}\right\|_{1} +
+\left\|\widehat{\Delta}^{S}_{M^{\perp}}\right\|_{1}\bigg)  \label{eq:10}
 \end{align}
@@
 \begin{equation}
-    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2} \leq
-    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
-    \frac{3\delta}{2}\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M})
-    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 2\gamma \|S^*_{M^\perp}\|_{1}
+    \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2} \leq
+    \frac{\delta}{2}\big\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} +
+    \frac{3\delta}{2}\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big)
+    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\gamma \big\|S^*_{M^\perp}\big\|_{1}
     \label{eq:11}
@@
 
-Second, we wish to control the lower bound of the term  $\frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}$ with respect to $\hat{\Delta}^{\alpha},\widehat{\Delta}^{L},\widehat{\Delta}^{S}$.
+Second, we wish to control the lower bound of the term  $\frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2}$ with respect to $\widehat{\Delta}^{\alpha},\widehat{\Delta}^{L},\widehat{\Delta}^{S}$.
 \begin{align}
-\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
-&= \|\widehat{\Theta}-\Theta^{*} \|_{F}^{2} \\ \nonumber
-&= \|\widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S}\|_{F}^{2} \\ \nonumber
-&= \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}+\widehat{\Delta}^{S}\|_{F}^{2} +
-2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ \\
-&=  \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2} +
-2 \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ +
-2 \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\  \label{eq:12}
+\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2}  \nonumber
+&= \big\|\widehat{\Theta}-\Theta^{*} \big\|_{F}^{2} \\ \nonumber
+&= \big\|\widehat\Delta^{\alpha\mathbbm{1}\mathbbm{1}^T} + \widehat\Delta^{L} + \widehat\Delta^{S}\big\|_{F}^{2} \\ \nonumber
+&= \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \big\|\widehat{\Delta}^{L}+\widehat{\Delta}^{S}\big\|_{F}^{2} +
+2 \big\langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \big\rangle\ \\
+&=  \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \big\|\widehat{\Delta}^{S}\big\|_{F}^{2} +
+2 \big\langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \big\rangle\ +
+2 \big\langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \big\rangle\  \label{eq:12}
 \end{align}
@@
 We want to get the further lower bound on trace inner product terms,
-$ \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $.
+$ \big\langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \big\rangle\ $, $ \big\langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \big\rangle\ $.
 To control the first trace inner product term, we use the relation $\widehat{\Delta}^{L}\mathbbm{1}=0$, apply the definition of dual norm on inner product term, apply triangular inequality on $\widehat{\Delta}^\alpha$, and lastly we apply the constraint imposed on $|\alpha|$ stated in Assumption \ref{Ass:2}.
@@
 \begin{align}
-    | \langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \nonumber
-    &= | \langle\,\widehat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\ \nonumber
-    &\leq \|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\widehat{\Delta}^{S}\|_1 \\ \nonumber
-    &\leq (|\widehat{\alpha}|+|\alpha^{*}|)\|\widehat{\Delta}^{S}\|_1\\
-    &\leq 2C\kappa\|\widehat{\Delta}^{S}\|_1  \label{eq:13}
+    \big| \big\langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\rangle\ \big| \nonumber
+    &= \big| \big\langle\,\widehat\Delta^{S},\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\rangle\ \big| \\ \nonumber
+    &\leq \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \big\|_{\infty} \big\|\widehat{\Delta}^{S}\big\|_1 \\ \nonumber
+    &\leq \bigg(\big|\widehat{\alpha}\big|+\big|\alpha^{*}\big|\bigg)\big\|\widehat{\Delta}^{S}\big\|_1\\
+    &\leq 2C\kappa\big\|\widehat{\Delta}^{S}\big\|_1  \label{eq:13}
 \end{align}
 
-To control the term $ \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ $, we first apply the definition of dual norm on trace inner product term, then apply triangular inequality on $\widehat{\Delta}^{L}$ and spikiness condition.
+To control the term $ \big\langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \big\rangle\ $, we first apply the definition of dual norm on trace inner product term, then apply triangular inequality on $\widehat{\Delta}^{L}$ and spikiness condition.
 
 \begin{align}
-    | \langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \rangle\ | \nonumber
-    &\leq \|\widehat{\Delta}^{L}\|_{\infty} \|\widehat{\Delta}^{S}\|_1\\ \nonumber
-    &\leq (\|\widehat{L}\|_{\infty} + \|L^{*}\|_{\infty})
-    \|\widehat{\Delta}^{S} \|_{1}\\
-    &\leq \big(\frac{2\kappa}{n}\big)\|\widehat{\Delta}^{S} \|_{1} \label{eq:14}
+    \big| \big\langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \big\rangle\ \big| \nonumber
+    &\leq \big\|\widehat{\Delta}^{L}\big\|_{\infty} \big\|\widehat{\Delta}^{S}\big\|_1\\ \nonumber
+    &\leq \bigg(\big\|\widehat{L}\big\|_{\infty} + \big\|L^{*}\big\|_{\infty}\bigg)
+    \big\|\widehat{\Delta}^{S} \big\|_{1}\\
+    &\leq \bigg(\frac{2\kappa}{n}\bigg)\big\|\widehat{\Delta}^{S} \big\|_{1} \label{eq:14}
 \end{align}
@@
 We can combine the inequality (\ref{eq:12}), (\ref{eq:13}) and (\ref{eq:14}).
-Then applying the assumption on regularization parameter $\gamma$, and the fact $\|\widehat{\Delta}^{L}\|_{\ast}\geq0$ sequentially, we can get,
+Then applying the assumption on regularization parameter $\gamma$, and the fact $\big\|\widehat{\Delta}^{L}\big\|_{\ast}\geq0$ sequentially, we can get,
 
 \begin{align}
-    \frac{\tau}{2}\|\widehat{\Delta}^{\Theta}\|_{F}^{2}  \nonumber
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2}
-    - \kappa\tau\bigg(\frac{Cn+1}{n}\bigg)\|\widehat{\Delta}^{S}\|_{1} \\ \nonumber
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\widehat{\Delta}^{S}\|_{1}\\
-    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S) \label{eq:26}
+    \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2}  \nonumber
+    &\geq \frac{\tau}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{S}\big\|_{F}^{2}
+    - \kappa\tau\bigg(\frac{Cn+1}{n}\bigg)\big\|\widehat{\Delta}^{S}\big\|_{1} \\ \nonumber
+    &\geq \frac{\tau}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{S}\big\|_{F}^{2} - \frac{\gamma}{2}\big\|\widehat{\Delta}^{S}\big\|_{1}\\
+    &\geq \frac{\tau}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{S}\big\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}\big(\widehat{\Delta}^L,\widehat{\Delta}^S\big) \label{eq:26}
 \end{align}
 
-By combining the relations (\ref{eq:11}) and (\ref{eq:26}), applying triangular inequality, $\mathbb{Q}(\widehat{\Delta}^L,\widehat{\Delta}^S)\leq \mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) + \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^{\perp}})$, and rearranging the term, we can get following inequality,
-\[
-    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} \\
-    \leq \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
-    2\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) +  \frac{\delta}{2} \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) +
-    2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 2\gamma
-    \|S^{*}_{M^\perp}\|_{1}
+By combining the relations (\ref{eq:11}) and (\ref{eq:26}), applying triangular inequality, $\mathbb{Q}\big(\widehat{\Delta}^L,\widehat{\Delta}^S\big)\leq \mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) + \mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^{\perp}}\big)$, and rearranging the term, we can get following inequality,
+\[
+    \frac{\tau}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{S}\big\|_{F}^{2} \\
+    \leq \frac{\delta}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} +
+    2\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) +  \frac{\delta}{2} \mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\big) +
+    2 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^{*}\big) + 2\gamma
+    \big\|S^{*}_{M^\perp}\big\|_{1}
 \]
@@
 \begin{align}
-    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} -
-    \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}
+    \frac{\tau}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{S}\big\|_{F}^{2} -
+    \frac{\delta}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}
     \leq
-    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}  \label{eq:42}
+    \frac{7\delta}{2}\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 4\gamma \big\|S^*_{M^\perp}\big\|_{1}  \label{eq:42}
 \end{align}
@@
     \nonumber
-    \delta\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M})
-    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L_{A}\|_{F} + \Psi(M)\gamma\|\widehat{\Delta}^S_M\|_{F}\\
-    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L\|_{F} + \Psi(M)\gamma\|\widehat{\Delta}^S\|_{F}  \label{eq:43}
+    \delta\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big)
+    \leq \sqrt{2k}\delta\big\|\widehat{\Delta}^L_{A}\big\|_{F} + \Psi(M)\gamma\big\|\widehat{\Delta}^S_M\big\|_{F}\\
+    \leq \sqrt{2k}\delta\big\|\widehat{\Delta}^L\big\|_{F} + \Psi(M)\gamma\big\|\widehat{\Delta}^S\big\|_{F}  \label{eq:43}
 \end{align}
@@
 Using Cauchy-Schwarz inequality, we can easily check the quantity $\Psi(M)$ is bounded by at most $\sqrt{s}$.
-Plugging in the relation ($\ref{eq:43}$) into ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$ yield the claim.
+Plugging in the relation ($\ref{eq:43}$) into ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}\big(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)$ yield the claim.
 \end{proof}

### 2019-10-07 Manuscript for submission/manuscript.tex
Update

@@
 Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of procedures for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.
+We put stars to the superscript of parameters to denote that they are ground truth.
+Readers can refer the meaning of each parameter in the model in Section \ref{sec:intro} and Section \ref{sec:model-form}.
 
@@
         where each row of $F^*$ has $\frac{n}{K}$ $1$'s and each column has only one $1$.
+        Note that the remaining entries of the matrix are filled with zeros.
         Then, we assume that $n_{l}$ papers share $l$ topics and $n_{m}$ papers share $m$ topics ($1 < l < m \leq K$).
@@
 Nodes that share the common factors are clustered. The cross cluster links are ad-hoc Citations.
-All the graphs are drawn via R package `igraph'.}
+All the graphs are drawn via the algorithm in \cite{fruchterman1991graph}.}
 \label{fig:figure1}
@@
 In Table \ref{tab:table2}, we provide $10$ pairs of papers that have the largest estimated $\widehat{S}_{ij}$.
-All the $10$ edges come from the pairs of papers from different communities.
-For instance, the first pair of papers comes from the Functional Analysis community and Variable Selection community.
-$\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
+All the $10$ edges come from the pairs of papers from different topics.
+For instance, the first pair of papers comes from the Functional Analysis topic and Variable Selection topic.
+The paper from Functional Analysis topic cites the paper from Variable Selection for borrowing a mathematical representation to build a theorem.
 Though it might appear to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
-The second pair of papers comes from the Mixed topics community (denoted as $\emph{Mixed}$) and the Variable Selection ($\emph{VarSel}$) community.
+The second pair of papers comes from the Mixed topics community and the Variable Selection community.
 This case is interesting since both papers study about variable selection problem, but they are classified in different communities and connected via an ad-hoc link.
-Specifically, the paper from $Mixed$ community study the variable selection problem under the non-parametric Bayesian framework, and compare their method with the one that is proposed in $\emph{VarSel}$ paper, ``Adaptive Lasso’’.
+Specifically, the authors in the paper from Mixed topics community study the variable selection problem under the non-parametric Bayesian framework, and compare their method with the ``Adaptive Lasso'' that is proposed in the paper from Variable Selection topic.
 

### 2019-10-07 Manuscript for submission/manuscript.tex
Update

@@
 \begin{tabular}{clclc}\hline
-Pair & Community & Title & \\
+Pair & Community & Title (Author, Year) & \\
 \hline
@@
      & Mixed      & Empirical {B}ayes selection of wavelet thresholds (IM. Johnstone, et al. $2005$)                         & \\
-9    & Mixed    & Nonparametric inferences for additive models (J.Fan, et al, $2005$)                  & \\
+9    & Mixed    & Nonparametric inferences for additive models (J.Fan, et al. $2005$)                  & \\
      & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models
-     (J.Fan, et al, $2011$)     & \\
+     (J.Fan, et al. $2011$)     & \\
 10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality
-    (J.Fan, et al, $2010$) & \\
-     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data  & \\
+    (J.Fan, et al. $2010$) & \\
+     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data (D.Zeng, et al. $2007$) & \\
 \hline
@@
     \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2} \leq
-    \frac{\delta}{2}\big\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} +
+    \frac{\delta}{2}\big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} +
     \frac{3\delta}{2}\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big)

### 2019-10-07 Manuscript for submission/manuscript.tex
Update

@@
 }
+
 %\newtheorem{theorem}{Theorem}[section]
@@
 %\newtheorem{example}[theorem]{Example}
-
+\newcommand{\Hquad}{\hspace{0.5em}}
 \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
@@
 
-\keywords{citation network, matrix decomposition, latent variable model, logistic regression model, convex optimization, ADMM}
+\keywords{citation network, matrix decomposition, latent variable model, logistic regression model, convex optimization, alternating direction method of multiplier}
 
@@
 \maketitle
-\footnotetext{\textbf{Abbreviations:} fused factor analysis and logistic graphical models, ADMM, network model}
+\footnotetext{\textbf{Abbreviations:} fused factor analysis and logistic graphical models, alternating direction method of multiplier, network model}
 
@@
 where $\alpha \in \mathbb{R}$ is a parameter and matrix $D \in \mathbb{R}^{K \times K}$ is a diagonal matrix: $D = \mbox{diag}\{d_{1},d_{2},\ldots,d_{K}\}$.
-We assume $d_{ii} > 0$ for $1 \le i \le K$.
+We assume $d_{i} > 0$ for $1 \le i \le K$.
 Another way to put \eqref{eq:logistic01} is
@@
 A justification of the above model is that when both node $i$ and node $j$ are related to topic $k$, they have a higher chance to cite one way or the other.
-We have assumed a common strengthen coefficient $d_k$ ($1\le k \le K$) for factor $k$, despite different nodes.
+We have assumed a common strength coefficient $d_k$ ($1\le k \le K$) for factor $k$, despite different nodes.
 We denote a matrix $F = \{f_1, f_2, \ldots, f_n\} \in \mathbb{R}^{K \times n}$.
@@
 The above delivers a factor analysis model.
-Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g.,\cite{joreskog1969general, mcdonald2014factor,lord2008statistical, rasch1980probabilistic, harman1960modern, joreskog1970general}).
+Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g., \cite{joreskog1969general, mcdonald2014factor,lord2008statistical, rasch1980probabilistic, harman1960modern, joreskog1970general}).
 
@@
     So there are $p$ questions that need to be answered, and each questions fall into above three categories.
-    If there are $n$ respondents to questions, we have $n$ independent data generated from same distribution.
+    If there are $n$ respondents to questions, they have $n$ independent data generated from the same distribution.
     In our case, the observed citation network can be thought of as one realization of a random graph.
@@
 \item FLaG approximates the original likelihood through constructing pseudo-likelihood function by taking advantage of conditional independence among the nodes.
-    In our model, likelihood function is directly accessible due to the conditional independence among edges given parameters.
+    In our model, likelihood function is directly accessible due to the conditional independence among edges.
 \end{enumerate}
@@
 In Section \ref{sec:model-form}, we will give a presentation on how to build a model, which can encode both the latent dependent structure due to the common topics and the remaining sparse ad-hoc dependent structure.
-In Section \ref{sec:estimate}, we will discuss the assumptions in our model and penalization on likelihood function that is constructed in Section \ref{sec:model-form}.
+In Section \ref{sec:estimate}, we will discuss the assumptions in our model and the penalization on the likelihood function, which is constructed in Section \ref{sec:model-form}.
 In Section \ref{sec:theorem}, we provide a non-asymptotic error bound of the estimator.
-Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem that is formulated in Section \ref{sec:estimate}.
-In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians.
+Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem.
+In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on a real citation network of statisticians.
 We finally conclude this work in Section \ref{sec:Con} with several open questions and some directions for future research.
@@
 
-\item To ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and an arbitrary matrix $L$, we assume that the eigen-vector of $L$ is centered, that is,
+\item Following the approaches that were mentioned in the Introduction, we propose to relax $F^T D F$ to $L$, where $L$ is a low rank matrix.
+Furthermore, to ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and an arbitrary matrix $L$, we assume that the eigen-vector of $L$ is centered, that is,
 \[
@@
 \]
-where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$'s. If we have $L=F^TDF$, this condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.
+where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$'s.
+Since we have $L=F^TDF$, this condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.
 
@@
 Directly maximizing the objective function in \eqref{eq:logistic08} is not going to be an easy task.
-Following the approaches that were mentioned in Introduction, we propose to relax $F^T D F$ to $L$, where $L$ is a low rank matrix.
 Consequently, the log-likelihood function in \eqref{eq:logistic08} can be rewritten as
@@
 After we have obtained $\widehat{S}$ in \eqref{eq:logistic10}, we can uncover the graphical model by investigating non-zero entries in $\widehat{S}$.
-On the other hand when we have calculated $\widehat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\widehat{L} = F^T D F.$
+On the other hand, when we have calculated $\widehat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\widehat{L} = F^T D F.$
 This is the price we have to pay for an amenable computational approach.
 The rank of estimated $\widehat{L}$ will be our estimate of the number of factors (i.e., the number of underlying common topics).
-For the issue on assigning the community membership of each node $i$, we will discuss this later in Section \ref{sec:Num-anal}.
+We will discuss the issue on assigning the community membership of each node $i$ later in Section \ref{sec:Num-anal}.
 
@@
 L_{ij}+S_{ij}\right)\right)}{1+\exp\left(\alpha+
-L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
+L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1.
 \end{equation}
@@
 \begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L}) \label{Ass:2}
-To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
+To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes an all one vector in $\mathbb{R}^{n}$.
 \end{assumption}
@@
 \begin{theorem} \label{Th:th1}
-Under the assumptions \ref{Ass:1}, \ref{Ass:2} and \ref{Ass:3},
+Under the Assumptions \ref{Ass:1}, \ref{Ass:2} and \ref{Ass:3},
 if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
@@
 whereas Agarwal, et al. \cite{agarwal2012noisy} work on a general linear observation model whose parameter is also
-characterized by sum of a low rank matrix and a sparse matrix.
+characterized by a sum of a low rank matrix and a sparse matrix.
 
@@
 Section \ref{sec:Num-anal} is divided into two parts.
-In Section \ref{sec:Syn-dat}, we conduct an empirical study of our proposed method with artificial graphical structures.
-In Section \ref{sec:citation_network}, we perform a real data analysis with citation network for statisticians.
+In Section \ref{sec:Syn-dat}, we conduct an empirical study of our proposed method with synthetic graphical structures.
+In Section \ref{sec:citation_network}, we perform a real data analysis with a citation network for statisticians.
 
@@
 Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of procedures for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.
-We put stars to the superscript of parameters to denote that they are ground truth.
+We put astroids in the superscript of parameters to denote that they are ground truth.
 Readers can refer the meaning of each parameter in the model in Section \ref{sec:intro} and Section \ref{sec:model-form}.
@@
 
-    \item Generate the weight coefficients of the factors $D^*_{ii}$ from the uniform distribution that is supported on $[19,20]$ $ \forall 1 \leq i \leq K$.
-        In this way, we can let the papers with same topic cluster together.
-
-    \item Remind that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
+    \item Generate the weight coefficients of the factors $D^*_{ii}$ from the uniform distribution that is supported on $[19,20]$, $ \forall 1 \leq i \leq K$.
+        In this way, we can leave the papers with same topic cluster together.
+
+    \item Recall that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
         In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
-        Specifically, we assume that there are $\frac{|S^*|}{_KC_{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
+        Specifically, we assume that there are $\frac{|S^*|}{\binom{K}{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
         This can be implemented via following steps:
@@
         \end{align*}
-        where each of them has arbitrary $\frac{|S^*|}{_KC_{2}}$ elements.
+        where each of them has arbitrary $\frac{|S^*|}{\binom{K}{2}}$ elements.
         2) Create a set $I_{S^*}$ whose elements are pairs of indices such that
@@
             I_{S^*} =
-            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{_KC_{2}} \bigg\},
+            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{\binom{K}{2}} \bigg\},
         \]
@@
     \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}},
-    \mbox{mode} |\widehat{S}^{\gamma,\delta}|: \mbox{subject to} 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X| \big\}
+    \mbox{mode} |\widehat{S}^{\gamma,\delta}|: \mbox{subject to} \Hquad 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X| \big\}.
 \]
@@
     (\gamma^{AIC},\delta^{AIC}):= \mbox{arg min}_{\gamma, \delta}
-    \mbox{AIC}(M)
-\]
-We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following four evaluation metrics.
+    \mbox{AIC}(M).
+\]
+We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following four evaluation metrics:
 
@@
 $M_2$ evaluates the positive selection rate of the sparse ad-hoc structure in network,
-and $M_3$ evaluates the false discovery rate of ad-hoc edges.
+$M_3$ evaluates the false discovery rate of ad-hoc edges, and
 $M_4$ calculates the proportion of mis-classified nodes to the entire nodes in the network.
@@
     \item Dimension Reduction (DimRed), which includes $14$ papers.
-    \item High-dimensional covariance estimation (CovEst), which includes $15$ papers.
-    \item Mixed topics (Mixed), which includes $98$ papers.
+    \item High-dimensional Covariance Estimation (CovEst), which includes $15$ papers.
+    \item Mixed Topics (Mixed), which includes $98$ papers.
 \end{itemize}
-From the sub-network $X^{\mbox{sub}}$, we got four meaningful topics: Bayesian Statistics, Functional/Longitudinal Data Analysis, Dimension Reduction, and high-dimensional covariance estimation.
+From the sub-network $X^{\mbox{sub}}$, we got four meaningful topics: Bayesian Statistics, Functional/Longitudinal Data Analysis, Dimension Reduction, and High-dimensional Covariance Estimation.
 Due to the small volume of each community, we could manually check that the false discovery for each community is all zero.
@@
 $2010$), are the examples of these papers.
-It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed topic classified as Mixed topic.
+It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed Topic classified as Mixed Topic.
 For instance, the paper, On the "degrees of freedom" on the LASSO (H. Zou, et al. $2007$), is classified as Mixed Topic paper.
 We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities.
-Actually, out of $11$ citation relationships it has with other papers, $6$ of them came from the relationships with papers from Mixed topics.
+Actually, out of $11$ citation relationships it has with other papers, $6$ of them came from the relationships with papers from Mixed Topics.
 
@@
 Though it might appear to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
-The second pair of papers comes from the Mixed topics community and the Variable Selection community.
+The second pair of papers comes from the Mixed Topics community and the Variable Selection community.
 This case is interesting since both papers study about variable selection problem, but they are classified in different communities and connected via an ad-hoc link.
-Specifically, the authors in the paper from Mixed topics community study the variable selection problem under the non-parametric Bayesian framework, and compare their method with the ``Adaptive Lasso'' that is proposed in the paper from Variable Selection topic.
+Specifically, the authors in the paper from Mixed Topics community study the variable selection problem under the Non-parametric Bayesian framework, and compare their method with the ``Adaptive Lasso'' that is proposed in the paper from Variable Selection topic.
 
@@
 \centering
-\begin{tabular}{clclc}\hline
+\begin{tabular}{clcl}\hline
 Pair & Community & Title (Author, Year) & \\
 \hline
-1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis (P.Hall, et al. $2006$)      & \\
-     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters (J.Fan, et al, $2004$)                       & \\
-2    & VarSel      & The adaptive lasso and its oracle properties (H.Zou, $2006$)                             & \\
+1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis (P. Hall, et al. $2006$)      & \\
+     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters (J. Fan, et al, $2004$)                       & \\
+2    & VarSel      & The adaptive lasso and its oracle properties (H. Zou, $2006$)                             & \\
      & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection (Y. Chung, et al. $2009$)    & \\
-3    & DimRed    & Contour projected dimension reduction (R.Luo, et al. $2009$)                                                     & \\
-     & VarSel    & Factor profiled sure independence screening (H.Wang, $2012$)& \\
-4    & VarSel    & Factor profiled sure independence screening (H.Wang, $2012$)& \\
-     & DimRed    & Sliced regression for dimension reduction (H.Wang, et al. $2012$) & \\
-5    & CovEst    & Two sample tests for high-dimensional covariance matrices (J.Li, et al. $2012$)& \\
-     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression (CH.Zhang, et al. $2008$)        & \\
-6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise (P.Hall, et al. $2010$)       & \\
-     & CovEst     & Regularized estimation of large covariance matrices (PJ.Bickel, et al. $2008$)    &  \\
+3    & DimRed    & Contour projected dimension reduction (R. Luo, et al. $2009$)                                                     & \\
+     & VarSel    & Factor profiled sure independence screening (H. Wang, $2012$)& \\
+4    & VarSel    & Factor profiled sure independence screening (H. Wang, $2012$)& \\
+     & DimRed    & Sliced regression for dimension reduction (H. Wang, et al. $2012$) & \\
+5    & CovEst    & Two sample tests for high-dimensional covariance matrices (J. Li, et al. $2012$)& \\
+     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression (CH. Zhang, et al. $2008$)        & \\
+6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise (P. Hall, et al. $2010$)       & \\
+     & CovEst     & Regularized estimation of large covariance matrices (PJ. Bickel, et al. $2008$)    &  \\
 7    & DimRed    & A constructive approach to the estimation of dimension reduction directions (Y. Xia. $2007$)       & \\
-     & VarSel     & Factor profiled sure independence screening (H.Wang, $2012$)    & \\
-8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors (TJ.Yen, $2011$) & \\
+     & VarSel     & Factor profiled sure independence screening (H. Wang, $2012$)    & \\
+8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors (TJ. Yen, $2011$) & \\
      & Mixed      & Empirical {B}ayes selection of wavelet thresholds (IM. Johnstone, et al. $2005$)                         & \\
-9    & Mixed    & Nonparametric inferences for additive models (J.Fan, et al. $2005$)                  & \\
+9    & Mixed    & Nonparametric inferences for additive models (J. Fan, et al. $2005$)                  & \\
      & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models
-     (J.Fan, et al. $2011$)     & \\
+     (J. Fan, et al. $2011$)     & \\
 10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality
-    (J.Fan, et al. $2010$) & \\
-     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data (D.Zeng, et al. $2007$) & \\
+    (J. Fan, et al. $2010$) & \\
+     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data (D. Zeng, et al. $2007$) & \\
 \hline
 \end{tabular}
-\caption{All the $10$ edges come from pairs of papers from different communities.
+\caption{Top $10$ edges come from pairs of papers from different communities.
 For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
@@
 \section{Appendix}
-In this Section, first we briefly introduce several notations, a notion on the decomposability of regularizer, and a useful lemma proved in the work \cite{agarwal2012noisy}.
-Then, we present Lemma \ref{le:le2} and its proof.
-Finally, we present the proof of our Theorem\ref{Th:th1}.
-
-\subsection{Preliminary}
+In this Section, first we briefly introduce several notations, a notion on the decomposability of regularizer, and a useful lemma proved in the work \cite{agarwal2012noisy} (Section\ref{App:Pre}).
+Then, we present Lemma \ref{le:le2} and its proof (Section \ref{App:Lemma2}).
+Finally, we present the proof of our Theorem\ref{Th:th1} (Section \ref{App:Theorem1}).
+
+\subsection{Preliminary} \label{App:Pre}
 Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $M$ as $P_{M}$.
@@
         \| A + B \|_{1} = \|A\|_{1} + \|B\|_{1},
-        \forall A \in M \mbox{and} B \in M^{\perp},
+        \forall A \in M \mbox{and} B \in M^{\perp}.
     \]
@@
 We will also use two results in our proof, which are presented and proved in the work \cite{agarwal2012noisy}.
-For the convenience of readers, we present them here as follows:
+For the convenience of readers, we present them here:
 %We will choose the model subspace $M$, which will be chosen such that the matrix $S^*$ lies within or close to $M$.
@@
         \mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) - \mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\big)
-        +2 \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\frac{\gamma}{\delta}\left\|S^*_{M^\perp}\right\|_{1}
+        +2 \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\frac{\gamma}{\delta}\left\|S^*_{M^\perp}\right\|_{1},
     \end{equation}
@@
 
-\subsection{Lemma \ref{le:le2}}
+\subsection{Lemma \ref{le:le2}} \label{App:Lemma2}
 \begin{lemma} \label{le:le2}
@@
     3\mathbb{Q}\left(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\right)+4 \sum_{j=k+1}^{n} \sigma_{j}\big(L^{*}\big) + 4\frac{\gamma}{\delta}
-    \left\|S^{*}_{M^\perp}\right\|_{1}
+    \left\|S^{*}_{M^\perp}\right\|_{1}.
 \]
@@
     h\big(\widehat{\Theta}\big) - h\big(\Theta^{*}\big)
-    \leq \delta \mathbb{Q}\big(L^{*},S^{*}\big) - \delta \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big)
+    \leq \delta \mathbb{Q}\big(L^{*},S^{*}\big) - \delta \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big).
 \end{equation}
@@
     &\geq -\frac{\delta}{2}\bigg(\big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\big\|_\ast + \big\|\widehat{\Delta}^{L}_{B}\big\|_\ast\bigg) - \frac{\gamma}{2} \bigg(\big\|\widehat{\Delta}^{S}_{M}\big\|_{1} +
-    \big\|\widehat{\Delta}^{S}_{M^\perp}\big\|_{1}\bigg) \label{eq:27}
+    \big\|\widehat{\Delta}^{S}_{M^\perp}\big\|_{1}\bigg). \label{eq:27}
 \end{align}
@@
     \mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) - \mathbb{Q}\big(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\big)
-    +2 \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\frac{\gamma}{\delta}\big\|S^*_{M^\perp}\big\|_{1}
+    +2 \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\frac{\gamma}{\delta}\big\|S^*_{M^\perp}\big\|_{1}.
 \end{equation}
@@
     3\mathbb{Q}\big(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\big)+4 \sum_{j=k+1}^{n} \sigma_{j}\big(L^{*}\big) + 4\frac{\gamma}{\delta}
-    \big\|S^{*}_{M^\perp}\big\|_{1}
+    \big\|S^{*}_{M^\perp}\big\|_{1}.
 \end{align*}
@@
 
-\subsection{Proof of Theorem \ref{Th:th1}}
+\subsection{Proof of Theorem \ref{Th:th1}} \label{App:Theorem1}
 \begin{proof}
@@
     h\big(\widehat{\Theta}\big) + \delta\big\|\widehat{L}\big\|_{*} + \gamma\big\|\widehat{S}\big\|_{1} \leq
-     h\big(\Theta^{*}\big) + \delta\big\|{L^{*}}\big\|_{*} + \gamma\big\|{S}^{*}\big\|_{1}
+     h\big(\Theta^{*}\big) + \delta\big\|{L^{*}}\big\|_{*} + \gamma\big\|{S}^{*}\big\|_{1}.
 \end{equation}
@@
 h\big(\widehat{\Theta}\big)-h\big(\Theta^{*}\big) \geq
-\big\langle\, \nabla_{\Theta}h\big(\Theta^{*}\big),\widehat{\Theta}-\Theta^{*}\big\rangle\ + \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2}
+\big\langle\, \nabla_{\Theta}h\big(\Theta^{*}\big),\widehat{\Theta}-\Theta^{*}\big\rangle\ + \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2}.
 \]
@@
     + \delta \big\|L^{*}\big\|_\ast + \gamma \big\|S^{*}\big\|_1
-    - \delta \big\|\widehat{L}\big\|_\ast - \gamma \big\|\widehat{S}\big\|_1
+    - \delta \big\|\widehat{L}\big\|_\ast - \gamma \big\|\widehat{S}\big\|_1.
 \end{equation}
@@
     -\big\langle\,\nabla_{\Theta}h\big(\Theta^{*}\big),\widehat{\Theta}-\Theta^{*}\big\rangle\
-    + \delta \mathbb{Q}\big(L^{*},S^{*}\big) - \delta \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big)
+    + \delta \mathbb{Q}\big(L^{*},S^{*}\big) - \delta \mathbb{Q}\big(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*}\big).
 \end{equation}
@@
 &\leq \frac{\delta}{2}\bigg(\big\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} + \big\|\widehat{\Delta}^{L}_{A}\big\|_\ast + \big\|\widehat{\Delta}^{L}_{B}\big\|_\ast\bigg) + \frac{\gamma}{2}\bigg(\left\|\widehat{\Delta}^{S}_{M}\right\|_{1} +
-\left\|\widehat{\Delta}^{S}_{M^{\perp}}\right\|_{1}\bigg)  \label{eq:10}
+\left\|\widehat{\Delta}^{S}_{M^{\perp}}\right\|_{1}\bigg).  \label{eq:10}
 \end{align}
@@
     \frac{3\delta}{2}\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big)
-    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\gamma \big\|S^*_{M^\perp}\big\|_{1}
+    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\gamma \big\|S^*_{M^\perp}\big\|_{1}.
     \label{eq:11}
@@
 2 \big\langle\, \widehat\Delta^{L} + \widehat\Delta^{S} ,\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \big\rangle\ +
-2 \big\langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \big\rangle\  \label{eq:12}
+2 \big\langle\, \widehat\Delta^{L}, \widehat\Delta^{S} \big\rangle.\label{eq:12}
 \end{align}
@@
     &\leq \bigg(\big|\widehat{\alpha}\big|+\big|\alpha^{*}\big|\bigg)\big\|\widehat{\Delta}^{S}\big\|_1\\
-    &\leq 2C\kappa\big\|\widehat{\Delta}^{S}\big\|_1  \label{eq:13}
+    &\leq 2C\kappa\big\|\widehat{\Delta}^{S}\big\|_1.  \label{eq:13}
 \end{align}
@@
     \big\|\widehat{\Delta}^{S} \big\|_{1}\\
-    &\leq \bigg(\frac{2\kappa}{n}\bigg)\big\|\widehat{\Delta}^{S} \big\|_{1} \label{eq:14}
+    &\leq \bigg(\frac{2\kappa}{n}\bigg)\big\|\widehat{\Delta}^{S} \big\|_{1}. \label{eq:14}
 \end{align}
@@
     &\geq \frac{\tau}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{S}\big\|_{F}^{2} - \frac{\gamma}{2}\big\|\widehat{\Delta}^{S}\big\|_{1}\\
-    &\geq \frac{\tau}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{S}\big\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}\big(\widehat{\Delta}^L,\widehat{\Delta}^S\big) \label{eq:26}
+    &\geq \frac{\tau}{2} \big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \frac{\tau}{2} \big\|\widehat{\Delta}^{S}\big\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}\big(\widehat{\Delta}^L,\widehat{\Delta}^S\big).
+\label{eq:26}
 \end{align}
@@
     2 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^{*}\big) + 2\gamma
-    \big\|S^{*}_{M^\perp}\big\|_{1}
+    \big\|S^{*}_{M^\perp}\big\|_{1}.
 \]
@@
     \leq
-    \frac{7\delta}{2}\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 4\gamma \big\|S^*_{M^\perp}\big\|_{1}  \label{eq:42}
+    \frac{7\delta}{2}\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 4\gamma \big\|S^*_{M^\perp}\big\|_{1}.  \label{eq:42}
 \end{align}
@@
     \leq \sqrt{2k}\delta\big\|\widehat{\Delta}^L_{A}\big\|_{F} + \Psi(M)\gamma\big\|\widehat{\Delta}^S_M\big\|_{F}\\
-    \leq \sqrt{2k}\delta\big\|\widehat{\Delta}^L\big\|_{F} + \Psi(M)\gamma\big\|\widehat{\Delta}^S\big\|_{F}  \label{eq:43}
+    \leq \sqrt{2k}\delta\big\|\widehat{\Delta}^L\big\|_{F} + \Psi(M)\gamma\big\|\widehat{\Delta}^S\big\|_{F}.  \label{eq:43}
 \end{align}
@@
 \[
-    \Psi(M):=\sup\limits_{U\in M,U\neq0}\frac{\|U\|_{1}}{\|U\|_{F}}
+    \Psi(M):=\sup\limits_{U\in M,U\neq0}\frac{\|U\|_{1}}{\|U\|_{F}}.
 \]

### 2019-10-08 Manuscript for submission/manuscript.tex
Update

@@
 %the first term in the objective function in (\ref{eq:Modified}) sums over all $(i,j)$ pairs.
-This slight modification leads to neither theoretical consequence nor noticeable difference in practice.
+We borrow the idea of this modification from the work of \cite{ma2017exploration}, where they also consider the latent factor model in analyzing the embedded topics in the network but without the sparse component.
+As stated in \cite{ma2017exploration}, this slight modification leads to neither theoretical consequence nor noticeable difference in practice.
 Let ($\widehat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:Modified}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth, which governs the data generating process.
@@
 \begin{tabular}{clcl}\hline
-Pair & Community & Title (Author, Year) & \\
+Pair & Community & Title  & \\
 \hline
-1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis (P. Hall, et al. $2006$)      & \\
-     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters (J. Fan, et al, $2004$)                       & \\
-2    & VarSel      & The adaptive lasso and its oracle properties (H. Zou, $2006$)                             & \\
-     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection (Y. Chung, et al. $2009$)    & \\
-3    & DimRed    & Contour projected dimension reduction (R. Luo, et al. $2009$)                                                     & \\
-     & VarSel    & Factor profiled sure independence screening (H. Wang, $2012$)& \\
-4    & VarSel    & Factor profiled sure independence screening (H. Wang, $2012$)& \\
-     & DimRed    & Sliced regression for dimension reduction (H. Wang, et al. $2012$) & \\
-5    & CovEst    & Two sample tests for high-dimensional covariance matrices (J. Li, et al. $2012$)& \\
-     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression (CH. Zhang, et al. $2008$)        & \\
-6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise (P. Hall, et al. $2010$)       & \\
-     & CovEst     & Regularized estimation of large covariance matrices (PJ. Bickel, et al. $2008$)    &  \\
-7    & DimRed    & A constructive approach to the estimation of dimension reduction directions (Y. Xia. $2007$)       & \\
-     & VarSel     & Factor profiled sure independence screening (H. Wang, $2012$)    & \\
-8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors (TJ. Yen, $2011$) & \\
-     & Mixed      & Empirical {B}ayes selection of wavelet thresholds (IM. Johnstone, et al. $2005$)                         & \\
-9    & Mixed    & Nonparametric inferences for additive models (J. Fan, et al. $2005$)                  & \\
-     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models
-     (J. Fan, et al. $2011$)     & \\
-10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality
-    (J. Fan, et al. $2010$) & \\
-     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data (D. Zeng, et al. $2007$) & \\
+1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       & \\
+     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                        & \\
+2    & VarSel      & The adaptive lasso and its oracle properties                              & \\
+     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection     & \\
+3    & DimRed    & Contour projected dimension reduction                                                      & \\
+     & VarSel    & Factor profiled sure independence screening & \\
+4    & VarSel    & Factor profiled sure independence screening & \\
+     & DimRed    & Sliced regression for dimension reduction  & \\
+5    & CovEst    & Two sample tests for high-dimensional covariance matrices & \\
+     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression         & \\
+6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise      & \\
+     & CovEst     & Regularized estimation of large covariance matrices   &  \\
+7    & DimRed    & A constructive approach to the estimation of dimension reduction directions       & \\
+     & VarSel     & Factor profiled sure independence screening   & \\
+8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors & \\
+     & Mixed      & Empirical {B}ayes selection of wavelet thresholds               & \\
+9    & Mixed    & Nonparametric inferences for additive models          & \\
+     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive model  & \\
+10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality & \\
+     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data & \\
+\hline \\
+\end{tabular}
+
+\begin{tabular}{ccccc}
 \hline
+Pair $1$                                                                                 & Pair $2$                                                                       & Pair $3$                                                                             & Pair $4$                                                                            & Pair $5$                                                                              \\ \hline
+\begin{tabular}[c]{@{}c@{}}P.
+Hall, et al.
+$2006$\\ J.
+Fan, et al.
+$2004$\end{tabular}     & \begin{tabular}[c]{@{}c@{}}H.
+Zou.
+$2006$\\ Y.
+Chung, et al.
+$2009$\end{tabular} & \begin{tabular}[c]{@{}c@{}}R.
+Luo, et al.
+$2009$\\ H.
+Wang.
+$2012$\end{tabular}        & \begin{tabular}[c]{@{}c@{}}H.
+Wang.
+$2012$\\ H.
+Wang, et al.
+$2012$\end{tabular}      & \begin{tabular}[c]{@{}c@{}}J.
+Li, et al.
+$2012$\\ CH.
+Zhang, et al.
+$2008$\end{tabular} \\ \hline
+Pair $6$                                                                                 & Pair $7$                                                                       & Pair $8$                                                                             & Pair $9$                                                                            & Pair $10$                                                                             \\ \hline
+\begin{tabular}[c]{@{}c@{}}P.
+Hall, et al.
+$2010$\\ PJ.
+Bickel, et al.
+$2008$\end{tabular} & \begin{tabular}[c]{@{}c@{}}Y.
+Xia.
+$2007$\\ H.
+Wang.
+$2012$\end{tabular}         & \begin{tabular}[c]{@{}c@{}}TJ.
+Yen.
+$2011$\\ IM.
+Johnstone, et al.
+$2005$\end{tabular} & \begin{tabular}[c]{@{}c@{}}J.
+Fan, et al.
+$2005$\\ J.
+Fan, et al.
+$2011$\end{tabular} & \begin{tabular}[c]{@{}c@{}}J.
+Fan, et al.
+$2010$\\ D.
+Zeng, et al.
+$2007$\end{tabular}
+\\ \hline
 \end{tabular}
 \caption{Top $10$ edges come from pairs of papers from different communities.
-For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
+Authors and years of publication for the papers in each pair are also presented.
+In the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem. 
 But they are not related in terms of topic.}
-\end{table}
 \label{tab:table2}
 %\end{landscape}
+\end{table}
 

### 2019-10-23 Manuscript for submission/manuscript.tex
polishing

@@
 
-\keywords{citation network, matrix decomposition, latent variable model, logistic regression model, convex optimization, alternating direction method of multiplier}
+\keywords{citation network, matrix decomposition, latent variable model, logistic regression model, convex optimization, alternating direction method of multiplier (ADMM)}
 
@@
 The proposed modeling framework is also related with the analysis of decomposing a matrix into low-rank and sparse components (\cite{agarwal2012noisy,candes2011robust,chandrasekaran2010latent, zhou2010stable}).
-Specifically, \cite{chandrasekaran2010latent} studies statistical inference of a multivariate Gaussian model whose precision matrix admits the form of a low-rank matrix plus a sparse matrix.
+Specifically, paper \cite{chandrasekaran2010latent} studies statistical inference of a multivariate Gaussian model whose precision matrix admits the form of a low-rank matrix plus a sparse matrix.
 The inference and optimization of the current model are different from the aforementioned cases.
@@
 Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem.
-In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on a real citation network of statisticians.
-We finally conclude this work in Section \ref{sec:Con} with several open questions and some directions for future research.
+In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, as well as an application of our model on a real citation network of statisticians.
+We finally conclude this work in Section \ref{sec:Con} with several open questions and some possible directions of future research.
 
@@
 \end{equation}
-
 %Astute readers might notice the slight difference of the first term in objective function between (\ref{eq:logistic10}) and (\ref{eq:Modified}).
@@
 %the first term in the objective function in (\ref{eq:Modified}) sums over all $(i,j)$ pairs.
+Note that we have $X_{ii}=0$ in our setting.
+
 We borrow the idea of this modification from the work of \cite{ma2017exploration}, where they also consider the latent factor model in analyzing the embedded topics in the network but without the sparse component.
@@
 Throughout the discussion, let $P^{*}=\bigg\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\bigg\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
-We then impose several assumptions for theoretical guarantees of our estimator.
+We describe several assumptions before we can establish theoretical guarantees of our estimator.
 
 \begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
-For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of the log-likelihood function is bounded away from zero ($\tau > 0$):
+For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}):
+$$
+h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}.
+$$
+We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of the log-likelihood function is bounded away from zero ($\tau > 0$):
 \[
 \nabla^{2}h(\Theta) = \mbox{diag}\Big(\mbox{vec}\Big(\frac{1}{n}\frac{\exp(\Theta)}{(1+\exp(\Theta))^{2}}
-\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
+\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}. 
 \]
@@
 
-\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L}) \label{Ass:2}
-To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes an all one vector in $\mathbb{R}^{n}$.
+\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$}) \label{Ass:2}
+To ensure the separation between $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes an all one vector in $\mathbb{R}^{n}$.
 \end{assumption}
 
-\begin{assumption} (\textbf{Spikiness of L and Constraint on $\alpha$}) \label{Ass:3}
-We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}.
+\begin{assumption} (\textbf{Spikiness of $L$ and Constraint on $\alpha$}) \label{Ass:3}
+We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on $L$, to ensure the separation of $L$ and matrix $S$ \cite{agarwal2012noisy}. 
 We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
@@
 \end{align}
-then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)$
+then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound of $e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)$:
 \begin{align} \label{theorem1}
@@
 $\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$.
-Each respective term is involved with estimating three model parameters, $\alpha, L$ and $S$.
+Each respective term is involved with estimating three model parameters: $\alpha, L$ and $S$.
 To be more specific, both $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ have two types of error:
@@
 We put astroids in the superscript of parameters to denote that they are ground truth.
-Readers can refer the meaning of each parameter in the model in Section \ref{sec:intro} and Section \ref{sec:model-form}.
+Readers can refer the meaning of each parameter in the model in Section \ref{sec:intro} and  \ref{sec:model-form}.
 
@@
 \end{enumerate}
-
 \begin{figure}[htbp]

### 2019-10-24 Manuscript for submission/manuscript.tex
polishing

@@
 %In third scenario, we consider a situation
-Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of procedures for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.
-We put astroids in the superscript of parameters to denote that they are ground truth.
+Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of steps for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.
+We put astroids in the superscripts of parameters to indicate that they are the ground truth.
 Readers can refer the meaning of each parameter in the model in Section \ref{sec:intro} and  \ref{sec:model-form}.
@@
         First, we assume that there are $n$ papers in the network, and $K$ topics are embedded in it.
-        Each of them consists of $\frac{n}{K}$ papers.
+        Each of them consists of roughly $\frac{n}{K}$ papers.
         This can be expressed in $F^*$ as follows:
@@
 
-    \item Recall that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
+    \item Recall that the positive entries of $S^*$ can characterize the links in the network, which cannot be accounted by the common topics.
         In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
         Specifically, we assume that there are $\frac{|S^*|}{\binom{K}{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
-        This can be implemented via following steps:
+        This can be implemented via the following steps:
         1) We construct $K$ sets $C^*_1,\dots,C^*_K$ that are defined as follows:
@@
 Notice that the nodes that share the common topics are clustered,
-and the cross clustered links are ad-hoc citations.
+and the cross clustered links are the ad-hoc citations.
 %ad-hoc links, which connect clusters of papers with $1$ topic, are colored in green.
@@
 (We will denote this number as $\widehat{K}^{\text{Scree}}$.)
-We want to note the readers that the scree-plot analysis serves as a good guideline for determining the range of grids to search over.
+We want to note that the scree-plot analysis serves as a good guideline for determining the range of grids to search over.
 With the estimate of the number of topics in the network in mind, we record the $\text{rank}(\widehat{L}^{\gamma,\delta})$ and $|\widehat{S}^{\gamma,\delta}|$ for each tuning parameter pair on a given grid.

### 2019-10-24 Manuscript for submission/manuscript.tex
polishing

@@
 We want to note that the scree-plot analysis serves as a good guideline for determining the range of grids to search over.
-With the estimate of the number of topics in the network in mind, we record the $\text{rank}(\widehat{L}^{\gamma,\delta})$ and $|\widehat{S}^{\gamma,\delta}|$ for each tuning parameter pair on a given grid.
+With the estimate of the number of topics in the network in mind, we record the $\text{rank}(\widehat{L}^{\gamma,\delta})$ and $|\widehat{S}^{\gamma,\delta}|$ (i.e., the cardinality of the set $\widehat{S}^{\gamma,\delta}$) for each tuning parameter pair on a given grid.
 We need to go through several iterations of this recording procedure to find a proper range of grid, in which we can get $\text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}}$
-and $10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X|$, via adjusting the range of grid for $\gamma$ and $\delta$ repeatedly.
+and $10^{-4}\|X\|_0 \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}\|X\|_0$, via adjusting the range of grid for $\gamma$ and $\delta$ repeatedly.
+Here $\|X\|_0$ denotes the number of nonzero entries in the matrix $X$.
 Once we find a grid, which satisfies above constraints, we choose a pair of tuning parameters: %($\gamma^{\text{Heu}},\delta^{\text{Heu}}$):
@@
     \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}},
-    \mbox{mode} |\widehat{S}^{\gamma,\delta}|: \mbox{subject to} \Hquad 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X| \big\}.
-\]
-One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) and the AIC, work where we recall that BIC and AIC are defined as follows:
+    \mbox{mode} |\widehat{S}^{\gamma,\delta}|: \mbox{subject to} \Hquad 10^{-4}\|X\|_0 \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}\|X\|_0 \big\}.
+\]
+One might wonder how the traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) and the Akaike information criterion (AIC), work.
+Recall that BIC and AIC are defined as follows:
 \[
@@
 Additional $1$ in the last term is due to $\hat{\alpha}$.
-We want to find a pair $(\gamma,\delta)$, which minimizes BIC($M$) and AIC($M$) as a function of $(\gamma,\delta)$ respectively, where we denote them as follows:
+We want to find a pair $(\gamma,\delta)$, which minimizes BIC($M$) or AIC($M$) as a function of $(\gamma,\delta)$, respectively, where we denote them as follows:
 \[
@@
 \]
-We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following four evaluation metrics:
-
+We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using the following four evaluation metrics:
 \begin{eqnarray*}
@@
 We present the evaluation results of the six cases via the four criteria, $M_1,M_2,M_3$, and $M_4$ in Table.\ref{tab:table1}.
-
-\subsubsection{Several Observations} \label{sec:obs}
-%Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
-%We apply a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
-%For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
-%Furthermore, we find one interesting phenomenon.
-%Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
-%Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
-\begin{enumerate}
-    \item \textbf{Model Selection.}
-    First and foremost, choosing a good pair of tuning parameters is critical when it comes to making a good statistical inference on data.
-    As presented in Table.\ref{tab:table1}, both BIC and AIC, which are well known for their model selection consistency in asymptotic setting, appear to under-estimate either the number of topics or the number of ad-hoc links in the networks in our synthetic settings.
-This may be caused by the fact that these traditional methods take the sample size into account, and therefore penalizes the model complexity too harshly.
-    In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics, and this strategy leads us to good model selection results for all the six cases considered in two scenarios.
-(See Fig.$\ref{fig:figure2}$)
 
@@
 
+\subsubsection{Several Observations} \label{sec:obs}
+%Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
+%We apply a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
+%For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
+%Furthermore, we find one interesting phenomenon.
+%Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
+%Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
+\begin{enumerate}
+    \item \textbf{Model Selection.}
+    First and foremost, choosing a good pair of tuning parameters is critical when it comes to making a good statistical inference on data.
+    As presented in Table.\ref{tab:table1}, both BIC and AIC, which are well known for their model selection consistency in asymptotic setting, appear to under-estimate both the number of topics and the number of ad-hoc links in the networks in our synthetic settings.
+This may be caused by the fact that these traditional methods take the sample size into account, and therefore penalizes the model complexity too harshly.
+    In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics, and this strategy leads us to good model selection results for all the six cases considered in two scenarios.
+(See Fig.$\ref{fig:figure2}$)
+
     \begin{figure}[htbp]
@@
         \caption{ Scree plots for six synthetic Networks.
-        $\hat{K}^{\mbox{Scree}}$ recovers the number of topics in the network correctly for all six cases.}
+        $\widehat{K}^{\mbox{Scree}}$ recovers the number of topics in the network correctly for all six cases.}
         \label{fig:figure2}
@@
     After fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether the $i$th paper belongs to the $k$th topic or not.
-    We apply a simple $k$-means clustering algorithm on the $\widehat{L}$ matrix’s $K$ eigenvectors where $K$ denotes the rank of matrix $\widehat{L}$.
+    We apply a simple $k$-means clustering algorithm on the $\widehat{L}$ matrix's  $K$ eigenvectors where $K$ denotes the rank of matrix $\widehat{L}$.
     %(We will denote column-wise concatenation of these $K$ eigenvectors as $\widehat{E}_{K} \in \mathbb{R}^{n\times K}$.)
-    For three cases in Scenario $1$, where each paper in the network only has one topic, we confirm that $k$-means algorithm performs well on classifying papers in the network.
-    However, in Scenario $2$ where we allow the papers in the network can have more than one topic, naive implementation of $k$-means algorithm entails a problem, since it is not able to afford the overlapped membership of nodes.
-    Here, we create a matrix $\widehat{E}_{K}\in \mathbb{R}^{n \times K}$, whose $i$th column corresponds to the $i$th eigenvector of the $\widehat{L}$.
-    In order to obtain a sense on how many clusters of papers exist in latent space, we project each row of the $\widehat{E}_{K}$ on the first and second principal components of data matrix $\widehat{E}_{K}$, and plot the projected points on $2$-dimensional plane.
-    We count the number of distinct clusters plotted on the plane. Subsequently, we run the $k$-means algorithm on the projected points.
-    Refer Table.\ref{tab:table1} and Fig.\ref{fig:figure3} for the references on how this procedure performs on six synthetic cases.
+    For the three cases in Scenario $1$, where each paper in the network only belongs to one topic, we confirm that $k$-means algorithm performs well on classifying papers in the network.
+    However, in Scenario $2$ where we allow the papers in the network can have more than one topics, naive implementation of the $k$-means algorithm entails a problem -- it is not able to cope with the overlapped membership of nodes.
+    In this case, we create a matrix $\widehat{E}_{K}\in \mathbb{R}^{n \times K}$, whose $i$th column corresponds to the $i$th eigenvector of the matrix $\widehat{L}$.
+    In order to obtain a sense on how many clusters of papers exist in the latent space, we project each row of the $\widehat{E}_{K}$ on the first and second principal components of data matrix $\widehat{E}_{K}$, and plot the projected points on a $2$-dimensional plane.
+    We count the number of distinct clusters plotted on the plane.
+    Subsequently, we run the $k$-means algorithm on the projected points.
+    Table.\ref{tab:table1} and Fig.\ref{fig:figure3} illustrate the result of the above procedure.
+    They result seem to be consistent with the underlying truth.
 
@@
 Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting dataset on citation network of papers from statistics journals.
-Specifically, this dataset is based upon all papers published from $2003$ to the first half of $2012$, from the four top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association and Journal of Royal Statistical Society (Series B).
+Specifically, this dataset is based upon all papers published from $2003$ to the first half of $2012$, from the four top statistical journals: Annals of Statistics, Biometrika, Journal of American Statistical Association, and Journal of Royal Statistical Society (Series B).
 Citational relationships of $3248$ papers are given in the form of adjacency matrix.
@@
 \ref{fig:figure4})
-In light of this, we conduct the analysis in two steps:
+In light of this, we conduct the analysis in the following two steps:
 \begin{enumerate}
@@
 Due to the small volume of each community, we could manually check that the false discovery for each community is all zero.
-(Full list of papers for each community is provided in $https://sites.google.com/site/namjoonsuh/publications$.)
-
-Sub-network structure has also a big collection of papers which we refer it as ``Mixed Topics'' cluster.
+(Full list of papers for each community is provided in {\em https://sites.google.com/site/namjoonsuh/publications}.)
+
+The sub-network structure has also a big collection of papers that we refer to as the ``Mixed Topics'' cluster.
 Not only could we see the papers with topics on Learning Theory, Non-parametric / Semi-parametric Statistics, Spatial Statistics, Theoretical Machine Learning, which does not seem to belong to any of the five communities listed above, but also we could identify the papers with combinations of two or three topics.
@@
 $2010$), are the examples of these papers.
-It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed Topic classified as Mixed Topic.
-For instance, the paper, On the "degrees of freedom" on the LASSO (H. Zou, et al. $2007$), is classified as Mixed Topic paper.
+It is also interesting to think about a reason on papers that seem to have obvious membership in one of $5$ communities other than Mixed Topic classified as Mixed Topic.
+For instance, the paper, On the ``degrees of freedom'' on the LASSO (H. Zou, et al. $2007$), is classified as Mixed Topic paper.
 We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities.
@@
 \end{tabular}
-\caption{Top $10$ edges come from pairs of papers from different communities.
+\caption{Top $10$ edges corresponding with the pairs of papers from different communities.
 Authors and years of publication for the papers in each pair are also presented.
-In the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
-But they are not related in terms of topic.}
+In the first pair, a $\emph{FuncAn}$ paper cites a $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.
+But they are not related in terms of {\it topic}.}
 \label{tab:table2}
@@
 
-We propose a new combined latent factor and sparse graphical model.
-We consider the regularized likelihood by means of $L_1$ and nuclear norm penalties.
-The computation of the regularized estimator is facilitated by developing an algorithm based on the alternating direction method of multiplier to optimize a non-smooth and convex objective function.
-The proposed method is applied to citation network of statisticians, and the estimated model renders good interpretative power.
-Specifically, our analysis on statistician's citation network sheds the new light on the interpretation of dataset.
-
-Nonetheless, there are still several questions remaining to be answered.
-First of all, it remains unclear on how to choose the proper tuning parameters.
-Classical methods for choosing tuning parameters such as BIC or AIC did not work in our case, since they tend to choose the most parsimonious models.
-We also do not have systematic ways to do cross validation in network data.
-Not only because it is computationally expensive procedure, but also because if we partition the network data, we can loose fair amount of information on dependent structures among edges.
-This problem is also closely related with determining the number of communities in network.
-In lieu of using BIC or AIC, our analysis is heavily relying on heuristic approach when choosing the tuning parameter, and during this procedure, we use the screeplot for determining number of communities in network.
+We propose a new model that combines the latent factors and a sparse graphical structure.
+We consider the regularized likelihood by means of the $L_1$ norm and the nuclear norm penalties.
+The computation of the regularized estimator is facilitated by developing an algorithm that is based on the alternating direction method of multiplier (ADMM), which optimizes a non-smooth however convex objective function.
+The proposed method is applied to a citation network of statisticians, and the estimated model renders some meaningful interpretations.
+We believe that our analysis on statistician's citation network sheds some new light on the interpretation of the data set.
+
+There are still several questions remaining to be answered.
+First of all, it remains unclear on how to choose the tuning parameters.
+Classical methods for choosing tuning parameters such as BIC or AIC tend to choose the most parsimonious models, which lead to an underestimation in our case.
+We also do not have systematic ways to do cross-validation in our network data.
+Not only because it is computationally expensive, but also because if we partition the network data, we can loose fair amount of information on dependent structures among the edges.
+This problem is also closely related to determining the number of communities in network.
+In lieu of using BIC or AIC, our analysis is heavily relying on a heuristic approach when choosing the tuning parameter, and during this procedure, we use the scree-plot to determine the number of communities in a network.
 Screeplot approach works well in general situation, but it does not necessarily always guarantee the correct estimate of number of communities.
-We need a more reliable and theoretically well understood way to determine $K$.
-
-Secondly, we only consider the undirected case which is somewhat unrealistic assumption for citation network in real world, in a sense that it is not usual for two papers to cite each other at the same time.
+We need a more systematic way to choose the parameters. 
+And it will be nice to derive some theoretical guarantees for the methods.
+
+Secondly, we only consider an undirected graph, which is somewhat inconsistent with a real citation network, which is directional.
 Since, in our research, we were interested in separating the low rank structure of edges and ad-hoc links in network, we did not take into account the directions of edges in our model.
-However, it would be interesting to consider incorporating the directed network into our matrix decomposition framework.
-
-Last but not least, when we assign the memberships of each nodes, we use $k$-means clustering algorithm.
-However, $k$-means algorithm turns out that it tends to assign nodes conservatively to each communities.
-For example, in Fig.$\ref{fig:figure4}$(left), we can see that bunch of Multiple Testing papers are assigned as Mixed cluster, and in Fig.$\ref{fig:figure4}$(right) also, many papers which should have been classified to among three communities other than mixed topic, have been assigned as Mixed topic community.
-This is probably because $k$-means does not allow overlapping membership of each nodes.
-It would be interesting to see what happens if we apply some clustering methods which allow the overlapped memberships of nodes in network.
+However, it would be interesting to study a similar problem on a directed graph.
+This is a future work.
+
+Last but not least, when we assign the memberships of each nodes, we adopt the $k$-means clustering algorithm.
+However, we notice that the $k$-means algorithm tends to assign nodes conservatively to each communities.
+For example, in Fig.
+\ref{fig:figure4} (left), we can see that a bunch of Multiple Testing papers are assigned as Mixed cluster, and in Fig.
+\ref{fig:figure4} (right), many papers that should have been classified to three communities other than the Mixed topic, have been assigned into the Mixed topic community.
+It would be interesting to experiment on some other clustering methods that accommodate overlapping memberships.
 
 \section{Appendix}
-In this Section, first we briefly introduce several notations, a notion on the decomposability of regularizer, and a useful lemma proved in the work \cite{agarwal2012noisy} (Section\ref{App:Pre}).
+
+In this Section, first we briefly introduce several notations, including a notion on the decomposability of regularizer, and a useful lemma that is proved in the work \cite{agarwal2012noisy} (Section\ref{App:Pre}).
 Then, we present Lemma \ref{le:le2} and its proof (Section \ref{App:Lemma2}).
-Finally, we present the proof of our Theorem\ref{Th:th1} (Section \ref{App:Theorem1}).
+Finally, we present the proof of our Theorem \ref{Th:th1} (Section \ref{App:Theorem1}).
 
@@
         \| A + B \|_{1} = \|A\|_{1} + \|B\|_{1},
-        \forall A \in M \mbox{and} B \in M^{\perp}.
+        \forall A \in M \mbox{ and } B \in M^{\perp}.
     \]

### 2019-10-25 Manuscript for submission/manuscript2.tex
remove one coauthor

--- 2019-10-24 Manuscript for submission/manuscript.tex
@@
 \author[2]{Eric Heim}
-\author[2]{Timothy Van Slyke}
-\author[2]{Lee Seversky}
+%\author[2]{Timothy Van Slyke}
+\author[3]{Lee Seversky}
 
@@
 
-\address[2]{\orgdiv{Information System Division (AFRL/RIS)}, \orgname{the Air Force Research Laboratory}, \orgaddress{Department of the Air Force, Air Force Materiel Command, AFRL/RIK - Rome, 26 Electronic Parkway, Rome,  \state{New York}, \country{USA}}}
+\address[2]{\orgdiv{Software Engineering Institute}, \orgname{Carnegie Mellon University}, \orgaddress{Pittsburgh, \state{PA}, \country{USA}}}
+
+\address[3]{\orgdiv{Information System Division (AFRL/RIS)}, \orgname{the Air Force Research Laboratory}, \orgaddress{Department of the Air Force, Air Force Materiel Command, AFRL/RIK - Rome, 26 Electronic Parkway, Rome,  \state{New York}, \country{USA}}}
 
@@
 The proposed model has a latent (i.e., factor analysis) model to represents the main technological trends (a.k.a., factors), and adds a sparse component that captures the remaining ad-hoc dependence.
-Parameter estimation are carried out through the construction of a joint-likelihood function of edges and properly chosen penalty terms.
+Parameter estimation is carried out through the construction of a joint-likelihood function of edges and properly chosen penalty terms.
 The convexity of the objective function allows us to develop an efficient algorithm, while the penalty terms push towards a low-dimensional latent component and a sparse graphical structure.
@@
 \author{Xiaoming Huo},
-\author{Eric Heim},
-\author{Timothy Van Slyke}, and
+\author{Eric Heim}, and 
+%\author{Timothy Van Slyke}, and
 \author{Lee Seversky}} (\cyear{2019}),
